### 2020-01-04 codebook.Rmd
Moved all old content of the repository (as Mitchell had set it up) to a new folder called "old_files", added the master data file, the codebook Rmd and re-created the html codebook within the project, and added the updated flowchart files showing the paper sampling/selection process.

---
title: "Codebook"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: true
  pdf_document:
    toc: yes
    toc_depth: 4
    latex_engine: xelatex
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = TRUE, # show warnings during codebook generation
  message = TRUE, # show messages during codebook generation
  error = TRUE, # do not interrupt codebook generation in case of errors,
                # usually better for debugging
  echo = TRUE  # show R code
)
ggplot2::theme_set(ggplot2::theme_bw())
pander::panderOptions("table.split.table", Inf)
```

```{r prepare_codebook}
library(codebook)
library(readxl)
library(here)
library(rio)

codebook_data <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", n_max = 243)
#Read codebook from second sheet in excel file.
dict <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "codebook")

#Add variable labels to data
var_label(codebook_data) <- dict_to_list(dict)
val_labels(codebook_data$include_in_analysis) <- c("excluded" = 0, "included" = 1)
val_labels(codebook_data$is_RR) <- c("CR" = 0, "RR"= 1)
val_labels(codebook_data$support_binary) <- c("no support" = 0, "partial or full support" = 1)
val_labels(codebook_data$is_replication) <- c("is not a replication" = 0, "is a replication" = 1)
val_labels(codebook_data$contains_replic) <- c("does not contain 'replic'" = 0, "contains 'replic'" = 1)
val_labels(codebook_data$hyp_from_fulltext) <- c("hypothesis from abstract alone" = 0, "hypothesis from full text" = 1)
val_labels(codebook_data$result_from_fulltext) <- c("result from abstract alone" = 0, "result from full text" = 1)
val_labels(codebook_data$coding_round) <- c("RR pilot" = 0,
                                            "main coding round" = 1,
                                            "CR replacements and late RR additions" = 2,
                                            "second CR replacement" = 3)
val_labels(codebook_data$uses_AS_coding) <- c("uses MS coding" = 0, "uses AS coding" = 1)
val_labels(codebook_data$coded_by_MS) <- c("not coded by MS" = 0, "coded by MS" = 1)
val_labels(codebook_data$evaluation_certainty_MS) <- c("not certain" = 1,
                                                       2,
                                                       3,
                                                       4,
                                                       "very certain" = 5)
val_labels(codebook_data$hypothesis_from_fulltext_MS) <- c("hypothesis from abstract alone" = 0, "hypothesis from full text" = 1)
val_labels(codebook_data$result_from_fulltext_MS) <- c("result from abstract alone" = 0, "result from full text" = 1)
val_labels(codebook_data$fulltext_available_MS) <- c("full text not available" = 0, "full text available" = 1)
val_labels(codebook_data$is_replication_old_MS) <- c("does not contain a replication" = 0, "contains a replication" = 1)
val_labels(codebook_data$is_original_old_MS) <- c("does not contain original work" = 0, "contains original work" = 1)
val_labels(codebook_data$coded_by_AS) <- c("not coded by AS" = 0, "coded by AS" = 1)
val_labels(codebook_data$evaluation_certainty_AS) <- c("not certain" = 1,
                                                       2,
                                                       3,
                                                       4,
                                                       "very certain" = 5)
val_labels(codebook_data$hypothesis_from_fulltext_AS) <- c("hypothesis from abstract alone" = 0, "hypothesis from full text" = 1)
val_labels(codebook_data$result_from_fulltext_AS) <- c("result from abstract alone" = 0, "result from full text" = 1)
val_labels(codebook_data$fulltext_available_AS) <- c("full text not available" = 0, "full text available" = 1)
val_labels(codebook_data$is_replication_old_AS) <- c("does not contain a replication" = 0, "contains a replication" = 1)
val_labels(codebook_data$is_original_old_AS) <- c("does not contain original work" = 0, "contains original work" = 1)
val_labels(codebook_data$is_replication_new_coded_by_AS) <- c("replication status not coded by AS" = 0, "replication status coded by AS" = 1)
val_labels(codebook_data$is_replication_new_AS) <- c("is not a replication" = 0, "is a replication" = 1)
val_labels(codebook_data$is_replication_new_coded_by_DL) <- c("replication status not coded by DL" = 0, "replication status coded by DL" = 1)
val_labels(codebook_data$is_replication_new_DL) <- c("is not a replication" = 0, "is a replication" = 1)
val_labels(codebook_data$is_replication_special_issue) <- c("not part of replication special issue" = 0, "part of replication special issue" = 1)
val_labels(codebook_data$hypothesis_intro_contains_replic) <- c("hypothesis intro does not contain 'replic'" = 0, "hypothesis intro contains 'replic'" = 1)

#Add meta data
metadata(codebook_data)$name <- "Positive Results in Registered Reports in Psychology"
metadata(codebook_data)$description <- "Coded variables to compare the proportion of papers that find support for their first tested hypothesis between Registered Reports and conventional reports in psychology"
metadata(codebook_data)$creator <- "Anne Scheel, Mitchell Schijen, Daniël Lakens"
metadata(codebook_data)$temporalCoverage <- "Winter 2018"

#Export codebook
rio::export(codebook_data, "positive_results_in_registered_reports_codebook.rds") # to R data structure file

```

```{r codebook}
codebook(codebook_data)
```

### 2020-01-04 R/rr_vs_cr_2019_r_conversion.R

@@ -1,371 +1,0 @@
-# clear R workspace
-rm(list = ls())
-# clear the console
-shell("cls")
-
-# install required packages if they are not already installed:
-if(!require(TOSTER)){
-  install.packages('TOSTER')
-}
-if(!require(readxl)){
-  install.packages('readxl')
-}
-# the gmodels package is currently not used
-if (!require(gmodels)) {
-  install.packages('gmodels')
-}
-
-# RR vs CR analysis
-
-# load libraries
-library(readxl)
-library(gmodels)
-library(TOSTER)
-
-# load the dataset from excel
-table <- read_excel("D:/Git Software Projects/positive_result_rates/Data/dataset_analysis_double_coding - 25_01_2019.xlsx")
-
-
-# ** RECODING **
-# some variables are stored as string, some need to be recoded
-attach(table)
-class(id)
-class(include_in_analysis)
-class(is_RR)
-class(hypothesis_full_text_as)
-class(hypothesis_full_text_ms) # character
-class(finding_conclusion_full_text_as)
-class(finding_conclusion_full_text_ms) # character
-class(full_text_available_as)
-class(full_text_available_ms)
-class(is_original_work_combined)
-class(is_original_work_as)
-class(is_original_work_ms) # character
-class(is_replication_combined)
-class(is_replication_as)
-class(is_replication_ms) # character
-detach(table)
-
-
-# final version of [has_support]
-# add has support variable
-table$has_support <- NA
-table$has_support[table$support_combined == "support"] <- 1
-table$has_support[table$support_combined == "partial support"] <- 1
-table$has_support[table$support_combined == "no support"] <- 0
-table(table$has_support,table$support_combined)
-
-# final version of [is_rr]
-# note: unlike the Stata script, type conversion is not needed.
-table$is_rr <- table$is_RR
-table(table$is_RR, table$is_rr)
-
-# intermediate: first look at demographics of RRs and CRs
-table(table$has_support,table$is_rr)
-
-# final version of [full_text_available]
-table$full_text_available <- NA
-table$full_text_available[table$full_text_available_as == 0] <- 0
-table$full_text_available[table$full_text_available_ms == 0] <- 0
-table$full_text_available[table$full_text_available_as == 1] <- 1
-table$full_text_available[table$full_text_available_ms == 1] <- 1
[…]

### 2020-01-04 old_files/R/rr_vs_cr_2019_r_conversion.R

@@ -1,0 +1,371 @@
+# clear R workspace
+rm(list = ls())
+# clear the console
+shell("cls")
+
+# install required packages if they are not already installed:
+if(!require(TOSTER)){
+  install.packages('TOSTER')
+}
+if(!require(readxl)){
+  install.packages('readxl')
+}
+# the gmodels package is currently not used
+if (!require(gmodels)) {
+  install.packages('gmodels')
+}
+
+# RR vs CR analysis
+
+# load libraries
+library(readxl)
+library(gmodels)
+library(TOSTER)
+
+# load the dataset from excel
+table <- read_excel("D:/Git Software Projects/positive_result_rates/Data/dataset_analysis_double_coding - 25_01_2019.xlsx")
+
+
+# ** RECODING **
+# some variables are stored as string, some need to be recoded
+attach(table)
+class(id)
+class(include_in_analysis)
+class(is_RR)
+class(hypothesis_full_text_as)
+class(hypothesis_full_text_ms) # character
+class(finding_conclusion_full_text_as)
+class(finding_conclusion_full_text_ms) # character
+class(full_text_available_as)
+class(full_text_available_ms)
+class(is_original_work_combined)
+class(is_original_work_as)
+class(is_original_work_ms) # character
+class(is_replication_combined)
+class(is_replication_as)
+class(is_replication_ms) # character
+detach(table)
+
+
+# final version of [has_support]
+# add has support variable
+table$has_support <- NA
+table$has_support[table$support_combined == "support"] <- 1
+table$has_support[table$support_combined == "partial support"] <- 1
+table$has_support[table$support_combined == "no support"] <- 0
+table(table$has_support,table$support_combined)
+
+# final version of [is_rr]
+# note: unlike the Stata script, type conversion is not needed.
+table$is_rr <- table$is_RR
+table(table$is_RR, table$is_rr)
+
+# intermediate: first look at demographics of RRs and CRs
+table(table$has_support,table$is_rr)
+
+# final version of [full_text_available]
+table$full_text_available <- NA
+table$full_text_available[table$full_text_available_as == 0] <- 0
+table$full_text_available[table$full_text_available_ms == 0] <- 0
+table$full_text_available[table$full_text_available_as == 1] <- 1
+table$full_text_available[table$full_text_available_ms == 1] <- 1
[…]

### 2020-01-05 manuscript.Rmd
Added the manuscript Rmd file and the two bib files (for references and software) and updated the Rmd file: changed "CR" to "SR"/"conventional" to "standard" throughout, added a caption for Figure 2 and notes for all tables, and added the code for Figure 3. Knitted the manuscript with the updated data.

---
title             : "Positive Results in Registered Reports"
shorttitle        : "Positive Results in Registered Reports"

author: 
  - name          : "Anne Scheel"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands"
    email         : "a.m.scheel@tue.nl"
  - name          : "Mitchell Schijen"
    affiliation   : "1"
  - name          : "Daniël Lakens"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"

note: "\\clearpage"

author_note:

abstract: >
  XXXXXXXXXXXXXXXXXXX

keywords          : "keyword 1, keyword 2, keyword 3"
wordcount         : "XXX"

header-includes:
  - \usepackage{float}
  - \usepackage{framed}
  - \usepackage{caption}
  - \usepackage{setspace}
  - \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
  - \newfloat{textbox}{thp}{lop}
  - \floatname{textbox}{Box}

bibliography      : ["prr.bib","prr_software.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "en-UK"
class             : "man"
output            : papaja::apa6_pdf
---

```{r include = FALSE}
library("papaja")
library("bookdown")
library("rmarkdown")
library("knitr")
library("TOSTER")
library("purrr")
library("lattice")
library("ggplot2")
library("dplyr")
library("stringr")
library("reshape2")
```

## Analysis
We planned to test our hypothesis in the following way (quoting directly from our preregistration, [https://osf.io/sy927](https://osf.io/sy927), point 9):

> A one-sided proportion test with an alpha level of $5\%$ will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports in psychology. 
> In addition to testing if there is a statistically significant difference between RRs and conventional reports, we will test if the difference is smaller than our smallest effect size of interest using an equivalence test for proportion tests with an alpha level of $5\%$ [@Lakens2018a].
> We determined our smallest effect size of interest to be the difference between the positive result rate in psychology ($91.5\%$) and the positive result rate in general social sciences ($85.5\%$) as reported by @Fanelli2010, i.e. a difference of $91.5\% - 85.5\% = 6\%$. 
> The rationale for choosing general social sciences as a comparison is that this discipline had the lowest positive result rate amongst the "soft" sciences [@Fanelli2010]. 
> The exact percentage for general social sciences was extracted from Figure 1 in @Fanelli2010 using the software WebPlotDigitizer [@Rohatgi2018].

We would accept our hypothesis that RRs have a lower positive result rate than SRs if we found a negative difference between RRs and SRs that was significantly different from 0 *and* not statistically equivalent to a range from $-6\%$ to $+6\%$ (both at $\alpha = 5\%$).

# Results

## Confirmatory Analyses
```{r include=FALSE}
#source("analysis.R")
# load the dataset from RDS created with codebook
alldata <- readRDS("positive_results_in_registered_reports_codebook.rds")
# alldata <- readRDS("C:/Users/20176208/surfdrive/Documents/_projects/_positiveresults/_data/positive_results_in_registered_reports_codebook.rds")
# alldata <- readRDS("~/surfdrive/Documents/_projects/_positiveresults/_data/positive_results_in_registered_reports_codebook.rds")

# remove excluded papers
included <- alldata[alldata$include_in_analysis==1,]

## 3. Run main preregistered analysis: the proportion of SRs with supported
## hypothesis compared to the proportion of RRs with supported hypothesis

# number of included SRs = 152
n.SR <- length(which(included$is_RR == 0))
# number of included RRs = 71
n.RR <- length(which(included$is_RR == 1))

# number of SRs with support = 146
n.support.SR <- length(which(included$is_RR == 0 & included$support_binary == 1))
# number of RRs with support = 31
n.support.RR <- length(which(included$is_RR == 1 & included$support_binary == 1))

# Positive result rate of SRs (proportion of SRs with support) = .9605
prop.support.SR <- n.support.SR/n.SR
# Positive result rate of RRs (proportion of RRs with support) = .4366
prop.support.RR <- n.support.RR/n.RR

## 3.1 Proportions test to test if RRs have a *lower* positive
## result rate than SRs (i.e., one-sided test)

proptestresult <- prop.test(c(n.support.SR, n.support.RR), c(n.SR, n.RR), alternative = "greater")

## 3.2 Equivalence test to test if the difference is larger than 6%
# Equivalence bounds/smallest effect size of interest (SESOI):
# As preregistered, we used the difference between the positive result
# rate in Psychology and in the lowest-scoring 'soft' science in 
# Fanelli (2010) as our SESOI. The lowest-scoring 'soft' science
# was General Social Sciences with a positive result rate of 85.5%
# (this number is not explicitly given in the text, so we extracted it
# from Figure 1 using WebPlotDigitizer). The positive result rate in 
# Psychology was 91.5%.
# Hence our SESOI is 91.5%-85.5% = 6%:

SESOI <- abs(91.5 - 85.5)/100

## Run proportions test and equivalence test using the TOSTER function
## TOSTtwo.prop:
tostresult <- TOSTtwo.prop(prop1 = prop.support.SR, 
                           prop2 = prop.support.RR, 
                           n1 = n.SR, 
                           n2 = n.RR, 
                           low_eqbound = -SESOI, 
                           high_eqbound = SESOI,
                           alpha = 0.05)

## Calculate confidence intervals for SR and RR PRR separately
SR.binom <- binom.test(x = prop.support.SR*n.SR, n = n.SR)
RR.binom <- binom.test(x = prop.support.RR*n.RR, n = n.RR)
```
`r n.support.SR` out of `r n.SR` SRs and `r n.support.RR` out of `r n.RR` RRs had positive results, meaning that the positive result rate was $`r printnum(prop.support.SR*100)` \%$ for SRs ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]) and $`r printnum(prop.support.RR*100)` \%$ for RRs ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]; see Fig. 1). 
The preregistered one-sided proportions test with an alpha level of $5\%$ showed that this difference of $-`r printnum((prop.support.SR-prop.support.RR)*100)`\%$ was statistically significant, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ at $\alpha = 5\%$, $z = `r printnum(min(tostresult$TOST_z1, tostresult$TOST_z2))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$. 
We thus accept our hypothesis that the positive result rate in RRs is lower than in SRs.

```{r echo=FALSE, warning=FALSE, fig.width=4, fig.height=3, fig.cap="Positive result rates for standard reports and Registered Reports. Error bars indicate 95% confidence intervals around the observed positive result rate."}

## 5. Create a plot for the main analysis

# Create a data frame to use for plotting the main result
mainplot.df <- data.frame(is_RR = c("SR", "SR", "RR", "RR"), 
                          support = c("supported", "not supported", 
                                   "supported", "not supported"),
                          value = c(prop.support.SR*100, (1-prop.support.SR)*100, 
                                    prop.support.RR*100, (1-prop.support.RR)*100),
                          lower = c(min(SR.binom$conf.int)*100, NA,
                                    min(RR.binom$conf.int)*100, NA),
                          upper = c(max(SR.binom$conf.int)*100, NA,
                                    max(RR.binom$conf.int)*100, NA))

# Plot the main result (positive result rate in SRs vs RRs)
ggplot(mainplot.df, aes(x = is_RR, y = value, fill = support)) +
                  geom_bar(stat = "identity", 
                           width = 0.5) +
  scale_fill_manual(values= c("#bcbddc", "#756bb1"),
                    name="first hypothesis") +
  annotate("text", label = "n = 152", x = 1, y = 105) +
  annotate("text", label = "n = 71", x = 2, y = 105) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.05, size = 0.5) +
  scale_x_discrete(breaks = waiver(), 
                   labels = c("SR" = "Standard\nReports (SRs)",
                              "RR" = "Registered\nReports (RRs)"), name = NULL)+ 
  scale_y_continuous(lim=c(0,110), breaks = c(seq(0, 100, 10)),
                     minor_breaks = c(seq(0, 100, 5)),
                     name = "% of papers", expand = c(0, 0))+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.margin = margin(0,0,0,-5))
```

## Exploratory Analyses
```{r include=FALSE}
## 4. Run exploratory analysis: the proportion of replication 
## studies with supported hypothesis compared to the proportion 
## of original studies with supported hypothesis

# total number of replication studies = 46
n.rep.total <- length(which(included$is_replication == 1))

# number of replication SRs = 4
n.rep.SR <- length(which(included$is_RR == 0 & 
                           included$is_replication == 1))
# proportion of replications among all SRs = 2.63%
prop.rep.SR <- n.rep.SR/n.SR

# number of replication RRs = 42
n.rep.RR <- length(which(included$is_RR == 1 & 
                           included$is_replication == 1))
# proportion of replications among all RRs = 59.15%
prop.rep.RR <- n.rep.RR/n.RR

# Positive result rate of *replication* SRs = 1
prop.rep.support.SR <- length(which(included$is_RR == 0 & 
                                    included$support_binary == 1 &
                                    included$is_replication == 1))/n.rep.SR
# Positive result rate of *original* SRs = .9595
prop.orig.support.SR <- length(which(included$is_RR == 0 & 
                                     included$support_binary == 1 &
                                     included$is_replication == 0))/(n.SR - n.rep.SR)

# Positive result rate of *replication* RRs = .4048
prop.rep.support.RR <- length(which(included$is_RR == 1 & 
                                    included$support_binary == 1 &
                                    included$is_replication == 1))/n.rep.RR
# Positive result rate of *original* RRs = .4828
prop.orig.support.RR <- length(which(included$is_RR == 1 & 
                                     included$support_binary == 1 &
                                     included$is_replication == 0))/(n.RR - n.rep.RR)

## Calculate confidence intervals for original vs 
## replication SRs and RRs
SR.orig.binom <- binom.test(x = prop.orig.support.SR*(n.SR-n.rep.SR), n = n.SR-n.rep.SR)
SR.rep.binom <- binom.test(x = prop.rep.support.SR*n.rep.SR, n = n.rep.SR)
RR.orig.binom <- binom.test(x = prop.orig.support.RR*(n.RR-n.rep.RR), n = n.RR-n.rep.RR)
RR.rep.binom <- binom.test(x = prop.rep.support.RR*n.rep.RR, n = n.rep.RR)

## 4.1 Proportions test to test if *original* RRs still have a lower 
## positive result rate than *original* SRs (i.e., one-sided test)
repproptest <- prop.test(c(prop.orig.support.SR*(n.SR-n.rep.SR), 
                           prop.orig.support.RR*(n.RR-n.rep.RR)), 
                         c(n.SR-n.rep.SR, n.RR-n.rep.RR), alternative = "greater")

## 4.2 Equivalence test to test if the difference is larger than 6%
# Equivalence bounds/smallest effect size of interest (SESOI):
# same as for main hypothesis test (6%)

SESOI <- abs(91.5 - 85.5)/100

## Run proportions test and equivalence test using the TOSTER function
## TOSTtwo.prop:
reptost <- TOSTtwo.prop(prop1 = prop.orig.support.SR, 
                        prop2 = prop.orig.support.RR, 
                        n1 = n.SR-n.rep.SR, 
                        n2 = n.RR-n.rep.RR, 
                        low_eqbound = -SESOI, 
                        high_eqbound = SESOI,
                        alpha = 0.05)

## 4.3 Create a table showing the positive result rate for replications vs
## original studies in RRs vs SRs
rep.table <- data.frame(group = c("SRs", "RRs"),
                        n.original = c(n.SR-n.rep.SR, n.RR-n.rep.RR),
                        pos.original = c(prop.orig.support.SR*(n.SR-n.rep.SR), 
                                         prop.orig.support.RR*(n.RR-n.rep.RR)),
                        percent.pos.original = c(prop.orig.support.SR*100,
                                                 prop.orig.support.RR*100), 
                        CI.original = c(paste(printnum(min(SR.orig.binom$conf.int)*100),
                                              printnum(max(SR.orig.binom$conf.int)*100), 
                                              sep = "; "),
                                        paste(printnum(min(RR.orig.binom$conf.int)*100),
                                              printnum(max(RR.orig.binom$conf.int)*100), 
                                              sep = "; ")),
                        n.rep = c(n.rep.SR, n.rep.RR),
                        pos.rep = c(prop.rep.support.SR*n.rep.SR, prop.rep.support.RR*n.rep.RR),
                        percent.pos.rep = c(prop.rep.support.SR*100, prop.rep.support.RR*100), 
                        CI.rep = c(paste(printnum(min(SR.rep.binom$conf.int)*100),
                                         printnum(max(SR.rep.binom$conf.int)*100), sep = "; "),
                                   paste(printnum(min(RR.rep.binom$conf.int)*100),
                                         printnum(max(RR.rep.binom$conf.int)*100), sep = "; ")))

```
As expected, direct replications were much more common among RRs than SRs: `r n.rep.RR` out of `r n.RR` RRs ($`r printnum(prop.rep.RR*100)`\%$), but only `r n.rep.SR` out of `r n.SR` SRs ($`r printnum(prop.rep.SR*100)`\%$) were classified as direct replications of previously published work. 
However, this difference cannot account for the stark overall difference between SRs and RRs described above: 
Although replication RRs in our sample indeed had a lower positive result rate than original RRs (see Table 1), the difference between original SRs and original RRs -- $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$ -- was still significantly different from 0 ($\chi^2 = `r printnum(repproptest$statistic)`$, $p `r printp(repproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(reptost$TOST_z1, reptost$TOST_z2))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
```{r echo = FALSE, results = 'asis'}
apa_table(
  rep.table
  , digits = c(0, 0, 0, 2, 0, 0, 0, 2, 0)
  , col.names = c("", "n", "supported", "\\%", "95\\% CI", "n", "supported", "\\%", "95\\% CI")
  , align = c("l", rep("r", 8))
  , caption = "Positive results in original studies vs replication studies"
  , note = "SRs = standard reports, RRs = Registered Reports"
  , added_stub_head = "Variables"
  , col_spanners = list(`original studies` = c(2, 5), `replication studies` = c(6, 9))
)
```

```{r include=FALSE}
## 5. Run exploratory analysis: compare SRs to Fanelli (2010)

# Number of Psychology papers in Fanelli (2010, from Fig. 1)
n.Fanelli <- 141
# Fanelli (2010) reports the positive result rate for Psychiatry&Psychology as
# 91.5% (p. 3). This is likely a rounded number since 141*0.915 = 129.015. For
# a more precise analysis, we assume that 129 out of 141 papers in Fanelli's 
# sample had positive results, giving a positive result rate of 129/141 = 0.9148936.
# In the following, we'll use this more precise number (129/141) in place of the
# 91.5% reported in the paper.
prop.support.Fanelli <- 129/141

## 5.1 Proportions test to test if the positive result rate of Psychology
## papers in Fanelli (2010) is different from SRs in our study

Fanelliproptest <- prop.test(c(prop.support.Fanelli*n.Fanelli,
                               prop.support.SR*n.SR),
                             c(n.Fanelli, n.SR), alternative = "two.sided")

## 5.2 Equivalence test to test if the difference is larger than +/-6%
# Equivalence bounds/smallest effect size of interest (SESOI):
# same as for main hypothesis test (6%)

SESOI <- abs(91.5 - 85.5)/100

## Run proportions test and equivalence test using the TOSTER function
## TOSTtwo.prop:
Fanellitost <- TOSTtwo.prop(prop1 = prop.support.Fanelli, 
                            prop2 = prop.support.SR, 
                            n1 = n.Fanelli, 
                            n2 = n.SR, 
                            low_eqbound = -SESOI, 
                            high_eqbound = SESOI,
                            alpha = 0.05)
```
Since our SR sample represents a direct replication of @Fanelli2010 for the discipline Psychiatry & Psychology, another interesting question to ask is how our results compare to Fanelli's.
The difference between the positive result rate for SRs in our sample ($`r printnum(prop.support.SR*100)`\%$) and Fanelli's ($`r printnum(prop.support.Fanelli*100)`\%$) is $`r printnum((prop.support.SR-prop.support.Fanelli)*100)`\%$. This difference is not significantly different from 0 in a two-sided proportions test ($\chi^2 = `r printnum(Fanelliproptest$statistic)`$, $p= `r printp(Fanelliproptest$p.value)`$) but also not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(Fanellitost$TOST_z1, Fanellitost$TOST_z2))`$, $p= `r printp(max(Fanellitost$TOST_p1, Fanellitost$TOST_p2))`$), both at $\alpha = 5\%$. 
In other words, we can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least $\pm `r SESOI*100`\%$ between them. 
The data are inconclusive.

```{r include=FALSE}
## 6. Analyse the phrases used to introduce hypotheses in RRs

## 6.1 Check how many RRs would have been discovered with the search
## phrase "test* the hypothes*"

# Create a new variable that indicates if the *title* contains 
# the phrase "test* the hypothes*" (TRUE vs FALSE)
included$searchphrase.in.title <- sapply(included$title, grepl, 
                                         pattern = "test\\w* the hypothes")
# Create a new variable that indicates if the *keywords* contain 
# the phrase "test* the hypothes*" (TRUE vs FALSE)
included$searchphrase.in.keywords <- sapply(included$keywords, grepl, 
                                            pattern = "test\\w* the hypothes")
# Create a new variable that indicates if the *abstract* contains 
# the phrase "test* the hypothes*" (TRUE vs FALSE)
included$searchphrase.in.abstract <- sapply(included$abstract, grepl, 
                                            pattern = "test\\w* the hypothes")

# Calculate the number of RRs that contain the search phrase in their abstract,
# title, or keywords: 2 RRs
testthehypothes.RR <- length(which(included$is_RR == 1 & 
                                     (included$searchphrase.in.abstract == TRUE |
                                        included$searchphrase.in.keywords == TRUE |
                                        included$searchphrase.in.title == TRUE)))
```

```{r include=FALSE}
## 6.2 Analyse the introduction phrases and create clusters of five "core words"
hypintros <- included[which(included$is_RR==1), c("id",
                                                  "support_binary",
                                                  "is_replication",
                                                  "hyp_from_fulltext",
                                                  "RR_hyp_intro_abstract", 
                                                  "RR_hyp_intro_fulltext")]

hypintros <- as.data.frame(hypintros)

hypintros$abstract.count <- ifelse(is.na(str_count(hypintros$RR_hyp_intro_abstract, ";")), 0, 
                                   str_count(hypintros$RR_hyp_intro_abstract, ";") + 1)
hypintros$fulltext.count <- ifelse(is.na(str_count(hypintros$RR_hyp_intro_fulltext, ";")), 0, 
                                   str_count(hypintros$RR_hyp_intro_fulltext, ";") + 1)

hypintros$introabstract.1 <- sapply(strsplit(hypintros$RR_hyp_intro_abstract, "; "), "[", 1)
hypintros$introabstract.2 <- sapply(strsplit(hypintros$RR_hyp_intro_abstract, "; "), "[", 2)
hypintros$introfulltext.1 <- sapply(strsplit(hypintros$RR_hyp_intro_fulltext, "; "), "[", 1)
hypintros$introfulltext.2 <- sapply(strsplit(hypintros$RR_hyp_intro_fulltext, "; "), "[", 2)
hypintros$introfulltext.3 <- sapply(strsplit(hypintros$RR_hyp_intro_fulltext, "; "), "[", 3)

# Determine how many replication RRs have more than 1 hypothesis introduction phrase: 10
length(which((hypintros$abstract.count+hypintros$fulltext.count)>1 & hypintros$is_replication==1))

# Determine how many original RRs have more than 1 hypothesis introduction phrase: 11
length(which((hypintros$abstract.count+hypintros$fulltext.count)>1 & hypintros$is_replication==0))

intros.long <- melt(hypintros, 
                    id.vars = c("id", "is_replication", "hyp_from_fulltext", 
                                "abstract.count", "fulltext.count"), 
                    measure.vars = c("introabstract.1", "introabstract.2", 
                                     "introfulltext.1", "introfulltext.2", "introfulltext.3"),
                    variable.name = "origin", value.name = "phrase", na.rm = TRUE)

intros.long$origin <- ifelse(sapply(intros.long$origin, grepl, pattern = "abstract"), "abstract", "fulltext")

# clean up: some phrases had "\n" at the end, remove that
intros.long$phrase <- sapply(strsplit(intros.long$phrase, "\n"), "[", 1)

intros.long$test <- sapply(intros.long$phrase, grepl, pattern = "test")
intros.long$hypothes <- sapply(intros.long$phrase, grepl, pattern = "hypothes", ignore.case = TRUE)
intros.long$replicat <- sapply(intros.long$phrase, grepl, pattern = "replicat")
intros.long$predict <- sapply(intros.long$phrase, grepl, pattern = "predict")
intros.long$examin <- sapply(intros.long$phrase, grepl, pattern = "examin")

uniquephrases <- unique(intros.long$phrase)
uniquewords <- unique(unlist(sapply(strsplit(uniquephrases, " "), unique)))
uniquewords <- uniquewords[order(uniquewords)]

wordstems.cleaned <- c("according", "aim", "assume", "attempt", 
                       "conduct", "critically", "establish", "examine", 
                       "expect", "experiment", "H1", "hypothes", 
                       "if",  "investigate", "performed", "predication", 
                       "predict", "present", "registered", "replicat", 
                       "report", "reproduce", "sought", "suggests", 
                       "test", "then")

wordoccurrences.df <- data.frame(word = wordstems.cleaned, count = NA)
for (i in 1:length(wordstems.cleaned)) {
  wordoccurrences.df$count[i] <- sum(sapply(grepl(wordstems.cleaned[i], 
                                            intros.long$phrase, 
                                            ignore.case = TRUE), sum))
}
wordoccurrences.df <- wordoccurrences.df[order(-wordoccurrences.df$count),]

# number of times "test*" and "hypothes*" co-occur
test.and.hypothes <- sum(grepl("test", intros.long$phrase) & grepl("hypothes", 
                                                intros.long$phrase,
                                                ignore.case = TRUE))

# number of hyp intros that contain either "test*" OR "hypothes*"
test.or.hypothes <- sum(grepl("test", intros.long$phrase) | grepl("hypothes", 
                                              intros.long$phrase,
                                              ignore.case = TRUE))

## HERE COME THE TABLES OF DEATH -- EXPAND AT YOUR OWN RISK ##
#######################################################################################
### MAKE TABLE FOR ORIGINAL HYPOTHESIS INTROS ###
### Original hypothesis intros have 7 categories:
# 1: hypothes*, test*
# 2: hypothes*
# 3: test*, predict*
# 4: test*
# 5: predict*
# 6: examin*
# 7: (other)

##*****************************************#
## PART 1: hypothes*, test*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
                                                intros.long$hypothes == TRUE &
                                                intros.long$test == TRUE &
                                                intros.long$replicat == FALSE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == FALSE)])

auxrow <- c("hypothes*, test*", "", 
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "abstract" &
                           intros.long$hypothes == TRUE &
                           intros.long$test == TRUE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "fulltext" &
                           intros.long$hypothes == TRUE &
                           intros.long$test == TRUE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$hypothes == TRUE &
                           intros.long$test == TRUE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)))

auxtable <- data.frame(core = rep(NA, length(phraselist)), phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                    & intros.long$origin == "abstract"
                                    & intros.long$is_replication == 0))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                    & intros.long$origin == "fulltext"
                                    & intros.long$is_replication == 0))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 0))

  auxtable <- auxtable[order(auxtable$phrase),]
 }

phrasetable.orig <- rbind(auxrow, auxtable)

##*****************************************#
## PART 2: hypothes*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
                                                intros.long$hypothes == TRUE &
                                                intros.long$test == FALSE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == FALSE)])
auxrow <- c("hypothes*", "", 
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "abstract" &
                           intros.long$hypothes == TRUE &
                           intros.long$test == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "fulltext" &
                           intros.long$hypothes == TRUE &
                           intros.long$test == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$hypothes == TRUE &
                           intros.long$test == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)))

auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 0))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 0))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 0))

  auxtable <- auxtable[order(auxtable$phrase),]
}
phrasetable.orig <- rbind(phrasetable.orig, auxrow, auxtable)

##*****************************************#
## PART 3: test*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
                                                intros.long$hypothes == FALSE &
                                                intros.long$test == TRUE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == FALSE)])
auxrow <- c("test*", "", 
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "abstract" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == TRUE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "fulltext" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == TRUE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$hypothes == FALSE &
                           intros.long$test == TRUE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)))

auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 0))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 0))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 0))

  auxtable <- auxtable[order(auxtable$phrase),]
}
phrasetable.orig <- rbind(phrasetable.orig, auxrow, auxtable)

##*****************************************#
## PART 4: test*, predict*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
                                                intros.long$hypothes == FALSE &
                                                intros.long$test == TRUE &
                                                intros.long$predict == TRUE &
                                                intros.long$examin == FALSE)])

auxtable <- data.frame(core = "test*, predict*", phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 0))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 0))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 0))

  auxtable <- auxtable[order(auxtable$phrase),]
}
phrasetable.orig <- rbind(phrasetable.orig, auxtable)

##*****************************************#
## PART 5: predict*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
                                                intros.long$hypothes == FALSE &
                                                intros.long$test == FALSE &
                                                intros.long$predict == TRUE &
                                                intros.long$examin == FALSE)])
auxrow <- c("predict*", "", 
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "abstract" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$predict == TRUE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "fulltext" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$predict == TRUE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$predict == TRUE &
                           intros.long$examin == FALSE)))

auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 0))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 0))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 0))

  auxtable <- auxtable[order(auxtable$phrase),]
}
phrasetable.orig <- rbind(phrasetable.orig, auxrow, auxtable)

##*****************************************#
## PART 6: examin*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
                                                intros.long$hypothes == FALSE &
                                                intros.long$test == FALSE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == TRUE)])
auxrow <- c("examin*", "", 
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "abstract" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == TRUE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "fulltext" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == TRUE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == TRUE)))

auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 0))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 0))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 0))

  auxtable <- auxtable[order(auxtable$phrase),]
}
phrasetable.orig <- rbind(phrasetable.orig, auxrow, auxtable)

##*****************************************#
## PART 7: (other)
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
                                                intros.long$hypothes == FALSE &
                                                intros.long$test == FALSE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == FALSE)])
auxrow <- c("(other)", "", 
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "abstract" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$origin == "fulltext" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 0 &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)))

auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 0))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 0))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 0))

  auxtable <- auxtable[order(auxtable$phrase),]
}
phrasetable.orig <- rbind(phrasetable.orig, auxrow, auxtable)

phrasetable.orig$core[which(is.na(phrasetable.orig$core))] <- ""
## THAT'S IT THE TABLE WITH ORIGINAL HYP INTROS IS DONE, SORRY FOR THE UGLY CODE ##

#######################################################################################
### MAKE TABLE FOR *REPLICATION* HYPOTHESIS INTROS ###
### Replication hypothesis intros have 10 categories:
# 1: hypothes*, test*
# 2: hypothes*, predict*
# 3: hypothes*, examin*
# 4: hypothes*
# 5: test*
# 6: replicat*
# 7: replicat*, examine*
# 8: predict*
# 9: examin*
#10: (other)

##*****************************************#
## PART 1: hypothes*, test*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
                                                intros.long$hypothes == TRUE &
                                                intros.long$test == TRUE &
                                                intros.long$replicat == FALSE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == FALSE)])

auxrow <- c("hypothes*, test*", "", 
            length(which(intros.long$is_replication == 1 &
                           intros.long$origin == "abstract" &
                           intros.long$hypothes == TRUE &
                           intros.long$test == TRUE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 1 &
                           intros.long$origin == "fulltext" &
                           intros.long$hypothes == TRUE &
                           intros.long$test == TRUE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 1 &
                           intros.long$hypothes == TRUE &
                           intros.long$test == TRUE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)))

auxtable <- data.frame(core = rep(NA, length(phraselist)), phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 1))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 1))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 1))

  auxtable <- auxtable[order(auxtable$phrase),]
}

phrasetable.rep <- rbind(auxrow, auxtable)

##*****************************************#
## PART 2: hypothes*, predict*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
                                                intros.long$hypothes == TRUE &
                                                intros.long$test == FALSE &
                                                intros.long$replicat == FALSE &
                                                intros.long$predict == TRUE &
                                                intros.long$examin == FALSE)])

auxtable <- data.frame(core = "hypothes*, predict*", phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 1))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 1))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 1))

  auxtable <- auxtable[order(auxtable$phrase),]
}

phrasetable.rep <- rbind(phrasetable.rep, auxtable)

##*****************************************#
## PART 3: hypothes*, examin*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
                                                intros.long$hypothes == TRUE &
                                                intros.long$test == FALSE &
                                                intros.long$replicat == FALSE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == TRUE)])

auxtable <- data.frame(core = "hypothes*, examin*", phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 1))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 1))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 1))

  auxtable <- auxtable[order(auxtable$phrase),]
}

phrasetable.rep <- rbind(phrasetable.rep, auxtable)

##*****************************************#
## PART 4: hypothes*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
                                                intros.long$hypothes == TRUE &
                                                intros.long$test == FALSE &
                                                intros.long$replicat == FALSE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == FALSE)])

auxrow <- c("hypothes*", "", 
            length(which(intros.long$is_replication == 1 &
                           intros.long$origin == "abstract" &
                           intros.long$hypothes == TRUE &
                           intros.long$test == FALSE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 1 &
                           intros.long$origin == "fulltext" &
                           intros.long$hypothes == TRUE &
                           intros.long$test == FALSE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 1 &
                           intros.long$hypothes == TRUE &
                           intros.long$test == FALSE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)))

auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 1))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 1))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 1))

  auxtable <- auxtable[order(auxtable$phrase),]
}

phrasetable.rep <- rbind(phrasetable.rep, auxrow, auxtable)

##*****************************************#
## PART 5: test*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
                                                intros.long$hypothes == FALSE &
                                                intros.long$test == TRUE &
                                                intros.long$replicat == FALSE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == FALSE)])

auxrow <- c("test*", "", 
            length(which(intros.long$is_replication == 1 &
                           intros.long$origin == "abstract" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == TRUE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 1 &
                           intros.long$origin == "fulltext" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == TRUE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 1 &
                           intros.long$hypothes == FALSE &
                           intros.long$test == TRUE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)))

auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 1))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 1))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 1))

  auxtable <- auxtable[order(auxtable$phrase),]
}

phrasetable.rep <- rbind(phrasetable.rep, auxrow, auxtable)

##*****************************************#
## PART 6: replicat*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
                                                intros.long$hypothes == FALSE &
                                                intros.long$test == FALSE &
                                                intros.long$replicat == TRUE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == FALSE)])

auxrow <- c("replicat*", "", 
            length(which(intros.long$is_replication == 1 &
                           intros.long$origin == "abstract" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$replicat == TRUE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 1 &
                           intros.long$origin == "fulltext" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$replicat == TRUE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 1 &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$replicat == TRUE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)))

auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 1))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 1))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 1))

  auxtable <- auxtable[order(auxtable$phrase),]
}

phrasetable.rep <- rbind(phrasetable.rep, auxrow, auxtable)

##*****************************************#
## PART 7: replicat*, examine*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
                                                intros.long$hypothes == FALSE &
                                                intros.long$test == FALSE &
                                                intros.long$replicat == TRUE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == TRUE)])

auxtable <- data.frame(core = "replicat*, examin*", phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 1))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 1))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 1))

  auxtable <- auxtable[order(auxtable$phrase),]
}

phrasetable.rep <- rbind(phrasetable.rep, auxtable)

##*****************************************#
## PART 8: predict*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
                                                intros.long$hypothes == FALSE &
                                                intros.long$test == FALSE &
                                                intros.long$replicat == FALSE &
                                                intros.long$predict == TRUE &
                                                intros.long$examin == FALSE)])

auxtable <- data.frame(core = "predict*", phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 1))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 1))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 1))

  auxtable <- auxtable[order(auxtable$phrase),]
}

phrasetable.rep <- rbind(phrasetable.rep, auxtable)

##*****************************************#
## PART 9: examin*
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
                                                intros.long$hypothes == FALSE &
                                                intros.long$test == FALSE &
                                                intros.long$replicat == FALSE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == TRUE)])

auxtable <- data.frame(core = "examin*", phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 1))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 1))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 1))

  auxtable <- auxtable[order(auxtable$phrase),]
}

phrasetable.rep <- rbind(phrasetable.rep, auxtable)

##*****************************************#
## PART 10: (other)
##*****************************************#
phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
                                                intros.long$hypothes == FALSE &
                                                intros.long$test == FALSE &
                                                intros.long$replicat == FALSE &
                                                intros.long$predict == FALSE &
                                                intros.long$examin == FALSE)])

auxrow <- c("(other)", "", 
            length(which(intros.long$is_replication == 1 &
                           intros.long$origin == "abstract" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 1 &
                           intros.long$origin == "fulltext" &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)),
            length(which(intros.long$is_replication == 1 &
                           intros.long$hypothes == FALSE &
                           intros.long$test == FALSE &
                           intros.long$replicat == FALSE &
                           intros.long$predict == FALSE &
                           intros.long$examin == FALSE)))

auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
                       count.abstract = NA, count.fulltext = NA, count.total = NA)

for (i in 1:length(phraselist)) {
  auxtable$phrase[i] <- phraselist[i]
  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "abstract"
                                             & intros.long$is_replication == 1))
  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
                                             & intros.long$origin == "fulltext"
                                             & intros.long$is_replication == 1))
  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
                                          & intros.long$is_replication == 1))

  auxtable <- auxtable[order(auxtable$phrase),]
}
phrasetable.rep <- rbind(phrasetable.rep, auxrow, auxtable)

phrasetable.rep$core[which(is.na(phrasetable.rep$core))] <- ""
## THAT'S IT FOR REPLICATION HYP INTROS, I'M REALLY SO SORRY!  ##
###################################################################################
```
Finally, we analysed the language that was used to introduce or signal hypotheses in RRs.
Does Fanelli's search phrase "test$^\ast$ the hypothes$^\ast$" capture hypothesis-testing RRs reasonably well? 
The answer is a resounding "no":
Searching the abstracts, titles, and keywords of the RR sample showed that only `r testthehypothes.RR`/`r n.RR` RRs would have been detected with this search phrase. 
Which analogous hypothesis-introduction phrases are used in RRs, and can they be summarised in a convenient way? 
To get an overview, we stripped the hypothesis quotes of RRs from all content-specific information and extracted "minimal" phrases that most distinctively indicated that a hypothesis was being described.
For example, from the hypothesis quote "(f)or Study 1, we predicted that participants reading about academic (vs. social) behaviors would show a better anagram performance" we extracted the hypothesis-introduction phrase "predicted that".

For the majority of RRs (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==1))`), we identified one hypothesis-introduction phrase; the remaining ones used two (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==2))` RRs), three (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==3))` RRs), or four (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==4))` RR) different phrases or had no identifiable hypothesis introduction (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==0))` RR).
In this total set of `r nrow(intros.long)` hypothesis introductions, we found `r length(uniquephrases)` unique phrases, showing substantial linguistic variation (see Tables 2 and 3).
In order to condense the information further, we listed all unique word stems (e.g., the word stem "hypothes$^\ast$" captures the words "hypothesis", "hypotheses", "hypothesize", "hypothesized", and so on) and analysed their frequency among all hypothesis introductions.
Excluding words that are common but too unspecific by themselves, such as "that", "to", or "whether", the five most frequent word stems were "hypothes$^\ast$" (`r wordoccurrences.df[1,2]` occurrences), "replicat$^\ast$" (`r wordoccurrences.df[2,2]`), "test$^\ast$" (`r wordoccurrences.df[3,2]`), "examine$^\ast$" (`r wordoccurrences.df[4,2]`), and "predict$^\ast$" (`r wordoccurrences.df[5,2]`). 
Clearly "test$^\ast$" and "hypothes$^\ast$" are quite popular, yet they co-occurred only `r test.and.hypothes` times and more than half of all hypothesis introductions (`r nrow(intros.long)-test.or.hypothes`/`r nrow(intros.long)`) contained neither word. Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 ($`r printnum(30/43*100)`\%$) hypothesis introductions found in original RRs contained either "test$^\ast$" or "hypothes$^\ast$" or both, while only 16 out of 54 ($`r printnum(16/54*100)`\%$) hypothesis introductions in direct replication RRs did.

We noticed that direct replication RRs generally tended to use different language to describe their hypothesis (or rather their goal). As the high frequency of the word stem "replicat$^\ast$" suggests, these studies were often not framed as new tests of a previously tested hypothesis, but as attempts to replicate a previously documented effect or to repeat a previously conducted experiment. 
Tables 2 and 3 list all unique hypothesis introductions and their frequency for original RRs and direct replication RRs, respectively, grouped by the five most frequent word stems ("hypothes$^\ast$", "replicat$^\ast$", "test$^\ast$", "examine$^\ast$", "predict$^\ast$"). 
Using five as a cutoff value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.

```{r echo = FALSE, results = 'asis'}
apa_table(
  phrasetable.orig
  , digits = c(0, 0, 0, 0, 0)
  , col.names = c("core word(s)", "introduction phrase", "abstract", 
                  "full text", "total")
  , align = c("l", "l", rep("r", 3))
  , caption = "Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)"
  , note = "This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, 9 papers contributed two each, one contributed three, and one contributed four."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(3, 5))
  , midrules = c(6, 16, 22, 23, 27, 32)
  , landscape = FALSE
  , font_size = "footnotesize"
  , escape = TRUE
)
```

```{r echo = FALSE, results = 'asis'}
apa_table(
  phrasetable.rep
  , digits = c(0, 0, 0, 0, 0)
  , col.names = c("core word(s)", "introduction phrase", "abstract", 
                  "full text", "total")
  , align = c("l", "l", rep("r", 3))
  , caption = "Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)"
  , note = "This table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no codeable hypothesis introduction. 30 papers contributed one phrase each, 7 papers contributed two each, and three contributed three each."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(3, 5))
  , midrules = c(4, 5, 6, 12, 16, 33, 34, 35, 36)
  , landscape = FALSE
  , font_size = "footnotesize"
  , escape = TRUE
)
```

# Discussion
```{r echo=FALSE, warning=FALSE, fig.width=6, fig.height=3, fig.cap=" "}
# Inferring the likely proportion of true hypotheses studied in the literature
# and statistical power based on the observed proportion of significant results

# t = proportion of true hypotheses
# a = alpha
# b = beta; i.e. 1-b = power
# PRR = positive result rate (proportion of significant results in the literature)
truehyps <- function(PRR, a, pwr){-(PRR - a)/((1-pwr) + a - 1)}
pwrfun <- function(t, a, PRR){(a*t+PRR-a)/(t)}

a <- 0.05

### 3 groups: original SRs, original RRs, all RRs

pwrprior.df <-  data.frame(t=c(1:1000)/1000)
pwrprior.df$group <- "all RRs (PRR = .4366, N = 71)"
pwrprior.df$lower <- pwrfun(t = pwrprior.df$t, a = a, PRR = min(RR.binom$conf.int))
pwrprior.df$estimate <- pwrfun(t = pwrprior.df$t, a = a, PRR = prop.support.RR)
pwrprior.df$upper <- pwrfun(t = pwrprior.df$t, a = a, PRR = max(RR.binom$conf.int))

pwrprior.origRR <- data.frame(t=c(1:1000)/1000)
pwrprior.origRR$group <- "original RRs (PRR = .5, n = 30)"
pwrprior.origRR$lower <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = min(RR.orig.binom$conf.int))
pwrprior.origRR$estimate <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = prop.orig.support.RR)
pwrprior.origRR$upper <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = max(RR.orig.binom$conf.int))

pwrprior.origSR <- data.frame(t=c(1:1000)/1000)
pwrprior.origSR$group <- "original SRs (PRR = .9595, n = 148)"
pwrprior.origSR$lower <- pwrfun(t = pwrprior.origSR$t, a = a, PRR = min(SR.orig.binom$conf.int))
pwrprior.origSR$estimate <- pwrfun(t = pwrprior.origSR$t, a = a, PRR = prop.orig.support.SR)
pwrprior.origSR$upper <- pwrfun(t = pwrprior.origSR$t, a = a, PRR = max(SR.orig.binom$conf.int))

pwrprior.df <- rbind(pwrprior.df, pwrprior.origRR, pwrprior.origSR)

pwrprior.df$lower[pwrprior.df$lower > 1 & pwrprior.df$upper > 1] <- NA
pwrprior.df$lower[pwrprior.df$lower > 1] <- 1
pwrprior.df$upper[pwrprior.df$upper > 1] <- 1

pwrprior.df$group <- factor(pwrprior.df$group, 
                            levels = c("original SRs (PRR = .9595, n = 148)",
                                       "original RRs (PRR = .5, n = 30)", 
                                       "all RRs (PRR = .4366, N = 71)"))

ggplot(pwrprior.df, aes(x = t, y = estimate, colour = group, fill = group,
                        linetype = group)) +
  geom_line(aes(y = estimate), size = 1) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .42, linetype = "blank") +
  scale_x_continuous(name="proportion of true hypotheses", 
                     limits=c(0.25, 1), 
                     breaks = c(seq(0.3, 1, 0.1)),
                     expand = c(0, 0)) +
  scale_y_continuous(name="statistical power", 
                     limits=c(0.25, 1), 
                     breaks = c(seq(0.3, 1, 0.1)),
                     expand = c(0, 0)) +
  scale_colour_manual(values = c("#0073C0", "#ED443F", "#2D132C"), name = NULL) +
  scale_fill_manual(values = c("#0073C0", "#ED443F", "#2D132C"), name = NULL) +
  scale_linetype_manual(values = c("solid", "dashed", "dotted"), name = NULL) +
  theme_bw()
```

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

### 2020-01-05 manuscript.tex
Added the manuscript Rmd file and the two bib files (for references and software) and updated the Rmd file: changed "CR" to "SR"/"conventional" to "standard" throughout, added a caption for Figure 2 and notes for all tables, and added the code for Figure 3. Knitted the manuscript with the updated data.

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[british,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Positive Results in Registered Reports},
            pdfauthor={Anne Scheel, Mitchell Schijen, \& Daniël Lakens},
            pdfkeywords={keyword 1, keyword 2, keyword 3},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\shorttitle{Positive Results in Registered Reports}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Eindhoven University of Technology}
\keywords{keyword 1, keyword 2, keyword 3\newline\indent Word count: XXX}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\usepackage{lineno}

\linenumbers
\usepackage{float}
\usepackage{framed}
\usepackage{caption}
\usepackage{setspace}
\captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
\newfloat{textbox}{thp}{lop}
\floatname{textbox}{Box}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=british]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[variant=british]{english}
\fi

\title{Positive Results in Registered Reports}
\author{Anne Scheel\textsuperscript{1}, Mitchell Schijen\textsuperscript{1}, \& Daniël Lakens\textsuperscript{1}}
\date{}

\authornote{

Correspondence concerning this article should be addressed to Anne Scheel, Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands. E-mail: \href{mailto:a.m.scheel@tue.nl}{\nolinkurl{a.m.scheel@tue.nl}}}
\note{\clearpage}
\abstract{
XXXXXXXXXXXXXXXXXXX

}

\begin{document}
\maketitle

\hypertarget{analysis}{%
\subsection{Analysis}\label{analysis}}

We planned to test our hypothesis in the following way (quoting directly from our preregistration, \url{https://osf.io/sy927}, point 9):

\begin{quote}
A one-sided proportion test with an alpha level of \(5\%\) will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports in psychology.
In addition to testing if there is a statistically significant difference between RRs and conventional reports, we will test if the difference is smaller than our smallest effect size of interest using an equivalence test for proportion tests with an alpha level of \(5\%\) (Lakens, Scheel, \& Isager, 2018).
We determined our smallest effect size of interest to be the difference between the positive result rate in psychology (\(91.5\%\)) and the positive result rate in general social sciences (\(85.5\%\)) as reported by Fanelli (2010), i.e.~a difference of \(91.5\% - 85.5\% = 6\%\).
The rationale for choosing general social sciences as a comparison is that this discipline had the lowest positive result rate amongst the \enquote{soft} sciences (Fanelli, 2010).
The exact percentage for general social sciences was extracted from Figure 1 in Fanelli (2010) using the software WebPlotDigitizer (Rohatgi, 2018).
\end{quote}

We would accept our hypothesis that RRs have a lower positive result rate than SRs if we found a negative difference between RRs and SRs that was significantly different from 0 \emph{and} not statistically equivalent to a range from \(-6\%\) to \(+6\%\) (both at \(\alpha = 5\%\)).

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{confirmatory-analyses}{%
\subsection{Confirmatory Analyses}\label{confirmatory-analyses}}

146 out of 152 SRs and 31 out of 71 RRs had positive results, meaning that the positive result rate was \(96.05 \%\) for SRs (\(95 \%\) CI {[}91.61, 98.54{]}) and \(43.66 \%\) for RRs (\(95 \%\) CI {[}31.91, 55.95{]}; see Fig. 1).
The preregistered one-sided proportions test with an alpha level of \(5\%\) showed that this difference of \(-52.39\%\) was statistically significant, \(\chi^2 = 77.96\), \(p < .001\).
Unsurprisingly, the difference was not statistically equivalent to a range between \(-6\%\) and \(6\%\) at \(\alpha = 5\%\), \(z = 7.61\), \(p > .999\), meaning that we cannot reject differences more extreme than \(6\%\).
We thus accept our hypothesis that the positive result rate in RRs is lower than in SRs.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}Positive result rates for standard reports and Registered Reports. Error bars indicate 95\% confidence intervals around the observed positive result rate.}
\end{figure}

\hypertarget{exploratory-analyses}{%
\subsection{Exploratory Analyses}\label{exploratory-analyses}}

As expected, direct replications were much more common among RRs than SRs: 41 out of 71 RRs (\(57.75\%\)), but only 4 out of 152 SRs (\(2.63\%\)) were classified as direct replications of previously published work.
However, this difference cannot account for the stark overall difference between SRs and RRs described above:
Although replication RRs in our sample indeed had a lower positive result rate than original RRs (see Table 1), the difference between original SRs and original RRs -- \(45.95\%\) -- was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-5}Positive results in original studies vs replication studies}
\begin{tabular}{lrrrrrrrr}
\toprule
 & \multicolumn{4}{c}{original studies} & \multicolumn{4}{c}{replication studies} \\
\cmidrule(r){2-5} \cmidrule(r){6-9}
 & n & supported & \% & 95\% CI & n & supported & \% & 95\% CI\\
\midrule
SRs & 148 & 142 & 95.95 & 91.39; 98.50 & 4 & 4 & 100.00 & 39.76; 100.00\\
RRs & 30 & 15 & 50.00 & 31.30; 68.70 & 41 & 16 & 39.02 & 24.20; 55.50\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} SRs = standard reports, RRs = Registered Reports}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

Since our SR sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question to ask is how our results compare to Fanelli's.
The difference between the positive result rate for SRs in our sample (\(96.05\%\)) and Fanelli's (\(91.49\%\)) is \(4.56\%\). This difference is not significantly different from 0 in a two-sided proportions test (\(\chi^2 = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = -3.73\), \(p= .306\)), both at \(\alpha = 5\%\).
In other words, we can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least \(\pm 6\%\) between them.
The data are inconclusive.

Finally, we analysed the language that was used to introduce or signal hypotheses in RRs.
Does Fanelli's search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} capture hypothesis-testing RRs reasonably well?
The answer is a resounding \enquote{no}:
Searching the abstracts, titles, and keywords of the RR sample showed that only 2/71 RRs would have been detected with this search phrase.
Which analogous hypothesis-introduction phrases are used in RRs, and can they be summarised in a convenient way?
To get an overview, we stripped the hypothesis quotes of RRs from all content-specific information and extracted \enquote{minimal} phrases that most distinctively indicated that a hypothesis was being described.
For example, from the hypothesis quote \enquote{(f)or Study 1, we predicted that participants reading about academic (vs.~social) behaviors would show a better anagram performance} we extracted the hypothesis-introduction phrase \enquote{predicted that}.

For the majority of RRs (49), we identified one hypothesis-introduction phrase; the remaining ones used two (16 RRs), three (4 RRs), or four (1 RR) different phrases or had no identifiable hypothesis introduction (1 RR).
In this total set of 97 hypothesis introductions, we found 64 unique phrases, showing substantial linguistic variation (see Tables 2 and 3).
In order to condense the information further, we listed all unique word stems (e.g., the word stem \enquote{hypothes\(^\ast\)} captures the words \enquote{hypothesis}, \enquote{hypotheses}, \enquote{hypothesize}, \enquote{hypothesized}, and so on) and analysed their frequency among all hypothesis introductions.
Excluding words that are common but too unspecific by themselves, such as \enquote{that}, \enquote{to}, or \enquote{whether}, the five most frequent word stems were \enquote{hypothes\(^\ast\)} (34 occurrences), \enquote{replicat\(^\ast\)} (24), \enquote{test\(^\ast\)} (20), \enquote{examine\(^\ast\)} (8), and \enquote{predict\(^\ast\)} (8).
Clearly \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times and more than half of all hypothesis introductions (51/97) contained neither word. Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions found in original RRs contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, while only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication RRs did.

We noticed that direct replication RRs generally tended to use different language to describe their hypothesis (or rather their goal). As the high frequency of the word stem \enquote{replicat\(^\ast\)} suggests, these studies were often not framed as new tests of a previously tested hypothesis, but as attempts to replicate a previously documented effect or to repeat a previously conducted experiment.
Tables 2 and 3 list all unique hypothesis introductions and their frequency for original RRs and direct replication RRs, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
Using five as a cutoff value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-9}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}
\footnotesize{
\begin{tabular}{llrrr}
\toprule
 &  & \multicolumn{3}{c}{source} \\
\cmidrule(r){3-5}
core word(s) & introduction phrase & abstract & full text & total\\
\midrule
hypothes*, test* &  & 3 & 2 & 5\\
 & test of ... hypotheses & 0 & 1 & 1\\
 & test of ... hypothesis & 1 & 0 & 1\\
 & test the hypothesis that & 1 & 0 & 1\\
 & tested ... hypotheses & 0 & 1 & 1\\
 & tested the hypothesis that & 1 & 0 & 1\\ \midrule
hypothes* &  & 5 & 12 & 17\\
 & (Hypothesis 1) & 0 & 1 & 1\\
 & Hypothesis 1 (H1): & 0 & 2 & 2\\
 & Hypothesis 1: & 0 & 1 & 1\\
 & Hypothesis 1a (H1a): & 0 & 1 & 1\\
 & hypothesis was & 0 & 1 & 1\\
 & Hypothesis: & 0 & 1 & 1\\
 & hypothesize that & 0 & 3 & 3\\
 & hypothesized that & 4 & 2 & 6\\
 & registered ... hypotheses & 1 & 0 & 1\\ \midrule
test* &  & 5 & 2 & 7\\
 & test if & 0 & 1 & 1\\
 & test whether & 1 & 1 & 2\\
 & tested whether & 2 & 0 & 2\\
 & testing & 1 & 0 & 1\\
 & to ... test & 1 & 0 & 1\\ \midrule
test*, predict* & test ... prediction & 0 & 1 & 1\\ \midrule
predict* &  & 4 & 0 & 4\\
 & had ... predictions & 1 & 0 & 1\\
 & predicted that & 2 & 0 & 2\\
 & predicts that & 1 & 0 & 1\\ \midrule
examin* &  & 5 & 0 & 5\\
 & examine whether & 2 & 0 & 2\\
 & examined & 1 & 0 & 1\\
 & examined whether & 1 & 0 & 1\\
 & to examine & 1 & 0 & 1\\ \midrule
(other) &  & 0 & 5 & 5\\
 & (H1) & 0 & 1 & 1\\
 & expected that & 0 & 1 & 1\\
 & if ... then & 0 & 1 & 1\\
 & predication that & 0 & 1 & 1\\
 & we expect & 0 & 1 & 1\\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, 9 papers contributed two each, one contributed three, and one contributed four.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-10}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
\footnotesize{
\begin{tabular}{llrrr}
\toprule
 &  & \multicolumn{3}{c}{source} \\
\cmidrule(r){3-5}
core word(s) & introduction phrase & abstract & full text & total\\
\midrule
hypothes*, test* &  & 2 & 1 & 3\\
 & test ... hypotheses & 0 & 1 & 1\\
 & test ... hypothesis & 1 & 0 & 1\\
 & tested ... hypotheses & 1 & 0 & 1\\ \midrule
hypothes*, predict* & hypotheses predicted & 1 & 0 & 1\\ \midrule
hypothes*, examin* & examined ... hypothesis & 1 & 0 & 1\\ \midrule
hypothes* &  & 2 & 5 & 7\\
 & according to ... hypothesis & 0 & 1 & 1\\
 & Hypotheses & 0 & 1 & 1\\
 & Hypothesis 1 (H1): & 0 & 1 & 1\\
 & hypothesize that & 0 & 1 & 1\\
 & hypothesized that & 2 & 1 & 3\\ \midrule
test* &  & 4 & 0 & 4\\
 & testing whether & 2 & 0 & 2\\
 & to ... test & 1 & 0 & 1\\
 & to test & 1 & 0 & 1\\ \midrule
replicat* &  & 20 & 3 & 23\\
 & aim ... to replicate & 0 & 1 & 1\\
 & aim at replicating & 1 & 0 & 1\\
 & aimed to replicate & 0 & 1 & 1\\
 & attempted to replicate & 1 & 0 & 1\\
 & attempts to replicate & 1 & 0 & 1\\
 & conducted ... replication & 3 & 0 & 3\\
 & conducted ... replications & 2 & 0 & 2\\
 & performed ... replication & 2 & 0 & 2\\
 & present ... replication & 1 & 0 & 1\\
 & present ... replications & 1 & 0 & 1\\
 & replicated ... experiment & 1 & 0 & 1\\
 & replicating & 0 & 1 & 1\\
 & report ... replication attempt & 1 & 0 & 1\\
 & report ... replications & 2 & 0 & 2\\
 & sought to replicate & 3 & 0 & 3\\
 & we replicated & 1 & 0 & 1\\ \midrule
replicat*, examin* & critically examine and replicate & 1 & 0 & 1\\ \midrule
predict* & predicted that & 2 & 0 & 2\\ \midrule
examin* & examine whether & 0 & 1 & 1\\ \midrule
(other) &  & 4 & 6 & 10\\
 & establish whether & 0 & 1 & 1\\
 & H1 & 0 & 2 & 2\\
 & investigate if & 1 & 0 & 1\\
 & sought to reproduce & 1 & 0 & 1\\
 & suggests that & 2 & 0 & 2\\
 & we ... conducted & 0 & 1 & 1\\
 & we assume & 0 & 1 & 1\\
 & we expect & 0 & 1 & 1\\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} This table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no codeable hypothesis introduction. 30 papers contributed one phrase each, 7 papers contributed two each, and three contributed three each.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Fanelli2010}{}%
Fanelli, D. (2010). "Positive" results increase down the hierarchy of the sciences. \emph{PLoS ONE}, \emph{5}(4), e10068. doi:\href{https://doi.org/10.1371/journal.pone.0010068}{10.1371/journal.pone.0010068}

\leavevmode\hypertarget{ref-Lakens2018a}{}%
Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence Testing for Psychological Research: A Tutorial. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269. doi:\href{https://doi.org/10.1016/j.ympev.2015.01.015}{10.1016/j.ympev.2015.01.015}

\leavevmode\hypertarget{ref-Rohatgi2018}{}%
Rohatgi, A. (2018). \emph{WebPlotDigitizer - Web Based Plot Digitizer}. Austin, Texas, USA. Retrieved from \url{https://automeris.io/WebPlotDigitizer}

\leavevmode\hypertarget{ref-Fanelli2010}{}%
Fanelli, D. (2010). "Positive" results increase down the hierarchy of the sciences. \emph{PLoS ONE}, \emph{5}(4), e10068. doi:\href{https://doi.org/10.1371/journal.pone.0010068}{10.1371/journal.pone.0010068}

\leavevmode\hypertarget{ref-Lakens2018a}{}%
Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence Testing for Psychological Research: A Tutorial. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269. doi:\href{https://doi.org/10.1016/j.ympev.2015.01.015}{10.1016/j.ympev.2015.01.015}

\leavevmode\hypertarget{ref-Rohatgi2018}{}%
Rohatgi, A. (2018). \emph{WebPlotDigitizer - Web Based Plot Digitizer}. Austin, Texas, USA. Retrieved from \url{https://automeris.io/WebPlotDigitizer}

\end{document}

### 2020-01-06 codebook.Rmd
no actual edits to anything, just file changes caused by me linking the repository to a second machine with a different system

@@
 library(readxl)
-library(here)
+#library(here)
 library(rio)
@@
 codebook_data <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", n_max = 243)
-#Read codebook from second sheet in excel file.
+
+# Read codebook from second sheet in Excel file.
 dict <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "codebook")
 
-#Add variable labels to data
+# Add variable labels to data (from Excel file)
 var_label(codebook_data) <- dict_to_list(dict)
+
+# Add value labels to data (manually)
 val_labels(codebook_data$include_in_analysis) <- c("excluded" = 0, "included" = 1)
-val_labels(codebook_data$is_RR) <- c("CR" = 0, "RR"= 1)
+val_labels(codebook_data$is_RR) <- c("SR" = 0, "RR"= 1)
 val_labels(codebook_data$support_binary) <- c("no support" = 0, "partial or full support" = 1)
@@
                                             "main coding round" = 1,
-                                            "CR replacements and late RR additions" = 2,
-                                            "second CR replacement" = 3)
+                                            "SR replacements and late RR additions" = 2,
+                                            "second SR replacement" = 3)
 val_labels(codebook_data$uses_AS_coding) <- c("uses MS coding" = 0, "uses AS coding" = 1)
@@
 
-#Add meta data
+# Add meta data
 metadata(codebook_data)$name <- "Positive Results in Registered Reports in Psychology"
-metadata(codebook_data)$description <- "Coded variables to compare the proportion of papers that find support for their first tested hypothesis between Registered Reports and conventional reports in psychology"
+metadata(codebook_data)$description <- "Coded variables to compare the proportion of papers that find support for their first tested hypothesis between Registered Reports and standard reports in psychology"
 metadata(codebook_data)$creator <- "Anne Scheel, Mitchell Schijen, Daniël Lakens"

### 2020-01-07 hypothesis_introduction_analyses.R
Broke up the code into four different scripts that get called in the manuscript Rmd. Code still needs a bit of cleaning up but I think this setup is a good solution.

@@ -1,0 +1,929 @@
+library("dplyr")
+library("stringr")
+library("reshape2")
+
+
+
+#source("analysis.R")
+# load the dataset from RDS created with codebook
+alldata <- readRDS("positive_results_in_registered_reports_codebook.rds")
+
+# remove excluded papers
+included <- alldata[alldata$include_in_analysis==1,]
+
+## 6. Analyse the phrases used to introduce hypotheses in RRs
+
+## 6.1 Check how many RRs would have been discovered with the search
+## phrase "test* the hypothes*"
+
+# Create a new variable that indicates if the *title* contains 
+# the phrase "test* the hypothes*" (TRUE vs FALSE)
+included$searchphrase.in.title <- sapply(included$title, grepl, 
+                                         pattern = "test\\w* the hypothes")
+# Create a new variable that indicates if the *keywords* contain 
+# the phrase "test* the hypothes*" (TRUE vs FALSE)
+included$searchphrase.in.keywords <- sapply(included$keywords, grepl, 
+                                            pattern = "test\\w* the hypothes")
+# Create a new variable that indicates if the *abstract* contains 
+# the phrase "test* the hypothes*" (TRUE vs FALSE)
+included$searchphrase.in.abstract <- sapply(included$abstract, grepl, 
+                                            pattern = "test\\w* the hypothes")
+
+# Calculate the number of RRs that contain the search phrase in their abstract,
+# title, or keywords: 2 RRs
+testthehypothes.RR <- length(which(included$is_RR == 1 & 
+                                     (included$searchphrase.in.abstract == TRUE |
+                                        included$searchphrase.in.keywords == TRUE |
+                                        included$searchphrase.in.title == TRUE)))
+
+## 6.2 Analyse the introduction phrases and create clusters of five "core words"
+
+
+hypintros <- included[which(included$is_RR==1), c("id",
+                                                  "support_binary",
+                                                  "is_replication",
+                                                  "hyp_from_fulltext",
+                                                  "RR_hyp_intro_abstract", 
+                                                  "RR_hyp_intro_fulltext")]
+
+hypintros <- as.data.frame(hypintros)
+
+hypintros$abstract.count <- ifelse(is.na(str_count(hypintros$RR_hyp_intro_abstract, ";")), 0, 
+                                   str_count(hypintros$RR_hyp_intro_abstract, ";") + 1)
[…]

### 2020-01-07 interrater_agreement.R

@@ -1,0 +1,152 @@
+# load the dataset from RDS created with codebook
+alldata <- readRDS("positive_results_in_registered_reports_codebook.rds")
+
+# remove excluded papers
+included <- alldata[alldata$include_in_analysis==1,]
+
+
+##==============================================================================##
+## 1. Calculate inter-rater agreement (between MS and AS) for main 
+## variable (support_binary)
+
+# number of papers coded by MS: 221 out of 223 = 99.10%
+support.coded.MS <- sum(included$coded_by_MS)
+# number of papers coded by AS: 70 out of 223 = 31.39%
+support.coded.AS <- sum(included$coded_by_AS)
+
+# number of RRs coded by AS: 23 out of 71 = 32.4%
+sum(included$coded_by_AS & included$is_RR)/sum(included$is_RR)
+# number of CRs coded by AS: 47 out of 152 = 30.9%
+sum(included$coded_by_AS & !included$is_RR)/sum(!included$is_RR)
+
+# number of papers double coded: 68 out of 223 = 30.49%
+support.doublecoded <- length(which(included$coded_by_MS == 1 & 
+                                      included$coded_by_AS ==1))
+
+# number of 'minor' disagreements, i.e. disagreement between 
+# full and partial support (no consequences for final analysis):
+# 15 out of 68 cases = 22.06%
+support.disagreement.minor <- length(which(included$support_orig_MS == "support" & 
+                                             included$support_orig_AS == 
+                                             "partial support")) +
+  length(which(included$support_orig_MS == 
+                 "partial support" &
+                 included$support_orig_AS == "support"))
+
+# Number of 'major' disagreements, i.e. disagreement between
+# no support and either full or partial support (consequential for
+# final analysis)
+
+# First create new variables where both full and partial 
+# support are re-coded as 1, no support as 0
+included$support_major_MS <- NA
+included$support_major_AS <- NA
+
+included[which(included$support_orig_MS == "support" | 
+                 included$support_orig_MS == "partial support"), 
+         "support_major_MS"] <- 1
+included[which(included$support_orig_AS == "support" | 
+                 included$support_orig_AS == "partial support"),
+         "support_major_AS"] <- 1
+included[which(included$support_orig_MS == "no support"), "support_major_MS"] <- 0
+included[which(included$support_orig_AS == "no support"), "support_major_AS"] <- 0
+
[…]

### 2020-01-07 power_baserate_plot.R

@@ -1,0 +1,61 @@
+library(ggplot2)
+
+# Inferring the likely proportion of true hypotheses studied in the literature
+# and statistical power based on the observed proportion of significant results
+
+# t = proportion of true hypotheses
+# a = alpha
+# b = beta; i.e. 1-b = power
+# PRR = positive result rate (proportion of significant results in the literature)
+truehyps <- function(PRR, a, pwr){-(PRR - a)/((1-pwr) + a - 1)}
+pwrfun <- function(t, a, PRR){(a*t+PRR-a)/(t)}
+
+a <- 0.05
+
+### 3 groups: original SRs, original RRs, all RRs
+
+pwrprior.df <-  data.frame(t=c(1:1000)/1000)
+pwrprior.df$group <- "all RRs (PRR = .4366, N = 71)"
+pwrprior.df$lower <- pwrfun(t = pwrprior.df$t, a = a, PRR = min(RR.binom$conf.int))
+pwrprior.df$estimate <- pwrfun(t = pwrprior.df$t, a = a, PRR = prop.support.RR)
+pwrprior.df$upper <- pwrfun(t = pwrprior.df$t, a = a, PRR = max(RR.binom$conf.int))   
+
+pwrprior.origRR <- data.frame(t=c(1:1000)/1000)
+pwrprior.origRR$group <- "original RRs (PRR = .5, n = 30)"
+pwrprior.origRR$lower <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = min(RR.orig.binom$conf.int))
+pwrprior.origRR$estimate <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = prop.orig.support.RR)
+pwrprior.origRR$upper <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = max(RR.orig.binom$conf.int))   
+
+pwrprior.origSR <- data.frame(t=c(1:1000)/1000)
+pwrprior.origSR$group <- "original SRs (PRR = .9595, n = 148)"
+pwrprior.origSR$lower <- pwrfun(t = pwrprior.origSR$t, a = a, PRR = min(SR.orig.binom$conf.int))
+pwrprior.origSR$estimate <- pwrfun(t = pwrprior.origSR$t, a = a, PRR = prop.orig.support.SR)
[…]

### 2020-01-07 quantitative_analyses.R

@@ -1,0 +1,273 @@
+library("TOSTER")
+library("ggplot2")
+library("dplyr")
+library("stringr")
+library("reshape2")
+
+
+#####################################################################################################
+#### CHUNK 1
+#####################################################################################################
+
+#source("analysis.R")
+# load the dataset from RDS created with codebook
+alldata <- readRDS("positive_results_in_registered_reports_codebook.rds")
+# alldata <- readRDS("C:/Users/20176208/surfdrive/Documents/_projects/_positiveresults/_data/positive_results_in_registered_reports_codebook.rds")
+# alldata <- readRDS("~/surfdrive/Documents/_projects/_positiveresults/_data/positive_results_in_registered_reports_codebook.rds")
+
+# remove excluded papers
+included <- alldata[alldata$include_in_analysis==1,]
+
+## 3. Run main preregistered analysis: the proportion of SRs with supported
+## hypothesis compared to the proportion of RRs with supported hypothesis
+
+# number of included SRs = 152
+n.SR <- length(which(included$is_RR == 0))
+# number of included RRs = 71
+n.RR <- length(which(included$is_RR == 1))
+
+# number of SRs with support = 146
+n.support.SR <- length(which(included$is_RR == 0 & included$support_binary == 1))
+# number of RRs with support = 31
+n.support.RR <- length(which(included$is_RR == 1 & included$support_binary == 1))
+
+# Positive result rate of SRs (proportion of SRs with support) = .9605
+prop.support.SR <- n.support.SR/n.SR
+# Positive result rate of RRs (proportion of RRs with support) = .4366
+prop.support.RR <- n.support.RR/n.RR
+
+## 3.1 Proportions test to test if RRs have a *lower* positive
+## result rate than SRs (i.e., one-sided test)
+
+proptestresult <- prop.test(c(n.support.SR, n.support.RR), c(n.SR, n.RR), alternative = "greater")
+
+
+## 3.2 Equivalence test to test if the difference is larger than 6%
+# Equivalence bounds/smallest effect size of interest (SESOI):
+# As preregistered, we used the difference between the positive result
+# rate in Psychology and in the lowest-scoring 'soft' science in 
+# Fanelli (2010) as our SESOI. The lowest-scoring 'soft' science
+# was General Social Sciences with a positive result rate of 85.5%
+# (this number is not explicitly given in the text, so we extracted it
[…]

### 2020-01-07 manuscript.Rmd
no actual edits to anything, just file changes caused by me linking the repository to a second machine with a different system
imported all text into the Rmd file, fixed all punctuation issues, soft-coded all numbers, and changed the code integration to calling separate scripts instead of doing everything inside the Rmd file

@@
 
+If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world. 
+When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability. 
+However, when published findings are systematically biased, cumulative science breaks down: 
+Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
+Unfortunately there are good reasons to believe that the psychology literature is not a faithful representation of all research psychologists conduct. 
+For more than half a century, scientists have repeatedly noticed a suspiciously high 'success' rate in psychology:
+Studying 362 empirical articles published in four psychology journals in 1955/56, @Sterling1959 found that a whopping $97.28\%$ of the studies that used significance tests rejected the null hypothesis.
+A replication of this study performed on articles published in 1986/87 reported $95.56\%$ statistically significant results [@Sterling1995]. 
+Similarly, a seminal study by @Fanelli2010 compared the literatures of 20 disciplines and found that $91.5\%$ of papers published in psychology reported support for their first or main hypothesis, the highest number of all disciplines in the study.
+For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$.
+In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes must consistently be very high (given the same study design).
+
+## A biased literature
+@Sterling1959 already suspected a selection process behind the numbers he found: 
+"(...) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of [statistical] significance" (p. 31). 
+This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature. 
+We can distinguish two broad categories of bias: "publication bias" and "questionable research practices". 
+Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
+These include editors and reviewers selectively rejecting manuscripts with negative results ["reviewer bias", @Mahoney1977; @Greenwald1975] and researchers deciding not to submit studies with negative results for publication ["file-drawering"; @Rosenthal1979].
+Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is [typically, though not always, leading to an inflated type-I error rate, see also @Lakens2019b].
+These include presenting unexpected results as having been predicted a priori [HARKing, short for "hypothesising after results are known"; @Kerr1998] and exploiting flexibility in data analysis to obtain statistically significant results ["p-hacking"; @Simmons2011].
+Evidence for both categories of bias exist: 
+Publication bias has been shown in peer review [@Mahoney1977; @Atkinson1982] and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results [@Franco2014; @Franco2016]; and QRPs have been admitted by scientists in several survey studies [@John2012; @Fiedler2016; @Agnoli2017].
+
+Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because because it weeds out  low-quality research that would only pollute the literature [@Winter2013; but see @vanAssen2014].
+How problematic selective publishing is in practice remains an empirical question: 
+If most negative results that are currently missing from the literature are the result of immature ideas or poorly conducted studies, we should expect that a literature in which studies are selected based on their quality but not based on their results  would contain a similar proportion of positive results as the current one.
+But how many positive results would such an unbiased literature contain in reality? 
+We set out to explore this question by comparing the rate of positive results in a sample from the current psychology literature to a set of studies that were published in a new format created to minimise QRPs and publication bias: Registered Reports.
+
+## Methods to mitigate bias
+An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection [for a historical overview, see @Wiseman2019].
+Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of p-hacking via restricted flexibility in data analysis.
+However, preregistration does not prevent file-drawering or reviewer bias and may thus be toothless in fighting publication bias. 
+A more effective safeguard against both publication bias and QRPs is promised by Registered Reports [@Chambers2013; @Nosek2014; @Chambers2015; @Jonas2016]. 
+Registered Reports (RRs) are a new publication format with a restructured submission timeline: 
+Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline to a journal. 
+The protocol undergoes peer review, and, if successful, receives "in-principle acceptance", meaning that the journal commits to publishing the final article following data collection regardless of the statistical significance of the results.
+The authors then collect and analyse the data and write up the final report. 
+The final report undergoes another round of peer review, but this time only to check if the authors adhered to the plan outlined in their protocol (and, if applicable, if the data passes pre-specified quality checks).
+RRs thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known. 
+Since its introduction at the journal Cortex in 2013, the format has rapidly gained popularity and is offered by 207 journals at the time of writing (http://cos.io/rr).
+
+In addition to bias protection, RRs promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
+Many journals offering RRs also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., $90\%$ power for a given effect size of interest).
+
+Assuming a constant alpha level, the rate of positive results in a literature is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
+The RR format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature [see e.g., @Maxwell2004; @Szucs2017].
+Therefore, if the emerging RR literature in psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in RRs (or a combination of the two).
+At this time, we have good reasons to believe in a difference in bias, but little reason to believe in a difference in the proportion of true hypotheses (at least regarding original hypotheses, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate (i.e., the proportion of supported hypotheses among all tested hypotheses).
+Considering the high standards for research quality in RRs, a large difference in positive results between RRs and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.
+
+## The current study
+The goal of our study was to test if RRs in psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as "standard reports", SRs), and to estimate the size of this potential difference.
+We set out to replicate a study by @Fanelli2010 on a new sample of standard reports in psychology and compared them to all published Registered Reports in psychology. 
+Fanelli searched for articles containing the phrase "test$^\ast$ the hypothes$^\ast$", drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
+For standard reports we used the same sampling method (restricted to the psychology discipline), and for RRs we relied on a database curated by the Center for Open Science (COS). 
+We chose Fanelli's method because Fanelli's -@Fanelli2010 and -@Fanelli2012 studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
+We additionally coded if studies were replications or original work because many published RRs are replications. 
+If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, and a higher proportion of replications among RRs than standard reports could therefore introduce a confound.
+
+In a recent commentary on benefits and challenges of open-science practices for early-career researchers, @Allen2019 conducted a similar investigation: 
+They coded the proportion of null results in the 127 biomedical and psychology RRs listed in the COS database as of September 2018. 
+We were not aware of their parallel efforts when we planned our study in September and October 2018. 
+Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in RRs (counting all hypotheses in each paper) and found $60.5\%$ unsupported hypotheses across all included RRs, $66\%$ for replication attempts, and $54.5\%$ for novel research.
+They compared these numbers to an estimate of $5-20\%$ null results in the standard literature. 
+This $5-20\%$ estimate is based on data from @Fanelli2012, who coded only the first hypothesis of each paper [identical to @Fanelli2010], and @Cristea2018], who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
+
+A major advantage of our study is that it allows us to draw a more meaningful comparison between RRs and the standard literature because we apply a previously used method [@Fanelli2010; @Fanelli2012] to both groups.
+In addition, we replicate @Fanelli2010 and provide data to evaluate his method: The search term "test$^\ast$ the hypothes$^\ast$" might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
+Therefore we also coded the phrases used to introduce hypotheses in RRs, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
+Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgments, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
+This allows others to verify (or contest) our results and provides an interesting resource for future meta-scientific research.
+
+# Methods
+After conducting a pilot to test the planned procedure we preregistered our study (https://osf.io/s8e97). 
+Methods and analyses described here were preregistered unless otherwise noted. 
+A detailed comparison of our preregistration and the eventual procedure is provided in the supplement. 
+We report how we determined our sample size, all data exclusions, and all measures in the study.
+
+## Sample
+We used the same method as @Fanelli2010 to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the RR population. 
+We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
+An overview of the sampling process and all exclusions are shown in Figure 1.
+
+For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase "test$^\ast$ the hypothes$^\ast$" and the ISSNs of all journals listed in the ESI Psychiatry/Psychology category.
+Using the same sample size as @Fanelli2010, we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed "20190120" (not specified in our preregistration, but no other seeds were tried).
+We initially excluded eight papers and replaced them (the decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had erroneously been excluded, leading to a final sample size of 152 rather than 150 (see Fig.
+1).
+
+```{r echo=FALSE, warning=FALSE, fig.cap="XXX ADD CAPTION", out.width = "\\textwidth"}
+
+knitr::include_graphics("Sampling_exclusions_and_resampling.pdf")
+```
+
+For Registered Reports we aimed to include all published RRs in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase "test$^\ast$ the hypothes$^\ast$".
+We downloaded a database of published RRs curated by the Center for Open Science[^1] (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than "Psychiatry/Psychology" or "Multidisciplinary" in the ESI.
+[^1]: https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9 
+Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 RRs published in Cortex because the ESI counts this journal towards the separate category "Neuroscience and Behavior".
+Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., Royal Society Open Science) were hand-coded by AS. 
+This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
+Following these exclusions, we verified the RR status of all remaining papers in our sample. 
+Papers were counted as RRs if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with https://cos.io/rr).
+For papers not clearly labelled as RRs we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly. 
+Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig.
+1).
+Note that we excluded all eight "Registered Replication Reports" [RRRs; @Simons2014; @Simons2018] in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing [@RRRwebsite].
+
+## Measures and coding procedure
+The main dependent variable was whether or not the first hypothesis was supported or not, as reported by the authors.
+We tried to follow Fanelli's [-@Fanelli2010] coding procedure as closely as possible, which he describes as follows:
+
+> By examining the abstract and/or full- text, it was determined whether the authors of each paper had concluded to have found a positive (full or partial) or negative (null or negative) support. 
+> If more than one hypothesis was being tested, only the first one to appear in the text was considered. 
+> We excluded meeting abstracts and papers that either did not test a hypothesis or for which we lacked sufficient information to determine the outcome. (p. 8)
+
+Like @Fanelli2010, we coded hypotheses as having received "support", "partial support", or "no support", which was recoded into a binary "support" (full or partial) vs "no support" variable for the analysis.
+Coding disagreements between full and partial support were deemed minor since they would not affect the final results, thus only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.
+
+Before preregistering our study, we conducted a pilot to assess if we could employ Fanelli's method successfully.
+Originally we had planned to first reproduce his results on the same sample of Psychiatry/Psychology articles used in @Fanelli2010. 
+Unfortunately the author refused to share the original data (or even a list of the coded articles) with us. 
+Instead, we received an excerpt which contained data for 11 records from the original sample, but no reference information of the coded articles (personal communication, 5th October 2018). 
+We were able to find these 11 articles based on the hypothesis quotes that had been coded, and used them as a pilot sample along with 10 randomly selected RRs. 
+MS and AS independently coded all 21 pilot articles with only one major disagreement in each group. 
+In the SR group, this disagreement was also the only case of major disagreement with Fanelli's original coding, which we deemed satisfying to proceed.
+
+```{r include=FALSE}
+source("interrater_agreement.R")
+```
+
+Based on our experiences during the pilot, we added one coding criterion: 
+If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first tested hypothesis rather than the first hypothesis mentioned in the text.
+In RRs we coded the first preregistered hypothesis, thus excluding unregistered pilot studies. 
+MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code ($`r sum(included$coded_by_AS & included$is_RR==1)`$ RRs $= `r printnum(sum(included$coded_by_AS & included$is_RR==1)/sum(included$is_RR==1)*100)`\%$ and $`r sum(included$coded_by_AS & included$is_RR==0)`$ SRs $= `r printnum(sum(included$coded_by_AS & included$is_RR==0)/sum(included$is_RR==0)*100)` \%$).
+Only `r support.disagreement.major` disagreements were major (Cohen's kappa = `r printp(kappa.support)`) and subsequently resolved by discussion; `r support.disagreement.minor` were minor (disagreement between "support" and "partial support").
+We preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+
+### Hypothesis introductions
+Selecting papers that use the phrase "test$^\ast$ the hypothes$^\ast$" might yield different results than alternative search phrases. 
+Getting a better overview of "natural" descriptions of hypotheses would be useful for future investigations of the generalisability of Fanelli's [-@Fanelli2010] results and could inspire new research questions.
+We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all RRs and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
+If MS and AS had coded different hypothesis quotes for a paper, MS's coding was used, unless disagreement resolution of the "hypothesis support" variable lead to AS's coding overruling MS's.
+
+### Replication status
+We also wanted to code if a study was a replication of a previously published one: 
+We expected a much larger proportion of RRs to be direct replications, many of which may have been motivated by scepticism of the original study. 
+A lower positive result rate in RRs could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias. 
+After an initial coding attempt with ill-defined coding criteria lead to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered): 
+We searched the full texts of all papers for the string "replic$^\ast$" [cf.
+@Makel2012; @Kohler2019; @Mueller-Langer2019; @Pridemore2018], and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
+Conceptual replications and internal replications were not counted as replications in this narrow sense: 
+The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
+AS coded all papers, DL double-coded `r rep.RR.coded.DL` RRs ($`r printnum(rep.RR.coded.DL/sum(included$is_RR)*100)` \%$) and `r rep.SR.coded.DL` SRs ($`r printnum(rep.RR.coded.DL/sum(included$is_RR==0)*100)` \%$).
+There were `r rep.disagreements` disagreements (Cohen's kappa = `r printp(kappa.rep)`), all were resolved by discussion.
+
+### Additional measures
+All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above. 
+All of these are documented in the Appendix and our shared dataset and codebook.
+
 ## Analysis
@@
 # Results
+```{r include=FALSE}
+source("quantitative_analyses.R")
+```
 
 ## Confirmatory Analyses
-```{r include=FALSE}
-#source("analysis.R")
-# load the dataset from RDS created with codebook
-alldata <- readRDS("positive_results_in_registered_reports_codebook.rds")
-# alldata <- readRDS("C:/Users/20176208/surfdrive/Documents/_projects/_positiveresults/_data/positive_results_in_registered_reports_codebook.rds")
-# alldata <- readRDS("~/surfdrive/Documents/_projects/_positiveresults/_data/positive_results_in_registered_reports_codebook.rds")
 
-# remove excluded papers
-included <- alldata[alldata$include_in_analysis==1,]
-
-## 3. Run main preregistered analysis: the proportion of SRs with supported
-## hypothesis compared to the proportion of RRs with supported hypothesis
-
-# number of included SRs = 152
-n.SR <- length(which(included$is_RR == 0))
-# number of included RRs = 71
-n.RR <- length(which(included$is_RR == 1))
-
-# number of SRs with support = 146
-n.support.SR <- length(which(included$is_RR == 0 & included$support_binary == 1))
-# number of RRs with support = 31
-n.support.RR <- length(which(included$is_RR == 1 & included$support_binary == 1))
-
-# Positive result rate of SRs (proportion of SRs with support) = .9605
-prop.support.SR <- n.support.SR/n.SR
-# Positive result rate of RRs (proportion of RRs with support) = .4366
-prop.support.RR <- n.support.RR/n.RR
-
-## 3.1 Proportions test to test if RRs have a *lower* positive
-## result rate than SRs (i.e., one-sided test)
-
-proptestresult <- prop.test(c(n.support.SR, n.support.RR), c(n.SR, n.RR), alternative = "greater")
-
-## 3.2 Equivalence test to test if the difference is larger than 6%
-# Equivalence bounds/smallest effect size of interest (SESOI):
-# As preregistered, we used the difference between the positive result
-# rate in Psychology and in the lowest-scoring 'soft' science in 
-# Fanelli (2010) as our SESOI. The lowest-scoring 'soft' science
-# was General Social Sciences with a positive result rate of 85.5%
-# (this number is not explicitly given in the text, so we extracted it
-# from Figure 1 using WebPlotDigitizer). The positive result rate in 
-# Psychology was 91.5%.
-# Hence our SESOI is 91.5%-85.5% = 6%:
-
-SESOI <- abs(91.5 - 85.5)/100
-
-## Run proportions test and equivalence test using the TOSTER function
-## TOSTtwo.prop:
-tostresult <- TOSTtwo.prop(prop1 = prop.support.SR, 
-                           prop2 = prop.support.RR, 
-                           n1 = n.SR, 
-                           n2 = n.RR, 
-                           low_eqbound = -SESOI, 
-                           high_eqbound = SESOI,
-                           alpha = 0.05)
-
-## Calculate confidence intervals for SR and RR PRR separately
-SR.binom <- binom.test(x = prop.support.SR*n.SR, n = n.SR)
-RR.binom <- binom.test(x = prop.support.RR*n.RR, n = n.RR)
-```
 `r n.support.SR` out of `r n.SR` SRs and `r n.support.RR` out of `r n.RR` RRs had positive results, meaning that the positive result rate was $`r printnum(prop.support.SR*100)` \%$ for SRs ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]) and $`r printnum(prop.support.RR*100)` \%$ for RRs ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]; see Fig.
 1).
-The preregistered one-sided proportions test with an alpha level of $5\%$ showed that this difference of $-`r printnum((prop.support.SR-prop.support.RR)*100)`\%$ was statistically significant, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
-Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ at $\alpha = 5\%$, $z = `r printnum(min(tostresult$TOST_z1, tostresult$TOST_z2))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
+The preregistered one-sided proportions test with an alpha level of $5\%$ showed that this difference of $-`r printnum((prop.support.SR-prop.support.RR)*100)` \%$ was statistically significant, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
+Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$ at $\alpha = 5\%$, $z = `r printnum(min(tostresult$TOST_z1, tostresult$TOST_z2))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
 We thus accept our hypothesis that the positive result rate in RRs is lower than in SRs.
@@
 Error bars indicate 95% confidence intervals around the observed positive result rate."}
-
-## 5. Create a plot for the main analysis
-
-# Create a data frame to use for plotting the main result
-mainplot.df <- data.frame(is_RR = c("SR", "SR", "RR", "RR"), 
-                          support = c("supported", "not supported", 
-                                   "supported", "not supported"),
-                          value = c(prop.support.SR*100, (1-prop.support.SR)*100, 
-                                    prop.support.RR*100, (1-prop.support.RR)*100),
-                          lower = c(min(SR.binom$conf.int)*100, NA,
-                                    min(RR.binom$conf.int)*100, NA),
-                          upper = c(max(SR.binom$conf.int)*100, NA,
-                                    max(RR.binom$conf.int)*100, NA))
-
-# Plot the main result (positive result rate in SRs vs RRs)
-ggplot(mainplot.df, aes(x = is_RR, y = value, fill = support)) +
-                  geom_bar(stat = "identity", 
-                           width = 0.5) +
-  scale_fill_manual(values= c("#bcbddc", "#756bb1"),
-                    name="first hypothesis") +
-  annotate("text", label = "n = 152", x = 1, y = 105) +
-  annotate("text", label = "n = 71", x = 2, y = 105) +
-  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.05, size = 0.5) +
-  scale_x_discrete(breaks = waiver(), 
-                   labels = c("SR" = "Standard\nReports (SRs)",
-                              "RR" = "Registered\nReports (RRs)"), name = NULL)+ 
-  scale_y_continuous(lim=c(0,110), breaks = c(seq(0, 100, 10)),
-                     minor_breaks = c(seq(0, 100, 5)),
-                     name = "% of papers", expand = c(0, 0))+
-  theme_minimal()+
-  theme(panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank(),
-        legend.margin = margin(0,0,0,-5))
+mainplot
 ```
@@
 ## Exploratory Analyses
-```{r include=FALSE}
-## 4. Run exploratory analysis: the proportion of replication 
-## studies with supported hypothesis compared to the proportion 
-## of original studies with supported hypothesis
-
-# total number of replication studies = 46
-n.rep.total <- length(which(included$is_replication == 1))
-
-# number of replication SRs = 4
-n.rep.SR <- length(which(included$is_RR == 0 & 
-                           included$is_replication == 1))
-# proportion of replications among all SRs = 2.63%
-prop.rep.SR <- n.rep.SR/n.SR
-
-# number of replication RRs = 42
-n.rep.RR <- length(which(included$is_RR == 1 & 
-                           included$is_replication == 1))
-# proportion of replications among all RRs = 59.15%
-prop.rep.RR <- n.rep.RR/n.RR
-
-# Positive result rate of *replication* SRs = 1
-prop.rep.support.SR <- length(which(included$is_RR == 0 & 
-                                    included$support_binary == 1 &
-                                    included$is_replication == 1))/n.rep.SR
-# Positive result rate of *original* SRs = .9595
-prop.orig.support.SR <- length(which(included$is_RR == 0 & 
-                                     included$support_binary == 1 &
-                                     included$is_replication == 0))/(n.SR - n.rep.SR)
-
-# Positive result rate of *replication* RRs = .4048
-prop.rep.support.RR <- length(which(included$is_RR == 1 & 
-                                    included$support_binary == 1 &
-                                    included$is_replication == 1))/n.rep.RR
-# Positive result rate of *original* RRs = .4828
-prop.orig.support.RR <- length(which(included$is_RR == 1 & 
-                                     included$support_binary == 1 &
-                                     included$is_replication == 0))/(n.RR - n.rep.RR)
-
-## Calculate confidence intervals for original vs 
-## replication SRs and RRs
-SR.orig.binom <- binom.test(x = prop.orig.support.SR*(n.SR-n.rep.SR), n = n.SR-n.rep.SR)
-SR.rep.binom <- binom.test(x = prop.rep.support.SR*n.rep.SR, n = n.rep.SR)
-RR.orig.binom <- binom.test(x = prop.orig.support.RR*(n.RR-n.rep.RR), n = n.RR-n.rep.RR)
-RR.rep.binom <- binom.test(x = prop.rep.support.RR*n.rep.RR, n = n.rep.RR)
-
-## 4.1 Proportions test to test if *original* RRs still have a lower 
-## positive result rate than *original* SRs (i.e., one-sided test)
-repproptest <- prop.test(c(prop.orig.support.SR*(n.SR-n.rep.SR), 
-                           prop.orig.support.RR*(n.RR-n.rep.RR)), 
-                         c(n.SR-n.rep.SR, n.RR-n.rep.RR), alternative = "greater")
-
-## 4.2 Equivalence test to test if the difference is larger than 6%
-# Equivalence bounds/smallest effect size of interest (SESOI):
-# same as for main hypothesis test (6%)
-
-SESOI <- abs(91.5 - 85.5)/100
-
-## Run proportions test and equivalence test using the TOSTER function
-## TOSTtwo.prop:
-reptost <- TOSTtwo.prop(prop1 = prop.orig.support.SR, 
-                        prop2 = prop.orig.support.RR, 
-                        n1 = n.SR-n.rep.SR, 
-                        n2 = n.RR-n.rep.RR, 
-                        low_eqbound = -SESOI, 
-                        high_eqbound = SESOI,
-                        alpha = 0.05)
-
-## 4.3 Create a table showing the positive result rate for replications vs
-## original studies in RRs vs SRs
-rep.table <- data.frame(group = c("SRs", "RRs"),
-                        n.original = c(n.SR-n.rep.SR, n.RR-n.rep.RR),
-                        pos.original = c(prop.orig.support.SR*(n.SR-n.rep.SR), 
-                                         prop.orig.support.RR*(n.RR-n.rep.RR)),
-                        percent.pos.original = c(prop.orig.support.SR*100,
-                                                 prop.orig.support.RR*100), 
-                        CI.original = c(paste(printnum(min(SR.orig.binom$conf.int)*100),
-                                              printnum(max(SR.orig.binom$conf.int)*100), 
-                                              sep = "; "),
-                                        paste(printnum(min(RR.orig.binom$conf.int)*100),
-                                              printnum(max(RR.orig.binom$conf.int)*100), 
-                                              sep = "; ")),
-                        n.rep = c(n.rep.SR, n.rep.RR),
-                        pos.rep = c(prop.rep.support.SR*n.rep.SR, prop.rep.support.RR*n.rep.RR),
-                        percent.pos.rep = c(prop.rep.support.SR*100, prop.rep.support.RR*100), 
-                        CI.rep = c(paste(printnum(min(SR.rep.binom$conf.int)*100),
-                                         printnum(max(SR.rep.binom$conf.int)*100), sep = "; "),
-                                   paste(printnum(min(RR.rep.binom$conf.int)*100),
-                                         printnum(max(RR.rep.binom$conf.int)*100), sep = "; ")))
-
-```
-As expected, direct replications were much more common among RRs than SRs: `r n.rep.RR` out of `r n.RR` RRs ($`r printnum(prop.rep.RR*100)`\%$), but only `r n.rep.SR` out of `r n.SR` SRs ($`r printnum(prop.rep.SR*100)`\%$) were classified as direct replications of previously published work.
+As described in the Method section, we only classified close or direct replications of previously published work as replications. 
+This means that our non-replication category also contains some conceptual replications and "internal" replications (where original and replication are published in the same paper). 
+For ease of communication we will nonetheless refer to this category as "original" studies.
+As expected, direct replications were much more common among Registered Reports than standard reports: `r n.rep.RR` out of `r n.RR` RRs ($`r printnum(prop.rep.RR*100)`\%$), but only `r n.rep.SR` out of `r n.SR` SRs ($`r printnum(prop.rep.SR*100)`\%$) were classified as direct replications of previously published work.
 However, this difference cannot account for the stark overall difference between SRs and RRs described above: 
@@
 
-```{r include=FALSE}
-## 5. Run exploratory analysis: compare SRs to Fanelli (2010)
-
-# Number of Psychology papers in Fanelli (2010, from Fig. 1)
-n.Fanelli <- 141
-# Fanelli (2010) reports the positive result rate for Psychiatry&Psychology as
-# 91.5% (p. 3). This is likely a rounded number since 141*0.915 = 129.015. For
-# a more precise analysis, we assume that 129 out of 141 papers in Fanelli's 
-# sample had positive results, giving a positive result rate of 129/141 = 0.9148936.
-# In the following, we'll use this more precise number (129/141) in place of the
-# 91.5% reported in the paper.
-prop.support.Fanelli <- 129/141
-
-## 5.1 Proportions test to test if the positive result rate of Psychology
-## papers in Fanelli (2010) is different from SRs in our study
-
-Fanelliproptest <- prop.test(c(prop.support.Fanelli*n.Fanelli,
-                               prop.support.SR*n.SR),
-                             c(n.Fanelli, n.SR), alternative = "two.sided")
-
-## 5.2 Equivalence test to test if the difference is larger than +/-6%
-# Equivalence bounds/smallest effect size of interest (SESOI):
-# same as for main hypothesis test (6%)
-
-SESOI <- abs(91.5 - 85.5)/100
-
-## Run proportions test and equivalence test using the TOSTER function
-## TOSTtwo.prop:
-Fanellitost <- TOSTtwo.prop(prop1 = prop.support.Fanelli, 
-                            prop2 = prop.support.SR, 
-                            n1 = n.Fanelli, 
-                            n2 = n.SR, 
-                            low_eqbound = -SESOI, 
-                            high_eqbound = SESOI,
-                            alpha = 0.05)
-```
 Since our SR sample represents a direct replication of @Fanelli2010 for the discipline Psychiatry & Psychology, another interesting question to ask is how our results compare to Fanelli's.
@@
 ```{r include=FALSE}
-## 6. Analyse the phrases used to introduce hypotheses in RRs
-
-## 6.1 Check how many RRs would have been discovered with the search
-## phrase "test* the hypothes*"
-
-# Create a new variable that indicates if the *title* contains 
-# the phrase "test* the hypothes*" (TRUE vs FALSE)
-included$searchphrase.in.title <- sapply(included$title, grepl, 
-                                         pattern = "test\\w* the hypothes")
-# Create a new variable that indicates if the *keywords* contain 
-# the phrase "test* the hypothes*" (TRUE vs FALSE)
-included$searchphrase.in.keywords <- sapply(included$keywords, grepl, 
-                                            pattern = "test\\w* the hypothes")
-# Create a new variable that indicates if the *abstract* contains 
-# the phrase "test* the hypothes*" (TRUE vs FALSE)
-included$searchphrase.in.abstract <- sapply(included$abstract, grepl, 
-                                            pattern = "test\\w* the hypothes")
-
-# Calculate the number of RRs that contain the search phrase in their abstract,
-# title, or keywords: 2 RRs
-testthehypothes.RR <- length(which(included$is_RR == 1 & 
-                                     (included$searchphrase.in.abstract == TRUE |
-                                        included$searchphrase.in.keywords == TRUE |
-                                        included$searchphrase.in.title == TRUE)))
+source("hypothesis_introduction_analyses.R")
 ```
-
-```{r include=FALSE}
-## 6.2 Analyse the introduction phrases and create clusters of five "core words"
-hypintros <- included[which(included$is_RR==1), c("id",
-                                                  "support_binary",
-                                                  "is_replication",
-                                                  "hyp_from_fulltext",
-                                                  "RR_hyp_intro_abstract", 
-                                                  "RR_hyp_intro_fulltext")]
-
-hypintros <- as.data.frame(hypintros)
-
-hypintros$abstract.count <- ifelse(is.na(str_count(hypintros$RR_hyp_intro_abstract, ";")), 0, 
-                                   str_count(hypintros$RR_hyp_intro_abstract, ";") + 1)
-hypintros$fulltext.count <- ifelse(is.na(str_count(hypintros$RR_hyp_intro_fulltext, ";")), 0, 
-                                   str_count(hypintros$RR_hyp_intro_fulltext, ";") + 1)
-
-hypintros$introabstract.1 <- sapply(strsplit(hypintros$RR_hyp_intro_abstract, "; "), "[", 1)
-hypintros$introabstract.2 <- sapply(strsplit(hypintros$RR_hyp_intro_abstract, "; "), "[", 2)
-hypintros$introfulltext.1 <- sapply(strsplit(hypintros$RR_hyp_intro_fulltext, "; "), "[", 1)
-hypintros$introfulltext.2 <- sapply(strsplit(hypintros$RR_hyp_intro_fulltext, "; "), "[", 2)
-hypintros$introfulltext.3 <- sapply(strsplit(hypintros$RR_hyp_intro_fulltext, "; "), "[", 3)
-
-# Determine how many replication RRs have more than 1 hypothesis introduction phrase: 10
-length(which((hypintros$abstract.count+hypintros$fulltext.count)>1 & hypintros$is_replication==1))
-
-# Determine how many original RRs have more than 1 hypothesis introduction phrase: 11
-length(which((hypintros$abstract.count+hypintros$fulltext.count)>1 & hypintros$is_replication==0))
-
-intros.long <- melt(hypintros, 
-                    id.vars = c("id", "is_replication", "hyp_from_fulltext", 
-                                "abstract.count", "fulltext.count"), 
-                    measure.vars = c("introabstract.1", "introabstract.2", 
-                                     "introfulltext.1", "introfulltext.2", "introfulltext.3"),
-                    variable.name = "origin", value.name = "phrase", na.rm = TRUE)
-
-intros.long$origin <- ifelse(sapply(intros.long$origin, grepl, pattern = "abstract"), "abstract", "fulltext")
-
-# clean up: some phrases had "\n" at the end, remove that
-intros.long$phrase <- sapply(strsplit(intros.long$phrase, "\n"), "[", 1)
-
-intros.long$test <- sapply(intros.long$phrase, grepl, pattern = "test")
-intros.long$hypothes <- sapply(intros.long$phrase, grepl, pattern = "hypothes", ignore.case = TRUE)
-intros.long$replicat <- sapply(intros.long$phrase, grepl, pattern = "replicat")
-intros.long$predict <- sapply(intros.long$phrase, grepl, pattern = "predict")
-intros.long$examin <- sapply(intros.long$phrase, grepl, pattern = "examin")
-
-uniquephrases <- unique(intros.long$phrase)
-uniquewords <- unique(unlist(sapply(strsplit(uniquephrases, " "), unique)))
-uniquewords <- uniquewords[order(uniquewords)]
-
-wordstems.cleaned <- c("according", "aim", "assume", "attempt", 
-                       "conduct", "critically", "establish", "examine", 
-                       "expect", "experiment", "H1", "hypothes", 
-                       "if",  "investigate", "performed", "predication", 
-                       "predict", "present", "registered", "replicat", 
-                       "report", "reproduce", "sought", "suggests", 
-                       "test", "then")
-
-wordoccurrences.df <- data.frame(word = wordstems.cleaned, count = NA)
-for (i in 1:length(wordstems.cleaned)) {
-  wordoccurrences.df$count[i] <- sum(sapply(grepl(wordstems.cleaned[i], 
-                                            intros.long$phrase, 
-                                            ignore.case = TRUE), sum))
-}
-wordoccurrences.df <- wordoccurrences.df[order(-wordoccurrences.df$count),]
-
-# number of times "test*" and "hypothes*" co-occur
-test.and.hypothes <- sum(grepl("test", intros.long$phrase) & grepl("hypothes", 
-                                                intros.long$phrase,
-                                                ignore.case = TRUE))
-
-# number of hyp intros that contain either "test*" OR "hypothes*"
-test.or.hypothes <- sum(grepl("test", intros.long$phrase) | grepl("hypothes", 
-                                              intros.long$phrase,
-                                              ignore.case = TRUE))
-
-## HERE COME THE TABLES OF DEATH -- EXPAND AT YOUR OWN RISK ##
-#######################################################################################
-### MAKE TABLE FOR ORIGINAL HYPOTHESIS INTROS ###
-### Original hypothesis intros have 7 categories:
-# 1: hypothes*, test*
-# 2: hypothes*
-# 3: test*, predict*
-# 4: test*
-# 5: predict*
-# 6: examin*
-# 7: (other)
-
-##*****************************************#
-## PART 1: hypothes*, test*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
-                                                intros.long$hypothes == TRUE &
-                                                intros.long$test == TRUE &
-                                                intros.long$replicat == FALSE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == FALSE)])
-
-auxrow <- c("hypothes*, test*", "", 
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "abstract" &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == TRUE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "fulltext" &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == TRUE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == TRUE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)))
-
-auxtable <- data.frame(core = rep(NA, length(phraselist)), phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                    & intros.long$origin == "abstract"
-                                    & intros.long$is_replication == 0))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                    & intros.long$origin == "fulltext"
-                                    & intros.long$is_replication == 0))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 0))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
- }
-
-phrasetable.orig <- rbind(auxrow, auxtable)
-
-##*****************************************#
-## PART 2: hypothes*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
-                                                intros.long$hypothes == TRUE &
-                                                intros.long$test == FALSE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == FALSE)])
-auxrow <- c("hypothes*", "", 
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "abstract" &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "fulltext" &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)))
-
-auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 0))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-phrasetable.orig <- rbind(phrasetable.orig, auxrow, auxtable)
-
-##*****************************************#
-## PART 3: test*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
-                                                intros.long$hypothes == FALSE &
-                                                intros.long$test == TRUE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == FALSE)])
-auxrow <- c("test*", "", 
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "abstract" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == TRUE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "fulltext" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == TRUE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == TRUE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)))
-
-auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 0))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-phrasetable.orig <- rbind(phrasetable.orig, auxrow, auxtable)
-
-##*****************************************#
-## PART 4: test*, predict*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
-                                                intros.long$hypothes == FALSE &
-                                                intros.long$test == TRUE &
-                                                intros.long$predict == TRUE &
-                                                intros.long$examin == FALSE)])
-
-auxtable <- data.frame(core = "test*, predict*", phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 0))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-phrasetable.orig <- rbind(phrasetable.orig, auxtable)
-
-##*****************************************#
-## PART 5: predict*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
-                                                intros.long$hypothes == FALSE &
-                                                intros.long$test == FALSE &
-                                                intros.long$predict == TRUE &
-                                                intros.long$examin == FALSE)])
-auxrow <- c("predict*", "", 
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "abstract" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == TRUE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "fulltext" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == TRUE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == TRUE &
-                           intros.long$examin == FALSE)))
-
-auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 0))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-phrasetable.orig <- rbind(phrasetable.orig, auxrow, auxtable)
-
-##*****************************************#
-## PART 6: examin*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
-                                                intros.long$hypothes == FALSE &
-                                                intros.long$test == FALSE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == TRUE)])
-auxrow <- c("examin*", "", 
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "abstract" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == TRUE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "fulltext" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == TRUE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == TRUE)))
-
-auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 0))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-phrasetable.orig <- rbind(phrasetable.orig, auxrow, auxtable)
-
-##*****************************************#
-## PART 7: (other)
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 0 &
-                                                intros.long$hypothes == FALSE &
-                                                intros.long$test == FALSE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == FALSE)])
-auxrow <- c("(other)", "", 
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "abstract" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$origin == "fulltext" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 0 &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)))
-
-auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 0))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 0))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-phrasetable.orig <- rbind(phrasetable.orig, auxrow, auxtable)
-
-phrasetable.orig$core[which(is.na(phrasetable.orig$core))] <- ""
-## THAT'S IT THE TABLE WITH ORIGINAL HYP INTROS IS DONE, SORRY FOR THE UGLY CODE ##
-
-#######################################################################################
-### MAKE TABLE FOR *REPLICATION* HYPOTHESIS INTROS ###
-### Replication hypothesis intros have 10 categories:
-# 1: hypothes*, test*
-# 2: hypothes*, predict*
-# 3: hypothes*, examin*
-# 4: hypothes*
-# 5: test*
-# 6: replicat*
-# 7: replicat*, examine*
-# 8: predict*
-# 9: examin*
-#10: (other)
-
-##*****************************************#
-## PART 1: hypothes*, test*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
-                                                intros.long$hypothes == TRUE &
-                                                intros.long$test == TRUE &
-                                                intros.long$replicat == FALSE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == FALSE)])
-
-auxrow <- c("hypothes*, test*", "", 
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$origin == "abstract" &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == TRUE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$origin == "fulltext" &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == TRUE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == TRUE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)))
-
-auxtable <- data.frame(core = rep(NA, length(phraselist)), phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 1))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-
-phrasetable.rep <- rbind(auxrow, auxtable)
-
-##*****************************************#
-## PART 2: hypothes*, predict*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
-                                                intros.long$hypothes == TRUE &
-                                                intros.long$test == FALSE &
-                                                intros.long$replicat == FALSE &
-                                                intros.long$predict == TRUE &
-                                                intros.long$examin == FALSE)])
-
-auxtable <- data.frame(core = "hypothes*, predict*", phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 1))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-
-phrasetable.rep <- rbind(phrasetable.rep, auxtable)
-
-##*****************************************#
-## PART 3: hypothes*, examin*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
-                                                intros.long$hypothes == TRUE &
-                                                intros.long$test == FALSE &
-                                                intros.long$replicat == FALSE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == TRUE)])
-
-auxtable <- data.frame(core = "hypothes*, examin*", phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 1))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-
-phrasetable.rep <- rbind(phrasetable.rep, auxtable)
-
-##*****************************************#
-## PART 4: hypothes*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
-                                                intros.long$hypothes == TRUE &
-                                                intros.long$test == FALSE &
-                                                intros.long$replicat == FALSE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == FALSE)])
-
-auxrow <- c("hypothes*", "", 
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$origin == "abstract" &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == FALSE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$origin == "fulltext" &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == FALSE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$hypothes == TRUE &
-                           intros.long$test == FALSE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)))
-
-auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 1))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-
-phrasetable.rep <- rbind(phrasetable.rep, auxrow, auxtable)
-
-##*****************************************#
-## PART 5: test*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
-                                                intros.long$hypothes == FALSE &
-                                                intros.long$test == TRUE &
-                                                intros.long$replicat == FALSE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == FALSE)])
-
-auxrow <- c("test*", "", 
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$origin == "abstract" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == TRUE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$origin == "fulltext" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == TRUE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == TRUE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)))
-
-auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 1))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-
-phrasetable.rep <- rbind(phrasetable.rep, auxrow, auxtable)
-
-##*****************************************#
-## PART 6: replicat*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
-                                                intros.long$hypothes == FALSE &
-                                                intros.long$test == FALSE &
-                                                intros.long$replicat == TRUE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == FALSE)])
-
-auxrow <- c("replicat*", "", 
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$origin == "abstract" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$replicat == TRUE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$origin == "fulltext" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$replicat == TRUE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$replicat == TRUE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)))
-
-auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 1))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-
-phrasetable.rep <- rbind(phrasetable.rep, auxrow, auxtable)
-
-##*****************************************#
-## PART 7: replicat*, examine*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
-                                                intros.long$hypothes == FALSE &
-                                                intros.long$test == FALSE &
-                                                intros.long$replicat == TRUE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == TRUE)])
-
-auxtable <- data.frame(core = "replicat*, examin*", phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 1))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-
-phrasetable.rep <- rbind(phrasetable.rep, auxtable)
-
-##*****************************************#
-## PART 8: predict*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
-                                                intros.long$hypothes == FALSE &
-                                                intros.long$test == FALSE &
-                                                intros.long$replicat == FALSE &
-                                                intros.long$predict == TRUE &
-                                                intros.long$examin == FALSE)])
-
-auxtable <- data.frame(core = "predict*", phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 1))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-
-phrasetable.rep <- rbind(phrasetable.rep, auxtable)
-
-##*****************************************#
-## PART 9: examin*
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
-                                                intros.long$hypothes == FALSE &
-                                                intros.long$test == FALSE &
-                                                intros.long$replicat == FALSE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == TRUE)])
-
-auxtable <- data.frame(core = "examin*", phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 1))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-
-phrasetable.rep <- rbind(phrasetable.rep, auxtable)
-
-##*****************************************#
-## PART 10: (other)
-##*****************************************#
-phraselist <- unique(intros.long$phrase[which(intros.long$is_replication == 1 &
-                                                intros.long$hypothes == FALSE &
-                                                intros.long$test == FALSE &
-                                                intros.long$replicat == FALSE &
-                                                intros.long$predict == FALSE &
-                                                intros.long$examin == FALSE)])
-
-auxrow <- c("(other)", "", 
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$origin == "abstract" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$origin == "fulltext" &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)),
-            length(which(intros.long$is_replication == 1 &
-                           intros.long$hypothes == FALSE &
-                           intros.long$test == FALSE &
-                           intros.long$replicat == FALSE &
-                           intros.long$predict == FALSE &
-                           intros.long$examin == FALSE)))
-
-auxtable <- data.frame(core = rep("", length(phraselist)), phrase = NA, 
-                       count.abstract = NA, count.fulltext = NA, count.total = NA)
-
-for (i in 1:length(phraselist)) {
-  auxtable$phrase[i] <- phraselist[i]
-  auxtable$count.abstract[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "abstract"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.fulltext[i] <- length(which(intros.long$phrase == phraselist[i]
-                                             & intros.long$origin == "fulltext"
-                                             & intros.long$is_replication == 1))
-  auxtable$count.total[i] <- length(which(intros.long$phrase == phraselist[i]
-                                          & intros.long$is_replication == 1))
-
-  auxtable <- auxtable[order(auxtable$phrase),]
-}
-phrasetable.rep <- rbind(phrasetable.rep, auxrow, auxtable)
-
-phrasetable.rep$core[which(is.na(phrasetable.rep$core))] <- ""
-## THAT'S IT FOR REPLICATION HYP INTROS, I'M REALLY SO SORRY!  ##
-###################################################################################
-```
-Finally, we analysed the language that was used to introduce or signal hypotheses in RRs.
-Does Fanelli's search phrase "test$^\ast$ the hypothes$^\ast$" capture hypothesis-testing RRs reasonably well? 
+Finally, we analysed the language that was used to introduce or refer to hypotheses in RRs.
+We were interested in whether the search phrase "test$^\ast$ the hypothes$^\ast$" used by Fanelli captured the way researchers write about hypothesis tests reasonably well.
 The answer is a resounding "no":
 Searching the abstracts, titles, and keywords of the RR sample showed that only `r testthehypothes.RR`/`r n.RR` RRs would have been detected with this search phrase. 
-Which analogous hypothesis-introduction phrases are used in RRs, and can they be summarised in a convenient way? 
-To get an overview, we stripped the hypothesis quotes of RRs from all content-specific information and extracted "minimal" phrases that most distinctively indicated that a hypothesis was being described.
+To get an overview of analogous hypothesis-introduction phrases researchers used in RRs, we stripped the hypothesis quotes of RRs from all content-specific information and extracted "minimal" phrases that most distinctively indicated that a hypothesis was being described.
 For example, from the hypothesis quote "(f)or Study 1, we predicted that participants reading about academic (vs.
@@
 In this total set of `r nrow(intros.long)` hypothesis introductions, we found `r length(uniquephrases)` unique phrases, showing substantial linguistic variation (see Tables 2 and 3).
-In order to condense the information further, we listed all unique word stems (e.g., the word stem "hypothes$^\ast$" captures the words "hypothesis", "hypotheses", "hypothesize", "hypothesized", and so on) and analysed their frequency among all hypothesis introductions.
+In order to condense the information, we listed all unique word stems (e.g., the word stem "hypothes$^\ast$" captures the words "hypothesis", "hypotheses", "hypothesize", "hypothesized", and so on) and analysed their frequency among all hypothesis introductions.
 Excluding words that are common but too unspecific by themselves, such as "that", "to", or "whether", the five most frequent word stems were "hypothes$^\ast$" (`r wordoccurrences.df[1,2]` occurrences), "replicat$^\ast$" (`r wordoccurrences.df[2,2]`), "test$^\ast$" (`r wordoccurrences.df[3,2]`), "examine$^\ast$" (`r wordoccurrences.df[4,2]`), and "predict$^\ast$" (`r wordoccurrences.df[5,2]`).
@@
 
-We noticed that direct replication RRs generally tended to use different language to describe their hypothesis (or rather their goal).
+We noticed that direct replication RRs generally tended to use different language to describe their hypothesis.
 As the high frequency of the word stem "replicat$^\ast$" suggests, these studies were often not framed as new tests of a previously tested hypothesis, but as attempts to replicate a previously documented effect or to repeat a previously conducted experiment.
+Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
 Tables 2 and 3 list all unique hypothesis introductions and their frequency for original RRs and direct replication RRs, respectively, grouped by the five most frequent word stems ("hypothes$^\ast$", "replicat$^\ast$", "test$^\ast$", "examine$^\ast$", "predict$^\ast$").
@@
 
+It is important to keep in mind that not all hypotheses could be coded from the abstract: For `r n.hypintro.fulltext.only` RRs, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
+Therefore we additionally tested how many of the RRs would have been detected in a regular search using our five most frequent word stems. 
+We searched their titles, abstracts, and keywords for "hypothes$^\ast$" OR "replicat$^\ast$" OR "test$^\ast$" OR "examine$^\ast$" OR "predict$^\ast$" and found that $`r n.hypintros.fivewords.RR`/`r n.RR`$ RRs ($`r printnum(n.hypintros.fivewords.RR/n.RR*100)` \%$) would have been detected this way.
+We do not know how well these search terms represent the population of hypothesis-testing studies in psychology, but a structured investigation of this question would be very useful for future meta-research.
+
 # Discussion
-```{r echo=FALSE, warning=FALSE, fig.width=6, fig.height=3, fig.cap=" "}
-# Inferring the likely proportion of true hypotheses studied in the literature
-# and statistical power based on the observed proportion of significant results
+We examined the proportion of psychology articles that find support for their first tested hypothesis and found a large difference ($`r printnum(prop.support.SR*100)` \%$ vs $`r printnum(prop.support.RR*100)` \%$) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
+More than half of the analysed RRs tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis ($`r printnum(prop.orig.support.SR*100)` \%$ vs $`r printnum(prop.orig.support.RR*100)` \%$).
+The introduction of Registered Reports has clearly led to a much larger proportion of null results appearing in the published literature compared to standard reports.
 
-# t = proportion of true hypotheses
-# a = alpha
-# b = beta; i.e. 1-b = power
-# PRR = positive result rate (proportion of significant results in the literature)
-truehyps <- function(PRR, a, pwr){-(PRR - a)/((1-pwr) + a - 1)}
-pwrfun <- function(t, a, PRR){(a*t+PRR-a)/(t)}
+The positive result rate we found in standard reports ($`r printnum(prop.support.SR*100)` \%$) is slightly higher than the $91.5\%$ reported by @Fanelli2010, although this difference was not statistically significant.
+Our replication in a more recent sample of the psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 [cf.
+@Fanelli2012].
+Furthermore, our estimate of the positive result rate for Registered Reports ($`r printnum(prop.support.RR*100)` \%$) is comparable to the $39.5\%$ reported by @Allen2019, despite some differences in method and studied population.
 
-a <- 0.05
+To explain the $`r printnum((prop.support.SR - prop.support.RR)*100)` \%$ gap between standard reports and Registered Reports, we must assume some combination of differences in bias, statistical power, or the proportion of true hypotheses researchers choose to examine.
+Figure 3 visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased. 
+For example, if we assume no publication bias and no QRPs, more than $90\%$ of the hypotheses authors of standard reports study must be true and study designs must have more than $90\%$ power for the true effect size.
+This is highly unlikely, meaning that the standard literature is unlikely to reflect reality. 
+As we noted above, there is good reason to assume that methodological rigour and statistical power in Registered Reports are as high, or higher, than in standard reports, leaving the rate of true hypotheses and bias as remaining explanations.
 
-### 3 groups: original SRs, original RRs, all RRs
+```{r echo=FALSE, warning=FALSE, fig.width=6, fig.height=3, fig.cap="XXX ADD CAPTION"}
+source("power_baserate_plot.R")
+power.baserate.plot
+```
 
-pwrprior.df <-  data.frame(t=c(1:1000)/1000)
-pwrprior.df$group <- "all RRs (PRR = .4366, N = 71)"
-pwrprior.df$lower <- pwrfun(t = pwrprior.df$t, a = a, PRR = min(RR.binom$conf.int))
-pwrprior.df$estimate <- pwrfun(t = pwrprior.df$t, a = a, PRR = prop.support.RR)
-pwrprior.df$upper <- pwrfun(t = pwrprior.df$t, a = a, PRR = max(RR.binom$conf.int))
+It is a-priori plausible that Registered Reports are currently used for a population of hypotheses that are less likely to be true: 
+For example, authors may use the format strategically for studies they expect to yield negative results (which would be difficult to publish otherwise). 
+However, assuming over $90\%$ true hypotheses in the standard literature is neither realistic, nor would it be desirable for a science that wants to advance knowledge beyond trivial facts. 
+We thus believe that this factor alone is not sufficient to explain the gap between the positive result rates in Registered Reports and standard reports. 
+Rather, the numbers strongly suggest a reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
 
-pwrprior.origRR <- data.frame(t=c(1:1000)/1000)
-pwrprior.origRR$group <- "original RRs (PRR = .5, n = 30)"
-pwrprior.origRR$lower <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = min(RR.orig.binom$conf.int))
-pwrprior.origRR$estimate <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = prop.orig.support.RR)
-pwrprior.origRR$upper <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = max(RR.orig.binom$conf.int))
+## Limitations
+We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports. 
+Because neither hypotheses, authors, nor editors are randomly assigned to each publication format we cannot draw firm conclusions about the causes that lead to a difference in the proportion of supported hypotheses.
+Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
+As mentioned above, it is a-priori plausible that the Registered Reports format is used selectively for particularly risky hypotheses. 
+This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in psychology. 
+It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias. 
+Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use. 
+This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
 
-pwrprior.origSR <- data.frame(t=c(1:1000)/1000)
-pwrprior.origSR$group <- "original SRs (PRR = .9595, n = 148)"
-pwrprior.origSR$lower <- pwrfun(t = pwrprior.origSR$t, a = a, PRR = min(SR.orig.binom$conf.int))
-pwrprior.origSR$estimate <- pwrfun(t = pwrprior.origSR$t, a = a, PRR = prop.orig.support.SR)
-pwrprior.origSR$upper <- pwrfun(t = pwrprior.origSR$t, a = a, PRR = max(SR.orig.binom$conf.int))
+A second limitation of the current study [and of @Fanelli2010] is that standard reports were selected using the search term "test$^\ast$ the hypothes$^\ast$". 
+As our results show, this phrase was virtually absent in the Registered Report population. 
+The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for "test$^\ast$ the hypothes$^\ast$" will miss most of the hypothesis-testing studies in the psychological literature.
+Results based on this search phrase may not generalise to all published studies. 
+For example, it is possible that authors are more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., "we examined the role of ...").
+If this were true, using other strategies to select standard reports might yield lower estimates for the positive result rate. 
+However, this does not seem to be the case: 
+Studies using different selection criteria for articles and hypotheses have found very similar rates of supported hypotheses. 
+For example, the positive result rates in @Sterling1959, @Sterling1995, and the original studies included in the Reproducibility Project: Psychology [@OSC2015] were $97.28\%$, $95.56\%$, and $97\%$, respectively.
+@Motyl2017 report $89.17\%$ and $92.01\%$ significant results for "critical" hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively. 
+Therefore, although the search term used to find standard reports might limit the generalisability of our results, this search strategy seems to yield comparable estimates as the selection strategies used in different studies.
 
-pwrprior.df <- rbind(pwrprior.df, pwrprior.origRR, pwrprior.origSR)
+A final limitation is the decision to code only the first reported hypothesis. 
+The first hypothesis test may not be representative for all hypothesis tests reported in a paper, and the order of reporting may differ between standard reports and Registered Reports. 
+Perhaps Registered Report authors are more likely to present their hypotheses in "chronological" order, whereas standard report authors tend to rearrange the order in which hypotheses are reported based on their outcomes, and present supported hypotheses first.
+Here again, the converging estimates from the four studies cited above (none of which use the first-hypothesis rule) make it seem unlikely that our result is an artefact of this decision. 
+Regardless of which hypothesis one chooses to analyse across a set of papers -- the first, the last, or the "critical" one -- the positive result rate turns out to be higher than what can be expected based on realistic estimates of the proportion of true hypotheses researchers study and the statistical power of their tests.
 
-pwrprior.df$lower[pwrprior.df$lower > 1 & pwrprior.df$upper > 1] <- NA
-pwrprior.df$lower[pwrprior.df$lower > 1] <- 1
-pwrprior.df$upper[pwrprior.df$upper > 1] <- 1
-
-pwrprior.df$group <- factor(pwrprior.df$group, 
-                            levels = c("original SRs (PRR = .9595, n = 148)",
-                                       "original RRs (PRR = .5, n = 30)", 
-                                       "all RRs (PRR = .4366, N = 71)"))
-
-ggplot(pwrprior.df, aes(x = t, y = estimate, colour = group, fill = group,
-                        linetype = group)) +
-  geom_line(aes(y = estimate), size = 1) + 
-  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .42, linetype = "blank") +
-  scale_x_continuous(name="proportion of true hypotheses", 
-                     limits=c(0.25, 1), 
-                     breaks = c(seq(0.3, 1, 0.1)),
-                     expand = c(0, 0)) +
-  scale_y_continuous(name="statistical power", 
-                     limits=c(0.25, 1), 
-                     breaks = c(seq(0.3, 1, 0.1)),
-                     expand = c(0, 0)) +
-  scale_colour_manual(values = c("#0073C0", "#ED443F", "#2D132C"), name = NULL) +
-  scale_fill_manual(values = c("#0073C0", "#ED443F", "#2D132C"), name = NULL) +
-  scale_linetype_manual(values = c("solid", "dashed", "dotted"), name = NULL) +
-  theme_bw()
-```
+## Conclusion
+Our study presents a systematic comparison of positive results in Registered Reports and the standard literature. 
+The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the published research we are used to. 
+Standard publication formats seem to lead scientists to miss out on many high-quality studies with negative results, which are available in the Registered Reports literature. 
+The absence of negative results is a serious threat to a cumulative science. 
+Reliable protection against questionable research practices and publication bias is crucial to ensure the integrity of the literature. 
+The Registered Reports format is a promising candidate for bias protection, but we are only at the beginning of understanding its effectiveness and robustness in different contexts and scientific disciplines.
 

### 2020-01-07 manuscript.tex
no actual edits to anything, just file changes caused by me linking the repository to a second machine with a different system
imported all text into the Rmd file, fixed all punctuation issues, soft-coded all numbers, and changed the code integration to calling separate scripts instead of doing everything inside the Rmd file

@@
-\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
 \PassOptionsToPackage{hyphens}{url}
 %
-\documentclass[british,,man,floatsintext]{apa6}
+\documentclass[
+  british,
+  ,man,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provides euro and other symbols
-\else % if luatex or xelatex
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
   \usepackage{unicode-math}
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
 }{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
   \IfFileExists{parskip.sty}{%
@@
     \setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\usepackage{hyperref}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
@@
   pdfauthor={Anne Scheel, Mitchell Schijen, \& Daniël Lakens},
+  pdflang={en-UK},
   pdfkeywords={keyword 1, keyword 2, keyword 3},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \shorttitle{Positive Results in Registered Reports}
@@
 \floatname{textbox}{Box}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[shorthands=off,main=british]{babel}
-\else
-  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
   \usepackage{polyglossia}
   \setmainlanguage[variant=british]{english}
+\else
+  \usepackage[shorthands=off,main=british]{babel}
 \fi
@@
 \maketitle
+
+If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world.
+When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability.
+However, when published findings are systematically biased, cumulative science breaks down:
+Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
+Unfortunately there are good reasons to believe that the psychology literature is not a faithful representation of all research psychologists conduct.
+For more than half a century, scientists have repeatedly noticed a suspiciously high \enquote{success} rate in psychology:
+Studying 362 empirical articles published in four psychology journals in 1955/56, Sterling (1959) found that a whopping \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
+A replication of this study performed on articles published in 1986/87 reported \(95.56\%\) statistically significant results (Sterling, Rosenbaum, \& Weinkam, 1995).
+Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in psychology reported support for their first or main hypothesis, the highest number of all disciplines in the study.
+For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
+In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes must consistently be very high (given the same study design).
+
+\hypertarget{a-biased-literature}{%
+\subsection{A biased literature}\label{a-biased-literature}}
+
+Sterling (1959) already suspected a selection process behind the numbers he found:
+\enquote{(\ldots) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of {[}statistical{]} significance} (p.~31).
+This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature.
+We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
+Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
+These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Mahoney, 1977; Greenwald, 1975) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
+Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate, see also Lakens, n.d.).
+These include presenting unexpected results as having been predicted a priori (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``p-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
+Evidence for both categories of bias exist:
+Publication bias has been shown in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; John, Loewenstein, \& Prelec, 2012).
+
+Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because because it weeds out low-quality research that would only pollute the literature (Winter \& Happee, 2013; but see van Assen, van Aert, Nuijten, \& Wicherts, 2014).
+How problematic selective publishing is in practice remains an empirical question:
+If most negative results that are currently missing from the literature are the result of immature ideas or poorly conducted studies, we should expect that a literature in which studies are selected based on their quality but not based on their results would contain a similar proportion of positive results as the current one.
+But how many positive results would such an unbiased literature contain in reality?
+We set out to explore this question by comparing the rate of positive results in a sample from the current psychology literature to a set of studies that were published in a new format created to minimise QRPs and publication bias: Registered Reports.
+
+\hypertarget{methods-to-mitigate-bias}{%
+\subsection{Methods to mitigate bias}\label{methods-to-mitigate-bias}}
+
+An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
+Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of p-hacking via restricted flexibility in data analysis.
+However, preregistration does not prevent file-drawering or reviewer bias and may thus be toothless in fighting publication bias.
+A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers, 2013; Chambers, Dienes, McIntosh, Rotshtein, \& Willmes, 2015; Jonas \& Cesario, 2016; Nosek \& Lakens, 2014).
+Registered Reports (RRs) are a new publication format with a restructured submission timeline:
+Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline to a journal.
+The protocol undergoes peer review, and, if successful, receives \enquote{in-principle acceptance}, meaning that the journal commits to publishing the final article following data collection regardless of the statistical significance of the results.
+The authors then collect and analyse the data and write up the final report.
+The final report undergoes another round of peer review, but this time only to check if the authors adhered to the plan outlined in their protocol (and, if applicable, if the data passes pre-specified quality checks).
+RRs thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
+Since its introduction at the journal Cortex in 2013, the format has rapidly gained popularity and is offered by 207 journals at the time of writing (\url{http://cos.io/rr}).
+
+In addition to bias protection, RRs promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
+Many journals offering RRs also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., \(90\%\) power for a given effect size of interest).
+
+Assuming a constant alpha level, the rate of positive results in a literature is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
+The RR format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature (see e.g., Maxwell, 2004; Szucs \& Ioannidis, 2017).
+Therefore, if the emerging RR literature in psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in RRs (or a combination of the two).
+At this time, we have good reasons to believe in a difference in bias, but little reason to believe in a difference in the proportion of true hypotheses (at least regarding original hypotheses, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate (i.e., the proportion of supported hypotheses among all tested hypotheses).
+Considering the high standards for research quality in RRs, a large difference in positive results between RRs and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.
+
+\hypertarget{the-current-study}{%
+\subsection{The current study}\label{the-current-study}}
+
+The goal of our study was to test if RRs in psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
+We set out to replicate a study by Fanelli (2010) on a new sample of standard reports in psychology and compared them to all published Registered Reports in psychology.
+Fanelli searched for articles containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}, drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
+For standard reports we used the same sampling method (restricted to the psychology discipline), and for RRs we relied on a database curated by the Center for Open Science (COS).
+We chose Fanelli's method because Fanelli's (2010) and (2012) studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
+We additionally coded if studies were replications or original work because many published RRs are replications.
+If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, and a higher proportion of replications among RRs than standard reports could therefore introduce a confound.
+
+In a recent commentary on benefits and challenges of open-science practices for early-career researchers, Allen \& Mehler (2019) conducted a similar investigation:
+They coded the proportion of null results in the 127 biomedical and psychology RRs listed in the COS database as of September 2018.
+We were not aware of their parallel efforts when we planned our study in September and October 2018.
+Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in RRs (counting all hypotheses in each paper) and found \(60.5\%\) unsupported hypotheses across all included RRs, \(66\%\) for replication attempts, and \(54.5\%\) for novel research.
+They compared these numbers to an estimate of \(5-20\%\) null results in the standard literature.
+This \(5-20\%\) estimate is based on data from Fanelli (2012), who coded only the first hypothesis of each paper (identical to Fanelli, 2010), and Cristea \& Ioannidis (2018){]}, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
+
+A major advantage of our study is that it allows us to draw a more meaningful comparison between RRs and the standard literature because we apply a previously used method (Fanelli, 2010, 2012) to both groups.
+In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
+Therefore we also coded the phrases used to introduce hypotheses in RRs, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
+Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgments, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
+This allows others to verify (or contest) our results and provides an interesting resource for future meta-scientific research.
+
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
+
+After conducting a pilot to test the planned procedure we preregistered our study (\url{https://osf.io/s8e97}).
+Methods and analyses described here were preregistered unless otherwise noted.
+A detailed comparison of our preregistration and the eventual procedure is provided in the supplement.
+We report how we determined our sample size, all data exclusions, and all measures in the study.
+
+\hypertarget{sample}{%
+\subsection{Sample}\label{sample}}
+
+We used the same method as Fanelli (2010) to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the RR population.
+We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
+An overview of the sampling process and all exclusions are shown in Figure 1.
+
+For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} and the ISSNs of all journals listed in the ESI Psychiatry/Psychology category.
+Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed \enquote{20190120} (not specified in our preregistration, but no other seeds were tried).
+We initially excluded eight papers and replaced them (the decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had erroneously been excluded, leading to a final sample size of 152 rather than 150 (see Fig.
+1).
+
+\begin{figure}
+\includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{XXX ADD CAPTION}\label{fig:unnamed-chunk-2}
+\end{figure}
+
+For Registered Reports we aimed to include all published RRs in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
+We downloaded a database of published RRs curated by the Center for Open Science{[}\^{}1{]} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
+{[}\^{}1{]}: \url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}
+Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 RRs published in Cortex because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
+Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., Royal Society Open Science) were hand-coded by AS.
+This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
+Following these exclusions, we verified the RR status of all remaining papers in our sample.
+Papers were counted as RRs if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
+For papers not clearly labelled as RRs we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
+Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig.
+1).
+Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d.).
+
+\hypertarget{measures-and-coding-procedure}{%
+\subsection{Measures and coding procedure}\label{measures-and-coding-procedure}}
+
+The main dependent variable was whether or not the first hypothesis was supported or not, as reported by the authors.
+We tried to follow Fanelli's (2010) coding procedure as closely as possible, which he describes as follows:
+
+\begin{quote}
+By examining the abstract and/or full- text, it was determined whether the authors of each paper had concluded to have found a positive (full or partial) or negative (null or negative) support.
+If more than one hypothesis was being tested, only the first one to appear in the text was considered.
+We excluded meeting abstracts and papers that either did not test a hypothesis or for which we lacked sufficient information to determine the outcome. (p.~8)
+\end{quote}
+
+Like Fanelli (2010), we coded hypotheses as having received \enquote{support}, \enquote{partial support}, or \enquote{no support}, which was recoded into a binary \enquote{support} (full or partial) vs \enquote{no support} variable for the analysis.
+Coding disagreements between full and partial support were deemed minor since they would not affect the final results, thus only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.
+
+Before preregistering our study, we conducted a pilot to assess if we could employ Fanelli's method successfully.
+Originally we had planned to first reproduce his results on the same sample of Psychiatry/Psychology articles used in Fanelli (2010).
+Unfortunately the author refused to share the original data (or even a list of the coded articles) with us.
+Instead, we received an excerpt which contained data for 11 records from the original sample, but no reference information of the coded articles (personal communication, 5th October 2018).
+We were able to find these 11 articles based on the hypothesis quotes that had been coded, and used them as a pilot sample along with 10 randomly selected RRs.
+MS and AS independently coded all 21 pilot articles with only one major disagreement in each group.
+In the SR group, this disagreement was also the only case of major disagreement with Fanelli's original coding, which we deemed satisfying to proceed.
+
+Based on our experiences during the pilot, we added one coding criterion:
+If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first tested hypothesis rather than the first hypothesis mentioned in the text.
+In RRs we coded the first preregistered hypothesis, thus excluding unregistered pilot studies.
+MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs \(= 33.80\%\) and \(47\) SRs \(= 30.92 \%\)).
+Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
+We preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+
+\hypertarget{hypothesis-introductions}{%
+\subsubsection{Hypothesis introductions}\label{hypothesis-introductions}}
+
+Selecting papers that use the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} might yield different results than alternative search phrases.
+Getting a better overview of \enquote{natural} descriptions of hypotheses would be useful for future investigations of the generalisability of Fanelli's (2010) results and could inspire new research questions.
+We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all RRs and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
+If MS and AS had coded different hypothesis quotes for a paper, MS's coding was used, unless disagreement resolution of the \enquote{hypothesis support} variable lead to AS's coding overruling MS's.
+
+\hypertarget{replication-status}{%
+\subsubsection{Replication status}\label{replication-status}}
+
+We also wanted to code if a study was a replication of a previously published one:
+We expected a much larger proportion of RRs to be direct replications, many of which may have been motivated by scepticism of the original study.
+A lower positive result rate in RRs could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
+After an initial coding attempt with ill-defined coding criteria lead to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
+We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf.~Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
+Conceptual replications and internal replications were not counted as replications in this narrow sense:
+The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
+AS coded all papers, DL double-coded 32 RRs (\(45.07 \%\)) and 99 SRs (\(21.05 \%\)).
+There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.
+
+\hypertarget{additional-measures}{%
+\subsubsection{Additional measures}\label{additional-measures}}
+
+All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above.
+All of these are documented in the Appendix and our shared dataset and codebook.
 
@@
 1).
-The preregistered one-sided proportions test with an alpha level of \(5\%\) showed that this difference of \(-52.39\%\) was statistically significant, \(\chi^2 = 77.96\), \(p < .001\).
-Unsurprisingly, the difference was not statistically equivalent to a range between \(-6\%\) and \(6\%\) at \(\alpha = 5\%\), \(z = 7.61\), \(p > .999\), meaning that we cannot reject differences more extreme than \(6\%\).
+The preregistered one-sided proportions test with an alpha level of \(5\%\) showed that this difference of \(-52.39 \%\) was statistically significant, \(\chi^2 = 77.96\), \(p < .001\).
+Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\), \(z = 7.61\), \(p > .999\), meaning that we cannot reject differences more extreme than \(6\%\).
 We thus accept our hypothesis that the positive result rate in RRs is lower than in SRs.
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{\label{fig:unnamed-chunk-3}Positive result rates for standard reports and Registered Reports. Error bars indicate 95\% confidence intervals around the observed positive result rate.}
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-5-1.pdf}
+\caption{\label{fig:unnamed-chunk-5}Positive result rates for standard reports and Registered Reports. Error bars indicate 95\% confidence intervals around the observed positive result rate.}
 \end{figure}
@@
 
-As expected, direct replications were much more common among RRs than SRs: 41 out of 71 RRs (\(57.75\%\)), but only 4 out of 152 SRs (\(2.63\%\)) were classified as direct replications of previously published work.
+As described in the Method section, we only classified close or direct replications of previously published work as replications.
+This means that our non-replication category also contains some conceptual replications and \enquote{internal} replications (where original and replication are published in the same paper).
+For ease of communication we will nonetheless refer to this category as \enquote{original} studies.
+As expected, direct replications were much more common among Registered Reports than standard reports: 41 out of 71 RRs (\(57.75\%\)), but only 4 out of 152 SRs (\(2.63\%\)) were classified as direct replications of previously published work.
 However, this difference cannot account for the stark overall difference between SRs and RRs described above:
@@
 \begin{threeparttable}
-\caption{\label{tab:unnamed-chunk-5}Positive results in original studies vs replication studies}
+\caption{\label{tab:unnamed-chunk-6}Positive results in original studies vs replication studies}
 \begin{tabular}{lrrrrrrrr}
@@
 
-Finally, we analysed the language that was used to introduce or signal hypotheses in RRs.
-Does Fanelli's search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} capture hypothesis-testing RRs reasonably well?
+Finally, we analysed the language that was used to introduce or refer to hypotheses in RRs.
+We were interested in whether the search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} used by Fanelli captured the way researchers write about hypothesis tests reasonably well.
 The answer is a resounding \enquote{no}:
 Searching the abstracts, titles, and keywords of the RR sample showed that only 2/71 RRs would have been detected with this search phrase.
-Which analogous hypothesis-introduction phrases are used in RRs, and can they be summarised in a convenient way?
-To get an overview, we stripped the hypothesis quotes of RRs from all content-specific information and extracted \enquote{minimal} phrases that most distinctively indicated that a hypothesis was being described.
+To get an overview of analogous hypothesis-introduction phrases researchers used in RRs, we stripped the hypothesis quotes of RRs from all content-specific information and extracted \enquote{minimal} phrases that most distinctively indicated that a hypothesis was being described.
 For example, from the hypothesis quote \enquote{(f)or Study 1, we predicted that participants reading about academic (vs.~social) behaviors would show a better anagram performance} we extracted the hypothesis-introduction phrase \enquote{predicted that}.
@@
 In this total set of 97 hypothesis introductions, we found 64 unique phrases, showing substantial linguistic variation (see Tables 2 and 3).
-In order to condense the information further, we listed all unique word stems (e.g., the word stem \enquote{hypothes\(^\ast\)} captures the words \enquote{hypothesis}, \enquote{hypotheses}, \enquote{hypothesize}, \enquote{hypothesized}, and so on) and analysed their frequency among all hypothesis introductions.
+In order to condense the information, we listed all unique word stems (e.g., the word stem \enquote{hypothes\(^\ast\)} captures the words \enquote{hypothesis}, \enquote{hypotheses}, \enquote{hypothesize}, \enquote{hypothesized}, and so on) and analysed their frequency among all hypothesis introductions.
 Excluding words that are common but too unspecific by themselves, such as \enquote{that}, \enquote{to}, or \enquote{whether}, the five most frequent word stems were \enquote{hypothes\(^\ast\)} (34 occurrences), \enquote{replicat\(^\ast\)} (24), \enquote{test\(^\ast\)} (20), \enquote{examine\(^\ast\)} (8), and \enquote{predict\(^\ast\)} (8).
@@
 
-We noticed that direct replication RRs generally tended to use different language to describe their hypothesis (or rather their goal).
+We noticed that direct replication RRs generally tended to use different language to describe their hypothesis.
 As the high frequency of the word stem \enquote{replicat\(^\ast\)} suggests, these studies were often not framed as new tests of a previously tested hypothesis, but as attempts to replicate a previously documented effect or to repeat a previously conducted experiment.
+Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
 Tables 2 and 3 list all unique hypothesis introductions and their frequency for original RRs and direct replication RRs, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
@@
 \begin{threeparttable}
-\caption{\label{tab:unnamed-chunk-9}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}
+\caption{\label{tab:unnamed-chunk-8}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}
 \footnotesize{
@@
 \begin{threeparttable}
-\caption{\label{tab:unnamed-chunk-10}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
+\caption{\label{tab:unnamed-chunk-9}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
 \footnotesize{
@@
 
+It is important to keep in mind that not all hypotheses could be coded from the abstract: For 21 RRs, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
+Therefore we additionally tested how many of the RRs would have been detected in a regular search using our five most frequent word stems.
+We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(68/71\) RRs (\(95.77 \%\)) would have been detected this way.
+We do not know how well these search terms represent the population of hypothesis-testing studies in psychology, but a structured investigation of this question would be very useful for future meta-research.
+
 \hypertarget{discussion}{%
@@
 
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
+We examined the proportion of psychology articles that find support for their first tested hypothesis and found a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
+More than half of the analysed RRs tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
+The introduction of Registered Reports has clearly led to a much larger proportion of null results appearing in the published literature compared to standard reports.
+
+The positive result rate we found in standard reports (\(96.05 \%\)) is slightly higher than the \(91.5\%\) reported by Fanelli (2010), although this difference was not statistically significant.
+Our replication in a more recent sample of the psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 (cf.~Fanelli, 2012).
+Furthermore, our estimate of the positive result rate for Registered Reports (\(43.66 \%\)) is comparable to the \(39.5\%\) reported by Allen \& Mehler (2019), despite some differences in method and studied population.
+
+To explain the \(52.39 \%\) gap between standard reports and Registered Reports, we must assume some combination of differences in bias, statistical power, or the proportion of true hypotheses researchers choose to examine.
+Figure 3 visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
+For example, if we assume no publication bias and no QRPs, more than \(90\%\) of the hypotheses authors of standard reports study must be true and study designs must have more than \(90\%\) power for the true effect size.
+This is highly unlikely, meaning that the standard literature is unlikely to reflect reality.
+As we noted above, there is good reason to assume that methodological rigour and statistical power in Registered Reports are as high, or higher, than in standard reports, leaving the rate of true hypotheses and bias as remaining explanations.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{\label{fig:unnamed-chunk-10}XXX ADD CAPTION}
+\end{figure}
+
+It is a-priori plausible that Registered Reports are currently used for a population of hypotheses that are less likely to be true:
+For example, authors may use the format strategically for studies they expect to yield negative results (which would be difficult to publish otherwise).
+However, assuming over \(90\%\) true hypotheses in the standard literature is neither realistic, nor would it be desirable for a science that wants to advance knowledge beyond trivial facts.
+We thus believe that this factor alone is not sufficient to explain the gap between the positive result rates in Registered Reports and standard reports.
+Rather, the numbers strongly suggest a reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
+
+\hypertarget{limitations}{%
+\subsection{Limitations}\label{limitations}}
+
+We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports.
+Because neither hypotheses, authors, nor editors are randomly assigned to each publication format we cannot draw firm conclusions about the causes that lead to a difference in the proportion of supported hypotheses.
+Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
+As mentioned above, it is a-priori plausible that the Registered Reports format is used selectively for particularly risky hypotheses.
+This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in psychology.
+It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias.
+Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use.
+This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
+
+A second limitation of the current study (and of Fanelli, 2010) is that standard reports were selected using the search term \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
+As our results show, this phrase was virtually absent in the Registered Report population.
+The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for \enquote{test\(^\ast\) the hypothes\(^\ast\)} will miss most of the hypothesis-testing studies in the psychological literature.
+Results based on this search phrase may not generalise to all published studies.
+For example, it is possible that authors are more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., \enquote{we examined the role of \ldots{}}).
+If this were true, using other strategies to select standard reports might yield lower estimates for the positive result rate.
+However, this does not seem to be the case:
+Studies using different selection criteria for articles and hypotheses have found very similar rates of supported hypotheses.
+For example, the positive result rates in Sterling (1959), Sterling et al.
+(1995), and the original studies included in the Reproducibility Project: Psychology (Collaboration, 2015) were \(97.28\%\), \(95.56\%\), and \(97\%\), respectively.
+Motyl et al. (2017) report \(89.17\%\) and \(92.01\%\) significant results for \enquote{critical} hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively.
+Therefore, although the search term used to find standard reports might limit the generalisability of our results, this search strategy seems to yield comparable estimates as the selection strategies used in different studies.
+
+A final limitation is the decision to code only the first reported hypothesis.
+The first hypothesis test may not be representative for all hypothesis tests reported in a paper, and the order of reporting may differ between standard reports and Registered Reports.
+Perhaps Registered Report authors are more likely to present their hypotheses in \enquote{chronological} order, whereas standard report authors tend to rearrange the order in which hypotheses are reported based on their outcomes, and present supported hypotheses first.
+Here again, the converging estimates from the four studies cited above (none of which use the first-hypothesis rule) make it seem unlikely that our result is an artefact of this decision.
+Regardless of which hypothesis one chooses to analyse across a set of papers -- the first, the last, or the \enquote{critical} one -- the positive result rate turns out to be higher than what can be expected based on realistic estimates of the proportion of true hypotheses researchers study and the statistical power of their tests.
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
+
+Our study presents a systematic comparison of positive results in Registered Reports and the standard literature.
+The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the published research we are used to.
+Standard publication formats seem to lead scientists to miss out on many high-quality studies with negative results, which are available in the Registered Reports literature.
+The absence of negative results is a serious threat to a cumulative science.
+Reliable protection against questionable research practices and publication bias is crucial to ensure the integrity of the literature.
+The Registered Reports format is a promising candidate for bias protection, but we are only at the beginning of understanding its effectiveness and robustness in different contexts and scientific disciplines.
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Agnoli2017}{}%
+Agnoli, F., Wicherts, J.
+M., Veldkamp, C.
+L.
+S., Albiero, P., \& Cubelli, R.
+(2017).
+Questionable research practices among italian research psychologists.
+\emph{PLOS ONE}, \emph{12}(3), e0172792.
+doi:\href{https://doi.org/10.1371/journal.pone.0172792}{10.1371/journal.pone.0172792}
+
+\leavevmode\hypertarget{ref-Allen2019}{}%
+Allen, C., \& Mehler, D.
+M.
+A.
+(2019).
+Open science challenges, benefits and tips in early career and beyond.
+\emph{PLOS Biology}, \emph{17}(5), e3000246.
+doi:\href{https://doi.org/10.1371/journal.pbio.3000246}{10.1371/journal.pbio.3000246}
+
+\leavevmode\hypertarget{ref-Atkinson1982}{}%
+Atkinson, D.
+R., Furlong, M.
+J., \& Wampold, B.
+E.
+(1982).
+Statistical significance, reviewer evaluations, and the scientific process: Is there a (statistically) significant relationship?
+\emph{Journal of Counseling Psychology}, \emph{29}(2), 189--194.
+doi:\href{https://doi.org/10.1037/0022-0167.29.2.189}{10.1037/0022-0167.29.2.189}
+
+\leavevmode\hypertarget{ref-Chambers2013}{}%
+Chambers, C. D. (2013). Registered reports: A new publishing initiative at Cortex, \emph{49}(3), 609--610. Retrieved from \url{http://orca.cf.ac.uk/45177/1/Chambers_Cortex_2013b_GreenOA.pdf}
+
+\leavevmode\hypertarget{ref-Chambers2015}{}%
+Chambers, C.
+D., Dienes, Z., McIntosh, R.
+D., Rotshtein, P., \& Willmes, K.
+(2015).
+Registered Reports: Realigning incentives in scientific publishing.
+\emph{Cortex}, \emph{66}, 1--2.
+doi:\href{https://doi.org/10.1016/j.cortex.2015.03.022}{10.1016/j.cortex.2015.03.022}
+
+\leavevmode\hypertarget{ref-OSC2015}{}%
+Collaboration, O.
+S.
+(2015).
+Estimating the reproducibility of psychological science.
+\emph{Science}, \emph{349}(6251), aac4716.
+doi:\href{https://doi.org/10.1126/science.aac4716}{10.1126/science.aac4716}
+
+\leavevmode\hypertarget{ref-Cristea2018}{}%
+Cristea, I.
+A., \& Ioannidis, J.
+P.
+A.
+(2018).
+P values in display items are ubiquitous and almost invariably significant: A survey of top science journals.
+\emph{PLOS ONE}, \emph{13}(5), e0197440.
+doi:\href{https://doi.org/10.1371/journal.pone.0197440}{10.1371/journal.pone.0197440}
+
 \leavevmode\hypertarget{ref-Fanelli2010}{}%
@@
 doi:\href{https://doi.org/10.1371/journal.pone.0010068}{10.1371/journal.pone.0010068}
+
+\leavevmode\hypertarget{ref-Fanelli2012}{}%
+Fanelli, D.
+(2012).
+Negative results are disappearing from most disciplines and countries.
+\emph{Scientometrics}, \emph{90}(3), 891--904.
+doi:\href{https://doi.org/10.1007/s11192-011-0494-7}{10.1007/s11192-011-0494-7}
+
+\leavevmode\hypertarget{ref-Fiedler2016}{}%
+Fiedler, K., \& Schwarz, N.
+(2016).
+Questionable Research Practices Revisited.
+\emph{Social Psychological and Personality Science}, \emph{7}(1), 45--52.
+doi:\href{https://doi.org/10.1177/1948550615612150}{10.1177/1948550615612150}
+
+\leavevmode\hypertarget{ref-Franco2014}{}%
+Franco, A., Malhotra, N., \& Simonovits, G.
+(2014).
+Publication bias in the social sciences: Unlocking the file drawer.
+\emph{Science}, \emph{345}(6203), 1502--1505.
+doi:\href{https://doi.org/10.1126/science.1255484}{10.1126/science.1255484}
+
+\leavevmode\hypertarget{ref-Franco2016}{}%
+Franco, A., Malhotra, N., \& Simonovits, G.
+(2016).
+Underreporting in Psychology Experiments: Evidence From a Study Registry.
+\emph{Social Psychological and Personality Science}, \emph{7}(1), 8--12.
+doi:\href{https://doi.org/10.1177/1948550615598377}{10.1177/1948550615598377}
+
+\leavevmode\hypertarget{ref-Greenwald1975}{}%
+Greenwald, A. G. (1975). Consequences of Prejudice Against the Null Hypothesis. \emph{Psychological Bulletin}, \emph{82}(1), 1--20.
+
+\leavevmode\hypertarget{ref-John2012}{}%
+John, L.
+K., Loewenstein, G., \& Prelec, D.
+(2012).
+Measuring the Prevalence of Questionable Research Practices With Incentives for Truth Telling.
+\emph{Psychological Science}, \emph{23}(5), 524--532.
+doi:\href{https://doi.org/10.1177/0956797611430953}{10.1177/0956797611430953}
+
+\leavevmode\hypertarget{ref-Jonas2016}{}%
+Jonas, K.
+J., \& Cesario, J.
+(2016).
+How can preregistration contribute to research in our field?
+\emph{Comprehensive Results in Social Psychology}, \emph{1}(1-3), 1--7.
+doi:\href{https://doi.org/10.1080/23743603.2015.1070611}{10.1080/23743603.2015.1070611}
+
+\leavevmode\hypertarget{ref-Kerr1998}{}%
+Kerr, N.
+L.
+(1998).
+HARKing: Hypothesizing after the results are known.
+\emph{Personality and Social Psychology Review}, \emph{2}(3), 196--217.
+doi:\href{https://doi.org/10.1207/s15327957pspr0203_4}{10.1207/s15327957pspr0203\_4}
+
+\leavevmode\hypertarget{ref-Kohler2019}{}%
+Köhler, T., \& Cortina, J.
+M.
+(2019).
+Play It Again, Sam!
+An Analysis of Constructive Replication in the Organizational Sciences.
+\emph{Journal of Management}, 014920631984398.
+doi:\href{https://doi.org/10.1177/0149206319843985}{10.1177/0149206319843985}
+
+\leavevmode\hypertarget{ref-Lakens2019b}{}%
+Lakens, D. (n.d.). The Value of Preregistration for Psychological Science: A Conceptual Analysis. doi:\href{https://doi.org/10.31234/osf.io/jbh4w}{10.31234/osf.io/jbh4w}
 
@@
 
+\leavevmode\hypertarget{ref-Mahoney1977}{}%
+Mahoney, M.
+J.
+(1977).
+Publication Prejudices: An Experimental Study of Confirmatory Bias in the Peer Review System.
+\emph{Cognitive Therapy and Research}, \emph{1}(2), 161--175.
+doi:\href{https://doi.org/10.1007/BF01173636}{10.1007/BF01173636}
+
+\leavevmode\hypertarget{ref-Makel2012}{}%
+Makel, M.
+C., Plucker, J.
+A., \& Hegarty, B.
+(2012).
+Replications in Psychology Research: How Often Do They Really Occur?
+\emph{Perspectives on Psychological Science}.
+doi:\href{https://doi.org/10.1177/1745691612460688}{10.1177/1745691612460688}
+
+\leavevmode\hypertarget{ref-Maxwell2004}{}%
+Maxwell, S.
+E.
+(2004).
+The Persistence of Underpowered Studies in Psychological Research: Causes, Consequences, and Remedies.
+\emph{Psychological Methods}, \emph{9}(2), 147--163.
+doi:\href{https://doi.org/10.1037/1082-989X.9.2.147}{10.1037/1082-989X.9.2.147}
+
+\leavevmode\hypertarget{ref-Motyl2017}{}%
+Motyl, M., Demos, A.
+P., Carsel, T.
+S., Hanson, B.
+E., Melton, Z.
+J., Mueller, A.
+B., \ldots{} Skitka, L.
+J.
+(2017).
+The state of social and personality science: Rotten to the core, not so bad, getting better, or getting worse?
+\emph{Journal of Personality and Social Psychology}, \emph{113}(1), 34--58.
+doi:\href{https://doi.org/10.1037/pspa0000084}{10.1037/pspa0000084}
+
+\leavevmode\hypertarget{ref-Mueller-Langer2019}{}%
+Mueller-Langer, F., Fecher, B., Harhoff, D., \& Wagner, G.
+G.
+(2019).
+Replication studies in economics---How many and which papers are chosen for replication, and why?
+\emph{Research Policy}, \emph{48}(1), 62--83.
+doi:\href{https://doi.org/10.1016/j.respol.2018.07.019}{10.1016/j.respol.2018.07.019}
+
+\leavevmode\hypertarget{ref-Nosek2014}{}%
+Nosek, B.
+A., \& Lakens, D.
+(2014).
+Registered Reports: A Method to Increase the Credibility of Published Results.
+\emph{Social Psychology}, \emph{45}(3), 137--141.
+doi:\href{https://doi.org/10.1027/1864-9335/a000192}{10.1027/1864-9335/a000192}
+
+\leavevmode\hypertarget{ref-Pridemore2018}{}%
+Pridemore, W.
+A., Makel, M.
+C., \& Plucker, J.
+A.
+(2018).
+Replication in Criminology and the Social Sciences.
+\emph{Annual Review of Criminology}, \emph{1}(1), 19--38.
+doi:\href{https://doi.org/10.1146/annurev-criminol-032317-091849}{10.1146/annurev-criminol-032317-091849}
+
+\leavevmode\hypertarget{ref-RRRwebsite}{}%
+\emph{Registered Replication Reports}. (n.d.). \emph{Association for Psychological Science - APS}. Retrieved December 28, 2019, from \url{https://www.psychologicalscience.org/publications/replication}
+
 \leavevmode\hypertarget{ref-Rohatgi2018}{}%
 Rohatgi, A. (2018). \emph{WebPlotDigitizer - Web Based Plot Digitizer}. Austin, Texas, USA. Retrieved from \url{https://automeris.io/WebPlotDigitizer}
+
+\leavevmode\hypertarget{ref-Rosenthal1979}{}%
+Rosenthal, R.
+(1979).
+The file drawer problem and tolerance for null results.
+\emph{Psychological Bulletin}, \emph{86}(3), 638--641.
+doi:\href{https://doi.org/10.1037/0033-2909.86.3.638}{10.1037/0033-2909.86.3.638}
+
+\leavevmode\hypertarget{ref-Simmons2011}{}%
+Simmons, J.
+P., Nelson, L.
+D., \& Simonsohn, U.
+(2011).
+False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
+\emph{Psychological Science}, \emph{22}(11), 1359--1366.
+doi:\href{https://doi.org/10.1177/0956797611417632}{10.1177/0956797611417632}
+
+\leavevmode\hypertarget{ref-Simons2018}{}%
+Simons, D.
+J.
+(2018).
+Introducing Advances in Methods and Practices in Psychological Science.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(1), 3--6.
+doi:\href{https://doi.org/10.1177/2515245918757424}{10.1177/2515245918757424}
+
+\leavevmode\hypertarget{ref-Simons2014}{}%
+Simons, D.
+J., Holcombe, A.
+O., \& Spellman, B.
+A.
+(2014).
+An Introduction to Registered Replication Reports at \emph{Perspectives} \emph{on} \emph{Psychological Science}.
+\emph{Perspectives on Psychological Science}, \emph{9}(5), 552--555.
+doi:\href{https://doi.org/10.1177/1745691614543974}{10.1177/1745691614543974}
+
+\leavevmode\hypertarget{ref-Sterling1959}{}%
+Sterling, T.
+D.
+(1959).
+Publication Decisions and their Possible Effects on Inferences Drawn from Tests of Significance---or Vice Versa.
+\emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.
+doi:\href{https://doi.org/10.1080/01621459.1959.10501497}{10.1080/01621459.1959.10501497}
+
+\leavevmode\hypertarget{ref-Sterling1995}{}%
+Sterling, T.
+D., Rosenbaum, W.
+L., \& Weinkam, J.
+J.
+(1995).
+Publication Decisions Revisited: The Effect of the Outcome of Statistical Tests on the Decision to Publish and Vice Versa.
+\emph{The American Statistician}, \emph{49}(1), 108.
+doi:\href{https://doi.org/10.2307/2684823}{10.2307/2684823}
+
+\leavevmode\hypertarget{ref-Szucs2017}{}%
+Szucs, D., \& Ioannidis, J.
+P.
+A.
+(2017).
+Empirical assessment of published effect sizes and power in the recent cognitive neuroscience and psychology literature.
+\emph{PLOS Biology}, \emph{15}(3), e2000797.
+doi:\href{https://doi.org/10.1371/journal.pbio.2000797}{10.1371/journal.pbio.2000797}
+
+\leavevmode\hypertarget{ref-vanAssen2014}{}%
+van Assen, M.
+A.
+L.
+M., van Aert, R.
+C.
+M., Nuijten, M.
+B., \& Wicherts, J.
+M.
+(2014).
+Why Publishing Everything Is More Effective than Selective Publishing of Statistically Significant Results.
+\emph{PLOS ONE}, \emph{9}(1), e84896.
+doi:\href{https://doi.org/10.1371/journal.pone.0084896}{10.1371/journal.pone.0084896}
+
+\leavevmode\hypertarget{ref-Winter2013}{}%
+Winter, J.
+de, \& Happee, R.
+(2013).
+Why Selective Publication of Statistically Significant Results Can Be Effective.
+\emph{PLOS ONE}, \emph{8}(6), e66463.
+doi:\href{https://doi.org/10.1371/journal.pone.0066463}{10.1371/journal.pone.0066463}
+
+\leavevmode\hypertarget{ref-Wiseman2019}{}%
+Wiseman, R., Watt, C., \& Kornbrot, D. (2019). Registered reports: An early example and analysis. \emph{PeerJ}, \emph{7}, e6232. doi:\href{https://doi.org/10.7717/peerj.6232}{10.7717/peerj.6232}
+
+\leavevmode\hypertarget{ref-Agnoli2017}{}%
+Agnoli, F., Wicherts, J.
+M., Veldkamp, C.
+L.
+S., Albiero, P., \& Cubelli, R.
+(2017).
+Questionable research practices among italian research psychologists.
+\emph{PLOS ONE}, \emph{12}(3), e0172792.
+doi:\href{https://doi.org/10.1371/journal.pone.0172792}{10.1371/journal.pone.0172792}
+
+\leavevmode\hypertarget{ref-Allen2019}{}%
+Allen, C., \& Mehler, D.
+M.
+A.
+(2019).
+Open science challenges, benefits and tips in early career and beyond.
+\emph{PLOS Biology}, \emph{17}(5), e3000246.
+doi:\href{https://doi.org/10.1371/journal.pbio.3000246}{10.1371/journal.pbio.3000246}
+
+\leavevmode\hypertarget{ref-Atkinson1982}{}%
+Atkinson, D.
+R., Furlong, M.
+J., \& Wampold, B.
+E.
+(1982).
+Statistical significance, reviewer evaluations, and the scientific process: Is there a (statistically) significant relationship?
+\emph{Journal of Counseling Psychology}, \emph{29}(2), 189--194.
+doi:\href{https://doi.org/10.1037/0022-0167.29.2.189}{10.1037/0022-0167.29.2.189}
+
+\leavevmode\hypertarget{ref-Chambers2013}{}%
+Chambers, C. D. (2013). Registered reports: A new publishing initiative at Cortex, \emph{49}(3), 609--610. Retrieved from \url{http://orca.cf.ac.uk/45177/1/Chambers_Cortex_2013b_GreenOA.pdf}
+
+\leavevmode\hypertarget{ref-Chambers2015}{}%
+Chambers, C.
+D., Dienes, Z., McIntosh, R.
+D., Rotshtein, P., \& Willmes, K.
+(2015).
+Registered Reports: Realigning incentives in scientific publishing.
+\emph{Cortex}, \emph{66}, 1--2.
+doi:\href{https://doi.org/10.1016/j.cortex.2015.03.022}{10.1016/j.cortex.2015.03.022}
+
+\leavevmode\hypertarget{ref-OSC2015}{}%
+Collaboration, O.
+S.
+(2015).
+Estimating the reproducibility of psychological science.
+\emph{Science}, \emph{349}(6251), aac4716.
+doi:\href{https://doi.org/10.1126/science.aac4716}{10.1126/science.aac4716}
+
+\leavevmode\hypertarget{ref-Cristea2018}{}%
+Cristea, I.
+A., \& Ioannidis, J.
+P.
+A.
+(2018).
+P values in display items are ubiquitous and almost invariably significant: A survey of top science journals.
+\emph{PLOS ONE}, \emph{13}(5), e0197440.
+doi:\href{https://doi.org/10.1371/journal.pone.0197440}{10.1371/journal.pone.0197440}
 
@@
 
+\leavevmode\hypertarget{ref-Mahoney1977}{}%
+Mahoney, M.
+J.
+(1977).
+Publication Prejudices: An Experimental Study of Confirmatory Bias in the Peer Review System.
+\emph{Cognitive Therapy and Research}, \emph{1}(2), 161--175.
+doi:\href{https://doi.org/10.1007/BF01173636}{10.1007/BF01173636}
+
+\leavevmode\hypertarget{ref-Makel2012}{}%
+Makel, M.
+C., Plucker, J.
+A., \& Hegarty, B.
+(2012).
+Replications in Psychology Research: How Often Do They Really Occur?
+\emph{Perspectives on Psychological Science}.
+doi:\href{https://doi.org/10.1177/1745691612460688}{10.1177/1745691612460688}
+
+\leavevmode\hypertarget{ref-Maxwell2004}{}%
+Maxwell, S.
+E.
+(2004).
+The Persistence of Underpowered Studies in Psychological Research: Causes, Consequences, and Remedies.
+\emph{Psychological Methods}, \emph{9}(2), 147--163.
+doi:\href{https://doi.org/10.1037/1082-989X.9.2.147}{10.1037/1082-989X.9.2.147}
+
+\leavevmode\hypertarget{ref-Motyl2017}{}%
+Motyl, M., Demos, A.
+P., Carsel, T.
+S., Hanson, B.
+E., Melton, Z.
+J., Mueller, A.
+B., \ldots{} Skitka, L.
+J.
+(2017).
+The state of social and personality science: Rotten to the core, not so bad, getting better, or getting worse?
+\emph{Journal of Personality and Social Psychology}, \emph{113}(1), 34--58.
+doi:\href{https://doi.org/10.1037/pspa0000084}{10.1037/pspa0000084}
+
+\leavevmode\hypertarget{ref-Mueller-Langer2019}{}%
+Mueller-Langer, F., Fecher, B., Harhoff, D., \& Wagner, G.
+G.
+(2019).
+Replication studies in economics---How many and which papers are chosen for replication, and why?
+\emph{Research Policy}, \emph{48}(1), 62--83.
+doi:\href{https://doi.org/10.1016/j.respol.2018.07.019}{10.1016/j.respol.2018.07.019}
+
+\leavevmode\hypertarget{ref-Nosek2014}{}%
+Nosek, B.
+A., \& Lakens, D.
+(2014).
+Registered Reports: A Method to Increase the Credibility of Published Results.
+\emph{Social Psychology}, \emph{45}(3), 137--141.
+doi:\href{https://doi.org/10.1027/1864-9335/a000192}{10.1027/1864-9335/a000192}
+
+\leavevmode\hypertarget{ref-Pridemore2018}{}%
+Pridemore, W.
+A., Makel, M.
+C., \& Plucker, J.
+A.
+(2018).
+Replication in Criminology and the Social Sciences.
+\emph{Annual Review of Criminology}, \emph{1}(1), 19--38.
+doi:\href{https://doi.org/10.1146/annurev-criminol-032317-091849}{10.1146/annurev-criminol-032317-091849}
+
+\leavevmode\hypertarget{ref-RRRwebsite}{}%
+\emph{Registered Replication Reports}. (n.d.). \emph{Association for Psychological Science - APS}. Retrieved December 28, 2019, from \url{https://www.psychologicalscience.org/publications/replication}
+
 \leavevmode\hypertarget{ref-Rohatgi2018}{}%
@@
 
+\leavevmode\hypertarget{ref-Rosenthal1979}{}%
+Rosenthal, R.
+(1979).
+The file drawer problem and tolerance for null results.
+\emph{Psychological Bulletin}, \emph{86}(3), 638--641.
+doi:\href{https://doi.org/10.1037/0033-2909.86.3.638}{10.1037/0033-2909.86.3.638}
+
+\leavevmode\hypertarget{ref-Simmons2011}{}%
+Simmons, J.
+P., Nelson, L.
+D., \& Simonsohn, U.
+(2011).
+False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
+\emph{Psychological Science}, \emph{22}(11), 1359--1366.
+doi:\href{https://doi.org/10.1177/0956797611417632}{10.1177/0956797611417632}
+
+\leavevmode\hypertarget{ref-Simons2018}{}%
+Simons, D.
+J.
+(2018).
+Introducing Advances in Methods and Practices in Psychological Science.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(1), 3--6.
+doi:\href{https://doi.org/10.1177/2515245918757424}{10.1177/2515245918757424}
+
+\leavevmode\hypertarget{ref-Simons2014}{}%
+Simons, D.
+J., Holcombe, A.
+O., \& Spellman, B.
+A.
+(2014).
+An Introduction to Registered Replication Reports at \emph{Perspectives} \emph{on} \emph{Psychological Science}.
+\emph{Perspectives on Psychological Science}, \emph{9}(5), 552--555.
+doi:\href{https://doi.org/10.1177/1745691614543974}{10.1177/1745691614543974}
+
+\leavevmode\hypertarget{ref-Sterling1959}{}%
+Sterling, T.
+D.
+(1959).
+Publication Decisions and their Possible Effects on Inferences Drawn from Tests of Significance---or Vice Versa.
+\emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.
+doi:\href{https://doi.org/10.1080/01621459.1959.10501497}{10.1080/01621459.1959.10501497}
+
+\leavevmode\hypertarget{ref-Sterling1995}{}%
+Sterling, T.
+D., Rosenbaum, W.
+L., \& Weinkam, J.
+J.
+(1995).
+Publication Decisions Revisited: The Effect of the Outcome of Statistical Tests on the Decision to Publish and Vice Versa.
+\emph{The American Statistician}, \emph{49}(1), 108.
+doi:\href{https://doi.org/10.2307/2684823}{10.2307/2684823}
+
+\leavevmode\hypertarget{ref-Szucs2017}{}%
+Szucs, D., \& Ioannidis, J.
+P.
+A.
+(2017).
+Empirical assessment of published effect sizes and power in the recent cognitive neuroscience and psychology literature.
+\emph{PLOS Biology}, \emph{15}(3), e2000797.
+doi:\href{https://doi.org/10.1371/journal.pbio.2000797}{10.1371/journal.pbio.2000797}
+
+\leavevmode\hypertarget{ref-vanAssen2014}{}%
+van Assen, M.
+A.
+L.
+M., van Aert, R.
+C.
+M., Nuijten, M.
+B., \& Wicherts, J.
+M.
+(2014).
+Why Publishing Everything Is More Effective than Selective Publishing of Statistically Significant Results.
+\emph{PLOS ONE}, \emph{9}(1), e84896.
+doi:\href{https://doi.org/10.1371/journal.pone.0084896}{10.1371/journal.pone.0084896}
+
+\leavevmode\hypertarget{ref-Winter2013}{}%
+Winter, J.
+de, \& Happee, R.
+(2013).
+Why Selective Publication of Statistically Significant Results Can Be Effective.
+\emph{PLOS ONE}, \emph{8}(6), e66463.
+doi:\href{https://doi.org/10.1371/journal.pone.0066463}{10.1371/journal.pone.0066463}
+
+\leavevmode\hypertarget{ref-Wiseman2019}{}%
+Wiseman, R., Watt, C., \& Kornbrot, D. (2019). Registered reports: An early example and analysis. \emph{PeerJ}, \emph{7}, e6232. doi:\href{https://doi.org/10.7717/peerj.6232}{10.7717/peerj.6232}
+
 \end{document}

### 2020-01-08 manuscript.Rmd
minor text change

@@
 1).
-Note that we excluded all eight "Registered Replication Reports" [RRRs; @Simons2014; @Simons2018] in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing [@RRRwebsite].
+Note that we excluded all eight "Registered Replication Reports" [RRRs; @Simons2014; @Simons2018] in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing [@RRRwebsite; decision was not preregistered].
 

### 2020-01-09 hypothesis_introduction_analyses.R
Fully commented and prettified analysis scripts (not completely done with power_baserate_plot.R yet)

@@ -1,76 +1,236 @@
-library("dplyr")
+#########################################################
+#####                                               #####
+##### Script 3: Qualitative analysis:               #####
+#####           Analysing the phrases used to       #####
+#####           introduce hypotheses in Registered  #####
+#####           Reports                             #####
+#####                                               #####
+#####-----------------------------------------------#####
+#####                                               #####
+##### Content:                                      #####
+#####  * 1: Setup                                   #####
+#####  * 2: Calculate how many Registered Reports   #####
+#####       would have been detected with the       #####
+#####       search phrase "test* the hypothes*"     #####
+#####  * 3: Analyse the hypothesis introduction     #####
+#####       phrases used in Registered Reports      #####
+#####       and find clusters (identify the five    #####
+#####       most frequent "core words")             #####
+#####  * 4: Create two tables listing all unique    #####
+#####       hypothesis introduction phrases in      #####
+#####       original and replication Registered     #####
+#####       Reports, respectively                   #####
+#####       !!CAUTION!! Extremely long and ugly     #####
+#####       code (ca. 750 lines)                    #####
+#####                                               #####
+##### Note:                                         #####
+#####   RR = Registered Report                      #####
+#####                                               #####
+#########################################################
+
+##==============================================================================##
+## 1. Setup: load packages and data 
+##==============================================================================##
+
+# Two packages are needed: stringr reshape2. Install them, if needed, by 
+# uncommenting the respective line(s):
+# install.packages("stringr")  # install stringr
+# install.packages("reshape2")  # install reshape2
+
+# Load packages:
 library("stringr")
 library("reshape2")
 
-
-
-#source("analysis.R")
-# load the dataset from RDS created with codebook
+# load the dataset from the RDS file created with codebook
 alldata <- readRDS("positive_results_in_registered_reports_codebook.rds")
-
 # remove excluded papers
 included <- alldata[alldata$include_in_analysis==1,]
 
-## 6. Analyse the phrases used to introduce hypotheses in RRs
 
-## 6.1 Check how many RRs would have been discovered with the search
[…]

### 2020-01-09 interrater_agreement.R

@@ -1,4 +1,22 @@
-# load the dataset from RDS created with codebook
+#########################################################
+#####                                               #####
+##### Script 1: Calculate inter-rater agreement     #####
+#####                                               #####
+#####-----------------------------------------------#####
+#####                                               #####
+##### Content:                                      #####
+#####  * 1: Inter-rater agreement for main          #####
+#####       outcome variable (support_binary)       #####
+#####  * 2: Inter-rater agreement for replication   #####
+#####       status variable (is_replication)        #####
+#####                                               #####
+##### Note:                                         #####
+#####   RR = Registered Report                      #####
+#####   SR = standard report                        #####
+#####                                               #####
+#########################################################
+
+# load the dataset from the RDS file created with codebook
 alldata <- readRDS("positive_results_in_registered_reports_codebook.rds")
 
 # remove excluded papers
@@ -7,56 +25,74 @@ included <- alldata[alldata$include_in_analysis==1,]
 
 ##==============================================================================##
 ## 1. Calculate inter-rater agreement (between MS and AS) for main 
-## variable (support_binary)
+##    variable (support_binary)
+##==============================================================================##
+
+## 1.1 Calculate number of papers coded by MS and AS, respectively, and
+##     number of double-coded papers
 
 # number of papers coded by MS: 221 out of 223 = 99.10%
 support.coded.MS <- sum(included$coded_by_MS)
-# number of papers coded by AS: 70 out of 223 = 31.39%
+# number of papers coded by AS: 71 out of 223 = 31.83%
 support.coded.AS <- sum(included$coded_by_AS)
 
-# number of RRs coded by AS: 23 out of 71 = 32.4%
+# number of RRs coded by AS: 24 out of 71 = 33.8%
 sum(included$coded_by_AS & included$is_RR)/sum(included$is_RR)
-# number of CRs coded by AS: 47 out of 152 = 30.9%
+# number of SRs coded by AS: 47 out of 152 = 30.9%
 sum(included$coded_by_AS & !included$is_RR)/sum(!included$is_RR)
 
-# number of papers double coded: 68 out of 223 = 30.49%
+# number of papers double coded: 69 out of 223 = 30.94%
 support.doublecoded <- length(which(included$coded_by_MS == 1 & 
                                       included$coded_by_AS ==1))
 
[…]

### 2020-01-09 power_baserate_plot.R

@@ -1,18 +1,88 @@
+#########################################################
+#####                                               #####
+##### Script 4: Calculate and plot power and the    #####
+#####           rate of true hypotheses for the     #####
+#####           observed positive result rates in   #####
+#####           the absence of bias                 #####
+#####                                               #####
+#####-----------------------------------------------#####
+#####                                               #####
+##### Content:                                      #####
+#####  * 1: Setup                                   #####
+#####  * 2: Functions to calculate power and rate   #####
+#####       of true hypotheses                      #####
+#####  * 3: Plot functions with observed positive   #####
+#####       result rates as input                   #####
+#####                                               #####
+##### Note:                                         #####
+#####   RR = Registered Report                      #####
+#####   SR = standard report                        #####
+#####   PRR = positive result rate                  #####
+#####                                               #####
+#########################################################
+
+##==============================================================================##
+## 1. Setup: load packages and data 
+##==============================================================================##
+
+# The ggplot2 packages is needed to create the plot. Install it, if needed, by 
+# uncommenting the following line:
+# install.packages("ggplot2")
+
+# Load ggplot2:
 library(ggplot2)
 
-# Inferring the likely proportion of true hypotheses studied in the literature
-# and statistical power based on the observed proportion of significant results
+# Load data: Creating the plot requires input from the main analysis script
+# (quantitative_analyses.R). In the RMarkdown file for the manuscript, this
+# script is already loaded when the code below is run. The respective variables
+# are *not* hard-coded or recalculated here to avoid errors or inconsistencies
+# if any changes to the data or main analysis script should be made in the future.
+# Therefore, if you wish to run this script outside of the RMarkdown environment 
+# of the manuscript, you first need to load the main analysis script (and with it,
+# the data). Adjust the code to load the script if necessary.
+source("quantitative_analyses.R")
 
-# t = proportion of true hypotheses
-# a = alpha
-# b = beta; i.e. 1-b = power
-# PRR = positive result rate (proportion of significant results in the literature)
-truehyps <- function(PRR, a, pwr){-(PRR - a)/((1-pwr) + a - 1)}
-pwrfun <- function(t, a, PRR){(a*t+PRR-a)/(t)}
 
+##==============================================================================##
[…]

### 2020-01-09 quantitative_analyses.R

@@ -1,34 +1,72 @@
+#########################################################
+#####                                               #####
+##### Script 2: Quantitative analyses               #####
+#####           (confirmatory and exploratory)      #####
+#####                                               #####
+#####-----------------------------------------------#####
+#####                                               #####
+##### Content:                                      #####
+#####  * 1: Setup                                   #####
+#####  * 2: Main confirmatory analysis:             #####
+#####       positive result rate in Registered      #####
+#####       Reports compared to standard reports    #####
+#####  * 3: Exploratory analysis:                   #####
+#####       positive result rate in replication     #####
+#####       studies compared to original studies    #####
+#####  * 4: Excploratory analysis:                  #####
+#####       positive result rate in standard        #####
+#####       reports compared to Fanelli (2010)      #####
+#####                                               #####
+##### Note:                                         #####
+#####   RR = Registered Report                      #####
+#####   SR = standard report                        #####
+#####                                               #####
+#########################################################
+
+##==============================================================================##
+## 1. Setup: load packages and data 
+##==============================================================================##
+
+# Three packages are needed: TOSTER to calculate equivalence tests, ggplot2 for
+# creating the plot for Figure 2 in the manuscript, and papaja for Table 1 in 
+# the manuscript. papaja was not yet on CRAN when this was written and has to 
+# be installed from Github, using the devtools package. Its role in this script
+# is very minor though -- all analyses can be reproduced without papaja.
+
+# Install packages if needed by uncommenting the respective line(s):
+# install.packages("TOSTER")  # install TOSTER
+# install.packages("ggplot2")  # install ggplot2
+# install.packages("devtools")  # install devtools to install papaja
+# devtools::install_github("crsh/papaja")  # install papaja
+
+# Load packages:
 library("TOSTER")
 library("ggplot2")
-library("dplyr")
-library("stringr")
-library("reshape2")
+library("papaja")
 
 
-#####################################################################################################
-#### CHUNK 1
[…]

### 2020-01-09 manuscript.Rmd
Edited Tables 2 and 3 after rearranging the order of hypothesis introduction phrases, and made Table 3 smaller to fit on one page.

@@
 However, this difference cannot account for the stark overall difference between SRs and RRs described above: 
-Although replication RRs in our sample indeed had a lower positive result rate than original RRs (see Table 1), the difference between original SRs and original RRs -- $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$ -- was still significantly different from 0 ($\chi^2 = `r printnum(repproptest$statistic)`$, $p `r printp(repproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(reptost$TOST_z1, reptost$TOST_z2))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
+Although replication RRs in our sample indeed had a lower positive result rate than original RRs (see Table 1), the difference between original SRs and original RRs -- $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$ -- was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(reptost$TOST_z1, reptost$TOST_z2))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
 ```{r echo = FALSE, results = 'asis'}
@@
   , caption = "Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)"
-  , note = "This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, 9 papers contributed two each, one contributed three, and one contributed four."
+  , note = "This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four."
   , added_stub_head = "Variables"
   , col_spanners = list(`source` = c(3, 5))
-  , midrules = c(6, 16, 22, 23, 27, 32)
+  , midrules = c(10, 16, 22, 23, 28, 32)
   , landscape = FALSE
@@
   phrasetable.rep
-  , digits = c(0, 0, 0, 0, 0)
-  , col.names = c("core word(s)", "introduction phrase", "abstract", 
-                  "full text", "total")
-  , align = c("l", "l", rep("r", 3))
+  , digits = c(0, 0, 0, 0, 0, 0, 0)
+  , col.names = c("", "core word(s)", "introduction phrase", "abstract", 
+                  "full text", "total", "")
+  , align = c("l", "l", "l", rep("r", 4))
   , caption = "Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)"
-  , note = "This table contains 53 hypothesis introduction phrases from 40 Registered Reports.
-One additional RR had no codeable hypothesis introduction.
-30 papers contributed one phrase each, 7 papers contributed two each, and three contributed three each."
+  , note = "Table contains 53 hypothesis introduction phrases from 40 Registered Reports.
+One additional RR had no hypothesis introduction.
+Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each."
   , added_stub_head = "Variables"
-  , col_spanners = list(`source` = c(3, 5))
-  , midrules = c(4, 5, 6, 12, 16, 33, 34, 35, 36)
+  , col_spanners = list(`source` = c(4, 6))
+  , midrules = c(6, 10, 11, 12, 29, 30, 34, 35, 36)
   , landscape = FALSE
-  , font_size = "footnotesize"
+  , font_size = "scriptsize"
   , escape = TRUE

### 2020-01-09 manuscript.tex
Edited Tables 2 and 3 after rearranging the order of hypothesis introduction phrases, and made Table 3 smaller to fit on one page.

@@
 1).
-Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d.).
+Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing {[}(``Registered Replication Reports,'' n.d.); decision was not preregistered{]}.
 
@@
 \midrule
-hypothes*, test* &  & 3 & 2 & 5\\
- & test of ... hypotheses & 0 & 1 & 1\\
- & test of ... hypothesis & 1 & 0 & 1\\
- & test the hypothesis that & 1 & 0 & 1\\
- & tested ... hypotheses & 0 & 1 & 1\\
- & tested the hypothesis that & 1 & 0 & 1\\ \midrule
 hypothes* &  & 5 & 12 & 17\\
@@
  & registered ... hypotheses & 1 & 0 & 1\\ \midrule
+hypothes*, test* &  & 3 & 2 & 5\\
+ & test of ... hypotheses & 0 & 1 & 1\\
+ & test of ... hypothesis & 1 & 0 & 1\\
+ & test the hypothesis that & 1 & 0 & 1\\
+ & tested ... hypotheses & 0 & 1 & 1\\
+ & tested the hypothesis that & 1 & 0 & 1\\ \midrule
 test* &  & 5 & 2 & 7\\
@@
 test*, predict* & test ... prediction & 0 & 1 & 1\\ \midrule
-predict* &  & 4 & 0 & 4\\
- & had ... predictions & 1 & 0 & 1\\
- & predicted that & 2 & 0 & 2\\
- & predicts that & 1 & 0 & 1\\ \midrule
 examin* &  & 5 & 0 & 5\\
@@
  & to examine & 1 & 0 & 1\\ \midrule
+predict* &  & 4 & 0 & 4\\
+ & had ... predictions & 1 & 0 & 1\\
+ & predicted that & 2 & 0 & 2\\
+ & predicts that & 1 & 0 & 1\\ \midrule
 (other) &  & 0 & 5 & 5\\
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, 9 papers contributed two each, one contributed three, and one contributed four.}
+\normalsize{\textit{Note.} This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four.}
 \end{tablenotes}
@@
 \caption{\label{tab:unnamed-chunk-9}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
-\footnotesize{
-\begin{tabular}{llrrr}
+\scriptsize{
+\begin{tabular}{lllrrrr}
 \toprule
- &  & \multicolumn{3}{c}{source} \\
-\cmidrule(r){3-5}
-core word(s) & introduction phrase & abstract & full text & total\\
+ &  &  & \multicolumn{3}{c}{source}  &\\
+\cmidrule(r){4-6}
+ & core word(s) & introduction phrase & abstract & full text & total & \\
 \midrule
-hypothes*, test* &  & 2 & 1 & 3\\
- & test ... hypotheses & 0 & 1 & 1\\
- & test ... hypothesis & 1 & 0 & 1\\
- & tested ... hypotheses & 1 & 0 & 1\\ \midrule
-hypothes*, predict* & hypotheses predicted & 1 & 0 & 1\\ \midrule
-hypothes*, examin* & examined ... hypothesis & 1 & 0 & 1\\ \midrule
-hypothes* &  & 2 & 5 & 7\\
- & according to ... hypothesis & 0 & 1 & 1\\
- & Hypotheses & 0 & 1 & 1\\
- & Hypothesis 1 (H1): & 0 & 1 & 1\\
- & hypothesize that & 0 & 1 & 1\\
- & hypothesized that & 2 & 1 & 3\\ \midrule
-test* &  & 4 & 0 & 4\\
- & testing whether & 2 & 0 & 2\\
- & to ... test & 1 & 0 & 1\\
- & to test & 1 & 0 & 1\\ \midrule
-replicat* &  & 20 & 3 & 23\\
- & aim ... to replicate & 0 & 1 & 1\\
- & aim at replicating & 1 & 0 & 1\\
- & aimed to replicate & 0 & 1 & 1\\
- & attempted to replicate & 1 & 0 & 1\\
- & attempts to replicate & 1 & 0 & 1\\
- & conducted ... replication & 3 & 0 & 3\\
- & conducted ... replications & 2 & 0 & 2\\
- & performed ... replication & 2 & 0 & 2\\
- & present ... replication & 1 & 0 & 1\\
- & present ... replications & 1 & 0 & 1\\
- & replicated ... experiment & 1 & 0 & 1\\
- & replicating & 0 & 1 & 1\\
- & report ... replication attempt & 1 & 0 & 1\\
- & report ... replications & 2 & 0 & 2\\
- & sought to replicate & 3 & 0 & 3\\
- & we replicated & 1 & 0 & 1\\ \midrule
-replicat*, examin* & critically examine and replicate & 1 & 0 & 1\\ \midrule
-predict* & predicted that & 2 & 0 & 2\\ \midrule
-examin* & examine whether & 0 & 1 & 1\\ \midrule
-(other) &  & 4 & 6 & 10\\
- & establish whether & 0 & 1 & 1\\
- & H1 & 0 & 2 & 2\\
- & investigate if & 1 & 0 & 1\\
- & sought to reproduce & 1 & 0 & 1\\
- & suggests that & 2 & 0 & 2\\
- & we ... conducted & 0 & 1 & 1\\
- & we assume & 0 & 1 & 1\\
- & we expect & 0 & 1 & 1\\
+ & hypothes* &  & 2 & 5 & 7 & \\
+ &  & according to ... hypothesis & 0 & 1 & 1 & \\
+ &  & Hypotheses & 0 & 1 & 1 & \\
+ &  & Hypothesis 1 (H1): & 0 & 1 & 1 & \\
+ &  & hypothesize that & 0 & 1 & 1 & \\
+ &  & hypothesized that & 2 & 1 & 3 & \\ \midrule
+ & hypothes*, test* &  & 2 & 1 & 3 & \\
+ &  & test ... hypotheses & 0 & 1 & 1 & \\
+ &  & test ... hypothesis & 1 & 0 & 1 & \\
+ &  & tested ... hypotheses & 1 & 0 & 1 & \\ \midrule
+ & hypothes*, examin* & examined ... hypothesis & 1 & 0 & 1 & \\ \midrule
+ & hypothes*, predict* & hypotheses predicted & 1 & 0 & 1 & \\ \midrule
+ & replicat* &  & 20 & 3 & 23 & \\
+ &  & aim ... to replicate & 0 & 1 & 1 & \\
+ &  & aim at replicating & 1 & 0 & 1 & \\
+ &  & aimed to replicate & 0 & 1 & 1 & \\
+ &  & attempted to replicate & 1 & 0 & 1 & \\
+ &  & attempts to replicate & 1 & 0 & 1 & \\
+ &  & conducted ... replication & 3 & 0 & 3 & \\
+ &  & conducted ... replications & 2 & 0 & 2 & \\
+ &  & performed ... replication & 2 & 0 & 2 & \\
+ &  & present ... replication & 1 & 0 & 1 & \\
+ &  & present ... replications & 1 & 0 & 1 & \\
+ &  & replicated ... experiment & 1 & 0 & 1 & \\
+ &  & replicating & 0 & 1 & 1 & \\
+ &  & report ... replication attempt & 1 & 0 & 1 & \\
+ &  & report ... replications & 2 & 0 & 2 & \\
+ &  & sought to replicate & 3 & 0 & 3 & \\
+ &  & we replicated & 1 & 0 & 1 & \\ \midrule
+ & replicat*, examin* & critically examine and replicate & 1 & 0 & 1 & \\ \midrule
+ & test* &  & 4 & 0 & 4 & \\
+ &  & testing whether & 2 & 0 & 2 & \\
+ &  & to ... test & 1 & 0 & 1 & \\
+ &  & to test & 1 & 0 & 1 & \\ \midrule
+ & examin* & examine whether & 0 & 1 & 1 & \\ \midrule
+ & predict* & predicted that & 2 & 0 & 2 & \\ \midrule
+ & (other) &  & 4 & 6 & 10 & \\
+ &  & establish whether & 0 & 1 & 1 & \\
+ &  & H1 & 0 & 2 & 2 & \\
+ &  & investigate if & 1 & 0 & 1 & \\
+ &  & sought to reproduce & 1 & 0 & 1 & \\
+ &  & suggests that & 2 & 0 & 2 & \\
+ &  & we ... conducted & 0 & 1 & 1 & \\
+ &  & we assume & 0 & 1 & 1 & \\
+ &  & we expect & 0 & 1 & 1 & \\
 \bottomrule
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} This table contains 53 hypothesis introduction phrases from 40 Registered Reports.
-One additional RR had no codeable hypothesis introduction.
-30 papers contributed one phrase each, 7 papers contributed two each, and three contributed three each.}
+\normalsize{\textit{Note.} Table contains 53 hypothesis introduction phrases from 40 Registered Reports.
+One additional RR had no hypothesis introduction.
+Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each.}
 \end{tablenotes}
@@
 Therefore we additionally tested how many of the RRs would have been detected in a regular search using our five most frequent word stems.
-We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(68/71\) RRs (\(95.77 \%\)) would have been detected this way.
+We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) RRs (\(97.18 \%\)) would have been detected this way.
 We do not know how well these search terms represent the population of hypothesis-testing studies in psychology, but a structured investigation of this question would be very useful for future meta-research.

### 2020-01-09 power_baserate_plot.R
finished commenting & prettifying code

@@ -57,12 +57,7 @@ source("quantitative_analyses.R")
 # a: alpha (the probability of a positive result when testing a false hypothesis), and
 # 1-b: power (the probability of a positive result when testing a true hypothesis)
 # 
-# Solving for t gives
-# t = (a - PRR)/(a + b - 1)
-# As a function:
-truehyps <- function(PRR, a, b){(a - PRR)/(a + b - 1)}
-
-# Solving the same equation for 1-b gives
+# Solving for 1-b gives
 # 1-b = (PRR - a + a*t)/t
 # As a function:
 pwrfun <- function(t, a, PRR){(PRR -a + a*t)/t}
@@ -83,36 +78,66 @@ a <- 0.05
 ##    * all RRs (n = 71)
 ##==============================================================================##
 
+## 3.1 Create a dataframe for each group and fill it with calculated power
+##     and baserate values
 
-pwrprior.df <-  data.frame(t=c(1:1000)/1000)
-pwrprior.df$group <- "all RRs (PRR = .4366, N = 71)"
-pwrprior.df$lower <- pwrfun(t = pwrprior.df$t, a = a, PRR = min(RR.binom$conf.int))
-pwrprior.df$estimate <- pwrfun(t = pwrprior.df$t, a = a, PRR = prop.support.RR)
-pwrprior.df$upper <- pwrfun(t = pwrprior.df$t, a = a, PRR = max(RR.binom$conf.int))   
+# Create dataframe for original SRs
+pwrprior.origSR <- data.frame(t=c(1:1000)/1000) # Enter values for t from .001 - 1
+pwrprior.origSR$group <- "original SRs (PRR = .9595, n = 148)" # group label (later used for plot)
 
-pwrprior.origRR <- data.frame(t=c(1:1000)/1000)
-pwrprior.origRR$group <- "original RRs (PRR = .5, n = 30)"
-pwrprior.origRR$lower <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = min(RR.orig.binom$conf.int))
-pwrprior.origRR$estimate <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = prop.orig.support.RR)
-pwrprior.origRR$upper <- pwrfun(t = pwrprior.origRR$t, a = a, PRR = max(RR.orig.binom$conf.int))   
-
-pwrprior.origSR <- data.frame(t=c(1:1000)/1000)
[…]

### 2020-01-10 manuscript/manuscript.Rmd
1. added a robustness check to the quantitative analysis script, 2. reorganised the folder structure (in accordance with Psych-DS), 3. changed code in the manuscript Rmd and in the analysis scripts to accommodate the new folder structure, 4. added the preregistration document with comments indicating adherence/deviations, 5. added a file with the full list of Psych journals from the ESI database

--- 2020-01-09 manuscript.Rmd
@@
 library("reshape2")
+library("here")
 ```
@@
 ```{r include=FALSE}
-source("interrater_agreement.R")
+source(here("analysis", "interrater_agreement.R"))
 ```
@@
 We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all RRs and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
-If MS and AS had coded different hypothesis quotes for a paper, MS's coding was used, unless disagreement resolution of the "hypothesis support" variable lead to AS's coding overruling MS's.
+.
 
@@
 ```{r include=FALSE}
-source("quantitative_analyses.R")
+source(here("analysis", "quantitative_analyses.R"))
 ```
@@
 ```{r include=FALSE}
-source("hypothesis_introduction_analyses.R")
+source(here("analysis", "hypothesis_introduction_analyses.R"))
 ```
@@
 ```{r echo=FALSE, warning=FALSE, fig.width=6, fig.height=3, fig.cap="XXX ADD CAPTION"}
-source("power_baserate_plot.R")
+source(here("analysis", "power_baserate_plot.R"))
 power.baserate.plot

### 2020-01-10 analysis/hypothesis_introduction_analyses.R

@@ -1,0 +1,1095 @@
+#########################################################
+#####                                               #####
+##### Script 3: Qualitative analysis:               #####
+#####           Analysing the phrases used to       #####
+#####           introduce hypotheses in Registered  #####
+#####           Reports                             #####
+#####                                               #####
+#####-----------------------------------------------#####
+#####                                               #####
+##### Content:                                      #####
+#####  * 1: Setup                                   #####
+#####  * 2: Calculate how many Registered Reports   #####
+#####       would have been detected with the       #####
+#####       search phrase "test* the hypothes*"     #####
+#####  * 3: Analyse the hypothesis introduction     #####
+#####       phrases used in Registered Reports      #####
+#####       and find clusters (identify the five    #####
+#####       most frequent "core words")             #####
+#####  * 4: Create two tables listing all unique    #####
+#####       hypothesis introduction phrases in      #####
+#####       original and replication Registered     #####
+#####       Reports, respectively                   #####
+#####       !!CAUTION!! Extremely long and ugly     #####
+#####       code (ca. 750 lines)                    #####
+#####                                               #####
+##### Note:                                         #####
+#####   RR = Registered Report                      #####
+#####                                               #####
+#########################################################
+
+##==============================================================================##
+## 1. Setup: load packages and data 
+##==============================================================================##
+
+# Three packages are needed: stringr, reshape2, and here (to locate the data 
+# file when loading it). If you want to run these analyses outside of our 
+# R project, you may need to adjust the command to load the data, and you can
+# do this without making use of the here package.
+# Install the packages, if needed, by uncommenting the respective line(s):
+# install.packages("here")  # install here
+# install.packages("stringr")  # install stringr
+# install.packages("reshape2")  # install reshape2
+
+# Load packages:
+library("here")
+library("stringr")
+library("reshape2")
+
+# load the dataset from the RDS file created with codebook
+alldata <- readRDS(here("raw_data", "positive_results_in_registered_reports_codebook.rds"))
+# remove excluded papers
[…]

### 2020-01-10 analysis/interrater_agreement.R

@@ -1,0 +1,214 @@
+#########################################################
+#####                                               #####
+##### Script 1: Calculate inter-rater agreement     #####
+#####                                               #####
+#####-----------------------------------------------#####
+#####                                               #####
+##### Content:                                      #####
+#####  * 1: Inter-rater agreement for main          #####
+#####       outcome variable (support_binary)       #####
+#####  * 2: Inter-rater agreement for replication   #####
+#####       status variable (is_replication)        #####
+#####                                               #####
+##### Note:                                         #####
+#####   RR = Registered Report                      #####
+#####   SR = standard report                        #####
+#####                                               #####
+#########################################################
+
+# The "here" package is needed to locate the data file when loading it. 
+# If you want to run this analysis outside of our R project, you may need
+# to adjust the command to load the data, and you can do that 
+# without making use of the here package. 
+# Install the package, if needed, by uncommenting the following line:
+# install.packages("here") 
+
+# Load package:
+library(here)
+
+# load the dataset from the RDS file created with codebook
+alldata <- readRDS(here("raw_data", "positive_results_in_registered_reports_codebook.rds"))
+
+# remove excluded papers
+included <- alldata[alldata$include_in_analysis==1,]
+
+
+##==============================================================================##
+## 1. Calculate inter-rater agreement (between MS and AS) for main 
+##    variable (support_binary)
+##==============================================================================##
+
+## 1.1 Calculate number of papers coded by MS and AS, respectively, and
+##     number of double-coded papers
+
+# number of papers coded by MS: 221 out of 223 = 99.10%
+support.coded.MS <- sum(included$coded_by_MS)
+# number of papers coded by AS: 71 out of 223 = 31.83%
+support.coded.AS <- sum(included$coded_by_AS)
+
+# number of RRs coded by AS: 24 out of 71 = 33.8%
+sum(included$coded_by_AS & included$is_RR)/sum(included$is_RR)
+# number of SRs coded by AS: 47 out of 152 = 30.9%
+sum(included$coded_by_AS & !included$is_RR)/sum(!included$is_RR)
+
+# number of papers double coded: 69 out of 223 = 30.94%
+support.doublecoded <- length(which(included$coded_by_MS == 1 & 
[…]

### 2020-01-10 analysis/power_baserate_plot.R

@@ -1,0 +1,157 @@
+#########################################################
+#####                                               #####
+##### Script 4: Calculate and plot power and the    #####
+#####           rate of true hypotheses for the     #####
+#####           observed positive result rates in   #####
+#####           the absence of bias                 #####
+#####                                               #####
+#####-----------------------------------------------#####
+#####                                               #####
+##### Content:                                      #####
+#####  * 1: Setup                                   #####
+#####  * 2: Functions to calculate power and rate   #####
+#####       of true hypotheses                      #####
+#####  * 3: Plot functions with observed positive   #####
+#####       result rates as input                   #####
+#####                                               #####
+##### Note:                                         #####
+#####   RR = Registered Report                      #####
+#####   SR = standard report                        #####
+#####   PRR = positive result rate                  #####
+#####                                               #####
+#########################################################
+
+##==============================================================================##
+## 1. Setup: load packages and data 
+##==============================================================================##
+
+# The ggplot2 package is needed to create the plot. 
+# Install the package, if needed, by uncommenting the following line:
+# install.packages("ggplot2") 
+
+# Load packages:
+library(ggplot2)
+
+# Load data: Creating the plot requires input from the main analysis script
+# (quantitative_analyses.R). In the RMarkdown file for the manuscript, this
+# script is already loaded when the code below is run. The respective variables
+# are *not* hard-coded or recalculated here to avoid errors or inconsistencies
+# if any changes to the data or main analysis script should be made in the future.
+# Therefore, if you wish to run this script outside of the RMarkdown environment 
+# of the manuscript, you first need to load the main analysis script (and with it,
+# the data). Adjust the code to load the script if necessary.
+
+# source("quantitative_analyses.R")
+
+
+##==============================================================================##
+## 2. Functions to calculate power and rate of true hypotheses 
[…]

### 2020-01-10 analysis/quantitative_analyses.R

@@ -1,0 +1,358 @@
+#########################################################
+#####                                               #####
+##### Script 2: Quantitative analyses               #####
+#####           (confirmatory and exploratory)      #####
+#####                                               #####
+#####-----------------------------------------------#####
+#####                                               #####
+##### Content:                                      #####
+#####  * 1: Setup                                   #####
+#####  * 2: Main confirmatory analysis:             #####
+#####       positive result rate in Registered      #####
+#####       Reports compared to standard reports    #####
+#####  * 3: Exploratory analysis:                   #####
+#####       positive result rate in replication     #####
+#####       studies compared to original studies    #####
+#####  * 4: Exploratory analysis:                   #####
+#####       positive result rate in standard        #####
+#####       reports compared to Fanelli (2010)      #####
+#####  * 5: Robustness check:                       #####
+#####       Run main analysis without replacement   #####
+#####       standard reports                        #####
+#####                                               #####
+##### Note:                                         #####
+#####   RR = Registered Report                      #####
+#####   SR = standard report                        #####
+#####                                               #####
+#########################################################
+
+##==============================================================================##
+## 1. Setup: load packages and data 
+##==============================================================================##
+
+# Four packages are needed: TOSTER to calculate equivalence tests, ggplot2 for
+# creating the plot for Figure 2 in the manuscript, papaja for Table 1 in 
+# the manuscript, and here to locate the data file when loading it. If you  
+# want to run these analyses outside of our R project, you may need to adjust
+# the command to load the data, and you can do this without making use of the
+# here package. papaja was not yet on CRAN when this was written and has to 
+# be installed from Github, using the devtools package. Its role in this script
+# is very minor though -- all analyses can be reproduced without papaja.
+
+# Install packages if needed by uncommenting the respective line(s):
+# install.packages("here")  # install here
[…]

### 2020-01-10 hypothesis_introduction_analyses.R

@@ -1,1090 +1,0 @@
-#########################################################
-#####                                               #####
-##### Script 3: Qualitative analysis:               #####
-#####           Analysing the phrases used to       #####
-#####           introduce hypotheses in Registered  #####
-#####           Reports                             #####
-#####                                               #####
-#####-----------------------------------------------#####
-#####                                               #####
-##### Content:                                      #####
-#####  * 1: Setup                                   #####
-#####  * 2: Calculate how many Registered Reports   #####
-#####       would have been detected with the       #####
-#####       search phrase "test* the hypothes*"     #####
-#####  * 3: Analyse the hypothesis introduction     #####
-#####       phrases used in Registered Reports      #####
-#####       and find clusters (identify the five    #####
-#####       most frequent "core words")             #####
-#####  * 4: Create two tables listing all unique    #####
-#####       hypothesis introduction phrases in      #####
-#####       original and replication Registered     #####
-#####       Reports, respectively                   #####
-#####       !!CAUTION!! Extremely long and ugly     #####
-#####       code (ca. 750 lines)                    #####
-#####                                               #####
-##### Note:                                         #####
-#####   RR = Registered Report                      #####
-#####                                               #####
-#########################################################
-
-##==============================================================================##
-## 1. Setup: load packages and data 
-##==============================================================================##
-
-# Two packages are needed: stringr reshape2. Install them, if needed, by 
-# uncommenting the respective line(s):
-# install.packages("stringr")  # install stringr
-# install.packages("reshape2")  # install reshape2
-
-# Load packages:
-library("stringr")
-library("reshape2")
-
-# load the dataset from the RDS file created with codebook
-alldata <- readRDS("positive_results_in_registered_reports_codebook.rds")
-# remove excluded papers
-included <- alldata[alldata$include_in_analysis==1,]
-
-
-##==============================================================================##
-## 2. Calculate how many RRs would have been discovered with the search
-##    phrase "test* the hypothes*" (i.e., when searching titles, abstracts,
-##    and keywords)
[…]

### 2020-01-10 interrater_agreement.R

@@ -1,204 +1,0 @@
-#########################################################
-#####                                               #####
-##### Script 1: Calculate inter-rater agreement     #####
-#####                                               #####
-#####-----------------------------------------------#####
-#####                                               #####
-##### Content:                                      #####
-#####  * 1: Inter-rater agreement for main          #####
-#####       outcome variable (support_binary)       #####
-#####  * 2: Inter-rater agreement for replication   #####
-#####       status variable (is_replication)        #####
-#####                                               #####
-##### Note:                                         #####
-#####   RR = Registered Report                      #####
-#####   SR = standard report                        #####
-#####                                               #####
-#########################################################
-
-# load the dataset from the RDS file created with codebook
-alldata <- readRDS("positive_results_in_registered_reports_codebook.rds")
-
-# remove excluded papers
-included <- alldata[alldata$include_in_analysis==1,]
-
-
-##==============================================================================##
-## 1. Calculate inter-rater agreement (between MS and AS) for main 
-##    variable (support_binary)
-##==============================================================================##
-
-## 1.1 Calculate number of papers coded by MS and AS, respectively, and
-##     number of double-coded papers
-
-# number of papers coded by MS: 221 out of 223 = 99.10%
-support.coded.MS <- sum(included$coded_by_MS)
-# number of papers coded by AS: 71 out of 223 = 31.83%
-support.coded.AS <- sum(included$coded_by_AS)
-
-# number of RRs coded by AS: 24 out of 71 = 33.8%
-sum(included$coded_by_AS & included$is_RR)/sum(included$is_RR)
-# number of SRs coded by AS: 47 out of 152 = 30.9%
-sum(included$coded_by_AS & !included$is_RR)/sum(!included$is_RR)
-
-# number of papers double coded: 69 out of 223 = 30.94%
-support.doublecoded <- length(which(included$coded_by_MS == 1 & 
-                                      included$coded_by_AS ==1))
-
-
-## 1.2 Calculate number of 'minor' disagreements, i.e. disagreement 
-##     between full and partial support (no consequences for final analysis)
-
-# Minor disagreement occurred in 15 out of 69 double-cded cases = 21.74%
-support.disagreement.minor <- length(which(
-                                      included$support_orig_MS == "support" & 
[…]

### 2020-01-10 power_baserate_plot.R

@@ -1,156 +1,0 @@
-#########################################################
-#####                                               #####
-##### Script 4: Calculate and plot power and the    #####
-#####           rate of true hypotheses for the     #####
-#####           observed positive result rates in   #####
-#####           the absence of bias                 #####
-#####                                               #####
-#####-----------------------------------------------#####
-#####                                               #####
-##### Content:                                      #####
-#####  * 1: Setup                                   #####
-#####  * 2: Functions to calculate power and rate   #####
-#####       of true hypotheses                      #####
-#####  * 3: Plot functions with observed positive   #####
-#####       result rates as input                   #####
-#####                                               #####
-##### Note:                                         #####
-#####   RR = Registered Report                      #####
-#####   SR = standard report                        #####
-#####   PRR = positive result rate                  #####
-#####                                               #####
-#########################################################
-
-##==============================================================================##
-## 1. Setup: load packages and data 
-##==============================================================================##
-
-# The ggplot2 packages is needed to create the plot. Install it, if needed, by 
-# uncommenting the following line:
-# install.packages("ggplot2")
-
-# Load ggplot2:
-library(ggplot2)
-
-# Load data: Creating the plot requires input from the main analysis script
-# (quantitative_analyses.R). In the RMarkdown file for the manuscript, this
-# script is already loaded when the code below is run. The respective variables
-# are *not* hard-coded or recalculated here to avoid errors or inconsistencies
-# if any changes to the data or main analysis script should be made in the future.
-# Therefore, if you wish to run this script outside of the RMarkdown environment 
-# of the manuscript, you first need to load the main analysis script (and with it,
-# the data). Adjust the code to load the script if necessary.
-source("quantitative_analyses.R")
-
-
-##==============================================================================##
-## 2. Functions to calculate power and rate of true hypotheses 
[…]

### 2020-01-10 quantitative_analyses.R

@@ -1,295 +1,0 @@
-#########################################################
-#####                                               #####
-##### Script 2: Quantitative analyses               #####
-#####           (confirmatory and exploratory)      #####
-#####                                               #####
-#####-----------------------------------------------#####
-#####                                               #####
-##### Content:                                      #####
-#####  * 1: Setup                                   #####
-#####  * 2: Main confirmatory analysis:             #####
-#####       positive result rate in Registered      #####
-#####       Reports compared to standard reports    #####
-#####  * 3: Exploratory analysis:                   #####
-#####       positive result rate in replication     #####
-#####       studies compared to original studies    #####
-#####  * 4: Excploratory analysis:                  #####
-#####       positive result rate in standard        #####
-#####       reports compared to Fanelli (2010)      #####
-#####                                               #####
-##### Note:                                         #####
-#####   RR = Registered Report                      #####
-#####   SR = standard report                        #####
-#####                                               #####
-#########################################################
-
-##==============================================================================##
-## 1. Setup: load packages and data 
-##==============================================================================##
-
-# Three packages are needed: TOSTER to calculate equivalence tests, ggplot2 for
-# creating the plot for Figure 2 in the manuscript, and papaja for Table 1 in 
-# the manuscript. papaja was not yet on CRAN when this was written and has to 
-# be installed from Github, using the devtools package. Its role in this script
-# is very minor though -- all analyses can be reproduced without papaja.
-
-# Install packages if needed by uncommenting the respective line(s):
-# install.packages("TOSTER")  # install TOSTER
-# install.packages("ggplot2")  # install ggplot2
-# install.packages("devtools")  # install devtools to install papaja
-# devtools::install_github("crsh/papaja")  # install papaja
-
-# Load packages:
-library("TOSTER")
-library("ggplot2")
-library("papaja")
-
-
-# load the dataset from the RDS file created with codebook
[…]

### 2020-01-10 raw_data/source_data/SR_sample_and_resample.R

@@ -1,0 +1,18 @@
+# Load all 1919 search results
+allSRs <- read.csv("SR_search_results_WoS_20190107.csv")
+
+# Draw a random sample of 150 papers and put them into a new dataframe
+set.seed(20190120)
+x <- sample(c(1:1919), 150)
+SRsample <- allSRs[x, ]
+
+# Sample 8 additional papers and put them into a new dataframe
+set.seed(20190120)
+replacement <- sample(c(1:1919), 158)[151:158]
+SRreplacement <- allSRs[replacement, ]
+
+# Sample 1 additional paper and put it into a new dataframe
+set.seed(20190120)
+replacement2 <- sample(c(1:1919), 159)[159]
+SRreplacement2 <- allSRs[replacement2, ]
+

### 2020-01-10 source_data/SR_sample_and_resample.R

@@ -1,18 +1,0 @@
-# Load all 1919 search results
-allSRs <- read.csv("SR_search_results_WoS_20190107.csv")
-
-# Draw a random sample of 150 papers and put them into a new dataframe
-set.seed(20190120)
-x <- sample(c(1:1919), 150)
-SRsample <- allSRs[x, ]
-
-# Sample 8 additional papers and put them into a new dataframe
-set.seed(20190120)
-replacement <- sample(c(1:1919), 158)[151:158]
-SRreplacement <- allSRs[replacement, ]
-
-# Sample 1 additional paper and put it into a new dataframe
-set.seed(20190120)
-replacement2 <- sample(c(1:1919), 159)[159]
-SRreplacement2 <- allSRs[replacement2, ]
-

### 2020-01-11 manuscript/manuscript.Rmd
Added figure captions/notes; minor fixes

@@
   - \usepackage{setspace}
+  - \captionsetup[figure]{font={stretch=1, footnotesize}}
   - \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
@@
 We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
-An overview of the sampling process and all exclusions are shown in Figure 1.
+An overview of the sampling process and all exclusions are shown in Figure\ \@ref(fig:sampling).
 
@@
 Using the same sample size as @Fanelli2010, we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed "20190120" (not specified in our preregistration, but no other seeds were tried).
-We initially excluded eight papers and replaced them (the decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had erroneously been excluded, leading to a final sample size of 152 rather than 150 (see Fig.
-1).
+We initially excluded eight papers and replaced them (the decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had erroneously been excluded, leading to a final sample size of 152 rather than 150 (see Fig.\ \@ref(fig:sampling)).
 
-```{r echo=FALSE, warning=FALSE, fig.cap="XXX ADD CAPTION", out.width = "\\textwidth"}
+(ref:sampling) Sampling process and exclusions for standard reports and Registered Reports.
+Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded.
+"Preregistered": study had been preregistered but was not a full RR; "results-blind review": article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); "ambiguous": Four of these had been treated as RRs but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance.
+We chose to exclude these cases to be conservative.
 
-knitr::include_graphics("Sampling_exclusions_and_resampling.pdf")
+```{r sampling, echo=FALSE, warning=FALSE, fig.cap = "(ref:sampling)", out.width = "\\textwidth"}
+
+knitr::include_graphics("Sampling_exclusions_and_resampling.png")
 ```
@@
 For Registered Reports we aimed to include all published RRs in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase "test$^\ast$ the hypothes$^\ast$".
-We downloaded a database of published RRs curated by the Center for Open Science[^1] (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than "Psychiatry/Psychology" or "Multidisciplinary" in the ESI.
-[^1]: https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9 
+We downloaded a database of published RRs curated by the Center for Open Science^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than "Psychiatry/Psychology" or "Multidisciplinary" in the ESI.
 Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 RRs published in Cortex because the ESI counts this journal towards the separate category "Neuroscience and Behavior".
@@
 For papers not clearly labelled as RRs we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly. 
-Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig.
-1).
-Note that we excluded all eight "Registered Replication Reports" [RRRs; @Simons2014; @Simons2018] in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing [@RRRwebsite; decision was not preregistered].
+Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig.\ \@ref(fig:sampling)).
+Note that we excluded all eight "Registered Replication Reports" [RRRs; @Simons2014; @Simons2018] in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing [@RRRwebsite, decision was not preregistered].
 
@@
 
-`r n.support.SR` out of `r n.SR` SRs and `r n.support.RR` out of `r n.RR` RRs had positive results, meaning that the positive result rate was $`r printnum(prop.support.SR*100)` \%$ for SRs ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]) and $`r printnum(prop.support.RR*100)` \%$ for RRs ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]; see Fig.
-1).
+`r n.support.SR` out of `r n.SR` SRs and `r n.support.RR` out of `r n.RR` RRs had positive results, meaning that the positive result rate was $`r printnum(prop.support.SR*100)` \%$ for SRs ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]) and $`r printnum(prop.support.RR*100)` \%$ for RRs ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]; see Fig.\ \@ref(fig:mainplot)).
 The preregistered one-sided proportions test with an alpha level of $5\%$ showed that this difference of $-`r printnum((prop.support.SR-prop.support.RR)*100)` \%$ was statistically significant, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
@@
 
-```{r echo=FALSE, warning=FALSE, fig.width=4, fig.height=3, fig.cap="Positive result rates for standard reports and Registered Reports.
-Error bars indicate 95% confidence intervals around the observed positive result rate."}
+(ref:mainplot) Positive result rates for standard reports and Registered Reports. Error bars indicate $95 \%$ confidence intervals around the observed positive result rate.
+
+```{r mainplot, echo=FALSE, warning=FALSE, fig.width=4, fig.height=3, fig.cap="(ref:mainplot)"}
 mainplot
@@
 Although replication RRs in our sample indeed had a lower positive result rate than original RRs (see Table 1), the difference between original SRs and original RRs -- $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$ -- was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(reptost$TOST_z1, reptost$TOST_z2))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
+
+(ref:table1) Positive results in original studies vs replication studies
+
 ```{r echo = FALSE, results = 'asis'}
@@
   , align = c("l", rep("r", 8))
-  , caption = "Positive results in original studies vs replication studies"
+  , caption = "(ref:table1)"
   , note = "SRs = standard reports, RRs = Registered Reports"
@@
 
+(ref:table2) Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)
+
 ```{r echo = FALSE, results = 'asis'}
@@
   , align = c("l", "l", rep("r", 3))
-  , caption = "Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)"
-  , note = "This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four."
+  , caption = "(ref:table2)"
+  , note = "Table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four."
   , added_stub_head = "Variables"
@@
 
+(ref:table3) Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)
+
 ```{r echo = FALSE, results = 'asis'}
@@
   , align = c("l", "l", "l", rep("r", 4))
-  , caption = "Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)"
+  , caption = "(ref:table3)"
   , note = "Table contains 53 hypothesis introduction phrases from 40 Registered Reports.
@@
 To explain the $`r printnum((prop.support.SR - prop.support.RR)*100)` \%$ gap between standard reports and Registered Reports, we must assume some combination of differences in bias, statistical power, or the proportion of true hypotheses researchers choose to examine.
-Figure 3 visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased. 
+Figure\ \@ref(fig:powerbaserate) visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
 For example, if we assume no publication bias and no QRPs, more than $90\%$ of the hypotheses authors of standard reports study must be true and study designs must have more than $90\%$ power for the true effect size.
@@
 
-```{r echo=FALSE, warning=FALSE, fig.width=6, fig.height=3, fig.cap="XXX ADD CAPTION"}
+(ref:powerbaserate) Combinations of the proportion of true hypotheses and statistical power that would produce the observed positive result rates given $\alpha = 5 \%$ and no bias.
+Shaded areas indicate $95\%$ confidence intervals.
+SRs = standard reports, RRs = Registered Reports, PRR = positive result rate.
+The curve for all SRs (i.e, including replications; $`r printnum(prop.support.SR*100)` \%$ positive results, $N = `r n.SR`$) is not shown because it is almost identical to the one for original SRs.
+Plotted values were calculated using the equation $PRR = \alpha*(1-t) + (1-\beta)*t$; with $PRR =$ positive result rate, $\alpha =$ probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), $1-\beta =$ probability of obtaining a positive result when testing a true hypothesis (power), and $t =$ proportion of true hypotheses; and solving for $t$ and $1-\beta$, respectively.
+
+```{r powerbaserate, echo=FALSE, warning=FALSE, fig.width=6, fig.height=3, fig.cap="(ref:powerbaserate"}
 source(here("analysis", "power_baserate_plot.R"))

### 2020-01-11 manuscript/manuscript.tex
1. added a robustness check to the quantitative analysis script, 2. reorganised the folder structure (in accordance with Psych-DS), 3. changed code in the manuscript Rmd and in the analysis scripts to accommodate the new folder structure, 4. added the preregistration document with comments indicating adherence/deviations, 5. added a file with the full list of Psych journals from the ESI database
Added figure captions/notes; minor fixes

--- 2020-01-09 manuscript.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
 \PassOptionsToPackage{hyphens}{url}
 %
-\documentclass[
-  british,
-  ,man,floatsintext]{apa6}
+\documentclass[british,,man,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
+  \usepackage{textcomp} % provides euro and other symbols
+\else % if luatex or xelatex
   \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
-% Use upquote if available, for straight quotes in verbatim environments
+% use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
+% use microtype if available
+\IfFileExists{microtype.sty}{%
 \usepackage[]{microtype}
@@
 }{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
 \IfFileExists{parskip.sty}{%
@@
 \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\usepackage{hyperref}
 \hypersetup{
@@
             pdfauthor={Anne Scheel, Mitchell Schijen, \& Daniël Lakens},
-  pdflang={en-UK},
             pdfkeywords={keyword 1, keyword 2, keyword 3},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+% set default figure placement to htbp
 \makeatletter
@@
 \makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+
 \shorttitle{Positive Results in Registered Reports}
@@
 \usepackage{setspace}
+\captionsetup[figure]{font={stretch=1, footnotesize}}
 \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
@@
 \floatname{textbox}{Box}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=british]{babel}
+\else
+  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
   \usepackage{polyglossia}
   \setmainlanguage[variant=british]{english}
-\else
-  \usepackage[shorthands=off,main=british]{babel}
 \fi
@@
 Sterling (1959) already suspected a selection process behind the numbers he found:
-\enquote{(\ldots) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of {[}statistical{]} significance} (p.~31).
+\enquote{(\ldots{}) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of {[}statistical{]} significance} (p.~31).
 This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature.
@@
 We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
-An overview of the sampling process and all exclusions are shown in Figure 1.
+An overview of the sampling process and all exclusions are shown in Figure~\ref{fig:sampling}.
 
@@
 Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed \enquote{20190120} (not specified in our preregistration, but no other seeds were tried).
-We initially excluded eight papers and replaced them (the decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had erroneously been excluded, leading to a final sample size of 152 rather than 150 (see Fig.
-1).
+We initially excluded eight papers and replaced them (the decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had erroneously been excluded, leading to a final sample size of 152 rather than 150 (see Fig.~\ref{fig:sampling}).
 
 \begin{figure}
-\includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{XXX ADD CAPTION}\label{fig:unnamed-chunk-2}
+\includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{Sampling process and exclusions for standard reports and Registered Reports.
+Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded.
+\enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: Four of these had been treated as RRs but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance.
+We chose to exclude these cases to be conservative.}\label{fig:sampling}
 \end{figure}
@@
 For Registered Reports we aimed to include all published RRs in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
-We downloaded a database of published RRs curated by the Center for Open Science{[}\^{}1{]} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
-{[}\^{}1{]}: \url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}
+We downloaded a database of published RRs curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
 Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 RRs published in Cortex because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
@@
 For papers not clearly labelled as RRs we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
-Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig.
-1).
-Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing {[}(``Registered Replication Reports,'' n.d.); decision was not preregistered{]}.
+Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig.~\ref{fig:sampling}).
+Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).
 
@@
 We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all RRs and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
-If MS and AS had coded different hypothesis quotes for a paper, MS's coding was used, unless disagreement resolution of the \enquote{hypothesis support} variable lead to AS's coding overruling MS's.
+.
 
@@
 After an initial coding attempt with ill-defined coding criteria lead to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
-We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf.~Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
+We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf.
+Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
 Conceptual replications and internal replications were not counted as replications in this narrow sense:
@@
 
-146 out of 152 SRs and 31 out of 71 RRs had positive results, meaning that the positive result rate was \(96.05 \%\) for SRs (\(95 \%\) CI {[}91.61, 98.54{]}) and \(43.66 \%\) for RRs (\(95 \%\) CI {[}31.91, 55.95{]}; see Fig.
-1).
+146 out of 152 SRs and 31 out of 71 RRs had positive results, meaning that the positive result rate was \(96.05 \%\) for SRs (\(95 \%\) CI {[}91.61, 98.54{]}) and \(43.66 \%\) for RRs (\(95 \%\) CI {[}31.91, 55.95{]}; see Fig.~\ref{fig:mainplot}).
 The preregistered one-sided proportions test with an alpha level of \(5\%\) showed that this difference of \(-52.39 \%\) was statistically significant, \(\chi^2 = 77.96\), \(p < .001\).
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-5-1.pdf}
-\caption{\label{fig:unnamed-chunk-5}Positive result rates for standard reports and Registered Reports. Error bars indicate 95\% confidence intervals around the observed positive result rate.}
+\includegraphics{manuscript_files/figure-latex/mainplot-1.pdf}
+\caption{\label{fig:mainplot}Positive result rates for standard reports and Registered Reports. Error bars indicate \(95 \%\) confidence intervals around the observed positive result rate.}
 \end{figure}
@@
 \begin{threeparttable}
-\caption{\label{tab:unnamed-chunk-6}Positive results in original studies vs replication studies}
+\caption{\label{tab:unnamed-chunk-4}Positive results in original studies vs replication studies}
 \begin{tabular}{lrrrrrrrr}
@@
 \begin{threeparttable}
-\caption{\label{tab:unnamed-chunk-8}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}
+\caption{\label{tab:unnamed-chunk-6}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}
 \footnotesize{
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four.}
+\normalsize{\textit{Note.} Table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four.}
 \end{tablenotes}
@@
 \begin{threeparttable}
-\caption{\label{tab:unnamed-chunk-9}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
+\caption{\label{tab:unnamed-chunk-7}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
 \scriptsize{
@@
 The positive result rate we found in standard reports (\(96.05 \%\)) is slightly higher than the \(91.5\%\) reported by Fanelli (2010), although this difference was not statistically significant.
-Our replication in a more recent sample of the psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 (cf.~Fanelli, 2012).
+Our replication in a more recent sample of the psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 (cf.
+Fanelli, 2012).
 Furthermore, our estimate of the positive result rate for Registered Reports (\(43.66 \%\)) is comparable to the \(39.5\%\) reported by Allen \& Mehler (2019), despite some differences in method and studied population.
@@
 To explain the \(52.39 \%\) gap between standard reports and Registered Reports, we must assume some combination of differences in bias, statistical power, or the proportion of true hypotheses researchers choose to examine.
-Figure 3 visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
+Figure~\ref{fig:powerbaserate} visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
 For example, if we assume no publication bias and no QRPs, more than \(90\%\) of the hypotheses authors of standard reports study must be true and study designs must have more than \(90\%\) power for the true effect size.
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{\label{fig:unnamed-chunk-10}XXX ADD CAPTION}
+\includegraphics{manuscript_files/figure-latex/powerbaserate-1.pdf}
+\caption{\label{fig:powerbaserate}(ref:powerbaserate}
 \end{figure}
@@
 \leavevmode\hypertarget{ref-Chambers2013}{}%
-Chambers, C. D. (2013). Registered reports: A new publishing initiative at Cortex, \emph{49}(3), 609--610. Retrieved from \url{http://orca.cf.ac.uk/45177/1/Chambers_Cortex_2013b_GreenOA.pdf}
+Chambers, C. (2013). Registered reports: A new publishing initiative at Cortex, \emph{49}(3), 609--610. Retrieved from \url{http://orca.cf.ac.uk/45177/1/Chambers_Cortex_2013b_GreenOA.pdf}
 
 \leavevmode\hypertarget{ref-Chambers2015}{}%
-Chambers, C.
-D., Dienes, Z., McIntosh, R.
-D., Rotshtein, P., \& Willmes, K.
+Chambers, C., Dienes, Z., McIntosh, R., Rotshtein, P., \& Willmes, K.
 (2015).

### 2020-01-11 analysis/02_quantitative_analyses.R
Changed script names and improved Figure 2 and Figure 3

@@ -136,25 +136,32 @@ mainplot.df <- data.frame(is_RR = c("SR", "SR", "RR", "RR"),
                           upper = c(max(SR.binom$conf.int)*100, NA,
                                     max(RR.binom$conf.int)*100, NA))
 
+# Reorder the group levels so that SRs come first, RRs second
+mainplot.df$is_RR <- factor(mainplot.df$is_RR, levels = c("SR", "RR"))
+
 # Plot the main result (positive result rate in SRs vs RRs)
 mainplot <- ggplot(mainplot.df, aes(x = is_RR, y = value, fill = support)) +
                     geom_bar(stat = "identity", 
                              width = 0.5) +
                     scale_fill_manual(values= c("#bcbddc", "#756bb1"),
                                       name="first hypothesis") +
-                    annotate("text", label = "n = 152", x = 1, y = 105) +
-                    annotate("text", label = "n = 71", x = 2, y = 105) +
+                    annotate("text", label = paste("N =", n.SR), 
+                             x = 1, y = 105, size = 5) +
+                    annotate("text", label = paste("N =", n.RR), 
+                             x = 2, y = 105, size = 5) +
                     geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.05, size = 0.5) +
                     scale_x_discrete(breaks = waiver(), 
-                                     labels = c("SR" = "Standard\nReports (SRs)",
-                                                "RR" = "Registered\nReports (RRs)"), name = NULL)+ 
+                                     labels = c("SR" = "Standard\nReports",
+                                                "RR" = "Registered\nReports"), 
+                                     name = NULL)+ 
                     scale_y_continuous(lim=c(0,110), breaks = c(seq(0, 100, 10)),
                                        minor_breaks = c(seq(0, 100, 5)),
                                        name = "% of papers", expand = c(0, 0))+
-                    theme_minimal()+
+                    theme_minimal(base_size = 20)+
                     theme(panel.grid.major.x = element_blank(),
                           panel.grid.minor.x = element_blank(),
-                          legend.margin = margin(0,0,0,-5))
+                          legend.margin = margin(0,0,0,-5.5)) +
+                    coord_fixed(ratio=0.03)
 
 
 ##==============================================================================##

### 2020-01-11 analysis/04_power_baserate_plot.R

@@ -41,7 +41,7 @@ library(ggplot2)
 # of the manuscript, you first need to load the main analysis script (and with it,
 # the data). Adjust the code to load the script if necessary.
 
-# source("quantitative_analyses.R")
+# source("02_quantitative_analyses.R")
 
 
 ##==============================================================================##
@@ -84,41 +84,59 @@ a <- 0.05
 
 # Create dataframe for original SRs
 pwrprior.origSR <- data.frame(t=c(1:1000)/1000) # Enter values for t from .001 - 1
-pwrprior.origSR$group <- "original SRs (PRR = .9595, n = 148)" # group label (later used for plot)
+pwrprior.origSR$group <- "origSRs" # group label (later used for plot)
 
 # Calculate values for power (1-b) for all values of t and:
 # - for the lower end of the 95% CI for the positive result rate
 # - for the positive result rate estimate
 # - for the upper end of the 95% CI for the positive result rate
-pwrprior.origSR$lower <- pwrfun(t = pwrprior.origSR$t, a = a, PRR = min(SR.orig.binom$conf.int))
-pwrprior.origSR$estimate <- pwrfun(t = pwrprior.origSR$t, a = a, PRR = prop.orig.support.SR)
-pwrprior.origSR$upper <- pwrfun(t = pwrprior.origSR$t, a = a, PRR = max(SR.orig.binom$conf.int))   
+pwrprior.origSR$lower <- pwrfun(t = pwrprior.origSR$t, 
+                                a = a, 
+                                PRR = min(SR.orig.binom$conf.int))
+pwrprior.origSR$estimate <- pwrfun(t = pwrprior.origSR$t, 
+                                   a = a, 
+                                   PRR = prop.orig.support.SR)
+pwrprior.origSR$upper <- pwrfun(t = pwrprior.origSR$t, 
+                                a = a, 
+                                PRR = max(SR.orig.binom$conf.int))   
 
 
 # Create dataframe for original RRs
 pwrprior.origRR <- data.frame(t=c(1:1000)/1000) # Enter values for t from .001 - 1
-pwrprior.origRR$group <- "original RRs (PRR = .5, n = 30)" # group label (later used for plot)
+pwrprior.origRR$group <- "origRRs" # group label (later used for plot)
 
 # Calculate values for power (1-b) for all values of t and:
 # - for the lower end of the 95% CI for the positive result rate
 # - for the positive result rate estimate
[…]

### 2020-01-11 manuscript/manuscript.Rmd
Adjusted formatting to make the manuscript work in journal mode. Caution: I installed the development branch of papaja to allow column-spanning tables!

@@
   - \usepackage{setspace}
-  - \captionsetup[figure]{font={stretch=1, footnotesize}}
+  - \captionsetup[figure]{font={stretch=1, small}, skip=11pt}
   - \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
@@
 footnotelist      : no
-lineno            : yes
+lineno            : no
 
 lang              : "en-UK"
-class             : "man"
+class             : "jou"
 output            : papaja::apa6_pdf
@@
 
-```{r sampling, echo=FALSE, warning=FALSE, fig.cap = "(ref:sampling)", out.width = "\\textwidth"}
+```{r sampling, echo=FALSE, warning=FALSE, fig.cap = "(ref:sampling)", out.width = "\\textwidth", fig.env="figure*"}
 
@@
 ```{r include=FALSE}
-source(here("analysis", "interrater_agreement.R"))
+source(here("analysis", "01_interrater_agreement.R"))
 ```
@@
 ```{r include=FALSE}
-source(here("analysis", "quantitative_analyses.R"))
+source(here("analysis", "02_quantitative_analyses.R"))
 ```
@@
 
-```{r mainplot, echo=FALSE, warning=FALSE, fig.width=4, fig.height=3, fig.cap="(ref:mainplot)"}
+```{r mainplot, echo=FALSE, warning=FALSE, fig.height=5, fig.cap="(ref:mainplot)"}
 mainplot
@@
 ```{r include=FALSE}
-source(here("analysis", "hypothesis_introduction_analyses.R"))
+source(here("analysis", "03_hypothesis_introduction_analyses.R"))
 ```
@@
   , landscape = FALSE
-  , font_size = "scriptsize"
+  , font_size = "footnotesize"
   , escape = TRUE
@@
 Shaded areas indicate $95\%$ confidence intervals.
-SRs = standard reports, RRs = Registered Reports, PRR = positive result rate.
+SRs = standard reports, RRs = Registered Reports.
 The curve for all SRs (i.e, including replications; $`r printnum(prop.support.SR*100)` \%$ positive results, $N = `r n.SR`$) is not shown because it is almost identical to the one for original SRs.
@@
 
-```{r powerbaserate, echo=FALSE, warning=FALSE, fig.width=6, fig.height=3, fig.cap="(ref:powerbaserate"}
-source(here("analysis", "power_baserate_plot.R"))
+```{r powerbaserate, echo=FALSE, fig.width=5, fig.height=3, fig.align='center', warning=FALSE, fig.cap="(ref:powerbaserate)",   out.width = "0.6\\textwidth", fig.env="figure*"}
+source(here("analysis", "04_power_baserate_plot.R"))
 power.baserate.plot

### 2020-01-11 manuscript/manuscript.tex
Adjusted formatting to make the manuscript work in journal mode. Caution: I installed the development branch of papaja to allow column-spanning tables!

@@
 %
-\documentclass[british,,man,floatsintext]{apa6}
+\documentclass[british,,jou,floatsintext]{apa6}
 \usepackage{lmodern}
@@
             pdftitle={Positive Results in Registered Reports},
-            pdfauthor={Anne Scheel, Mitchell Schijen, \& Daniël Lakens},
             pdfkeywords={keyword 1, keyword 2, keyword 3},
@@
 
-\shorttitle{Positive Results in Registered Reports}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Eindhoven University of Technology}
-\keywords{keyword 1, keyword 2, keyword 3\newline\indent Word count: XXX}
+% Manuscript styling
 \usepackage{csquotes}
@@
 
+% Table formatting
 \usepackage{longtable}
 \usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
-
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
 \newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
 \makeatletter
@@
 
-\usepackage{lineno}
-
-\linenumbers
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\makeatother
+\shorttitle{Positive Results in Registered Reports}
+\author{Anne Scheel\textsuperscript{1}, Mitchell Schijen\textsuperscript{1}, \& Daniël Lakens\textsuperscript{1}}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Eindhoven University of Technology}
+\authornote{
+
+Correspondence concerning this article should be addressed to Anne Scheel, Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands. E-mail: a.m.scheel@tue.nl}
+\note{\textbackslash{}clearpage}
+\keywords{keyword 1, keyword 2, keyword 3\newline\indent Word count: XXX}
+\usepackage{dblfloatfix}
+
 \usepackage{float}
@@
 \usepackage{setspace}
-\captionsetup[figure]{font={stretch=1, footnotesize}}
+\captionsetup[figure]{font={stretch=1, small}, skip=11pt}
 \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
@@
 \title{Positive Results in Registered Reports}
-\author{Anne Scheel\textsuperscript{1}, Mitchell Schijen\textsuperscript{1}, \& Daniël Lakens\textsuperscript{1}}
+
 \date{}
 
-\authornote{
-
-Correspondence concerning this article should be addressed to Anne Scheel, Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands.
-E-mail: \href{mailto:a.m.scheel@tue.nl}{\nolinkurl{a.m.scheel@tue.nl}}}
-\note{\clearpage}
 \abstract{
 XXXXXXXXXXXXXXXXXXX
-
 }
@@
 
-\begin{figure}
+\begin{figure*}
 \includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{Sampling process and exclusions for standard reports and Registered Reports.
@@
 We chose to exclude these cases to be conservative.}\label{fig:sampling}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{table}[tbp]
+\begin{table*}[tbp]
+
 \begin{center}
 \begin{threeparttable}
+
 \caption{\label{tab:unnamed-chunk-4}Positive results in original studies vs replication studies}
+
 \begin{tabular}{lrrrrrrrr}
@@
 \end{tabular}
+
 \begin{tablenotes}[para]
@@
 \end{tablenotes}
+
 \end{threeparttable}
 \end{center}
-\end{table}
+
+\end{table*}
 
@@
 
-\begin{table}[tbp]
+\begin{table*}[tbp]
+
 \begin{center}
 \begin{threeparttable}
+
 \caption{\label{tab:unnamed-chunk-6}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}
+
 \footnotesize{
+
 \begin{tabular}{llrrr}
@@
 \end{tabular}
+
 }
+
 \begin{tablenotes}[para]
@@
 \end{tablenotes}
+
 \end{threeparttable}
 \end{center}
-\end{table}
-
-\begin{table}[tbp]
+
+\end{table*}
+
+\begin{table*}[tbp]
+
 \begin{center}
 \begin{threeparttable}
+
 \caption{\label{tab:unnamed-chunk-7}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
-\scriptsize{
+
+\footnotesize{
+
 \begin{tabular}{lllrrrr}
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/powerbaserate-1.pdf}
-\caption{\label{fig:powerbaserate}(ref:powerbaserate}
-\end{figure}
+\begin{figure*}
+
+{\centering \includegraphics[width=0.6\textwidth]{manuscript_files/figure-latex/powerbaserate-1}
+
+}
+
+\caption{Combinations of the proportion of true hypotheses and statistical power that would produce the observed positive result rates given \(\alpha = 5 \%\) and no bias.
+Shaded areas indicate \(95\%\) confidence intervals.
+SRs = standard reports, RRs = Registered Reports.
+The curve for all SRs (i.e, including replications; \(96.05 \%\) positive results, \(N = 152\)) is not shown because it is almost identical to the one for original SRs.
+Plotted values were calculated using the equation \(PRR = \alpha*(1-t) + (1-\beta)*t\); with \(PRR =\) positive result rate, \(\alpha =\) probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), \(1-\beta =\) probability of obtaining a positive result when testing a true hypothesis (power), and \(t =\) proportion of true hypotheses; and solving for \(t\) and \(1-\beta\), respectively.}\label{fig:powerbaserate}
+\end{figure*}
 
@@
 \emph{PLOS ONE}, \emph{12}(3), e0172792.
-doi:\href{https://doi.org/10.1371/journal.pone.0172792}{10.1371/journal.pone.0172792}
+\url{https://doi.org/10.1371/journal.pone.0172792}
 
@@
 \emph{PLOS Biology}, \emph{17}(5), e3000246.
-doi:\href{https://doi.org/10.1371/journal.pbio.3000246}{10.1371/journal.pbio.3000246}
+\url{https://doi.org/10.1371/journal.pbio.3000246}
 
@@
 \emph{Journal of Counseling Psychology}, \emph{29}(2), 189--194.
-doi:\href{https://doi.org/10.1037/0022-0167.29.2.189}{10.1037/0022-0167.29.2.189}
+\url{https://doi.org/10.1037/0022-0167.29.2.189}
 
@@
 \emph{Cortex}, \emph{66}, 1--2.
-doi:\href{https://doi.org/10.1016/j.cortex.2015.03.022}{10.1016/j.cortex.2015.03.022}
+\url{https://doi.org/10.1016/j.cortex.2015.03.022}
 
 \leavevmode\hypertarget{ref-OSC2015}{}%
-Collaboration, O.
-S.
-(2015).
-Estimating the reproducibility of psychological science.
-\emph{Science}, \emph{349}(6251), aac4716.
-doi:\href{https://doi.org/10.1126/science.aac4716}{10.1126/science.aac4716}
+Collaboration, O. S. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716. \url{https://doi.org/10.1126/science.aac4716}
 
@@
 \emph{PLOS ONE}, \emph{13}(5), e0197440.
-doi:\href{https://doi.org/10.1371/journal.pone.0197440}{10.1371/journal.pone.0197440}
+\url{https://doi.org/10.1371/journal.pone.0197440}
 
 \leavevmode\hypertarget{ref-Fanelli2010}{}%
-Fanelli, D.
-(2010).
-"Positive" results increase down the hierarchy of the sciences.
-\emph{PLoS ONE}, \emph{5}(4), e10068.
-doi:\href{https://doi.org/10.1371/journal.pone.0010068}{10.1371/journal.pone.0010068}
+Fanelli, D. (2010). "Positive" results increase down the hierarchy of the sciences. \emph{PLoS ONE}, \emph{5}(4), e10068. \url{https://doi.org/10.1371/journal.pone.0010068}
 
 \leavevmode\hypertarget{ref-Fanelli2012}{}%
-Fanelli, D.
-(2012).
-Negative results are disappearing from most disciplines and countries.
-\emph{Scientometrics}, \emph{90}(3), 891--904.
-doi:\href{https://doi.org/10.1007/s11192-011-0494-7}{10.1007/s11192-011-0494-7}
+Fanelli, D. (2012). Negative results are disappearing from most disciplines and countries. \emph{Scientometrics}, \emph{90}(3), 891--904. \url{https://doi.org/10.1007/s11192-011-0494-7}
 
 \leavevmode\hypertarget{ref-Fiedler2016}{}%
-Fiedler, K., \& Schwarz, N.
-(2016).
-Questionable Research Practices Revisited.
-\emph{Social Psychological and Personality Science}, \emph{7}(1), 45--52.
-doi:\href{https://doi.org/10.1177/1948550615612150}{10.1177/1948550615612150}
+Fiedler, K., \& Schwarz, N. (2016). Questionable Research Practices Revisited. \emph{Social Psychological and Personality Science}, \emph{7}(1), 45--52. \url{https://doi.org/10.1177/1948550615612150}
 
@@
 \emph{Science}, \emph{345}(6203), 1502--1505.
-doi:\href{https://doi.org/10.1126/science.1255484}{10.1126/science.1255484}
+\url{https://doi.org/10.1126/science.1255484}
 
@@
 \emph{Social Psychological and Personality Science}, \emph{7}(1), 8--12.
-doi:\href{https://doi.org/10.1177/1948550615598377}{10.1177/1948550615598377}
+\url{https://doi.org/10.1177/1948550615598377}
 
@@
 \emph{Psychological Science}, \emph{23}(5), 524--532.
-doi:\href{https://doi.org/10.1177/0956797611430953}{10.1177/0956797611430953}
+\url{https://doi.org/10.1177/0956797611430953}
 
@@
 \emph{Comprehensive Results in Social Psychology}, \emph{1}(1-3), 1--7.
-doi:\href{https://doi.org/10.1080/23743603.2015.1070611}{10.1080/23743603.2015.1070611}
+\url{https://doi.org/10.1080/23743603.2015.1070611}
 
 \leavevmode\hypertarget{ref-Kerr1998}{}%
-Kerr, N.
-L.
-(1998).
-HARKing: Hypothesizing after the results are known.
-\emph{Personality and Social Psychology Review}, \emph{2}(3), 196--217.
-doi:\href{https://doi.org/10.1207/s15327957pspr0203_4}{10.1207/s15327957pspr0203\_4}
+Kerr, N. L. (1998). HARKing: Hypothesizing after the results are known. \emph{Personality and Social Psychology Review}, \emph{2}(3), 196--217. \url{https://doi.org/10.1207/s15327957pspr0203_4}
 
@@
 \emph{Journal of Management}, 014920631984398.
-doi:\href{https://doi.org/10.1177/0149206319843985}{10.1177/0149206319843985}
+\url{https://doi.org/10.1177/0149206319843985}
 
 \leavevmode\hypertarget{ref-Lakens2019b}{}%
-Lakens, D. (n.d.). The Value of Preregistration for Psychological Science: A Conceptual Analysis. doi:\href{https://doi.org/10.31234/osf.io/jbh4w}{10.31234/osf.io/jbh4w}
+Lakens, D. (n.d.). The Value of Preregistration for Psychological Science: A Conceptual Analysis. \url{https://doi.org/10.31234/osf.io/jbh4w}
 
@@
 \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269.
-doi:\href{https://doi.org/10.1016/j.ympev.2015.01.015}{10.1016/j.ympev.2015.01.015}
+\url{https://doi.org/10.1016/j.ympev.2015.01.015}
 
@@
 \emph{Cognitive Therapy and Research}, \emph{1}(2), 161--175.
-doi:\href{https://doi.org/10.1007/BF01173636}{10.1007/BF01173636}
+\url{https://doi.org/10.1007/BF01173636}
 
@@
 \emph{Perspectives on Psychological Science}.
-doi:\href{https://doi.org/10.1177/1745691612460688}{10.1177/1745691612460688}
+\url{https://doi.org/10.1177/1745691612460688}
 
@@
 \emph{Psychological Methods}, \emph{9}(2), 147--163.
-doi:\href{https://doi.org/10.1037/1082-989X.9.2.147}{10.1037/1082-989X.9.2.147}
+\url{https://doi.org/10.1037/1082-989X.9.2.147}
 
@@
 \emph{Journal of Personality and Social Psychology}, \emph{113}(1), 34--58.
-doi:\href{https://doi.org/10.1037/pspa0000084}{10.1037/pspa0000084}
+\url{https://doi.org/10.1037/pspa0000084}
 
@@
 \emph{Research Policy}, \emph{48}(1), 62--83.
-doi:\href{https://doi.org/10.1016/j.respol.2018.07.019}{10.1016/j.respol.2018.07.019}
+\url{https://doi.org/10.1016/j.respol.2018.07.019}
 
@@
 \emph{Social Psychology}, \emph{45}(3), 137--141.
-doi:\href{https://doi.org/10.1027/1864-9335/a000192}{10.1027/1864-9335/a000192}
+\url{https://doi.org/10.1027/1864-9335/a000192}
 
@@
 \emph{Annual Review of Criminology}, \emph{1}(1), 19--38.
-doi:\href{https://doi.org/10.1146/annurev-criminol-032317-091849}{10.1146/annurev-criminol-032317-091849}
+\url{https://doi.org/10.1146/annurev-criminol-032317-091849}
 
 \leavevmode\hypertarget{ref-RRRwebsite}{}%
-\emph{Registered Replication Reports}. (n.d.). \emph{Association for Psychological Science - APS}. Retrieved December 28, 2019, from \url{https://www.psychologicalscience.org/publications/replication}
+Registered Replication Reports. (n.d.). Retrieved December 28, 2019, from \url{https://www.psychologicalscience.org/publications/replication}
 
@@
 \leavevmode\hypertarget{ref-Rosenthal1979}{}%
-Rosenthal, R.
-(1979).
-The file drawer problem and tolerance for null results.
-\emph{Psychological Bulletin}, \emph{86}(3), 638--641.
-doi:\href{https://doi.org/10.1037/0033-2909.86.3.638}{10.1037/0033-2909.86.3.638}
+Rosenthal, R. (1979). The file drawer problem and tolerance for null results. \emph{Psychological Bulletin}, \emph{86}(3), 638--641. \url{https://doi.org/10.1037/0033-2909.86.3.638}
 
@@
 \emph{Psychological Science}, \emph{22}(11), 1359--1366.
-doi:\href{https://doi.org/10.1177/0956797611417632}{10.1177/0956797611417632}
+\url{https://doi.org/10.1177/0956797611417632}
 
@@
 \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(1), 3--6.
-doi:\href{https://doi.org/10.1177/2515245918757424}{10.1177/2515245918757424}
+\url{https://doi.org/10.1177/2515245918757424}
 
@@
 \emph{Perspectives on Psychological Science}, \emph{9}(5), 552--555.
-doi:\href{https://doi.org/10.1177/1745691614543974}{10.1177/1745691614543974}
+\url{https://doi.org/10.1177/1745691614543974}
 
@@
 \emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.
-doi:\href{https://doi.org/10.1080/01621459.1959.10501497}{10.1080/01621459.1959.10501497}
+\url{https://doi.org/10.1080/01621459.1959.10501497}
 
@@
 \emph{The American Statistician}, \emph{49}(1), 108.
-doi:\href{https://doi.org/10.2307/2684823}{10.2307/2684823}
+\url{https://doi.org/10.2307/2684823}
 
@@
 \emph{PLOS Biology}, \emph{15}(3), e2000797.
-doi:\href{https://doi.org/10.1371/journal.pbio.2000797}{10.1371/journal.pbio.2000797}
+\url{https://doi.org/10.1371/journal.pbio.2000797}
 
@@
 \emph{PLOS ONE}, \emph{9}(1), e84896.
-doi:\href{https://doi.org/10.1371/journal.pone.0084896}{10.1371/journal.pone.0084896}
+\url{https://doi.org/10.1371/journal.pone.0084896}
 
@@
 \emph{PLOS ONE}, \emph{8}(6), e66463.
-doi:\href{https://doi.org/10.1371/journal.pone.0066463}{10.1371/journal.pone.0066463}
+\url{https://doi.org/10.1371/journal.pone.0066463}
 
 \leavevmode\hypertarget{ref-Wiseman2019}{}%
-Wiseman, R., Watt, C., \& Kornbrot, D. (2019). Registered reports: An early example and analysis. \emph{PeerJ}, \emph{7}, e6232. doi:\href{https://doi.org/10.7717/peerj.6232}{10.7717/peerj.6232}
+Wiseman, R., Watt, C., \& Kornbrot, D. (2019). Registered reports: An early example and analysis. \emph{PeerJ}, \emph{7}, e6232. \url{https://doi.org/10.7717/peerj.6232}
 

### 2020-01-11 analysis/02_quantitative_analyses.R
minor changes to mainplot

@@ -146,10 +146,11 @@ mainplot <- ggplot(mainplot.df, aes(x = is_RR, y = value, fill = support)) +
                     scale_fill_manual(values= c("#bcbddc", "#756bb1"),
                                       name="first hypothesis") +
                     annotate("text", label = paste("N =", n.SR), 
-                             x = 1, y = 105, size = 5) +
+                             x = 1, y = 105) +
                     annotate("text", label = paste("N =", n.RR), 
-                             x = 2, y = 105, size = 5) +
-                    geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.05, size = 0.5) +
+                             x = 2, y = 105) +
+                    geom_errorbar(aes(ymin = lower, ymax = upper), 
+                                  width = 0.05, size = 0.5) +
                     scale_x_discrete(breaks = waiver(), 
                                      labels = c("SR" = "Standard\nReports",
                                                 "RR" = "Registered\nReports"), 
@@ -157,7 +158,7 @@ mainplot <- ggplot(mainplot.df, aes(x = is_RR, y = value, fill = support)) +
                     scale_y_continuous(lim=c(0,110), breaks = c(seq(0, 100, 10)),
                                        minor_breaks = c(seq(0, 100, 5)),
                                        name = "% of papers", expand = c(0, 0))+
-                    theme_minimal(base_size = 20)+
+                    theme_minimal()+
                     theme(panel.grid.major.x = element_blank(),
                           panel.grid.minor.x = element_blank(),
                           legend.margin = margin(0,0,0,-5.5)) +

### 2020-01-11 manuscript/manuscript.Rmd
Added disclosures and R citations

@@
 footnotelist      : no
-lineno            : no
+lineno            : yes
 
 lang              : "en-UK"
-class             : "jou"
+class             : "man"
 output            : papaja::apa6_pdf
@@
 library("TOSTER")
-library("purrr")
-library("lattice")
 library("ggplot2")
-library("dplyr")
 library("stringr")
@@
 library("here")
+library("codebook")
 ```
@@
 Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is [typically, though not always, leading to an inflated type-I error rate, see also @Lakens2019b].
-These include presenting unexpected results as having been predicted a priori [HARKing, short for "hypothesising after results are known"; @Kerr1998] and exploiting flexibility in data analysis to obtain statistically significant results ["p-hacking"; @Simmons2011].
+These include presenting unexpected results as having been predicted a priori [HARKing, short for "hypothesising after results are known"; @Kerr1998] and exploiting flexibility in data analysis to obtain statistically significant results ["*p*-hacking"; @Simmons2011].
 Evidence for both categories of bias exist: 
@@
 
-```{r sampling, echo=FALSE, warning=FALSE, fig.cap = "(ref:sampling)", out.width = "\\textwidth", fig.env="figure*"}
+```{r sampling, echo=FALSE, warning=FALSE, fig.cap = "(ref:sampling)", out.width = "\\textwidth"}
+
+# Important additional chunk option when using journal mode: fig.env="figure*"
 
@@
 
-```{r mainplot, echo=FALSE, warning=FALSE, fig.height=5, fig.cap="(ref:mainplot)"}
+```{r mainplot, echo=FALSE, warning=FALSE, fig.height=4, fig.cap="(ref:mainplot)"}
 mainplot
+
+#####
+# Important alternative code and settings when using journal mode:
+# 1. set fig.height=5 in chunk options
+# 2. use the plot code below instead of `mainplot`
+#    (otherwise font will be too small)!
+#
+# ggplot(mainplot.df, aes(x = is_RR, y = value, fill = support)) +
+#                     geom_bar(stat = "identity", 
+#                              width = 0.5) +
+#                     scale_fill_manual(values= c("#bcbddc", "#756bb1"),
+#                                       name="first hypothesis") +
+#                     annotate("text", label = paste("N =", n.SR), 
+#                              x = 1, y = 105, size = 5) +
+#                     annotate("text", label = paste("N =", n.RR), 
+#                              x = 2, y = 105, size = 5) +
+#                     geom_errorbar(aes(ymin = lower, ymax = upper), 
+#                                   width = 0.05, size = 0.5) +
+#                     scale_x_discrete(breaks = waiver(), 
+#                                      labels = c("SR" = "Standard\nReports",
+#                                                 "RR" = "Registered\nReports"), 
+#                                      name = NULL)+ 
+#                     scale_y_continuous(lim=c(0,110), breaks = c(seq(0, 100, 10)),
+#                                        minor_breaks = c(seq(0, 100, 5)),
+#                                        name = "% of papers", expand = c(0, 0))+
+#                     theme_minimal(base_size = 20)+
+#                     theme(panel.grid.major.x = element_blank(),
+#                           panel.grid.minor.x = element_blank(),
+#                           legend.margin = margin(0,0,0,-5.5)) +
+#                     coord_fixed(ratio=0.03)
 ```
@@
 ```{r echo = FALSE, results = 'asis'}
+# Important alternative settings when using journal mode: font_size = "footnotesize"
 apa_table(
@@
   , landscape = FALSE
-  , font_size = "footnotesize"
+  , font_size = "scriptsize"
   , escape = TRUE
@@
 
-```{r powerbaserate, echo=FALSE, fig.width=5, fig.height=3, fig.align='center', warning=FALSE, fig.cap="(ref:powerbaserate)",   out.width = "0.6\\textwidth", fig.env="figure*"}
+```{r powerbaserate, echo=FALSE, fig.width=5, fig.height=3, fig.align='center', warning=FALSE, fig.cap="(ref:powerbaserate)", out.width = "0.8\\textwidth"}
+
+# Important altrnative chunk options when using journal mode: 
+# 1. use out.width="0.6\\textwidth"
+# 2. set fig.env="figure*"
+
 source(here("analysis", "04_power_baserate_plot.R"))
@@
 
+```{r include=FALSE}
+r_refs(file = "prr_software.bib")
+my_citation <- cite_r(file = "prr_software.bib")
+```
+
+## Disclosures
+### Data, materials, and online resources
+The data and code necessary to reproduce all analyses reported here, as well as additional supplementary information, is available at <https://osf.io/dbhgr>.
+The manuscript, including the figures and statistical analyses, was created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.
+
+### Conflicts of Interest
+The authors declare that they have no conflicts of interest with respect to the authorship or the publication of this article.
+
+### Author Contributions
+Conceptualisation: A.S.
+and D.L.; data curation, formal analysis, and software: A.S.
+and M.S.; investigation, methodology, and validation: A.S., M.S., and D.L; supervision: A.S and D.L.; visualisation and writing -- original draft: A.S; writing -- review and editing: A.S., M.S., and D.L.
+
+### Acknowledgments
+This work was funded by VIDI grant 452-17-013. We would like to thank Stuart Ritchie for valuable comments that helped improve this manuscript.
+
 # References

### 2020-01-11 manuscript/manuscript.tex
Added disclosures and R citations

@@
 %
-\documentclass[british,,jou,floatsintext]{apa6}
+\documentclass[british,,man,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 \keywords{keyword 1, keyword 2, keyword 3\newline\indent Word count: XXX}
-\usepackage{dblfloatfix}
-
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{float}
@@
 Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate, see also Lakens, n.d.).
-These include presenting unexpected results as having been predicted a priori (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``p-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
+These include presenting unexpected results as having been predicted a priori (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
 Evidence for both categories of bias exist:
@@
 
-\begin{figure*}
+\begin{figure}
 \includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{Sampling process and exclusions for standard reports and Registered Reports.
@@
 We chose to exclude these cases to be conservative.}\label{fig:sampling}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{table*}[tbp]
+\begin{table}[tbp]
 
@@
 
-\end{table*}
+\end{table}
 
@@
 
-\end{table*}
-
-\begin{table*}[tbp]
+\end{table}
+
+\begin{table}[tbp]
 
@@
 
-\footnotesize{
+\scriptsize{
 
@@
 
-\begin{figure*}
-
-{\centering \includegraphics[width=0.6\textwidth]{manuscript_files/figure-latex/powerbaserate-1}
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\textwidth]{manuscript_files/figure-latex/powerbaserate-1}
 
@@
 Plotted values were calculated using the equation \(PRR = \alpha*(1-t) + (1-\beta)*t\); with \(PRR =\) positive result rate, \(\alpha =\) probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), \(1-\beta =\) probability of obtaining a positive result when testing a true hypothesis (power), and \(t =\) proportion of true hypotheses; and solving for \(t\) and \(1-\beta\), respectively.}\label{fig:powerbaserate}
-\end{figure*}
+\end{figure}
 
@@
 
+\hypertarget{disclosures}{%
+\subsection{Disclosures}\label{disclosures}}
+
+\hypertarget{data-materials-and-online-resources}{%
+\subsubsection{Data, materials, and online resources}\label{data-materials-and-online-resources}}
+
+The data and code necessary to reproduce all analyses reported here, as well as additional supplementary information, is available at \url{https://osf.io/dbhgr}.
+The manuscript, including the figures and statistical analyses, was created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.1; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rmarkdown} (Version 2.0; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
+
+\hypertarget{conflicts-of-interest}{%
+\subsubsection{Conflicts of Interest}\label{conflicts-of-interest}}
+
+The authors declare that they have no conflicts of interest with respect to the authorship or the publication of this article.
+
+\hypertarget{author-contributions}{%
+\subsubsection{Author Contributions}\label{author-contributions}}
+
+Conceptualisation: A.S.
+and D.L.; data curation, formal analysis, and software: A.S.
+and M.S.; investigation, methodology, and validation: A.S., M.S., and D.L; supervision: A.S and D.L.; visualisation and writing -- original draft: A.S; writing -- review and editing: A.S., M.S., and D.L.
+
+\hypertarget{acknowledgments}{%
+\subsubsection{Acknowledgments}\label{acknowledgments}}
+
+This work was funded by VIDI grant 452-17-013. We would like to thank Stuart Ritchie for valuable comments that helped improve this manuscript.
+
 \hypertarget{references}{%
@@
 
+\leavevmode\hypertarget{ref-R-codebook}{}%
+Arslan, R. C. (2018). How to automatically generate rich codebooks from study metadata. PsyArxiv. \url{https://doi.org/10.31234/osf.io/5qc6h}
+
 \leavevmode\hypertarget{ref-Atkinson1982}{}%
@@
 
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
 \leavevmode\hypertarget{ref-Chambers2013}{}%
@@
 \url{https://doi.org/10.1177/0149206319843985}
+
+\leavevmode\hypertarget{ref-R-TOSTER}{}%
+Lakens, D.
+(2017).
+Equivalence tests: A practical primer for t-tests, correlations, and meta-analyses.
+\emph{Social Psychological and Personality Science}, \emph{1}, 1--8.
+\url{https://doi.org/10.1177/1948550617697177}
 
@@
 
+\leavevmode\hypertarget{ref-R-here}{}%
+Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}
+
 \leavevmode\hypertarget{ref-Nosek2014}{}%
@@
 
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
 \leavevmode\hypertarget{ref-RRRwebsite}{}%
@@
 Rosenthal, R. (1979). The file drawer problem and tolerance for null results. \emph{Psychological Bulletin}, \emph{86}(3), 638--641. \url{https://doi.org/10.1037/0033-2909.86.3.638}
+
+\leavevmode\hypertarget{ref-RStudioTeam2019}{}%
+RStudio Team. (2019). \emph{RStudio: Integrated development environment for r}. Boston, MA: RStudio, Inc. Retrieved from \url{http://www.rstudio.com/}
 
@@
 
+\leavevmode\hypertarget{ref-R-reshape2}{}%
+Wickham, H. (2007). Reshaping data with the reshape package. \emph{Journal of Statistical Software}, \emph{21}(12), 1--20. Retrieved from \url{http://www.jstatsoft.org/v21/i12/}
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
 \leavevmode\hypertarget{ref-Winter2013}{}%
@@
 Wiseman, R., Watt, C., \& Kornbrot, D. (2019). Registered reports: An early example and analysis. \emph{PeerJ}, \emph{7}, e6232. \url{https://doi.org/10.7717/peerj.6232}
+
+\leavevmode\hypertarget{ref-R-knitr}{}%
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
+
+\leavevmode\hypertarget{ref-R-bookdown}{}%
+Xie, Y. (2016). \emph{Bookdown: Authoring books and technical documents with R markdown}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://github.com/rstudio/bookdown}
+
+\leavevmode\hypertarget{ref-R-rmarkdown}{}%
+Xie, Y., Allaire, J., \& Grolemund, G. (2018). \emph{R markdown: The definitive guide}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://bookdown.org/yihui/rmarkdown}
 
@@
 
+\leavevmode\hypertarget{ref-R-knitr}{}%
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
+
+\leavevmode\hypertarget{ref-R-bookdown}{}%
+Xie, Y. (2016). \emph{Bookdown: Authoring books and technical documents with R markdown}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://github.com/rstudio/bookdown}
+
+\leavevmode\hypertarget{ref-R-rmarkdown}{}%
+Xie, Y., Allaire, J., \& Grolemund, G. (2018). \emph{R markdown: The definitive guide}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://bookdown.org/yihui/rmarkdown}
+
 \end{document}

### 2020-01-12 manuscript/manuscript.Rmd
Added new abstract, title, keywords etc., formatting tweaks

--- 2020-01-11 manuscript/manuscript.Rmd
@@
 ---
-title             : "Positive Results in Registered Reports"
-shorttitle        : "Positive Results in Registered Reports"
+title             : "An excess of positive results: Comparing the standard Psychology literature with Registered Reports"
+shorttitle        : "Positive Results in Standard vs Registered Reports"
 
 author: 
-  - name          : "Anne Scheel"
+  - name          : "Anne M. Scheel"
     affiliation   : "1"
@@
 
-note: "\\clearpage"
+note:
 
@@
 abstract: >
-  XXXXXXXXXXXXXXXXXXX
+  When scientific studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the research scientists conduct.
+Psychology researchers have been concerned about the degree of distortion publication bias and “questionable research practices” have caused in their own literature, and developed new research and publication practices that aim to minimise these biases.
+Registered Reports are a new publication format in which peer review and the decision to publish take place before the study results are known.
+We compared the results in the full population of published Registered Reports in Psychology ($N = 71$, as of November 2018) with a random sample of hypothesis-testing studies from the standard literature ($N = 152$) by searching 633 journals for the phrase ‘test* the hypothes*’ [replicating a method by @Fanelli2010].
+Analysing the first hypothesis reported in each paper, we found $96.05\%$ positive results in standard reports, but only $43.66\%$ positive results in Registered Reports.
+The difference remained nearly as large when direct replications were excluded from the analysis ($95.95\%$ vs $50\%$ positive results).
+Although our study is not a direct test of the effects of publication bias and questionable research practices on the literature, the large gap between standard reports and Registered Reports suggests that psychologists under-report negative results to an extent that threatens cumulative science.
 
-keywords          : "keyword 1, keyword 2, keyword 3"
-wordcount         : "XXX"
+keywords          : "Publication bias, Registered Reports"
+wordcount         : "6395"
 
@@
 
-In addition to bias protection, RRs promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
-Many journals offering RRs also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., $90\%$ power for a given effect size of interest).
+In addition to bias protection, Registered Reportss promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
+Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., $90\%$ power for a given effect size of interest).
 
 Assuming a constant alpha level, the rate of positive results in a literature is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
-The RR format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature [see e.g., @Maxwell2004; @Szucs2017].
-Therefore, if the emerging RR literature in psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in RRs (or a combination of the two).
+The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature [see e.g., @Maxwell2004; @Szucs2017].
+Therefore, if the emerging Registered Reports literature in psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
 At this time, we have good reasons to believe in a difference in bias, but little reason to believe in a difference in the proportion of true hypotheses (at least regarding original hypotheses, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate (i.e., the proportion of supported hypotheses among all tested hypotheses).
-Considering the high standards for research quality in RRs, a large difference in positive results between RRs and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.
+Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.
 
 ## The current study
-The goal of our study was to test if RRs in psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as "standard reports", SRs), and to estimate the size of this potential difference.
+The goal of our study was to test if Registered Reports in psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as "standard reports", SRs), and to estimate the size of this potential difference.
 We set out to replicate a study by @Fanelli2010 on a new sample of standard reports in psychology and compared them to all published Registered Reports in psychology. 
 Fanelli searched for articles containing the phrase "test$^\ast$ the hypothes$^\ast$", drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
-For standard reports we used the same sampling method (restricted to the psychology discipline), and for RRs we relied on a database curated by the Center for Open Science (COS). 
+For standard reports we used the same sampling method (restricted to the psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS). 
 We chose Fanelli's method because Fanelli's -@Fanelli2010 and -@Fanelli2012 studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
-We additionally coded if studies were replications or original work because many published RRs are replications. 
-If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, and a higher proportion of replications among RRs than standard reports could therefore introduce a confound.
+We additionally coded if studies were replications or original work because many published Registered Reports are replications. 
+If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, and a higher proportion of replications among Registered Reports than standard reports could therefore introduce a confound.
 
 In a recent commentary on benefits and challenges of open-science practices for early-career researchers, @Allen2019 conducted a similar investigation: 
-They coded the proportion of null results in the 127 biomedical and psychology RRs listed in the COS database as of September 2018. 
+They coded the proportion of null results in the 127 biomedical and psychology Registered Reports listed in the COS database as of September 2018. 
 We were not aware of their parallel efforts when we planned our study in September and October 2018. 
-Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in RRs (counting all hypotheses in each paper) and found $60.5\%$ unsupported hypotheses across all included RRs, $66\%$ for replication attempts, and $54.5\%$ for novel research.
+Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found $60.5\%$ unsupported hypotheses across all included Registered Reports, $66\%$ for replication attempts, and $54.5\%$ for novel research.
 They compared these numbers to an estimate of $5-20\%$ null results in the standard literature. 
@@
 
-A major advantage of our study is that it allows us to draw a more meaningful comparison between RRs and the standard literature because we apply a previously used method [@Fanelli2010; @Fanelli2012] to both groups.
+A major advantage of our study is that it allows us to draw a more meaningful comparison between Registered Reports and the standard literature because we apply a previously used method [@Fanelli2010; @Fanelli2012] to both groups.
 In addition, we replicate @Fanelli2010 and provide data to evaluate his method: The search term "test$^\ast$ the hypothes$^\ast$" might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
-Therefore we also coded the phrases used to introduce hypotheses in RRs, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
-Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgments, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
+Therefore we also coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
+Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
 This allows others to verify (or contest) our results and provides an interesting resource for future meta-scientific research.
@@
 ## Sample
-We used the same method as @Fanelli2010 to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the RR population. 
+We used the same method as @Fanelli2010 to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population. 
 We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
@@
 Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded.
-"Preregistered": study had been preregistered but was not a full RR; "results-blind review": article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); "ambiguous": Four of these had been treated as RRs but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance.
+"Preregistered": study had been preregistered but was not a full RR; "results-blind review": article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); "ambiguous": Four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance.
 We chose to exclude these cases to be conservative.
@@
 
+# Important additional chunk option when using journal mode: fig.env="figure*"
+
 knitr::include_graphics("Sampling_exclusions_and_resampling.png")
@@
 
-For Registered Reports we aimed to include all published RRs in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase "test$^\ast$ the hypothes$^\ast$".
-We downloaded a database of published RRs curated by the Center for Open Science^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than "Psychiatry/Psychology" or "Multidisciplinary" in the ESI.
-Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 RRs published in Cortex because the ESI counts this journal towards the separate category "Neuroscience and Behavior".
+For Registered Reports we aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase "test$^\ast$ the hypothes$^\ast$".
+We downloaded a database of published Registered Reports curated by the Center for Open Science (https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9, retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than "Psychiatry/Psychology" or "Multidisciplinary" in the ESI.
+Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in Cortex because the ESI counts this journal towards the separate category "Neuroscience and Behavior".
 Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., Royal Society Open Science) were hand-coded by AS. 
 This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
-Following these exclusions, we verified the RR status of all remaining papers in our sample. 
-Papers were counted as RRs if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with https://cos.io/rr).
-For papers not clearly labelled as RRs we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly. 
-Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig.\ \@ref(fig:sampling)).
+
+Following these exclusions, we verified the Registered Reports status of all remaining papers in our sample. 
+Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with https://cos.io/rr).
+For papers not clearly labelled as Registered Reports we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly. 
+Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.\ \@ref(fig:sampling)).
 Note that we excluded all eight "Registered Replication Reports" [RRRs; @Simons2014; @Simons2018] in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing [@RRRwebsite, decision was not preregistered].
@@
 Instead, we received an excerpt which contained data for 11 records from the original sample, but no reference information of the coded articles (personal communication, 5th October 2018). 
-We were able to find these 11 articles based on the hypothesis quotes that had been coded, and used them as a pilot sample along with 10 randomly selected RRs. 
+We were able to find these 11 articles based on the hypothesis quotes that had been coded, and used them as a pilot sample along with 10 randomly selected Registered Reports. 
 MS and AS independently coded all 21 pilot articles with only one major disagreement in each group. 
-In the SR group, this disagreement was also the only case of major disagreement with Fanelli's original coding, which we deemed satisfying to proceed.
+In the standard reports group, this disagreement was also the only case of major disagreement with Fanelli's original coding, which we deemed satisfying to proceed.
 
@@
 If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first tested hypothesis rather than the first hypothesis mentioned in the text.
-In RRs we coded the first preregistered hypothesis, thus excluding unregistered pilot studies. 
+In Registered Reports we coded the first preregistered hypothesis, thus excluding unregistered pilot studies. 
 MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code ($`r sum(included$coded_by_AS & included$is_RR==1)`$ RRs $= `r printnum(sum(included$coded_by_AS & included$is_RR==1)/sum(included$is_RR==1)*100)`\%$ and $`r sum(included$coded_by_AS & included$is_RR==0)`$ SRs $= `r printnum(sum(included$coded_by_AS & included$is_RR==0)/sum(included$is_RR==0)*100)` \%$).
@@
 Getting a better overview of "natural" descriptions of hypotheses would be useful for future investigations of the generalisability of Fanelli's [-@Fanelli2010] results and could inspire new research questions.
-We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all RRs and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
+We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all Registered Reports and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
 .
@@
 We also wanted to code if a study was a replication of a previously published one: 
-We expected a much larger proportion of RRs to be direct replications, many of which may have been motivated by scepticism of the original study. 
-A lower positive result rate in RRs could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias. 
+We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study. 
+A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias. 
 After an initial coding attempt with ill-defined coding criteria lead to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered): 
@@
 The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
-AS coded all papers, DL double-coded `r rep.RR.coded.DL` RRs ($`r printnum(rep.RR.coded.DL/sum(included$is_RR)*100)` \%$) and `r rep.SR.coded.DL` SRs ($`r printnum(rep.RR.coded.DL/sum(included$is_RR==0)*100)` \%$).
+AS coded all papers, DL double-coded `r rep.RR.coded.DL` Registered Reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR)*100)` \%$) and `r rep.SR.coded.DL` standard reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR==0)*100)` \%$).
 There were `r rep.disagreements` disagreements (Cohen's kappa = `r printp(kappa.rep)`), all were resolved by discussion.
@@
 
-We would accept our hypothesis that RRs have a lower positive result rate than SRs if we found a negative difference between RRs and SRs that was significantly different from 0 *and* not statistically equivalent to a range from $-6\%$ to $+6\%$ (both at $\alpha = 5\%$).
+We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if we found a negative difference between Registered Reports and standard reports that was significantly different from 0 *and* not statistically equivalent to a range from $-6\%$ to $+6\%$ (both at $\alpha = 5\%$).
 
@@
 
-`r n.support.SR` out of `r n.SR` SRs and `r n.support.RR` out of `r n.RR` RRs had positive results, meaning that the positive result rate was $`r printnum(prop.support.SR*100)` \%$ for SRs ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]) and $`r printnum(prop.support.RR*100)` \%$ for RRs ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]; see Fig.\ \@ref(fig:mainplot)).
+`r n.support.SR` out of `r n.SR` standard reports and `r n.support.RR` out of `r n.RR` Registered Reports had positive results, meaning that the positive result rate was $`r printnum(prop.support.SR*100)` \%$ for standard reports ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]) and $`r printnum(prop.support.RR*100)` \%$ for Registered Reports ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]; see Fig.\ \@ref(fig:mainplot)).
 The preregistered one-sided proportions test with an alpha level of $5\%$ showed that this difference of $-`r printnum((prop.support.SR-prop.support.RR)*100)` \%$ was statistically significant, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
 Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$ at $\alpha = 5\%$, $z = `r printnum(min(tostresult$TOST_z1, tostresult$TOST_z2))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
-We thus accept our hypothesis that the positive result rate in RRs is lower than in SRs.
+We thus accept our hypothesis that the positive result rate in Registered Reports is lower than in standard reports.
 
@@
 ```{r mainplot, echo=FALSE, warning=FALSE, fig.height=5, fig.cap="(ref:mainplot)"}
-mainplot
+#mainplot
+
+#####
+# Important alternative code and settings when using journal mode:
+# 1. set fig.height=5 in chunk options (it's 4 in manuscript mode)
+# 2. use the plot code below instead of `mainplot`
+#    (otherwise font will be too small)!
+#
+ggplot(mainplot.df, aes(x = is_RR, y = value, fill = support)) +
+                    geom_bar(stat = "identity",
+                             width = 0.5) +
+                    scale_fill_manual(values= c("#bcbddc", "#756bb1"),
+                                      name="first hypothesis") +
+                    annotate("text", label = paste("N =", n.SR),
+                             x = 1, y = 105, size = 5) +
+                    annotate("text", label = paste("N =", n.RR),
+                             x = 2, y = 105, size = 5) +
+                    geom_errorbar(aes(ymin = lower, ymax = upper),
+                                  width = 0.05, size = 0.5) +
+                    scale_x_discrete(breaks = waiver(),
+                                     labels = c("SR" = "Standard\nReports",
+                                                "RR" = "Registered\nReports"),
+                                     name = NULL)+
+                    scale_y_continuous(lim=c(0,110), breaks = c(seq(0, 100, 10)),
+                                       minor_breaks = c(seq(0, 100, 5)),
+                                       name = "% of papers", expand = c(0, 0))+
+                    theme_minimal(base_size = 20)+
+                    theme(panel.grid.major.x = element_blank(),
+                          panel.grid.minor.x = element_blank(),
+                          legend.margin = margin(0,0,0,-5.5)) +
+                    coord_fixed(ratio=0.03)
 ```
@@
 For ease of communication we will nonetheless refer to this category as "original" studies.
-As expected, direct replications were much more common among Registered Reports than standard reports: `r n.rep.RR` out of `r n.RR` RRs ($`r printnum(prop.rep.RR*100)`\%$), but only `r n.rep.SR` out of `r n.SR` SRs ($`r printnum(prop.rep.SR*100)`\%$) were classified as direct replications of previously published work.
-However, this difference cannot account for the stark overall difference between SRs and RRs described above: 
-Although replication RRs in our sample indeed had a lower positive result rate than original RRs (see Table 1), the difference between original SRs and original RRs -- $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$ -- was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(reptost$TOST_z1, reptost$TOST_z2))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
+As expected, direct replications were much more common among Registered Reports than standard reports: `r n.rep.RR` out of `r n.RR` Registered Reports ($`r printnum(prop.rep.RR*100)`\%$), but only `r n.rep.SR` out of `r n.SR` standard reports ($`r printnum(prop.rep.SR*100)`\%$) were classified as direct replications of previously published work.
+However, this difference cannot account for the stark overall difference between standard reports and Registered Reports described above: 
+Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports -- $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$ -- was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(reptost$TOST_z1, reptost$TOST_z2))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
 
@@
 
-Since our SR sample represents a direct replication of @Fanelli2010 for the discipline Psychiatry & Psychology, another interesting question to ask is how our results compare to Fanelli's.
-The difference between the positive result rate for SRs in our sample ($`r printnum(prop.support.SR*100)`\%$) and Fanelli's ($`r printnum(prop.support.Fanelli*100)`\%$) is $`r printnum((prop.support.SR-prop.support.Fanelli)*100)`\%$.
+Since our standard reports sample represents a direct replication of @Fanelli2010 for the discipline Psychiatry & Psychology, another interesting question to ask is how our results compare to Fanelli's.
+The difference between the positive result rate for standard reports in our sample ($`r printnum(prop.support.SR*100)`\%$) and Fanelli's ($`r printnum(prop.support.Fanelli*100)`\%$) is $`r printnum((prop.support.SR-prop.support.Fanelli)*100)`\%$.
 This difference is not significantly different from 0 in a two-sided proportions test ($\chi^2 = `r printnum(Fanelliproptest$statistic)`$, $p= `r printp(Fanelliproptest$p.value)`$) but also not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(Fanellitost$TOST_z1, Fanellitost$TOST_z2))`$, $p= `r printp(max(Fanellitost$TOST_p1, Fanellitost$TOST_p2))`$), both at $\alpha = 5\%$.
@@
 ```
-Finally, we analysed the language that was used to introduce or refer to hypotheses in RRs.
+Finally, we analysed the language that was used to introduce or refer to hypotheses in Registered Reports.
 We were interested in whether the search phrase "test$^\ast$ the hypothes$^\ast$" used by Fanelli captured the way researchers write about hypothesis tests reasonably well.
 The answer is a resounding "no":
-Searching the abstracts, titles, and keywords of the RR sample showed that only `r testthehypothes.RR`/`r n.RR` RRs would have been detected with this search phrase. 
-To get an overview of analogous hypothesis-introduction phrases researchers used in RRs, we stripped the hypothesis quotes of RRs from all content-specific information and extracted "minimal" phrases that most distinctively indicated that a hypothesis was being described.
+Searching the abstracts, titles, and keywords of the Registered Reports sample showed that only `r testthehypothes.RR`/`r n.RR` Registered Reports would have been detected with this search phrase. 
+To get an overview of analogous hypothesis-introduction phrases researchers used in Registered Reports, we stripped the hypothesis quotes of Registered Reports from all content-specific information and extracted "minimal" phrases that most distinctively indicated that a hypothesis was being described.
 For example, from the hypothesis quote "(f)or Study 1, we predicted that participants reading about academic (vs.
@@
 
-For the majority of RRs (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==1))`), we identified one hypothesis-introduction phrase; the remaining ones used two (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==2))` RRs), three (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==3))` RRs), or four (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==4))` RR) different phrases or had no identifiable hypothesis introduction (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==0))` RR).
+For the majority of Registered Reports (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==1))`), we identified one hypothesis-introduction phrase; the remaining ones used two (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==2))` RRs), three (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==3))` RRs), or four (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==4))` RR) different phrases or had no identifiable hypothesis introduction (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==0))` RR).
 In this total set of `r nrow(intros.long)` hypothesis introductions, we found `r length(uniquephrases)` unique phrases, showing substantial linguistic variation (see Tables 2 and 3).
@@
 Clearly "test$^\ast$" and "hypothes$^\ast$" are quite popular, yet they co-occurred only `r test.and.hypothes` times and more than half of all hypothesis introductions (`r nrow(intros.long)-test.or.hypothes`/`r nrow(intros.long)`) contained neither word.
-Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 ($`r printnum(30/43*100)`\%$) hypothesis introductions found in original RRs contained either "test$^\ast$" or "hypothes$^\ast$" or both, while only 16 out of 54 ($`r printnum(16/54*100)`\%$) hypothesis introductions in direct replication RRs did.
+Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 ($`r printnum(30/43*100)`\%$) hypothesis introductions found in original Registered Reports contained either "test$^\ast$" or "hypothes$^\ast$" or both, while only 16 out of 54 ($`r printnum(16/54*100)`\%$) hypothesis introductions in direct replication Registered Reports did.
 
-We noticed that direct replication RRs generally tended to use different language to describe their hypothesis.
+We noticed that direct replication Registered Reports generally tended to use different language to describe their hypothesis.
 As the high frequency of the word stem "replicat$^\ast$" suggests, these studies were often not framed as new tests of a previously tested hypothesis, but as attempts to replicate a previously documented effect or to repeat a previously conducted experiment.
 Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
-Tables 2 and 3 list all unique hypothesis introductions and their frequency for original RRs and direct replication RRs, respectively, grouped by the five most frequent word stems ("hypothes$^\ast$", "replicat$^\ast$", "test$^\ast$", "examine$^\ast$", "predict$^\ast$").
-Using five as a cutoff value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.
+Tables 2 and 3 list all unique hypothesis introductions and their frequency for original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems ("hypothes$^\ast$", "replicat$^\ast$", "test$^\ast$", "examine$^\ast$", "predict$^\ast$").
+Using five as a cut-off value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.
 
@@
 ```{r echo = FALSE, results = 'asis'}
+# Important alternative settings when using journal mode: font_size = "footnotesize"
+# (it's scriptsize in manuscript mode)
 apa_table(
@@
 
-It is important to keep in mind that not all hypotheses could be coded from the abstract: For `r n.hypintro.fulltext.only` RRs, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
-Therefore we additionally tested how many of the RRs would have been detected in a regular search using our five most frequent word stems. 
-We searched their titles, abstracts, and keywords for "hypothes$^\ast$" OR "replicat$^\ast$" OR "test$^\ast$" OR "examine$^\ast$" OR "predict$^\ast$" and found that $`r n.hypintros.fivewords.RR`/`r n.RR`$ RRs ($`r printnum(n.hypintros.fivewords.RR/n.RR*100)` \%$) would have been detected this way.
+It is important to keep in mind that not all hypotheses could be coded from the abstract: For `r n.hypintro.fulltext.only` Registered Reports, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
+Therefore we additionally tested how many of the Registered Reports would have been detected in a regular search using our five most frequent word stems. 
+We searched their titles, abstracts, and keywords for "hypothes$^\ast$" OR "replicat$^\ast$" OR "test$^\ast$" OR "examine$^\ast$" OR "predict$^\ast$" and found that $`r n.hypintros.fivewords.RR`/`r n.RR`$ Registered Reports ($`r printnum(n.hypintros.fivewords.RR/n.RR*100)` \%$) would have been detected this way.
 We do not know how well these search terms represent the population of hypothesis-testing studies in psychology, but a structured investigation of this question would be very useful for future meta-research.
@@
 We examined the proportion of psychology articles that find support for their first tested hypothesis and found a large difference ($`r printnum(prop.support.SR*100)` \%$ vs $`r printnum(prop.support.RR*100)` \%$) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
-More than half of the analysed RRs tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis ($`r printnum(prop.orig.support.SR*100)` \%$ vs $`r printnum(prop.orig.support.RR*100)` \%$).
+More than half of the analysed Registered Reports tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis ($`r printnum(prop.orig.support.SR*100)` \%$ vs $`r printnum(prop.orig.support.RR*100)` \%$).
 The introduction of Registered Reports has clearly led to a much larger proportion of null results appearing in the published literature compared to standard reports.
@@
 ```{r powerbaserate, echo=FALSE, fig.width=5, fig.height=3, fig.align='center', warning=FALSE, fig.cap="(ref:powerbaserate)", out.width = "0.6\\textwidth", fig.env="figure*"}
+
+# Important altrnative chunk options when using journal mode: 
+# 1. use out.width="0.6\\textwidth" (it's 0.8 in manuscript mode)
+# 2. set fig.env="figure*"
+
 source(here("analysis", "04_power_baserate_plot.R"))
@@
 
+```{r include=FALSE}
+r_refs(file = "prr_software.bib")
+my_citation <- cite_r(file = "prr_software.bib")
+```
+
+## Disclosures
+### Data, materials, and online resources
+The data and code necessary to reproduce all analyses reported here, as well as additional supplementary information, is available at <https://osf.io/dbhgr>.
+The manuscript including figures and statistical analyses, the appendix, and the codebook available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.
+
+### Conflicts of Interest
+The authors declare that they have no conflicts of interest with respect to the authorship or the publication of this article.
+
+### Author Contributions
+Conceptualisation: A.S.
+and D.L.; data curation, formal analysis, and software: A.S.
+and M.S.; investigation, methodology, and validation: A.S., M.S., and D.L; supervision: A.S and D.L.; visualisation and writing -- original draft: A.S; writing -- review and editing: A.S., M.S., and D.L.
+
+### Acknowledgements
+This work was funded by VIDI grant 452-17-013. We thank Stuart Ritchie for valuable comments that helped improve this manuscript.
+
 # References
 
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.2in}
+\setlength{\leftskip}{0.2in}

### 2020-01-12 manuscript/manuscript.tex
Added new abstract, title, keywords etc., formatting tweaks

@@
 \hypersetup{
-            pdftitle={Positive Results in Registered Reports},
-            pdfkeywords={keyword 1, keyword 2, keyword 3},
+            pdftitle={An excess of positive results: Comparing the standard Psychology literature with Registered Reports},
+            pdfkeywords={Publication bias, Registered Reports},
             pdfborder={0 0 0},
@@
 \makeatother
-\shorttitle{Positive Results in Registered Reports}
-\author{Anne Scheel\textsuperscript{1}, Mitchell Schijen\textsuperscript{1}, \& Daniël Lakens\textsuperscript{1}}
+\shorttitle{Positive Results in Standard vs Registered Reports}
+\author{Anne M. Scheel\textsuperscript{1}, Mitchell Schijen\textsuperscript{1}, \& Daniël Lakens\textsuperscript{1}}
 \affiliation{
@@
 
-Correspondence concerning this article should be addressed to Anne Scheel, Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands. E-mail: a.m.scheel@tue.nl}
-\note{\textbackslash{}clearpage}
-\keywords{keyword 1, keyword 2, keyword 3\newline\indent Word count: XXX}
-\usepackage{lineno}
-
-\linenumbers
+Correspondence concerning this article should be addressed to Anne M. Scheel, Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands. E-mail: a.m.scheel@tue.nl}
+\keywords{Publication bias, Registered Reports\newline\indent Word count: 6395}
+\usepackage{dblfloatfix}
+
 \usepackage{float}
@@
 
-\title{Positive Results in Registered Reports}
+\title{An excess of positive results: Comparing the standard Psychology literature with Registered Reports}
 
@@
 \abstract{
-XXXXXXXXXXXXXXXXXXX
+When scientific studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the research scientists conduct.
+Psychology researchers have been concerned about the degree of distortion publication bias and ``questionable research practices'' have caused in their own literature, and developed new research and publication practices that aim to minimise these biases.
+Registered Reports are a new publication format in which peer review and the decision to publish take place before the study results are known.
+We compared the results in the full population of published Registered Reports in Psychology (\(N = 71\), as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (\(N = 152\)) by searching 633 journals for the phrase `test* the hypothes*' (replicating a method by Fanelli, 2010).
+Analysing the first hypothesis reported in each paper, we found \(96.05\%\) positive results in standard reports, but only \(43.66\%\) positive results in Registered Reports.
+The difference remained nearly as large when direct replications were excluded from the analysis (\(95.95\%\) vs \(50\%\) positive results).
+Although our study is not a direct test of the effects of publication bias and questionable research practices on the literature, the large gap between standard reports and Registered Reports suggests that psychologists under-report negative results to an extent that threatens cumulative science.
 }
@@
 
-In addition to bias protection, RRs promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
-Many journals offering RRs also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., \(90\%\) power for a given effect size of interest).
+In addition to bias protection, Registered Reportss promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
+Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., \(90\%\) power for a given effect size of interest).
 
 Assuming a constant alpha level, the rate of positive results in a literature is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
-The RR format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature (see e.g., Maxwell, 2004; Szucs \& Ioannidis, 2017).
-Therefore, if the emerging RR literature in psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in RRs (or a combination of the two).
+The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature (see e.g., Maxwell, 2004; Szucs \& Ioannidis, 2017).
+Therefore, if the emerging Registered Reports literature in psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
 At this time, we have good reasons to believe in a difference in bias, but little reason to believe in a difference in the proportion of true hypotheses (at least regarding original hypotheses, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate (i.e., the proportion of supported hypotheses among all tested hypotheses).
-Considering the high standards for research quality in RRs, a large difference in positive results between RRs and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.
+Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.
 
@@
 
-The goal of our study was to test if RRs in psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
+The goal of our study was to test if Registered Reports in psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
 We set out to replicate a study by Fanelli (2010) on a new sample of standard reports in psychology and compared them to all published Registered Reports in psychology.
 Fanelli searched for articles containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}, drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
-For standard reports we used the same sampling method (restricted to the psychology discipline), and for RRs we relied on a database curated by the Center for Open Science (COS).
+For standard reports we used the same sampling method (restricted to the psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS).
 We chose Fanelli's method because Fanelli's (2010) and (2012) studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
-We additionally coded if studies were replications or original work because many published RRs are replications.
-If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, and a higher proportion of replications among RRs than standard reports could therefore introduce a confound.
+We additionally coded if studies were replications or original work because many published Registered Reports are replications.
+If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, and a higher proportion of replications among Registered Reports than standard reports could therefore introduce a confound.
 
 In a recent commentary on benefits and challenges of open-science practices for early-career researchers, Allen \& Mehler (2019) conducted a similar investigation:
-They coded the proportion of null results in the 127 biomedical and psychology RRs listed in the COS database as of September 2018.
+They coded the proportion of null results in the 127 biomedical and psychology Registered Reports listed in the COS database as of September 2018.
 We were not aware of their parallel efforts when we planned our study in September and October 2018.
-Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in RRs (counting all hypotheses in each paper) and found \(60.5\%\) unsupported hypotheses across all included RRs, \(66\%\) for replication attempts, and \(54.5\%\) for novel research.
+Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found \(60.5\%\) unsupported hypotheses across all included Registered Reports, \(66\%\) for replication attempts, and \(54.5\%\) for novel research.
 They compared these numbers to an estimate of \(5-20\%\) null results in the standard literature.
@@
 
-A major advantage of our study is that it allows us to draw a more meaningful comparison between RRs and the standard literature because we apply a previously used method (Fanelli, 2010, 2012) to both groups.
+A major advantage of our study is that it allows us to draw a more meaningful comparison between Registered Reports and the standard literature because we apply a previously used method (Fanelli, 2010, 2012) to both groups.
 In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
-Therefore we also coded the phrases used to introduce hypotheses in RRs, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
-Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgments, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
+Therefore we also coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
+Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
 This allows others to verify (or contest) our results and provides an interesting resource for future meta-scientific research.
@@
 
-We used the same method as Fanelli (2010) to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the RR population.
+We used the same method as Fanelli (2010) to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
 We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
@@
 
-\begin{figure}
+\begin{figure*}
 \includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{Sampling process and exclusions for standard reports and Registered Reports.
 Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded.
-\enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: Four of these had been treated as RRs but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance.
+\enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: Four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance.
 We chose to exclude these cases to be conservative.}\label{fig:sampling}
-\end{figure}
-
-For Registered Reports we aimed to include all published RRs in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
-We downloaded a database of published RRs curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
-Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 RRs published in Cortex because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
+\end{figure*}
+
+For Registered Reports we aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
+We downloaded a database of published Registered Reports curated by the Center for Open Science (\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}, retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
+Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in Cortex because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
 Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., Royal Society Open Science) were hand-coded by AS.
 This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
-Following these exclusions, we verified the RR status of all remaining papers in our sample.
-Papers were counted as RRs if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
-For papers not clearly labelled as RRs we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
-Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig.~\ref{fig:sampling}).
+
+Following these exclusions, we verified the Registered Reports status of all remaining papers in our sample.
+Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
+For papers not clearly labelled as Registered Reports we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
+Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
 Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).
@@
 Instead, we received an excerpt which contained data for 11 records from the original sample, but no reference information of the coded articles (personal communication, 5th October 2018).
-We were able to find these 11 articles based on the hypothesis quotes that had been coded, and used them as a pilot sample along with 10 randomly selected RRs.
+We were able to find these 11 articles based on the hypothesis quotes that had been coded, and used them as a pilot sample along with 10 randomly selected Registered Reports.
 MS and AS independently coded all 21 pilot articles with only one major disagreement in each group.
-In the SR group, this disagreement was also the only case of major disagreement with Fanelli's original coding, which we deemed satisfying to proceed.
+In the standard reports group, this disagreement was also the only case of major disagreement with Fanelli's original coding, which we deemed satisfying to proceed.
 
@@
 If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first tested hypothesis rather than the first hypothesis mentioned in the text.
-In RRs we coded the first preregistered hypothesis, thus excluding unregistered pilot studies.
+In Registered Reports we coded the first preregistered hypothesis, thus excluding unregistered pilot studies.
 MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs \(= 33.80\%\) and \(47\) SRs \(= 30.92 \%\)).
@@
 Getting a better overview of \enquote{natural} descriptions of hypotheses would be useful for future investigations of the generalisability of Fanelli's (2010) results and could inspire new research questions.
-We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all RRs and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
+We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all Registered Reports and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
 .
@@
 We also wanted to code if a study was a replication of a previously published one:
-We expected a much larger proportion of RRs to be direct replications, many of which may have been motivated by scepticism of the original study.
-A lower positive result rate in RRs could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
+We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study.
+A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
 After an initial coding attempt with ill-defined coding criteria lead to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
@@
 The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
-AS coded all papers, DL double-coded 32 RRs (\(45.07 \%\)) and 99 SRs (\(21.05 \%\)).
+AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(21.05 \%\)).
 There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.
@@
 
-We would accept our hypothesis that RRs have a lower positive result rate than SRs if we found a negative difference between RRs and SRs that was significantly different from 0 \emph{and} not statistically equivalent to a range from \(-6\%\) to \(+6\%\) (both at \(\alpha = 5\%\)).
+We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if we found a negative difference between Registered Reports and standard reports that was significantly different from 0 \emph{and} not statistically equivalent to a range from \(-6\%\) to \(+6\%\) (both at \(\alpha = 5\%\)).
 
@@
 
-146 out of 152 SRs and 31 out of 71 RRs had positive results, meaning that the positive result rate was \(96.05 \%\) for SRs (\(95 \%\) CI {[}91.61, 98.54{]}) and \(43.66 \%\) for RRs (\(95 \%\) CI {[}31.91, 55.95{]}; see Fig.~\ref{fig:mainplot}).
+146 out of 152 standard reports and 31 out of 71 Registered Reports had positive results, meaning that the positive result rate was \(96.05 \%\) for standard reports (\(95 \%\) CI {[}91.61, 98.54{]}) and \(43.66 \%\) for Registered Reports (\(95 \%\) CI {[}31.91, 55.95{]}; see Fig.~\ref{fig:mainplot}).
 The preregistered one-sided proportions test with an alpha level of \(5\%\) showed that this difference of \(-52.39 \%\) was statistically significant, \(\chi^2 = 77.96\), \(p < .001\).
 Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\), \(z = 7.61\), \(p > .999\), meaning that we cannot reject differences more extreme than \(6\%\).
-We thus accept our hypothesis that the positive result rate in RRs is lower than in SRs.
+We thus accept our hypothesis that the positive result rate in Registered Reports is lower than in standard reports.
 
@@
 For ease of communication we will nonetheless refer to this category as \enquote{original} studies.
-As expected, direct replications were much more common among Registered Reports than standard reports: 41 out of 71 RRs (\(57.75\%\)), but only 4 out of 152 SRs (\(2.63\%\)) were classified as direct replications of previously published work.
-However, this difference cannot account for the stark overall difference between SRs and RRs described above:
-Although replication RRs in our sample indeed had a lower positive result rate than original RRs (see Table 1), the difference between original SRs and original RRs -- \(45.95\%\) -- was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
-
-\begin{table}[tbp]
+As expected, direct replications were much more common among Registered Reports than standard reports: 41 out of 71 Registered Reports (\(57.75\%\)), but only 4 out of 152 standard reports (\(2.63\%\)) were classified as direct replications of previously published work.
+However, this difference cannot account for the stark overall difference between standard reports and Registered Reports described above:
+Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports -- \(45.95\%\) -- was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
+
+\begin{table*}[tbp]
 
@@
 
-\end{table}
-
-Since our SR sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question to ask is how our results compare to Fanelli's.
-The difference between the positive result rate for SRs in our sample (\(96.05\%\)) and Fanelli's (\(91.49\%\)) is \(4.56\%\).
+\end{table*}
+
+Since our standard reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question to ask is how our results compare to Fanelli's.
+The difference between the positive result rate for standard reports in our sample (\(96.05\%\)) and Fanelli's (\(91.49\%\)) is \(4.56\%\).
 This difference is not significantly different from 0 in a two-sided proportions test (\(\chi^2 = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = -3.73\), \(p= .306\)), both at \(\alpha = 5\%\).
@@
 
-Finally, we analysed the language that was used to introduce or refer to hypotheses in RRs.
+Finally, we analysed the language that was used to introduce or refer to hypotheses in Registered Reports.
 We were interested in whether the search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} used by Fanelli captured the way researchers write about hypothesis tests reasonably well.
 The answer is a resounding \enquote{no}:
-Searching the abstracts, titles, and keywords of the RR sample showed that only 2/71 RRs would have been detected with this search phrase.
-To get an overview of analogous hypothesis-introduction phrases researchers used in RRs, we stripped the hypothesis quotes of RRs from all content-specific information and extracted \enquote{minimal} phrases that most distinctively indicated that a hypothesis was being described.
+Searching the abstracts, titles, and keywords of the Registered Reports sample showed that only 2/71 Registered Reports would have been detected with this search phrase.
+To get an overview of analogous hypothesis-introduction phrases researchers used in Registered Reports, we stripped the hypothesis quotes of Registered Reports from all content-specific information and extracted \enquote{minimal} phrases that most distinctively indicated that a hypothesis was being described.
 For example, from the hypothesis quote \enquote{(f)or Study 1, we predicted that participants reading about academic (vs.~social) behaviors would show a better anagram performance} we extracted the hypothesis-introduction phrase \enquote{predicted that}.
 
-For the majority of RRs (49), we identified one hypothesis-introduction phrase; the remaining ones used two (16 RRs), three (4 RRs), or four (1 RR) different phrases or had no identifiable hypothesis introduction (1 RR).
+For the majority of Registered Reports (49), we identified one hypothesis-introduction phrase; the remaining ones used two (16 RRs), three (4 RRs), or four (1 RR) different phrases or had no identifiable hypothesis introduction (1 RR).
 In this total set of 97 hypothesis introductions, we found 64 unique phrases, showing substantial linguistic variation (see Tables 2 and 3).
@@
 Clearly \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times and more than half of all hypothesis introductions (51/97) contained neither word.
-Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions found in original RRs contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, while only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication RRs did.
-
-We noticed that direct replication RRs generally tended to use different language to describe their hypothesis.
+Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions found in original Registered Reports contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, while only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication Registered Reports did.
+
+We noticed that direct replication Registered Reports generally tended to use different language to describe their hypothesis.
 As the high frequency of the word stem \enquote{replicat\(^\ast\)} suggests, these studies were often not framed as new tests of a previously tested hypothesis, but as attempts to replicate a previously documented effect or to repeat a previously conducted experiment.
 Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
-Tables 2 and 3 list all unique hypothesis introductions and their frequency for original RRs and direct replication RRs, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
-Using five as a cutoff value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.
-
-\begin{table}[tbp]
+Tables 2 and 3 list all unique hypothesis introductions and their frequency for original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
+Using five as a cut-off value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.
+
+\begin{table*}[tbp]
 
@@
 
-\end{table}
-
-\begin{table}[tbp]
+\end{table*}
+
+\begin{table*}[tbp]
 
@@
 
-\scriptsize{
+\footnotesize{
 
@@
 
-\end{table}
-
-It is important to keep in mind that not all hypotheses could be coded from the abstract: For 21 RRs, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
-Therefore we additionally tested how many of the RRs would have been detected in a regular search using our five most frequent word stems.
-We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) RRs (\(97.18 \%\)) would have been detected this way.
+\end{table*}
+
+It is important to keep in mind that not all hypotheses could be coded from the abstract: For 21 Registered Reports, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
+Therefore we additionally tested how many of the Registered Reports would have been detected in a regular search using our five most frequent word stems.
+We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) Registered Reports (\(97.18 \%\)) would have been detected this way.
 We do not know how well these search terms represent the population of hypothesis-testing studies in psychology, but a structured investigation of this question would be very useful for future meta-research.
@@
 We examined the proportion of psychology articles that find support for their first tested hypothesis and found a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
-More than half of the analysed RRs tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
+More than half of the analysed Registered Reports tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
 The introduction of Registered Reports has clearly led to a much larger proportion of null results appearing in the published literature compared to standard reports.
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=0.8\textwidth]{manuscript_files/figure-latex/powerbaserate-1}
+\begin{figure*}
+
+{\centering \includegraphics[width=0.6\textwidth]{manuscript_files/figure-latex/powerbaserate-1}
 
@@
 Plotted values were calculated using the equation \(PRR = \alpha*(1-t) + (1-\beta)*t\); with \(PRR =\) positive result rate, \(\alpha =\) probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), \(1-\beta =\) probability of obtaining a positive result when testing a true hypothesis (power), and \(t =\) proportion of true hypotheses; and solving for \(t\) and \(1-\beta\), respectively.}\label{fig:powerbaserate}
-\end{figure}
+\end{figure*}
 
@@
 The data and code necessary to reproduce all analyses reported here, as well as additional supplementary information, is available at \url{https://osf.io/dbhgr}.
-The manuscript, including the figures and statistical analyses, was created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.1; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rmarkdown} (Version 2.0; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
+The manuscript including figures and statistical analyses, the appendix, and the codebook available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.1; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rmarkdown} (Version 2.0; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
 
@@
 
-\hypertarget{acknowledgments}{%
-\subsubsection{Acknowledgments}\label{acknowledgments}}
-
-This work was funded by VIDI grant 452-17-013. We would like to thank Stuart Ritchie for valuable comments that helped improve this manuscript.
+\hypertarget{acknowledgements}{%
+\subsubsection{Acknowledgements}\label{acknowledgements}}
+
+This work was funded by VIDI grant 452-17-013. We thank Stuart Ritchie for valuable comments that helped improve this manuscript.
 
@@
 
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.2in}
+\setlength{\leftskip}{0.2in}
 

### 2020-01-12 raw_data/codebook.Rmd
1. added a robustness check to the quantitative analysis script, 2. reorganised the folder structure (in accordance with Psych-DS), 3. changed code in the manuscript Rmd and in the analysis scripts to accommodate the new folder structure, 4. added the preregistration document with comments indicating adherence/deviations, 5. added a file with the full list of Psych journals from the ESI database
double-checked dataset and updated codebook

--- 2020-01-06 codebook.Rmd
@@
 
-```{r prepare_codebook}
+```{r include=FALSE}
+library(here)
 library(codebook)
 library(readxl)
-#library(here)
 library(rio)
+```
 
+```{r prepare_codebook}
 codebook_data <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", n_max = 243)
@@
 # Read codebook from second sheet in Excel file.
-dict <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "codebook")
+dict <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "data_dictionary")
 
@@
                                             "SR replacements and late RR additions" = 2,
-                                            "second SR replacement" = 3)
+                                            "second SR replacement" = 3,
+                                            "RR protocol replacement" = 4)
 val_labels(codebook_data$uses_AS_coding) <- c("uses MS coding" = 0, "uses AS coding" = 1)
@@
 # Add meta data
-metadata(codebook_data)$name <- "Positive Results in Registered Reports in Psychology"
-metadata(codebook_data)$description <- "Coded variables to compare the proportion of papers that find support for their first tested hypothesis between Registered Reports and standard reports in psychology"
-metadata(codebook_data)$creator <- "Anne Scheel, Mitchell Schijen, Daniël Lakens"
+metadata(codebook_data)$name <- "Positive Results in Standard vs Registered Reports"
+metadata(codebook_data)$description <- "Coded variables to compare the proportion of papers that find support for their first tested hypothesis between Registered Reports and standard reports in Psychology"
+metadata(codebook_data)$creator <- list(
+      "@type" = "Person",
+      givenName = "Anne", familyName = "Scheel",
+      affiliation = list("@type" = "Organization",
+        name = "Eindhoven University of Technology"),
+      "@type" = "Person",
+      givenName = " Mitchell", familiyName = "Schijen",
+      "@type" = "Person",
+      givenName = "Daniël", familiyName = "Lakens")
 metadata(codebook_data)$temporalCoverage <- "Winter 2018"

### 2020-01-13 raw_data/positive_results_in_registered_reports_codebook.Rmd
updated codebook and added .tsv version of dataset to comply with Psych-DS

--- 2020-01-12 raw_data/codebook.Rmd
@@
 library(codebook)
-library(readxl)
 library(rio)
@@
 ```{r prepare_codebook}
-codebook_data <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", n_max = 243)
+codebook_data <- import("positive_results_in_registered_reports_masterfile_data.xlsx")
 
 # Read codebook from second sheet in Excel file.
-dict <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "data_dictionary")
+dict <- import("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "data_dictionary")
 
@@
 #Export codebook
-rio::export(codebook_data, "positive_results_in_registered_reports_codebook.rds") # to R data structure file
+rio::export(codebook_data, "positive_results_in_registered_reports_data.rds") # to R data structure file
 

### 2020-01-13 analysis/01_interrater_agreement.R
updated slightly changed dataset name

@@ -27,7 +27,7 @@
 library(here)
 
 # load the dataset from the RDS file created with codebook
-alldata <- readRDS(here("raw_data", "positive_results_in_registered_reports_codebook.rds"))
+alldata <- readRDS(here("raw_data", "positive_results_in_registered_reports_data.rds"))
 
 # remove excluded papers
 included <- alldata[alldata$include_in_analysis==1,]

### 2020-01-13 analysis/02_quantitative_analyses.R

@@ -53,7 +53,7 @@ library("papaja")
 library("here")
 
 # load the dataset from the RDS file created with codebook
-alldata <- readRDS(here("raw_data", "positive_results_in_registered_reports_codebook.rds"))
+alldata <- readRDS(here("raw_data", "positive_results_in_registered_reports_data.rds"))
 # remove excluded papers
 included <- alldata[alldata$include_in_analysis==1,]
 

### 2020-01-13 analysis/03_hypothesis_introduction_analyses.R

@@ -47,7 +47,7 @@ library("stringr")
 library("reshape2")
 
 # load the dataset from the RDS file created with codebook
-alldata <- readRDS(here("raw_data", "positive_results_in_registered_reports_codebook.rds"))
+alldata <- readRDS(here("raw_data", "positive_results_in_registered_reports_data.rds"))
 # remove excluded papers
 included <- alldata[alldata$include_in_analysis==1,]
 

### 2020-01-13 appendix/appendix.Rmd
added appendix

---
title         : "Appendix"
shorttitle    : "Positive Results in Standard vs Registered Reports -- Appendix"

lang  : "en-UK"
output: pdf_document

---

```{r include = FALSE}
library("papaja")
library("bookdown")
library("rmarkdown")
library("knitr")
library("here")
```

\raggedright

This document contains additional information about the methods and analyses reported in the manuscript '**An excess of positive results: Comparing the standard Psychology literature with Registered Reports**', as well as an additional robustness analysis (see section 4.1).

# 1. Project timeline
| Time | Event |
|----:|:-------------|
| Early September 2018 | Project starts as the Bachelor End Project (BEP) of Mitchell Schijen (MS) under the supervision of Anne Scheel (AS) and Daniël Lakens (DL) at Eindhoven University of Technology | 
| | |
| November 2018 | Registered Reports population is determined by retrieving the Zotero database curated by the Center for Open Science |
| | |
| Early December 2018 | Piloting |
| | |
| 7th December 2018 | Study is preregistered at https://osf.io/s8e97 |
| | |
| January 2019 | - Standard reports sample is drawn |
| | - MS and AS code all sampled standard reports and all Registered Reports (coding round 1) |
| | - MS submits BEP thesis |
| | |
| Spring/summer 2019 | - Three unclear cases from the RRs sample are confirmed as RRs and coded (coding round 2) | 
| | - Eight new standard reports are sampled and coded to replace the excluded ones (coding round 2); one of them has to be excluded and gets replaced by resampling (coding round 3) |
| | - AS and DL develop new coding criteria for replication status and re-code all SRs and RRs accordingly |
| | |
| Autumn 2019 | - One RR and 2 SRs are found to have been been excluded erroneously in coding round 1 and should be included (i.e., sampling 8 replacement SRs had led to oversampling and a final sample of 152 SRs) |
| | - We find that one RR had accidentally been coded based only on the Stage-1 protocol (including pilot data but no final results) and replace it with the final Stage-2 report (coding round 4) |
| | - AS revises the hypothesis introduction phrases for all RRs (based on the existing hypothesis quotes)|

# 2. Comparison of preregistration and eventual procedure
We preregistered our study on 7th December 2018. 
The preregistration document can be found at https://osf.io/sy927/. 
To facilitate the comparison between the preregistration and the procedure and analyses we eventually carried out, we annotated the preregistration document in Word, adding comments that for each 'decision unit' note whether it was carried out as preregistered and give a brief overview of relevant changes or additional details. 
The annotated preregistration document is provided in the file `appendix/preregistration_annotated.docx`.

# 3. Method
## 3.1 Sample
### 3.1.1 Registered Reports
As described in the main manuscript, we selected Registered Reports by retrieving the Registered Reports database curated by the Center for Open Science (COS, https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9) on 19th November 2018, determining the discipline each paper belonged to and excluding all non-Psychology papers, and then verifying if all Psychology papers on the list were indeed Registered Reports. 
The file `raw_data/source_data/RR_database_categorised_Nov2018.csv` contains the full list of papers that were included in the COS database when we accessed and copied it. 
The file also contains a variable indicating the discipline category we identified for each paper ('Discipline'), whether the papers was indeed a Registered Report ('RR', only checked for Psychology papers), and optional comments with details regarding this coding process ('comments').

##### Excluding Registered Replication Reports (RRRs):
The decision to exclude all RRRs was made during the main data collection (coding round 1), i.e. after piloting and after the study had been preregistered. 
MS and AS both noted that RRRs were particularly difficult to code because no clear hypothesis and/or no clear conclusions could be identified. 
This lead us to look up the editorial information for the RRR format, which clearly states that RRRs are not supposed to test hypotheses:  
'The conclusion of a Registered Replication Report should avoid categorizing each result as a success or failure to replicate. Instead, it should focus on the cumulative estimate of the effect size' (retrieved from https://www.psychologicalscience.org/publications/replication). 
Therefore we decided to categorically exclude all RRRs, regardless of whether or not we were able to code them.

### 3.1.2 Standard reports
Fanelli (2010) describes his sampling strategy as follows: 
'The sentence "test$^\ast$ the hypothes$^\ast$" was used to search all 10837 journals in the Essential Science Indicators database, which classifies journals univocally in 22 disciplines. When the number of papers retrieved from one discipline exceeded 150, papers were selected using a random number generator' (p. 8). 
The author informed us that the search was carried out in Web of Science using a Boolean search query which contained the key phrase and the full list of journal names for each scientific discipline (personal communication, 5th October 2018).
We implemented this exact procedure with the following changes: 
We used a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018), we only searched journals from the 'Psychiatry/Psychology' discipline, we used ISSNs instead of journal names in our search query (to prevent the risk that names of journals on the list could be sub-strings of names of journals not on the list, which would then be searched as well), and we restricted the search to papers published between 2013 and 2018 (to match them to the RR population).

Using a programming script written in Processing (The Processing Foundation, 2019) a single search query compatible with Web of Science was generated that contained the key phrase that had to occur in the paper ('test$^\ast$ the hypothes$^\ast$'), as well as the desired publication years (2013 up to and including 2018), and the ISSNs of all 633 journals listed as Psychiatry/Psychology journals in the ESI database (the journal list is provided in the file `raw_data/source_data/ESI_journallist_Psychology_20181204.xlsx`). 
The resulting search query is available in the file `raw_data/source_data/SR_search_query_WoS.txt`.

The search yielded 1919 results which were exported and saved in the file `raw_data/source_data/SR_search_results_WoS_20190107.csv`. 
We randomly selected 150 papers from this list using the sample() function in R and the seed '20190120':
```{r eval=FALSE}
# Load all 1919 search results
allSRs <- read.csv("SR_search_results_WoS_20190107.csv")

# Draw a random sample of 150 papers and put them into a new dataframe
set.seed(20190120)
x <- sample(c(1:1919), 150)
SRsample <- allSRs[x, ]
```

The same strategy and random seed were used to sample 8 replacement papers and later another replacement paper after one of the initial 8 had to be excluded:

```{r eval=FALSE}
# Sample 8 additional papers and put them into a new dataframe
set.seed(20190120)
replacement <- sample(c(1:1919), 158)[151:158]
SRreplacement <- allSRs[replacement, ]

# Sample 1 additional paper and put it into a new dataframe
set.seed(20190120)
replacement2 <- sample(c(1:1919), 159)[159]
SRreplacement2 <- allSRs[replacement2, ]
```
We checked if there was any overlap between the SR sample and the RR population (naturally, the SR sample should not contain any RRs) but this was not the case at any point.

## 3.2 Coding procedure
### 3.2.1 Hypothesis support
In our email correspondence with Daniele Fanelli, we asked for potential additional details of the coding procedure, but were told that not 'much more' than the information given in Fanelli (2010) had been used for coding instructions. 
All criteria we used are described in the main manuscript.

### 3.2.2 Replication status
Since the difference between replication studies and original studies was not the main focus of our paper, and because definitions of (e.g.) direct versus conceptual replications can be difficult to apply, we originally aimed for a 'lightweight' coding criterion and coded two binary variables: 'contains replication' and 'contains original work'. 
Both of these pertained to a full paper and were not restricted to the first hypothesis, meaning that a paper could be coded as 'contains a replication' even if the coded hypothesis was clearly novel. 
A paper could be coded as containing only replication research (i.e., 'contains replication' = 1, 'contains original work' = 0), only original work (i.e., 'contains replication' = 0, 'contains original work' = 1), or both (i.e., 'contains replication' = 1, 'contains original work' = 1), but not neither. 
However, we did not define any precise criteria for what would vs would not constitute a replication, which lead to coding disagreements between MS and AS for a relatively large number of papers (MS had used a relatively lenient, AS a quite strict definition of 'contains replication'). 
We therefore decided (after MS had completed his BEP thesis) to completely revise the way in which replication status was coded.

The main reason why we coded replication status in the first place was the idea that direct replication studies may sometimes or often be motivated by the authors' scepticisim of the original result, and that such direct replication studies may be overrepresented in the Registered Reports population compared to the standard literature. 
Therefore, we chose to focus on whether the authors' goal appeared to be to test if a previously published result holds up by conducting a close replication of the respective original study. 
We would thus ignore replications that had the goal to test if a hypothesis or method holds in a new context or population (i.e., that did not have the goal to challenge or verify the results in the original context or population) and 'internal' replications (i.e., replications of studies published in the same paper).

To limit the amount of work that would be caused by re-analysing all coded hypotheses, we decided to first search the full texts of all papers for the string 'replic' and only re-analyse the hypotheses of papers that contained the string (assuming that it would be highly unlikely that authors conducting a close replication in the way described above would not use words such as 'replication' or 'replicate' anywhere in their paper).

### 3.2.3 Hypothesis introductions
Hypothesis introduction phrases were first coded by MS and AS as short phrases taken from the coded hypothesis quotes. 
The idea was to extract phrases roughly analogous to Fanelli's (2010) search phrase 'test$^\ast$ the hypothes$^\ast$', but no clear coding criteria were defined. 
For the final analysis of hypothesis introductions in Registered Reports, AS revised the coding for all Registered Reports (but not standard reports) by starting with the coded hypothesis quotes and extracting minimal phrases that signalled that a hypothesis was being tested, stripped from all content-specific details in a consistent manner across all papers. 
Rather than focussing on the 'best' or just the first identifiable phrase, all identifiable hypothesis introduction phrases were coded, meaning that each paper could have one or several phrases. 
There was only one Registered Report for which no hypothesis introduction could be identified.

The revised hypothesis introduction phrases were captured in two new variables, 'RR_hyp_intro_abstract' and 'RR_hyp_intro_fulltext', depending on whether the phrase had been found in the abstract or the full text of the respective paper (this information was relevant since typically the contents of abstracts, but not full texts, are searchable via search engines). 
The revised hypothesis introduction phrases were coded by AS alone and not double-coded. 
However, they are very similar to the phrases coded by MS and AS in the initial coding round (the main difference being increased consistency across papers).

### 3.2.4 Additional measures
For the sake of completeness, we report all other recorded measures not described thus far in the following (*all* recorded measures are included and described in the dataset `raw_data/positive_results_in_registered_reports_masterfile_data.xlsx`).

* We coded direct quotes of either 'finding', 'conclusion', or both, depending on how the hypothesis-relevant results were reported (we adopted these two variables from the data excerpt provided by Fanelli). 
* To track the coding process and facilitate double-coding and disagreement resolution, we coded 
  + time spent per paper
  + coding certainty (scale from 1 = not certain to 5 = very certain), 
  + if the full text could be accessed
  + if the hypothesis had been coded from the abstract or full text
  + if the finding/conclusion had been coded from the abstract or full text
  + any individual coder's remarks
  + any remarks regarding the resolution of coding disagreements
* While revising our coding criteria for replication status, we also coded if the coded hypothesis introduction for a paper contained the string 'replic' and if a paper was part of a special issue focussed on replication, but in the end did not use these two variables (we did not run any analyses on them).

# 4. Analyses
## 4.1 Robustness analysis
Our preregistration does not specify whether or not excluded standard reports would be replaced (by resampling). 
In the initial analysis for his BEP thesis, MS did not replace any papers due to time constraints (his analysis included 142 SRs and 68 RRs), but we later decided that the SR sample should be filled up to achieve the planned sample size of 150 standard reports. 
As mentioned above and in the manuscript, we resampled SRs until 8 additional ones that met our inclusion criteria had been found, but later realised that 2 SRs excluded in the initial analysis should actually be included, meaning that we had oversampled and achieved a sample size of 152 rather than 150.

Because the decision to add 8 SRs could potentially affect our results, we re-ran our main analysis without the resampled papers as a robustness check. 
This analysis thus includes the 144 standard reports from the first sample we drew that met our inclusion criteria and the same 71 Registered Reports as the main analysis reported in the manuscript. 
Note that these are 3 Registered Reports more than included in MS' initial analysis: One had been part of the initial sample but was excluded for reasons we later found were erroneous, and two were cases about whose Registered Report status we were not sufficiently sure at the time of MS' initial analysis, but which we later learned met the Registered Reports criteria and could be included.

```{r include=FALSE}
source(here("analysis", "02_quantitative_analyses.R"))
```
Of the `r n.SR.round1` standard reports sampled in Round 1,  `r n.support.SR.round1` had positive results, a positive result rate of $`r printnum(prop.support.SR.round1*100)` \%$ ($95 \%$ CI [`r printnum(min(SR.binom.round1$conf.int)*100)`, `r printnum(max(SR.binom.round1$conf.int)*100)`]). 
The difference between this group of standard reports and all Registered Reports ($`r printnum((prop.support.SR.round1-prop.support.RR)*100)` \%$) is thus nearly identical to the one found in the main analysis ($`r printnum((prop.support.SR-prop.support.RR)*100)` \%$). 
Recalculating the one-sided proportions test and the equivalence test (both with an alpha level of $5\%$) shows that this difference is still statistically significant, $\chi^2 = `r printnum(proptestresult.robcheck$statistic)`$, $p `r printp(proptestresult.robcheck$p.value)`$, and still not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$, $z = `r printnum(min(tostresult.robcheck$TOST_z1, tostresult.robcheck$TOST_z2))`$, $p `r printp(max(tostresult.robcheck$TOST_p1, tostresult.robcheck$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
We thus conclude that the decision to replace excluded standard reports by resampling does not affect our results or conclusions in a meaningful way.

## 4.2 Calculating combinations of the proportion of true hypotheses and statistical power compatible with the observed results (Figure 3) 
The following serves to further explain the calculation and reasoning underlying Figure 3 in the manuscript.

Psychologists most commonly test hypotheses using frequentist statistics, specifically null-hypothesis significance testing (NHST). 
Typically this means testing a null hypothesis which predicts that the tested effect or relationship is exactly zero. 
If a significant *p*-value is observed ($p < \alpha$, typically with $\alpha = .05$), the null hypothesis is rejected and its complement, the alternative hypothesis (which predicts that the tested effect or relationship is *not* zero), is accepted. 
Usually it is the alternative hypothesis that researchers are interested in, or that most closely corresponds to the 'research hypothesis' that is being studied.

For example, a research hypothesis could be 'watching an episode of Sesame Street increases positive affect as measured with the PANAS'. 
This hypothesis would typically be studied by testing the null hypothesis that the effect of watching Sesame Street on positive affect is exactly zero. 
A significant result would then be interpreted as *support* for the research hypothesis. 
This is why we refer to significant results as 'positive' results: 
They are typically used to argue in favour of the research hypothesis presented by the researcher, not to argue *against* the null hypothesis (which mainly serves as a statistical tool and is not itself of focal interest).

Statistically, the probability of observing a significant result depends on three factors: the probability that the tested null hypothesis is true, the probability of obtaining a significant result when the null hypothesis is true ($\alpha$), and the probability of obtaining a significant result when the null hypothesis is false (power, i.e. $1-\beta$). 
However, if research hypotheses are commonly the alternative hypothesis and thus complementary to the null hypothesis (meaning that if one is true, the other must be false, and vice versa), and significant results are 'positive' results in favour of the research hypothesis, we can flip the language in the following way:

> The probability of observing a positive result depends on three factors: the probability that the research hypothesis is true (i.e., that the null hypothesis is false), the probability of obtaining a positive result when the tested research hypothesis is false ($\alpha$), and the probability of obtaining a positive result when the research hypothesis is true (power, i.e. $1-\beta$).

This can be expressed in the equation presented in the note of Figure 3 in the manuscript:
   $$PRR = (1-t)*\alpha + t*(1-\beta)$$
$PRR$ is the positive result rate (the proportion of positive results, i.e. the number of positive results divided by the number of all results), $t$ is the proportion of true (research) hypotheses (i.e., the number of true hypotheses divided by the number of all hypotheses), $\alpha$ is the probability of obtaining a positive result when testing a false hypothesis, and $1-\beta$ is the probability of obtaining a positive result when testing a true hypothesis (power).
By solving this equation for $t$ and for $1-\beta$, respectively, we can calculate the combinations of these two factors that would produce a given positive result rate for a given level of $\alpha$.
Figure 3 in the manuscript was produced by solving for power, $1 - \beta = (PRR - \alpha + \alpha * t) / t$, and calculating power for all levels of $t$ from 0 to 1, $\alpha = .05$, and the observed positive result rates of original standard reports, original Registered Reports, and all Registered Reports.

This calculation and the plot shown in Figure 3 are extreme simplifications of the research process and not intended for drawing inferences about (e.g.) how many of the hypotheses tested in the literature are true versus false. 
However, we believe that it serves as a useful illustration of the assumptions that would be necessary to explain our results without referring to an influence of publication bias or error inflation.

### 2020-01-13 preprint/manuscript.Rmd
minor tweaks, updated bib file

--- 2020-01-12 manuscript/manuscript.Rmd
@@
 abstract: >
-  When scientific studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the research scientists conduct.
-Psychology researchers have been concerned about the degree of distortion publication bias and “questionable research practices” have caused in their own literature, and developed new research and publication practices that aim to minimise these biases.
-Registered Reports are a new publication format in which peer review and the decision to publish take place before the study results are known.
-We compared the results in the full population of published Registered Reports in Psychology ($N = 71$, as of November 2018) with a random sample of hypothesis-testing studies from the standard literature ($N = 152$) by searching 633 journals for the phrase ‘test* the hypothes*’ [replicating a method by @Fanelli2010].
+  When studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the evidence for scientific claims.
+Psychological scientists have been concerned about the degree of distortion in their literature due to publication bias and inflated Type-1 error rates.
+Registered Reports were developed with the goal to minimise such biases: In this new publication format, peer review and the decision to publish take place before the study results are known.
+We compared the results in the full population of published Registered Reports in Psychology ($N = 71$ as of November 2018) with a random sample of hypothesis-testing studies from the standard literature ($N = 152$) by searching 633 journals for the phrase ‘test* the hypothes*’ [replicating a method by @Fanelli2010].
 Analysing the first hypothesis reported in each paper, we found $96.05\%$ positive results in standard reports, but only $43.66\%$ positive results in Registered Reports.
 The difference remained nearly as large when direct replications were excluded from the analysis ($95.95\%$ vs $50\%$ positive results).
-Although our study is not a direct test of the effects of publication bias and questionable research practices on the literature, the large gap between standard reports and Registered Reports suggests that psychologists under-report negative results to an extent that threatens cumulative science.
+This large gap suggests that psychologists under-report negative results to an extent that threatens cumulative science.
+Although our study did not directly test the effectiveness of Registered Reports at reducing bias, these results show that the introduction of Registered Reports has led to a much larger proportion of negative results appearing in the published literature compared to standard reports.
 
-keywords          : "Publication bias, Registered Reports"
-wordcount         : "6395"
+keywords          : "Publication bias, Registered Reports, hypothesis testing"
+wordcount         : "6408"
 
@@
 library("knitr")
+library("here")
 library("TOSTER")
@@
 library("reshape2")
-library("here")
-library("codebook")
+library("codebook") # not needed to knit the manuscript, but loaded here so it automatically gets cited at the end since it was used to create the codebook
+library("rio") # not needed to knit the manuscript, but loaded here so it automatically gets cited at the end since it was used to create the codebook
 ```
@@
 The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for "test$^\ast$ the hypothes$^\ast$" will miss most of the hypothesis-testing studies in the psychological literature.
-Results based on this search phrase may not generalise to all published studies. 
+Results based on this search phrase may thus not generalise to all published studies. 
 For example, it is possible that authors are more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., "we examined the role of ...").

### 2020-01-13 preprint/manuscript.tex
minor tweaks, updated bib file

--- 2020-01-12 manuscript/manuscript.tex
@@
             pdftitle={An excess of positive results: Comparing the standard Psychology literature with Registered Reports},
-            pdfkeywords={Publication bias, Registered Reports},
+            pdfkeywords={Publication bias, Registered Reports, hypothesis testing},
             pdfborder={0 0 0},
@@
 
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
 % Manuscript styling
@@
 Correspondence concerning this article should be addressed to Anne M. Scheel, Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands. E-mail: a.m.scheel@tue.nl}
-\keywords{Publication bias, Registered Reports\newline\indent Word count: 6395}
+\keywords{Publication bias, Registered Reports, hypothesis testing\newline\indent Word count: 6408}
 \usepackage{dblfloatfix}
@@
 \abstract{
-When scientific studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the research scientists conduct.
-Psychology researchers have been concerned about the degree of distortion publication bias and ``questionable research practices'' have caused in their own literature, and developed new research and publication practices that aim to minimise these biases.
-Registered Reports are a new publication format in which peer review and the decision to publish take place before the study results are known.
-We compared the results in the full population of published Registered Reports in Psychology (\(N = 71\), as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (\(N = 152\)) by searching 633 journals for the phrase `test* the hypothes*' (replicating a method by Fanelli, 2010).
+When studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the evidence for scientific claims.
+Psychological scientists have been concerned about the degree of distortion in their literature due to publication bias and inflated Type-1 error rates.
+Registered Reports were developed with the goal to minimise such biases: In this new publication format, peer review and the decision to publish take place before the study results are known.
+We compared the results in the full population of published Registered Reports in Psychology (\(N = 71\) as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (\(N = 152\)) by searching 633 journals for the phrase `test* the hypothes*' (replicating a method by Fanelli, 2010).
 Analysing the first hypothesis reported in each paper, we found \(96.05\%\) positive results in standard reports, but only \(43.66\%\) positive results in Registered Reports.
 The difference remained nearly as large when direct replications were excluded from the analysis (\(95.95\%\) vs \(50\%\) positive results).
-Although our study is not a direct test of the effects of publication bias and questionable research practices on the literature, the large gap between standard reports and Registered Reports suggests that psychologists under-report negative results to an extent that threatens cumulative science.
+This large gap suggests that psychologists under-report negative results to an extent that threatens cumulative science.
+Although our study did not directly test the effectiveness of Registered Reports at reducing bias, these results show that the introduction of Registered Reports has led to a much larger proportion of negative results appearing in the published literature compared to standard reports.
 }
@@
 
-In a recent commentary on benefits and challenges of open-science practices for early-career researchers, Allen \& Mehler (2019) conducted a similar investigation:
+In a recent commentary on benefits and challenges of open-science practices for early-career researchers, Allen and Mehler (2019) conducted a similar investigation:
 They coded the proportion of null results in the 127 biomedical and psychology Registered Reports listed in the COS database as of September 2018.
@@
 They compared these numbers to an estimate of \(5-20\%\) null results in the standard literature.
-This \(5-20\%\) estimate is based on data from Fanelli (2012), who coded only the first hypothesis of each paper (identical to Fanelli, 2010), and Cristea \& Ioannidis (2018){]}, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
+This \(5-20\%\) estimate is based on data from Fanelli (2012), who coded only the first hypothesis of each paper (identical to Fanelli, 2010), and Cristea and Ioannidis (2018){]}, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
 
@@
 Fanelli, 2012).
-Furthermore, our estimate of the positive result rate for Registered Reports (\(43.66 \%\)) is comparable to the \(39.5\%\) reported by Allen \& Mehler (2019), despite some differences in method and studied population.
+Furthermore, our estimate of the positive result rate for Registered Reports (\(43.66 \%\)) is comparable to the \(39.5\%\) reported by Allen and Mehler (2019), despite some differences in method and studied population.
 
@@
 The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for \enquote{test\(^\ast\) the hypothes\(^\ast\)} will miss most of the hypothesis-testing studies in the psychological literature.
-Results based on this search phrase may not generalise to all published studies.
+Results based on this search phrase may thus not generalise to all published studies.
 For example, it is possible that authors are more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., \enquote{we examined the role of \ldots{}}).
@@
 For example, the positive result rates in Sterling (1959), Sterling et al.
-(1995), and the original studies included in the Reproducibility Project: Psychology (Collaboration, 2015) were \(97.28\%\), \(95.56\%\), and \(97\%\), respectively.
+(1995), and the original studies included in the Reproducibility Project: Psychology (Open Science Collaboration, 2015) were \(97.28\%\), \(95.56\%\), and \(97\%\), respectively.
 Motyl et al. (2017) report \(89.17\%\) and \(92.01\%\) significant results for \enquote{critical} hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively.
@@
 The data and code necessary to reproduce all analyses reported here, as well as additional supplementary information, is available at \url{https://osf.io/dbhgr}.
-The manuscript including figures and statistical analyses, the appendix, and the codebook available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.1; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rmarkdown} (Version 2.0; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
+The manuscript including figures and statistical analyses, the appendix, and the codebook available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
 
@@
 
-\leavevmode\hypertarget{ref-OSC2015}{}%
-Collaboration, O. S. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716. \url{https://doi.org/10.1126/science.aac4716}
+\leavevmode\hypertarget{ref-R-rio}{}%
+Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018). \emph{Rio: A swiss-army knife for data file i/o}.
 
@@
 \url{https://doi.org/10.1027/1864-9335/a000192}
+
+\leavevmode\hypertarget{ref-OSC2015}{}%
+Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716. \url{https://doi.org/10.1126/science.aac4716}
 
@@
 
-\leavevmode\hypertarget{ref-Agnoli2017}{}%
-Agnoli, F., Wicherts, J.
-M., Veldkamp, C.
-L.
-S., Albiero, P., \& Cubelli, R.
-(2017).
-Questionable research practices among italian research psychologists.
-\emph{PLOS ONE}, \emph{12}(3), e0172792.
-\url{https://doi.org/10.1371/journal.pone.0172792}
-
-\leavevmode\hypertarget{ref-Allen2019}{}%
-Allen, C., \& Mehler, D.
-M.
-A.
-(2019).
-Open science challenges, benefits and tips in early career and beyond.
-\emph{PLOS Biology}, \emph{17}(5), e3000246.
-\url{https://doi.org/10.1371/journal.pbio.3000246}
-
-\leavevmode\hypertarget{ref-R-codebook}{}%
-Arslan, R. C. (2018). How to automatically generate rich codebooks from study metadata. PsyArxiv. \url{https://doi.org/10.31234/osf.io/5qc6h}
-
-\leavevmode\hypertarget{ref-Atkinson1982}{}%
-Atkinson, D.
-R., Furlong, M.
-J., \& Wampold, B.
-E.
-(1982).
-Statistical significance, reviewer evaluations, and the scientific process: Is there a (statistically) significant relationship?
-\emph{Journal of Counseling Psychology}, \emph{29}(2), 189--194.
-\url{https://doi.org/10.1037/0022-0167.29.2.189}
-
-\leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
-
-\leavevmode\hypertarget{ref-Chambers2013}{}%
-Chambers, C. (2013). Registered reports: A new publishing initiative at Cortex, \emph{49}(3), 609--610. Retrieved from \url{http://orca.cf.ac.uk/45177/1/Chambers_Cortex_2013b_GreenOA.pdf}
-
-\leavevmode\hypertarget{ref-Chambers2015}{}%
-Chambers, C., Dienes, Z., McIntosh, R., Rotshtein, P., \& Willmes, K.
-(2015).
-Registered Reports: Realigning incentives in scientific publishing.
-\emph{Cortex}, \emph{66}, 1--2.
-\url{https://doi.org/10.1016/j.cortex.2015.03.022}
-
-\leavevmode\hypertarget{ref-OSC2015}{}%
-Collaboration, O. S. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716. \url{https://doi.org/10.1126/science.aac4716}
-
-\leavevmode\hypertarget{ref-Cristea2018}{}%
-Cristea, I.
-A., \& Ioannidis, J.
-P.
-A.
-(2018).
-P values in display items are ubiquitous and almost invariably significant: A survey of top science journals.
-\emph{PLOS ONE}, \emph{13}(5), e0197440.
-\url{https://doi.org/10.1371/journal.pone.0197440}
-
-\leavevmode\hypertarget{ref-Fanelli2010}{}%
-Fanelli, D. (2010). "Positive" results increase down the hierarchy of the sciences. \emph{PLoS ONE}, \emph{5}(4), e10068. \url{https://doi.org/10.1371/journal.pone.0010068}
-
-\leavevmode\hypertarget{ref-Fanelli2012}{}%
-Fanelli, D. (2012). Negative results are disappearing from most disciplines and countries. \emph{Scientometrics}, \emph{90}(3), 891--904. \url{https://doi.org/10.1007/s11192-011-0494-7}
-
-\leavevmode\hypertarget{ref-Fiedler2016}{}%
-Fiedler, K., \& Schwarz, N. (2016). Questionable Research Practices Revisited. \emph{Social Psychological and Personality Science}, \emph{7}(1), 45--52. \url{https://doi.org/10.1177/1948550615612150}
-
-\leavevmode\hypertarget{ref-Franco2014}{}%
-Franco, A., Malhotra, N., \& Simonovits, G.
-(2014).
-Publication bias in the social sciences: Unlocking the file drawer.
-\emph{Science}, \emph{345}(6203), 1502--1505.
-\url{https://doi.org/10.1126/science.1255484}
-
-\leavevmode\hypertarget{ref-Franco2016}{}%
-Franco, A., Malhotra, N., \& Simonovits, G.
-(2016).
-Underreporting in Psychology Experiments: Evidence From a Study Registry.
-\emph{Social Psychological and Personality Science}, \emph{7}(1), 8--12.
-\url{https://doi.org/10.1177/1948550615598377}
-
-\leavevmode\hypertarget{ref-Greenwald1975}{}%
-Greenwald, A. G. (1975). Consequences of Prejudice Against the Null Hypothesis. \emph{Psychological Bulletin}, \emph{82}(1), 1--20.
-
-\leavevmode\hypertarget{ref-John2012}{}%
-John, L.
-K., Loewenstein, G., \& Prelec, D.
-(2012).
-Measuring the Prevalence of Questionable Research Practices With Incentives for Truth Telling.
-\emph{Psychological Science}, \emph{23}(5), 524--532.
-\url{https://doi.org/10.1177/0956797611430953}
-
-\leavevmode\hypertarget{ref-Jonas2016}{}%
-Jonas, K.
-J., \& Cesario, J.
-(2016).
-How can preregistration contribute to research in our field?
-\emph{Comprehensive Results in Social Psychology}, \emph{1}(1-3), 1--7.
-\url{https://doi.org/10.1080/23743603.2015.1070611}
-
-\leavevmode\hypertarget{ref-Kerr1998}{}%
-Kerr, N. L. (1998). HARKing: Hypothesizing after the results are known. \emph{Personality and Social Psychology Review}, \emph{2}(3), 196--217. \url{https://doi.org/10.1207/s15327957pspr0203_4}
-
-\leavevmode\hypertarget{ref-Kohler2019}{}%
-Köhler, T., \& Cortina, J.
-M.
-(2019).
-Play It Again, Sam!
-An Analysis of Constructive Replication in the Organizational Sciences.
-\emph{Journal of Management}, 014920631984398.
-\url{https://doi.org/10.1177/0149206319843985}
-
-\leavevmode\hypertarget{ref-R-TOSTER}{}%
-Lakens, D.
-(2017).
-Equivalence tests: A practical primer for t-tests, correlations, and meta-analyses.
-\emph{Social Psychological and Personality Science}, \emph{1}, 1--8.
-\url{https://doi.org/10.1177/1948550617697177}
-
-\leavevmode\hypertarget{ref-Lakens2019b}{}%
-Lakens, D. (n.d.). The Value of Preregistration for Psychological Science: A Conceptual Analysis. \url{https://doi.org/10.31234/osf.io/jbh4w}
-
-\leavevmode\hypertarget{ref-Lakens2018a}{}%
-Lakens, D., Scheel, A.
-M., \& Isager, P.
-M.
-(2018).
-Equivalence Testing for Psychological Research: A Tutorial.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269.
-\url{https://doi.org/10.1016/j.ympev.2015.01.015}
-
-\leavevmode\hypertarget{ref-Mahoney1977}{}%
-Mahoney, M.
-J.
-(1977).
-Publication Prejudices: An Experimental Study of Confirmatory Bias in the Peer Review System.
-\emph{Cognitive Therapy and Research}, \emph{1}(2), 161--175.
-\url{https://doi.org/10.1007/BF01173636}
-
-\leavevmode\hypertarget{ref-Makel2012}{}%
-Makel, M.
-C., Plucker, J.
-A., \& Hegarty, B.
-(2012).
-Replications in Psychology Research: How Often Do They Really Occur?
-\emph{Perspectives on Psychological Science}.
-\url{https://doi.org/10.1177/1745691612460688}
-
-\leavevmode\hypertarget{ref-Maxwell2004}{}%
-Maxwell, S.
-E.
-(2004).
-The Persistence of Underpowered Studies in Psychological Research: Causes, Consequences, and Remedies.
-\emph{Psychological Methods}, \emph{9}(2), 147--163.
-\url{https://doi.org/10.1037/1082-989X.9.2.147}
-
-\leavevmode\hypertarget{ref-Motyl2017}{}%
-Motyl, M., Demos, A.
-P., Carsel, T.
-S., Hanson, B.
-E., Melton, Z.
-J., Mueller, A.
-B., \ldots{} Skitka, L.
-J.
-(2017).
-The state of social and personality science: Rotten to the core, not so bad, getting better, or getting worse?
-\emph{Journal of Personality and Social Psychology}, \emph{113}(1), 34--58.
-\url{https://doi.org/10.1037/pspa0000084}
-
-\leavevmode\hypertarget{ref-Mueller-Langer2019}{}%
-Mueller-Langer, F., Fecher, B., Harhoff, D., \& Wagner, G.
-G.
-(2019).
-Replication studies in economics---How many and which papers are chosen for replication, and why?
-\emph{Research Policy}, \emph{48}(1), 62--83.
-\url{https://doi.org/10.1016/j.respol.2018.07.019}
-
-\leavevmode\hypertarget{ref-R-here}{}%
-Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}
-
-\leavevmode\hypertarget{ref-Nosek2014}{}%
-Nosek, B.
-A., \& Lakens, D.
-(2014).
-Registered Reports: A Method to Increase the Credibility of Published Results.
-\emph{Social Psychology}, \emph{45}(3), 137--141.
-\url{https://doi.org/10.1027/1864-9335/a000192}
-
-\leavevmode\hypertarget{ref-Pridemore2018}{}%
-Pridemore, W.
-A., Makel, M.
-C., \& Plucker, J.
-A.
-(2018).
-Replication in Criminology and the Social Sciences.
-\emph{Annual Review of Criminology}, \emph{1}(1), 19--38.
-\url{https://doi.org/10.1146/annurev-criminol-032317-091849}
-
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
-
-\leavevmode\hypertarget{ref-RRRwebsite}{}%
-Registered Replication Reports. (n.d.). Retrieved December 28, 2019, from \url{https://www.psychologicalscience.org/publications/replication}
-
-\leavevmode\hypertarget{ref-Rohatgi2018}{}%
-Rohatgi, A. (2018). \emph{WebPlotDigitizer - Web Based Plot Digitizer}. Austin, Texas, USA. Retrieved from \url{https://automeris.io/WebPlotDigitizer}
-
-\leavevmode\hypertarget{ref-Rosenthal1979}{}%
-Rosenthal, R. (1979). The file drawer problem and tolerance for null results. \emph{Psychological Bulletin}, \emph{86}(3), 638--641. \url{https://doi.org/10.1037/0033-2909.86.3.638}
-
-\leavevmode\hypertarget{ref-RStudioTeam2019}{}%
-RStudio Team. (2019). \emph{RStudio: Integrated development environment for r}. Boston, MA: RStudio, Inc. Retrieved from \url{http://www.rstudio.com/}
-
-\leavevmode\hypertarget{ref-Simmons2011}{}%
-Simmons, J.
-P., Nelson, L.
-D., \& Simonsohn, U.
-(2011).
-False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
-\emph{Psychological Science}, \emph{22}(11), 1359--1366.
-\url{https://doi.org/10.1177/0956797611417632}
-
-\leavevmode\hypertarget{ref-Simons2018}{}%
-Simons, D.
-J.
-(2018).
-Introducing Advances in Methods and Practices in Psychological Science.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(1), 3--6.
-\url{https://doi.org/10.1177/2515245918757424}
-
-\leavevmode\hypertarget{ref-Simons2014}{}%
-Simons, D.
-J., Holcombe, A.
-O., \& Spellman, B.
-A.
-(2014).
-An Introduction to Registered Replication Reports at \emph{Perspectives} \emph{on} \emph{Psychological Science}.
-\emph{Perspectives on Psychological Science}, \emph{9}(5), 552--555.
-\url{https://doi.org/10.1177/1745691614543974}
-
-\leavevmode\hypertarget{ref-Sterling1959}{}%
-Sterling, T.
-D.
-(1959).
-Publication Decisions and their Possible Effects on Inferences Drawn from Tests of Significance---or Vice Versa.
-\emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.
-\url{https://doi.org/10.1080/01621459.1959.10501497}
-
-\leavevmode\hypertarget{ref-Sterling1995}{}%
-Sterling, T.
-D., Rosenbaum, W.
-L., \& Weinkam, J.
-J.
-(1995).
-Publication Decisions Revisited: The Effect of the Outcome of Statistical Tests on the Decision to Publish and Vice Versa.
-\emph{The American Statistician}, \emph{49}(1), 108.
-\url{https://doi.org/10.2307/2684823}
-
-\leavevmode\hypertarget{ref-Szucs2017}{}%
-Szucs, D., \& Ioannidis, J.
-P.
-A.
-(2017).
-Empirical assessment of published effect sizes and power in the recent cognitive neuroscience and psychology literature.
-\emph{PLOS Biology}, \emph{15}(3), e2000797.
-\url{https://doi.org/10.1371/journal.pbio.2000797}
-
-\leavevmode\hypertarget{ref-vanAssen2014}{}%
-van Assen, M.
-A.
-L.
-M., van Aert, R.
-C.
-M., Nuijten, M.
-B., \& Wicherts, J.
-M.
-(2014).
-Why Publishing Everything Is More Effective than Selective Publishing of Statistically Significant Results.
-\emph{PLOS ONE}, \emph{9}(1), e84896.
-\url{https://doi.org/10.1371/journal.pone.0084896}
-
-\leavevmode\hypertarget{ref-R-reshape2}{}%
-Wickham, H. (2007). Reshaping data with the reshape package. \emph{Journal of Statistical Software}, \emph{21}(12), 1--20. Retrieved from \url{http://www.jstatsoft.org/v21/i12/}
-
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
-Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
-
-\leavevmode\hypertarget{ref-R-stringr}{}%
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
-
-\leavevmode\hypertarget{ref-Winter2013}{}%
-Winter, J.
-de, \& Happee, R.
-(2013).
-Why Selective Publication of Statistically Significant Results Can Be Effective.
-\emph{PLOS ONE}, \emph{8}(6), e66463.
-\url{https://doi.org/10.1371/journal.pone.0066463}
-
-\leavevmode\hypertarget{ref-Wiseman2019}{}%
-Wiseman, R., Watt, C., \& Kornbrot, D. (2019). Registered reports: An early example and analysis. \emph{PeerJ}, \emph{7}, e6232. \url{https://doi.org/10.7717/peerj.6232}
-
-\leavevmode\hypertarget{ref-R-knitr}{}%
-Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
-
-\leavevmode\hypertarget{ref-R-bookdown}{}%
-Xie, Y. (2016). \emph{Bookdown: Authoring books and technical documents with R markdown}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://github.com/rstudio/bookdown}
-
-\leavevmode\hypertarget{ref-R-rmarkdown}{}%
-Xie, Y., Allaire, J., \& Grolemund, G. (2018). \emph{R markdown: The definitive guide}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://bookdown.org/yihui/rmarkdown}
-
 \end{document}

### 2020-01-13 appendix/appendix.Rmd
fixed typos

@@
 MS and AS both noted that RRRs were particularly difficult to code because no clear hypothesis and/or no clear conclusions could be identified. 
-This lead us to look up the editorial information for the RRR format, which clearly states that RRRs are not supposed to test hypotheses:  
+This led us to look up the editorial information for the RRR format, which clearly states that RRRs are not supposed to test hypotheses:  
 'The conclusion of a Registered Replication Report should avoid categorizing each result as a success or failure to replicate.
@@
 A paper could be coded as containing only replication research (i.e., 'contains replication' = 1, 'contains original work' = 0), only original work (i.e., 'contains replication' = 0, 'contains original work' = 1), or both (i.e., 'contains replication' = 1, 'contains original work' = 1), but not neither.
-However, we did not define any precise criteria for what would vs would not constitute a replication, which lead to coding disagreements between MS and AS for a relatively large number of papers (MS had used a relatively lenient, AS a quite strict definition of 'contains replication').
+However, we did not define any precise criteria for what would vs would not constitute a replication, which led to coding disagreements between MS and AS for a relatively large number of papers (MS had used a relatively lenient, AS a quite strict definition of 'contains replication').
 We therefore decided (after MS had completed his BEP thesis) to completely revise the way in which replication status was coded.
 
-The main reason why we coded replication status in the first place was the idea that direct replication studies may sometimes or often be motivated by the authors' scepticisim of the original result, and that such direct replication studies may be overrepresented in the Registered Reports population compared to the standard literature.
+The main reason why we coded replication status in the first place was the idea that direct replication studies may sometimes or often be motivated by the authors' scepticism of the original result, and that such direct replication studies may be overrepresented in the Registered Reports population compared to the standard literature.
 Therefore, we chose to focus on whether the authors' goal appeared to be to test if a previously published result holds up by conducting a close replication of the respective original study. 

### 2020-01-13 preprint/manuscript.Rmd
fixed typos

@@
 A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias. 
-After an initial coding attempt with ill-defined coding criteria lead to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered): 
+After an initial coding attempt with ill-defined coding criteria led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered): 
 We searched the full texts of all papers for the string "replic$^\ast$" [cf.
@@
 We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports. 
-Because neither hypotheses, authors, nor editors are randomly assigned to each publication format we cannot draw firm conclusions about the causes that lead to a difference in the proportion of supported hypotheses.
+Because neither hypotheses, authors, nor editors were randomly assigned to each publication format we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
 Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.

### 2020-01-13 preprint/manuscript.Rmd
minor tweaks

@@
 When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability. 
-However, when published findings are systematically biased, cumulative science breaks down: 
+But when published findings are systematically biased, cumulative science breaks down: 
 Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
-Unfortunately there are good reasons to believe that the psychology literature is not a faithful representation of all research psychologists conduct. 
-For more than half a century, scientists have repeatedly noticed a suspiciously high 'success' rate in psychology:
-Studying 362 empirical articles published in four psychology journals in 1955/56, @Sterling1959 found that a whopping $97.28\%$ of the studies that used significance tests rejected the null hypothesis.
+Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct. 
+For more than half a century, scientists have repeatedly noticed a suspiciously high "success" rate in Psychology:
+Studying 362 empirical articles published in four Psychology journals in 1955/56, @Sterling1959 found that a whopping $97.28\%$ of the studies that used significance tests rejected the null hypothesis.
 A replication of this study performed on articles published in 1986/87 reported $95.56\%$ statistically significant results [@Sterling1995]. 
-Similarly, a seminal study by @Fanelli2010 compared the literatures of 20 disciplines and found that $91.5\%$ of papers published in psychology reported support for their first or main hypothesis, the highest number of all disciplines in the study.
+Similarly, a seminal study by @Fanelli2010 compared the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology reported support for their first or main hypothesis, the highest estimate of all disciplines in the study.
 For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$.
-In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes must consistently be very high (given the same study design).
+In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very high.
 
@@
 Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
-These include editors and reviewers selectively rejecting manuscripts with negative results ["reviewer bias", @Mahoney1977; @Greenwald1975] and researchers deciding not to submit studies with negative results for publication ["file-drawering"; @Rosenthal1979].
+These include editors and reviewers selectively rejecting manuscripts with negative results ["reviewer bias", @Greenwald1975; @Mahoney1977] and researchers deciding not to submit studies with negative results for publication ["file-drawering"; @Rosenthal1979].
 Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is [typically, though not always, leading to an inflated type-I error rate, see also @Lakens2019b].
@@
 
-Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because because it weeds out  low-quality research that would only pollute the literature [@Winter2013; but see @vanAssen2014].
+Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature [@Winter2013; but see @vanAssen2014].
 How problematic selective publishing is in practice remains an empirical question: 
@@
 But how many positive results would such an unbiased literature contain in reality? 
-We set out to explore this question by comparing the rate of positive results in a sample from the current psychology literature to a set of studies that were published in a new format created to minimise QRPs and publication bias: Registered Reports.
+We set out to explore this question by comparing the rate of positive results in a sample from the current Psychology literature to a set of studies that were published in a new format created to minimise QRPs and publication bias: Registered Reports.
 
@@
 An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection [for a historical overview, see @Wiseman2019].
-Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of p-hacking via restricted flexibility in data analysis.
+Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of *p*-hacking via restricted flexibility in data analysis.
 However, preregistration does not prevent file-drawering or reviewer bias and may thus be toothless in fighting publication bias. 
@@
 The final report undergoes another round of peer review, but this time only to check if the authors adhered to the plan outlined in their protocol (and, if applicable, if the data passes pre-specified quality checks).
-RRs thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known. 
-Since its introduction at the journal Cortex in 2013, the format has rapidly gained popularity and is offered by 207 journals at the time of writing (http://cos.io/rr).
+Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known. 
+Since its introduction at the journal Cortex in 2013, the format has rapidly gained popularity and is offered by 222 journals at the time of writing (http://cos.io/rr).
 
@@
 
-Assuming a constant alpha level, the rate of positive results in a literature is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
+Assuming a constant alpha level, the rate of positive results in a literature (i.e., the proportion of supported hypotheses among all tested hypotheses) is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
 The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature [see e.g., @Maxwell2004; @Szucs2017].
-Therefore, if the emerging Registered Reports literature in psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
-At this time, we have good reasons to believe in a difference in bias, but little reason to believe in a difference in the proportion of true hypotheses (at least regarding original hypotheses, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate (i.e., the proportion of supported hypotheses among all tested hypotheses).
+Therefore, if the emerging Registered Reports literature in Psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
+At this time, we have good reasons to believe in a difference in bias, but less reason to believe in a difference in the proportion of true hypotheses (at least regarding original hypotheses, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate.
 Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.
@@
 ## The current study
-The goal of our study was to test if Registered Reports in psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as "standard reports", SRs), and to estimate the size of this potential difference.
-We set out to replicate a study by @Fanelli2010 on a new sample of standard reports in psychology and compared them to all published Registered Reports in psychology. 
+The goal of our study was to test if Registered Reports in Psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as "standard reports", SRs), and to estimate the size of this potential difference.
+We set out to replicate a study by @Fanelli2010 on a new sample of standard reports in Psychology and compared them to all published Registered Reports in Psychology. 
 Fanelli searched for articles containing the phrase "test$^\ast$ the hypothes$^\ast$", drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
-For standard reports we used the same sampling method (restricted to the psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS). 
-We chose Fanelli's method because Fanelli's -@Fanelli2010 and -@Fanelli2012 studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
+For standard reports we used the same sampling method (restricted to the Psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS). 
+We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies. 
 We additionally coded if studies were replications or original work because many published Registered Reports are replications. 
-If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, and a higher proportion of replications among Registered Reports than standard reports could therefore introduce a confound.
+If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, which could lead to a larger proportion of negative results regardless of bias.
 
 In a recent commentary on benefits and challenges of open-science practices for early-career researchers, @Allen2019 conducted a similar investigation: 
-They coded the proportion of null results in the 127 biomedical and psychology Registered Reports listed in the COS database as of September 2018. 
+They coded the proportion of null results in the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018. 
 We were not aware of their parallel efforts when we planned our study in September and October 2018. 
@@
 They compared these numbers to an estimate of $5-20\%$ null results in the standard literature. 
-This $5-20\%$ estimate is based on data from @Fanelli2012, who coded only the first hypothesis of each paper [identical to @Fanelli2010], and @Cristea2018], who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
+This $5-20\%$ estimate is based on data from @Fanelli2012, who coded only the first hypothesis of each paper [identical to @Fanelli2010], and @Cristea2018, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
 
@@
 Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
-This allows others to verify (or contest) our results and provides an interesting resource for future meta-scientific research.
+This allows others to verify (or contest) our results and may provide an interesting resource for future meta-scientific research.
 
 # Methods
-After conducting a pilot to test the planned procedure we preregistered our study (https://osf.io/s8e97). 
+After conducting a pilot to test the planned procedure, we preregistered our study (https://osf.io/s8e97). 
 Methods and analyses described here were preregistered unless otherwise noted. 
@@
 We searched their titles, abstracts, and keywords for "hypothes$^\ast$" OR "replicat$^\ast$" OR "test$^\ast$" OR "examine$^\ast$" OR "predict$^\ast$" and found that $`r n.hypintros.fivewords.RR`/`r n.RR`$ Registered Reports ($`r printnum(n.hypintros.fivewords.RR/n.RR*100)` \%$) would have been detected this way.
-We do not know how well these search terms represent the population of hypothesis-testing studies in psychology, but a structured investigation of this question would be very useful for future meta-research.
+We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question would be very useful for future meta-research.
 
 # Discussion
-We examined the proportion of psychology articles that find support for their first tested hypothesis and found a large difference ($`r printnum(prop.support.SR*100)` \%$ vs $`r printnum(prop.support.RR*100)` \%$) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
+We examined the proportion of Psychology articles that find support for their first tested hypothesis and found a large difference ($`r printnum(prop.support.SR*100)` \%$ vs $`r printnum(prop.support.RR*100)` \%$) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
 More than half of the analysed Registered Reports tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis ($`r printnum(prop.orig.support.SR*100)` \%$ vs $`r printnum(prop.orig.support.RR*100)` \%$).
@@
 The positive result rate we found in standard reports ($`r printnum(prop.support.SR*100)` \%$) is slightly higher than the $91.5\%$ reported by @Fanelli2010, although this difference was not statistically significant.
-Our replication in a more recent sample of the psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 [cf.
+Our replication in a more recent sample of the Psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 [cf.
 @Fanelli2012].
@@
 As mentioned above, it is a-priori plausible that the Registered Reports format is used selectively for particularly risky hypotheses. 
-This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in psychology. 
+This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in Psychology. 
 It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias. 

### 2020-01-13 preprint/manuscript.tex
minor tweaks

@@
 When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability.
-However, when published findings are systematically biased, cumulative science breaks down:
+But when published findings are systematically biased, cumulative science breaks down:
 Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
-Unfortunately there are good reasons to believe that the psychology literature is not a faithful representation of all research psychologists conduct.
-For more than half a century, scientists have repeatedly noticed a suspiciously high \enquote{success} rate in psychology:
-Studying 362 empirical articles published in four psychology journals in 1955/56, Sterling (1959) found that a whopping \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
+Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
+For more than half a century, scientists have repeatedly noticed a suspiciously high \enquote{success} rate in Psychology:
+Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that a whopping \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
 A replication of this study performed on articles published in 1986/87 reported \(95.56\%\) statistically significant results (Sterling, Rosenbaum, \& Weinkam, 1995).
-Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in psychology reported support for their first or main hypothesis, the highest number of all disciplines in the study.
+Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first or main hypothesis, the highest estimate of all disciplines in the study.
 For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
-In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes must consistently be very high (given the same study design).
+In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very high.
 
@@
 Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
-These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Mahoney, 1977; Greenwald, 1975) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
-Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate, see also Lakens, n.d.).
+These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Greenwald, 1975; Mahoney, 1977) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
+Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate, see also Lakens, 2019).
 These include presenting unexpected results as having been predicted a priori (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
@@
 
-Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because because it weeds out low-quality research that would only pollute the literature (Winter \& Happee, 2013; but see van Assen, van Aert, Nuijten, \& Wicherts, 2014).
+Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature (Winter \& Happee, 2013; but see van Assen, van Aert, Nuijten, \& Wicherts, 2014).
 How problematic selective publishing is in practice remains an empirical question:
@@
 But how many positive results would such an unbiased literature contain in reality?
-We set out to explore this question by comparing the rate of positive results in a sample from the current psychology literature to a set of studies that were published in a new format created to minimise QRPs and publication bias: Registered Reports.
+We set out to explore this question by comparing the rate of positive results in a sample from the current Psychology literature to a set of studies that were published in a new format created to minimise QRPs and publication bias: Registered Reports.
 
@@
 An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
-Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of p-hacking via restricted flexibility in data analysis.
+Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of \emph{p}-hacking via restricted flexibility in data analysis.
 However, preregistration does not prevent file-drawering or reviewer bias and may thus be toothless in fighting publication bias.
@@
 The final report undergoes another round of peer review, but this time only to check if the authors adhered to the plan outlined in their protocol (and, if applicable, if the data passes pre-specified quality checks).
-RRs thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
-Since its introduction at the journal Cortex in 2013, the format has rapidly gained popularity and is offered by 207 journals at the time of writing (\url{http://cos.io/rr}).
+Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
+Since its introduction at the journal Cortex in 2013, the format has rapidly gained popularity and is offered by 222 journals at the time of writing (\url{http://cos.io/rr}).
 
@@
 
-Assuming a constant alpha level, the rate of positive results in a literature is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
+Assuming a constant alpha level, the rate of positive results in a literature (i.e., the proportion of supported hypotheses among all tested hypotheses) is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
 The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature (see e.g., Maxwell, 2004; Szucs \& Ioannidis, 2017).
-Therefore, if the emerging Registered Reports literature in psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
-At this time, we have good reasons to believe in a difference in bias, but little reason to believe in a difference in the proportion of true hypotheses (at least regarding original hypotheses, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate (i.e., the proportion of supported hypotheses among all tested hypotheses).
+Therefore, if the emerging Registered Reports literature in Psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
+At this time, we have good reasons to believe in a difference in bias, but less reason to believe in a difference in the proportion of true hypotheses (at least regarding original hypotheses, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate.
 Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.
@@
 
-The goal of our study was to test if Registered Reports in psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
-We set out to replicate a study by Fanelli (2010) on a new sample of standard reports in psychology and compared them to all published Registered Reports in psychology.
+The goal of our study was to test if Registered Reports in Psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
+We set out to replicate a study by Fanelli (2010) on a new sample of standard reports in Psychology and compared them to all published Registered Reports in Psychology.
 Fanelli searched for articles containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}, drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
-For standard reports we used the same sampling method (restricted to the psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS).
-We chose Fanelli's method because Fanelli's (2010) and (2012) studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
+For standard reports we used the same sampling method (restricted to the Psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS).
+We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
 We additionally coded if studies were replications or original work because many published Registered Reports are replications.
-If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, and a higher proportion of replications among Registered Reports than standard reports could therefore introduce a confound.
+If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, which could lead to a larger proportion of negative results regardless of bias.
 
 In a recent commentary on benefits and challenges of open-science practices for early-career researchers, Allen and Mehler (2019) conducted a similar investigation:
-They coded the proportion of null results in the 127 biomedical and psychology Registered Reports listed in the COS database as of September 2018.
+They coded the proportion of null results in the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018.
 We were not aware of their parallel efforts when we planned our study in September and October 2018.
@@
 They compared these numbers to an estimate of \(5-20\%\) null results in the standard literature.
-This \(5-20\%\) estimate is based on data from Fanelli (2012), who coded only the first hypothesis of each paper (identical to Fanelli, 2010), and Cristea and Ioannidis (2018){]}, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
+This \(5-20\%\) estimate is based on data from Fanelli (2012), who coded only the first hypothesis of each paper (identical to Fanelli, 2010), and Cristea and Ioannidis (2018), who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
 
@@
 Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
-This allows others to verify (or contest) our results and provides an interesting resource for future meta-scientific research.
+This allows others to verify (or contest) our results and may provide an interesting resource for future meta-scientific research.
 
@@
 
-After conducting a pilot to test the planned procedure we preregistered our study (\url{https://osf.io/s8e97}).
+After conducting a pilot to test the planned procedure, we preregistered our study (\url{https://osf.io/s8e97}).
 Methods and analyses described here were preregistered unless otherwise noted.
@@
 A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
-After an initial coding attempt with ill-defined coding criteria lead to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
+After an initial coding attempt with ill-defined coding criteria led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
 We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf.
@@
 We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) Registered Reports (\(97.18 \%\)) would have been detected this way.
-We do not know how well these search terms represent the population of hypothesis-testing studies in psychology, but a structured investigation of this question would be very useful for future meta-research.
+We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question would be very useful for future meta-research.
 
@@
 
-We examined the proportion of psychology articles that find support for their first tested hypothesis and found a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
+We examined the proportion of Psychology articles that find support for their first tested hypothesis and found a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
 More than half of the analysed Registered Reports tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
@@
 The positive result rate we found in standard reports (\(96.05 \%\)) is slightly higher than the \(91.5\%\) reported by Fanelli (2010), although this difference was not statistically significant.
-Our replication in a more recent sample of the psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 (cf.
+Our replication in a more recent sample of the Psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 (cf.
 Fanelli, 2012).
@@
 We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports.
-Because neither hypotheses, authors, nor editors are randomly assigned to each publication format we cannot draw firm conclusions about the causes that lead to a difference in the proportion of supported hypotheses.
+Because neither hypotheses, authors, nor editors were randomly assigned to each publication format we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
 Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
 As mentioned above, it is a-priori plausible that the Registered Reports format is used selectively for particularly risky hypotheses.
-This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in psychology.
+This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in Psychology.
 It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias.
@@
 \leavevmode\hypertarget{ref-Lakens2019b}{}%
-Lakens, D. (n.d.). The Value of Preregistration for Psychological Science: A Conceptual Analysis. \url{https://doi.org/10.31234/osf.io/jbh4w}
+Lakens, D. (2019). The Value of Preregistration for Psychological Science: A Conceptual Analysis. \url{https://doi.org/10.31234/osf.io/jbh4w}
 

### 2020-01-13 preprint/manuscript.Rmd
minor tweaks

@@
 We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
-An overview of the sampling process and all exclusions are shown in Figure\ \@ref(fig:sampling).
+An overview of the sampling process and all exclusions is shown in Figure\ \@ref(fig:sampling).
 
@@
 Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded.
-"Preregistered": study had been preregistered but was not a full RR; "results-blind review": article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); "ambiguous": Four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance.
-We chose to exclude these cases to be conservative.
+"Preregistered": study had been preregistered but was not a full RR; "results-blind review": article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); "ambiguous": four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance (we chose to exclude these cases to be conservative).
 
@@
 Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with https://cos.io/rr).
-For papers not clearly labelled as Registered Reports we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly. 
+For papers not clearly labelled as Registered Reports, we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly. 
 Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.\ \@ref(fig:sampling)).
@@
 ## Measures and coding procedure
-The main dependent variable was whether or not the first hypothesis was supported or not, as reported by the authors.
+The main dependent variable was whether the first hypothesis was supported or not, as reported by the authors.
 We tried to follow Fanelli's [-@Fanelli2010] coding procedure as closely as possible, which he describes as follows:
@@
 Like @Fanelli2010, we coded hypotheses as having received "support", "partial support", or "no support", which was recoded into a binary "support" (full or partial) vs "no support" variable for the analysis.
-Coding disagreements between full and partial support were deemed minor since they would not affect the final results, thus only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.
+Coding disagreements between full and partial support were deemed minor since they would not affect the final results.
+Thus, only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.
 
@@
 Based on our experiences during the pilot, we added one coding criterion: 
-If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first tested hypothesis rather than the first hypothesis mentioned in the text.
+If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first *tested* hypothesis rather than the first hypothesis mentioned in the text.
 In Registered Reports we coded the first preregistered hypothesis, thus excluding unregistered pilot studies. 
-MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code ($`r sum(included$coded_by_AS & included$is_RR==1)`$ RRs $= `r printnum(sum(included$coded_by_AS & included$is_RR==1)/sum(included$is_RR==1)*100)`\%$ and $`r sum(included$coded_by_AS & included$is_RR==0)`$ SRs $= `r printnum(sum(included$coded_by_AS & included$is_RR==0)/sum(included$is_RR==0)*100)` \%$).
+MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code ($`r sum(included$coded_by_AS & included$is_RR==1)`$ RRs and $`r sum(included$coded_by_AS & included$is_RR==0)`$ SRs).
 Only `r support.disagreement.major` disagreements were major (Cohen's kappa = `r printp(kappa.support)`) and subsequently resolved by discussion; `r support.disagreement.minor` were minor (disagreement between "support" and "partial support").
-We preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+We had preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
 
@@
 A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias. 
-After an initial coding attempt with ill-defined coding criteria led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered): 
+After an initial coding attempt with ill-defined coding criteria had led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered): 
 We searched the full texts of all papers for the string "replic$^\ast$" [cf.
-@Makel2012; @Kohler2019; @Mueller-Langer2019; @Pridemore2018], and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
+@Makel2012; @Kohler2019; @Mueller-Langer2019; @Pridemore2018], and for papers that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
 Conceptual replications and internal replications were not counted as replications in this narrow sense: 
-The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
-AS coded all papers, DL double-coded `r rep.RR.coded.DL` Registered Reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR)*100)` \%$) and `r rep.SR.coded.DL` standard reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR==0)*100)` \%$).
+The reason to code replication status was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
+AS coded all papers, DL double-coded `r rep.RR.coded.DL` Registered Reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR)*100)` \%$) and `r rep.SR.coded.DL` standard reports ($`r printnum(rep.SR.coded.DL/sum(included$is_RR==0)*100)` \%$).
 There were `r rep.disagreements` disagreements (Cohen's kappa = `r printp(kappa.rep)`), all were resolved by discussion.
@@
 All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above. 
-All of these are documented in the Appendix and our shared dataset and codebook.
+All of these are documented in the Appendix and in our shared dataset and codebook.
 
@@
 
-> A one-sided proportion test with an alpha level of $5\%$ will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports in psychology.
+> A one-sided proportion test with an alpha level of $5\%$ will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports [we later changed the term to "standard reports"] in psychology.
 > In addition to testing if there is a statistically significant difference between RRs and conventional reports, we will test if the difference is smaller than our smallest effect size of interest using an equivalence test for proportion tests with an alpha level of $5\%$ [@Lakens2018a].
@@
 However, this difference cannot account for the stark overall difference between standard reports and Registered Reports described above: 
-Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports -- $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$ -- was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(reptost$TOST_z1, reptost$TOST_z2))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
+Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports, $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$, was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(reptost$TOST_z1, reptost$TOST_z2))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
 
@@
 
-Since our standard reports sample represents a direct replication of @Fanelli2010 for the discipline Psychiatry & Psychology, another interesting question to ask is how our results compare to Fanelli's.
+Since our standard-reports sample represents a direct replication of @Fanelli2010 for the discipline Psychiatry & Psychology, another interesting question to ask is how our results compare to Fanelli's.
 The difference between the positive result rate for standard reports in our sample ($`r printnum(prop.support.SR*100)`\%$) and Fanelli's ($`r printnum(prop.support.Fanelli*100)`\%$) is $`r printnum((prop.support.SR-prop.support.Fanelli)*100)`\%$.
@@
 Finally, we analysed the language that was used to introduce or refer to hypotheses in Registered Reports.
-We were interested in whether the search phrase "test$^\ast$ the hypothes$^\ast$" used by Fanelli captured the way researchers write about hypothesis tests reasonably well.
+We were interested in whether the search phrase "test$^\ast$ the hypothes$^\ast$" used by Fanelli captures the way researchers write about hypothesis tests reasonably well.
 The answer is a resounding "no":
@@
 Clearly "test$^\ast$" and "hypothes$^\ast$" are quite popular, yet they co-occurred only `r test.and.hypothes` times and more than half of all hypothesis introductions (`r nrow(intros.long)-test.or.hypothes`/`r nrow(intros.long)`) contained neither word.
-Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 ($`r printnum(30/43*100)`\%$) hypothesis introductions found in original Registered Reports contained either "test$^\ast$" or "hypothes$^\ast$" or both, while only 16 out of 54 ($`r printnum(16/54*100)`\%$) hypothesis introductions in direct replication Registered Reports did.
+Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 ($`r printnum(30/43*100)`\%$) hypothesis introductions found in original Registered Reports contained either "test$^\ast$" or "hypothes$^\ast$" or both, but the same was true for only 16 out of 54 ($`r printnum(16/54*100)`\%$) hypothesis introductions in direct replication Registered Reports.
 
@@
 Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
-Tables 2 and 3 list all unique hypothesis introductions and their frequency for original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems ("hypothes$^\ast$", "replicat$^\ast$", "test$^\ast$", "examine$^\ast$", "predict$^\ast$").
+
+Tables 2 and 3 list all unique hypothesis introductions and their frequency in original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems ("hypothes$^\ast$", "replicat$^\ast$", "test$^\ast$", "examine$^\ast$", "predict$^\ast$").
 Using five as a cut-off value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.
@@
 Therefore we additionally tested how many of the Registered Reports would have been detected in a regular search using our five most frequent word stems. 
-We searched their titles, abstracts, and keywords for "hypothes$^\ast$" OR "replicat$^\ast$" OR "test$^\ast$" OR "examine$^\ast$" OR "predict$^\ast$" and found that $`r n.hypintros.fivewords.RR`/`r n.RR`$ Registered Reports ($`r printnum(n.hypintros.fivewords.RR/n.RR*100)` \%$) would have been detected this way.
+We searched titles, abstracts, and keywords for "hypothes$^\ast$" OR "replicat$^\ast$" OR "test$^\ast$" OR "examine$^\ast$" OR "predict$^\ast$" and found that $`r n.hypintros.fivewords.RR`/`r n.RR`$ Registered Reports ($`r printnum(n.hypintros.fivewords.RR/n.RR*100)` \%$) would have been detected this way.
 We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question would be very useful for future meta-research.
@@
 The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the published research we are used to.
-Standard publication formats seem to lead scientists to miss out on many high-quality studies with negative results, which are available in the Registered Reports literature. 
+Standard publication formats seem to lead psychological scientists to miss out on many high-quality studies with negative results, which are available in the Registered Reports literature.
 The absence of negative results is a serious threat to a cumulative science.
-Reliable protection against questionable research practices and publication bias is crucial to ensure the integrity of the literature. 
-The Registered Reports format is a promising candidate for bias protection, but we are only at the beginning of understanding its effectiveness and robustness in different contexts and scientific disciplines.
+In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a much more credible record of the research scientists conduct.
 

### 2020-01-13 preprint/manuscript.tex
minor tweaks

@@
 We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
-An overview of the sampling process and all exclusions are shown in Figure~\ref{fig:sampling}.
+An overview of the sampling process and all exclusions is shown in Figure~\ref{fig:sampling}.
 
@@
 Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded.
-\enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: Four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance.
-We chose to exclude these cases to be conservative.}\label{fig:sampling}
+\enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance (we chose to exclude these cases to be conservative).}\label{fig:sampling}
 \end{figure*}
@@
 Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
-For papers not clearly labelled as Registered Reports we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
+For papers not clearly labelled as Registered Reports, we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
 Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
@@
 
-The main dependent variable was whether or not the first hypothesis was supported or not, as reported by the authors.
+The main dependent variable was whether the first hypothesis was supported or not, as reported by the authors.
 We tried to follow Fanelli's (2010) coding procedure as closely as possible, which he describes as follows:
@@
 Like Fanelli (2010), we coded hypotheses as having received \enquote{support}, \enquote{partial support}, or \enquote{no support}, which was recoded into a binary \enquote{support} (full or partial) vs \enquote{no support} variable for the analysis.
-Coding disagreements between full and partial support were deemed minor since they would not affect the final results, thus only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.
+Coding disagreements between full and partial support were deemed minor since they would not affect the final results.
+Thus, only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.
 
@@
 Based on our experiences during the pilot, we added one coding criterion:
-If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first tested hypothesis rather than the first hypothesis mentioned in the text.
+If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first \emph{tested} hypothesis rather than the first hypothesis mentioned in the text.
 In Registered Reports we coded the first preregistered hypothesis, thus excluding unregistered pilot studies.
-MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs \(= 33.80\%\) and \(47\) SRs \(= 30.92 \%\)).
+MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
 Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
-We preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+We had preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
 
@@
 A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
-After an initial coding attempt with ill-defined coding criteria led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
+After an initial coding attempt with ill-defined coding criteria had led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
 We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf.
-Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
+Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for papers that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
 Conceptual replications and internal replications were not counted as replications in this narrow sense:
-The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
-AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(21.05 \%\)).
+The reason to code replication status was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
+AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(65.13 \%\)).
 There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.
@@
 All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above.
-All of these are documented in the Appendix and our shared dataset and codebook.
+All of these are documented in the Appendix and in our shared dataset and codebook.
 
@@
 \begin{quote}
-A one-sided proportion test with an alpha level of \(5\%\) will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports in psychology.
+A one-sided proportion test with an alpha level of \(5\%\) will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports {[}we later changed the term to \enquote{standard reports}{]} in psychology.
 In addition to testing if there is a statistically significant difference between RRs and conventional reports, we will test if the difference is smaller than our smallest effect size of interest using an equivalence test for proportion tests with an alpha level of \(5\%\) (Lakens, Scheel, \& Isager, 2018).
@@
 However, this difference cannot account for the stark overall difference between standard reports and Registered Reports described above:
-Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports -- \(45.95\%\) -- was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
+Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports, \(45.95\%\), was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
 
@@
 
-Since our standard reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question to ask is how our results compare to Fanelli's.
+Since our standard-reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question to ask is how our results compare to Fanelli's.
 The difference between the positive result rate for standard reports in our sample (\(96.05\%\)) and Fanelli's (\(91.49\%\)) is \(4.56\%\).
@@
 Finally, we analysed the language that was used to introduce or refer to hypotheses in Registered Reports.
-We were interested in whether the search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} used by Fanelli captured the way researchers write about hypothesis tests reasonably well.
+We were interested in whether the search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} used by Fanelli captures the way researchers write about hypothesis tests reasonably well.
 The answer is a resounding \enquote{no}:
@@
 Clearly \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times and more than half of all hypothesis introductions (51/97) contained neither word.
-Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions found in original Registered Reports contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, while only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication Registered Reports did.
+Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions found in original Registered Reports contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, but the same was true for only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication Registered Reports.
 
@@
 Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
-Tables 2 and 3 list all unique hypothesis introductions and their frequency for original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
+
+Tables 2 and 3 list all unique hypothesis introductions and their frequency in original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
 Using five as a cut-off value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.
@@
 Therefore we additionally tested how many of the Registered Reports would have been detected in a regular search using our five most frequent word stems.
-We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) Registered Reports (\(97.18 \%\)) would have been detected this way.
+We searched titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) Registered Reports (\(97.18 \%\)) would have been detected this way.
 We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question would be very useful for future meta-research.
@@
 The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the published research we are used to.
-Standard publication formats seem to lead scientists to miss out on many high-quality studies with negative results, which are available in the Registered Reports literature.
+Standard publication formats seem to lead psychological scientists to miss out on many high-quality studies with negative results, which are available in the Registered Reports literature.
 The absence of negative results is a serious threat to a cumulative science.
-Reliable protection against questionable research practices and publication bias is crucial to ensure the integrity of the literature.
-The Registered Reports format is a promising candidate for bias protection, but we are only at the beginning of understanding its effectiveness and robustness in different contexts and scientific disciplines.
+In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?} The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a much more credible record of the research scientists conduct.
 

### 2020-01-13 appendix/appendix.Rmd
minor changes to explanations of Figure 3

@@
 Figure 3 in the manuscript was produced by solving for power, $1 - \beta = (PRR - \alpha + \alpha * t) / t$, and calculating power for all levels of $t$ from 0 to 1, $\alpha = .05$, and the observed positive result rates of original standard reports, original Registered Reports, and all Registered Reports.
-
-This calculation and the plot shown in Figure 3 are extreme simplifications of the research process and not intended for drawing inferences about (e.g.) how many of the hypotheses tested in the literature are true versus false.
-However, we believe that it serves as a useful illustration of the assumptions that would be necessary to explain our results without referring to an influence of publication bias or error inflation.

### 2020-01-13 preprint/manuscript.Rmd
minor changes to explanations of Figure 3

@@
 # Discussion
-We examined the proportion of Psychology articles that find support for their first tested hypothesis and found a large difference ($`r printnum(prop.support.SR*100)` \%$ vs $`r printnum(prop.support.RR*100)` \%$) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
-More than half of the analysed Registered Reports tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis ($`r printnum(prop.orig.support.SR*100)` \%$ vs $`r printnum(prop.orig.support.RR*100)` \%$).
+We examined the proportion of Psychology articles that find support for their first tested hypothesis and discovered a large difference ($`r printnum(prop.support.SR*100)` \%$ vs $`r printnum(prop.support.RR*100)` \%$) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
+More than half of the analysed hypothesis tests in Registered Reports were direct replications of previous work, but the difference between standard reports and Registered Reports was still large when direct replications were excluded from the analysis ($`r printnum(prop.orig.support.SR*100)` \%$ vs $`r printnum(prop.orig.support.RR*100)` \%$).
 The introduction of Registered Reports has clearly led to a much larger proportion of null results appearing in the published literature compared to standard reports.
@@
 This is highly unlikely, meaning that the standard literature is unlikely to reflect reality. 
-As we noted above, there is good reason to assume that methodological rigour and statistical power in Registered Reports are as high, or higher, than in standard reports, leaving the rate of true hypotheses and bias as remaining explanations.
+As we noted above, there is good reason to assume that methodological rigour and statistical power in Registered Reports are as high as in standard reports or higher, leaving the rate of true hypotheses and bias as remaining explanations.
 
@@
 The curve for all SRs (i.e, including replications; $`r printnum(prop.support.SR*100)` \%$ positive results, $N = `r n.SR`$) is not shown because it is almost identical to the one for original SRs.
-Plotted values were calculated using the equation $PRR = \alpha*(1-t) + (1-\beta)*t$; with $PRR =$ positive result rate, $\alpha =$ probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), $1-\beta =$ probability of obtaining a positive result when testing a true hypothesis (power), and $t =$ proportion of true hypotheses; and solving for $t$ and $1-\beta$, respectively.
+Plotted values were calculated using the equation $PRR = \alpha*(1-t) + (1-\beta)*t$; with $PRR =$ positive result rate, $\alpha =$ probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), $1-\beta =$ probability of obtaining a positive result when testing a true hypothesis (power), and $t =$ proportion of true hypotheses; and solving for $t$ and $1-\beta$, respectively (with the simplifying assumption that all studies in one group have the same power).
 
@@
 We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports. 
-Because neither hypotheses, authors, nor editors were randomly assigned to each publication format we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
+Because neither hypotheses, authors, nor editors were randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
 Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.

### 2020-01-13 preprint/manuscript.tex
minor changes to explanations of Figure 3

@@
 
-We examined the proportion of Psychology articles that find support for their first tested hypothesis and found a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
-More than half of the analysed Registered Reports tested hypotheses based on direct replications, but the difference between standard reports and Registered Reports was still large when all direct replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
+We examined the proportion of Psychology articles that find support for their first tested hypothesis and discovered a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
+More than half of the analysed hypothesis tests in Registered Reports were direct replications of previous work, but the difference between standard reports and Registered Reports was still large when direct replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
 The introduction of Registered Reports has clearly led to a much larger proportion of null results appearing in the published literature compared to standard reports.
@@
 This is highly unlikely, meaning that the standard literature is unlikely to reflect reality.
-As we noted above, there is good reason to assume that methodological rigour and statistical power in Registered Reports are as high, or higher, than in standard reports, leaving the rate of true hypotheses and bias as remaining explanations.
+As we noted above, there is good reason to assume that methodological rigour and statistical power in Registered Reports are as high as in standard reports or higher, leaving the rate of true hypotheses and bias as remaining explanations.
 
@@
 The curve for all SRs (i.e, including replications; \(96.05 \%\) positive results, \(N = 152\)) is not shown because it is almost identical to the one for original SRs.
-Plotted values were calculated using the equation \(PRR = \alpha*(1-t) + (1-\beta)*t\); with \(PRR =\) positive result rate, \(\alpha =\) probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), \(1-\beta =\) probability of obtaining a positive result when testing a true hypothesis (power), and \(t =\) proportion of true hypotheses; and solving for \(t\) and \(1-\beta\), respectively.}\label{fig:powerbaserate}
+Plotted values were calculated using the equation \(PRR = \alpha*(1-t) + (1-\beta)*t\); with \(PRR =\) positive result rate, \(\alpha =\) probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), \(1-\beta =\) probability of obtaining a positive result when testing a true hypothesis (power), and \(t =\) proportion of true hypotheses; and solving for \(t\) and \(1-\beta\), respectively (with the simplifying assumption that all studies in one group have the same power).}\label{fig:powerbaserate}
 \end{figure*}
@@
 We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports.
-Because neither hypotheses, authors, nor editors were randomly assigned to each publication format we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
+Because neither hypotheses, authors, nor editors were randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
 Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.

### 2020-01-13 preprint/manuscript.Rmd
small updates

@@
 keywords          : "Publication bias, Registered Reports, hypothesis testing"
-wordcount         : "6408"
+#wordcount         : "6465"
 
@@
 
-knitr::include_graphics("Sampling_exclusions_and_resampling.png")
+knitr::include_graphics("sampling_process_flowchart.png")
 ```
@@
 The first hypothesis test may not be representative for all hypothesis tests reported in a paper, and the order of reporting may differ between standard reports and Registered Reports. 
-Perhaps Registered Report authors are more likely to present their hypotheses in "chronological" order, whereas standard report authors tend to rearrange the order in which hypotheses are reported based on their outcomes, and present supported hypotheses first.
+Perhaps Registered-Report authors are more likely to present their hypotheses in "chronological" order, whereas standard-report authors tend to rearrange the order in which hypotheses are reported based on their outcomes, and present supported hypotheses first.
 Here again, the converging estimates from the four studies cited above (none of which use the first-hypothesis rule) make it seem unlikely that our result is an artefact of this decision. 
@@
 In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
-In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a much more credible record of the research scientists conduct.
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a more credible record of the research scientists conduct.
 

### 2020-01-13 preprint/manuscript.tex
small updates

@@
 Correspondence concerning this article should be addressed to Anne M. Scheel, Den Dolech 1, Atlas 9.417, 5600 MB, Eindhoven, The Netherlands. E-mail: a.m.scheel@tue.nl}
-\keywords{Publication bias, Registered Reports, hypothesis testing\newline\indent Word count: 6408}
+\keywords{Publication bias, Registered Reports, hypothesis testing}
 \usepackage{dblfloatfix}
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{Sampling process and exclusions for standard reports and Registered Reports.
+\includegraphics[width=\textwidth]{sampling_process_flowchart} \caption{Sampling process and exclusions for standard reports and Registered Reports.
 Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded.
@@
 The first hypothesis test may not be representative for all hypothesis tests reported in a paper, and the order of reporting may differ between standard reports and Registered Reports.
-Perhaps Registered Report authors are more likely to present their hypotheses in \enquote{chronological} order, whereas standard report authors tend to rearrange the order in which hypotheses are reported based on their outcomes, and present supported hypotheses first.
+Perhaps Registered-Report authors are more likely to present their hypotheses in \enquote{chronological} order, whereas standard-report authors tend to rearrange the order in which hypotheses are reported based on their outcomes, and present supported hypotheses first.
 Here again, the converging estimates from the four studies cited above (none of which use the first-hypothesis rule) make it seem unlikely that our result is an artefact of this decision.
@@
 In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?} The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
-In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a much more credible record of the research scientists conduct.
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a more credible record of the research scientists conduct.
 

### 2020-01-13 appendix/appendix.Rmd
added links to Disclosures and Appendix

@@
 To facilitate the comparison between the preregistration and the procedure and analyses we eventually carried out, we annotated the preregistration document in Word, adding comments that for each 'decision unit' note whether it was carried out as preregistered and give a brief overview of relevant changes or additional details.
-The annotated preregistration document is provided in the file `appendix/preregistration_annotated.docx`.
+The annotated preregistration document is provided in the file [`appendix/preregistration_annotated.docx`](https://osf.io/e79vb/) (to view the annotations the file must be opened with a word processor like MS Word).
 
@@
 ### 3.1.1 Registered Reports
-As described in the main manuscript, we selected Registered Reports by retrieving the Registered Reports database curated by the Center for Open Science (COS, https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9) on 19th November 2018, determining the discipline each paper belonged to and excluding all non-Psychology papers, and then verifying if all Psychology papers on the list were indeed Registered Reports.
-The file `raw_data/source_data/RR_database_categorised_Nov2018.csv` contains the full list of papers that were included in the COS database when we accessed and copied it. 
+As described in the main manuscript, we selected Registered Reports by retrieving the Registered Reports database curated by the Center for Open Science^[retrieved from https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (COS) on 19th November 2018, determining the discipline each paper belonged to and excluding all non-Psychology papers, and then verifying if all Psychology papers on the list were indeed Registered Reports.
+The file [`raw_data/source_data/RR_database_categorised_Nov2018.csv`](https://osf.io/8ybrk/) contains the full list of papers that were included in the COS database when we accessed and copied it. 
 The file also contains a variable indicating the discipline category we identified for each paper ('Discipline'), whether the papers was indeed a Registered Report ('RR', only checked for Psychology papers), and optional comments with details regarding this coding process ('comments').
@@
 We implemented this exact procedure with the following changes: 
-We used a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018), we only searched journals from the 'Psychiatry/Psychology' discipline, we used ISSNs instead of journal names in our search query (to prevent the risk that names of journals on the list could be sub-strings of names of journals not on the list, which would then be searched as well), and we restricted the search to papers published between 2013 and 2018 (to match them to the RR population).
+We used a current version of the Essential Science Indicators (ESI) database^[retrieved from http://help.incites.clarivate.com/incitesLiveESI/ESIGroup/overviewESI/esiJournalsList.html] (retrieved on 4th December 2018), we only searched journals from the 'Psychiatry/Psychology' discipline, we used ISSNs instead of journal names in our search query (to prevent the risk that names of journals on the list could be sub-strings of names of journals not on the list, which would then be searched as well), and we restricted the search to papers published between 2013 and 2018 (to match them to the RR population).
 

### 2020-01-13 preprint/manuscript.Rmd
added links to Disclosures and Appendix

@@
   - \usepackage{setspace}
-  - \captionsetup[figure]{font={stretch=1, small}, skip=11pt}
+  - \captionsetup[figure]{font={stretch=1, small}, skip=12pt}
   - \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
@@
 ### Data, materials, and online resources
-The data and code necessary to reproduce all analyses reported here, as well as additional supplementary information, is available at <https://osf.io/dbhgr>.
-The manuscript including figures and statistical analyses, the appendix, and the codebook available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.
+The data and code necessary to reproduce all analyses reported here, as well as the [Appendix](https://osf.io/vcqya/), the [preregistration document](https://osf.io/sy927/) and additional supplementary files, are available at <https://osf.io/dbhgr>.
+The manuscript including figures and statistical analyses, the Appendix, and the [codebook](https://osf.io/6jrkz/) available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.
 

### 2020-01-13 raw_data/positive_results_in_registered_reports_codebook.Rmd
changed dataset file name and updated codebook accordingly

@@
 ```{r prepare_codebook}
-codebook_data <- import("positive_results_in_registered_reports_masterfile_data.xlsx")
+codebook_data <- import("positive_results_in_registered_reports_data.xlsx")
 
 # Read codebook from second sheet in Excel file.
-dict <- import("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "data_dictionary")
+dict <- import("positive_results_in_registered_reports_data.xlsx", sheet = "data_dictionary")
 

### 2020-01-13 appendix/appendix.Rmd
added links to appendix

@@
 This document contains additional information about the methods and analyses reported in the manuscript '**An excess of positive results: Comparing the standard Psychology literature with Registered Reports**', as well as an additional robustness analysis (see section 4.1).
+This PDF was created in RMarkdown.
+The reproducible RMarkdown file, containing embedded code for the analysis in section 4.1, is available in our online repository at <https://osf.io/dbhgr> ([`appendix/appendix.Rmd`](https://osf.io/t4kc3/)).
 
@@
 
-Using a programming script written in Processing (The Processing Foundation, 2019) a single search query compatible with Web of Science was generated that contained the key phrase that had to occur in the paper ('test$^\ast$ the hypothes$^\ast$'), as well as the desired publication years (2013 up to and including 2018), and the ISSNs of all 633 journals listed as Psychiatry/Psychology journals in the ESI database (the journal list is provided in the file `raw_data/source_data/ESI_journallist_Psychology_20181204.xlsx`).
-The resulting search query is available in the file `raw_data/source_data/SR_search_query_WoS.txt`.
+Using a programming script written in Processing (The Processing Foundation, 2019) a single search query compatible with Web of Science was generated that contained the key phrase that had to occur in the paper ('test$^\ast$ the hypothes$^\ast$'), as well as the desired publication years (2013 up to and including 2018), and the ISSNs of all 633 journals listed as Psychiatry/Psychology journals in the ESI database (the journal list is provided in the file [`raw_data/source_data/ESI_journallist_Psychology_20181204.csv`](https://osf.io/x938b/)).
+The resulting search query is available in the file [`raw_data/source_data/SR_search_query_WoS.txt`](https://osf.io/9xah6/).
 
-The search yielded 1919 results which were exported and saved in the file `raw_data/source_data/SR_search_results_WoS_20190107.csv`. 
+The search yielded 1919 results which were exported and saved in the file [`raw_data/source_data/SR_search_results_WoS_20190107.csv`](https://osf.io/q5fgd/). 
 We randomly selected 150 papers from this list using the sample() function in R and the seed '20190120':
@@
 ### 3.2.4 Additional measures
-For the sake of completeness, we report all other recorded measures not described thus far in the following (*all* recorded measures are included and described in the dataset `raw_data/positive_results_in_registered_reports_masterfile_data.xlsx`).
+For the sake of completeness, we report all other recorded measures not described thus far in the following (*all* recorded measures are included and described in the dataset [`raw_data/positive_results_in_registered_reports_data.xlsx`](https://osf.io/aqr2s/)).
 

### 2020-01-13 preprint/manuscript.tex
added links to Disclosures and Appendix
final check

@@
 \usepackage{setspace}
-\captionsetup[figure]{font={stretch=1, small}, skip=11pt}
+\captionsetup[figure]{font={stretch=1, small}, skip=12pt}
 \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
@@
 
-The data and code necessary to reproduce all analyses reported here, as well as additional supplementary information, is available at \url{https://osf.io/dbhgr}.
-The manuscript including figures and statistical analyses, the appendix, and the codebook available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
+The data and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/vcqya/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration document} and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
+The manuscript including figures and statistical analyses, the Appendix, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
 

### 2020-01-14 preprint/manuscript.Rmd
changed one sentence in the Discussion and two in the description of replication status coding

@@
 Assuming a constant alpha level, the rate of positive results in a literature (i.e., the proportion of supported hypotheses among all tested hypotheses) is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
-The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature [see e.g., @Maxwell2004; @Szucs2017].
+The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature [see e.g., @Maxwell2004; @Szucs2017; @SingletonThorn2019].
 Therefore, if the emerging Registered Reports literature in Psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
@@
 For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase "test$^\ast$ the hypothes$^\ast$" and the ISSNs of all journals listed in the ESI Psychiatry/Psychology category.
-Using the same sample size as @Fanelli2010, we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed "20190120" (not specified in our preregistration, but no other seeds were tried).
-We initially excluded eight papers and replaced them (the decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had erroneously been excluded, leading to a final sample size of 152 rather than 150 (see Fig.\ \@ref(fig:sampling)).
+Using the same sample size as @Fanelli2010, we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed "20190120" (seed was not preregistered, but no other seeds were tried).
+We initially excluded eight papers and replaced them (decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had been excluded erroneously, leading to a final sample size of 152 (see Fig.\ \@ref(fig:sampling)).
 
@@
 For Registered Reports we aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase "test$^\ast$ the hypothes$^\ast$".
-We downloaded a database of published Registered Reports curated by the Center for Open Science (https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9, retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than "Psychiatry/Psychology" or "Multidisciplinary" in the ESI.
+We downloaded a database of published Registered Reports curated by the Center for Open Science^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than "Psychiatry/Psychology" or "Multidisciplinary" in the ESI.
 Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in Cortex because the ESI counts this journal towards the separate category "Neuroscience and Behavior".
@@
 We searched the full texts of all papers for the string "replic$^\ast$" [cf.
-@Makel2012; @Kohler2019; @Mueller-Langer2019; @Pridemore2018], and for papers that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
-Conceptual replications and internal replications were not counted as replications in this narrow sense: 
-The reason to code replication status was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
+@Makel2012; @Kohler2019; @Mueller-Langer2019; @Pridemore2018], and for papers that did contain it determined whether the coded hypothesis was a close replication with the goal to verify a previously published result.
+Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
 AS coded all papers, DL double-coded `r rep.RR.coded.DL` Registered Reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR)*100)` \%$) and `r rep.SR.coded.DL` standard reports ($`r printnum(rep.SR.coded.DL/sum(included$is_RR==0)*100)` \%$).
@@
 Figure\ \@ref(fig:powerbaserate) visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
-For example, if we assume no publication bias and no QRPs, more than $90\%$ of the hypotheses authors of standard reports study must be true and study designs must have more than $90\%$ power for the true effect size.
+For example, assuming no publication bias and no QRPs, even if all hypotheses authors of standard reports tested were true, their study designs would need to have more than $90\%$ power for the true effect size.
 This is highly unlikely, meaning that the standard literature is unlikely to reflect reality. 

### 2020-01-14 preprint/manuscript.tex
changed one sentence in the Discussion and two in the description of replication status coding

@@
 Assuming a constant alpha level, the rate of positive results in a literature (i.e., the proportion of supported hypotheses among all tested hypotheses) is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
-The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature (see e.g., Maxwell, 2004; Szucs \& Ioannidis, 2017).
+The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature (see e.g., Maxwell, 2004; Singleton Thorn, Dudgeon, \& Fidler, 2019; Szucs \& Ioannidis, 2017).
 Therefore, if the emerging Registered Reports literature in Psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
@@
 For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} and the ISSNs of all journals listed in the ESI Psychiatry/Psychology category.
-Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed \enquote{20190120} (not specified in our preregistration, but no other seeds were tried).
-We initially excluded eight papers and replaced them (the decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had erroneously been excluded, leading to a final sample size of 152 rather than 150 (see Fig.~\ref{fig:sampling}).
+Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed \enquote{20190120} (seed was not preregistered, but no other seeds were tried).
+We initially excluded eight papers and replaced them (decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had been excluded erroneously, leading to a final sample size of 152 (see Fig.~\ref{fig:sampling}).
 
@@
 For Registered Reports we aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
-We downloaded a database of published Registered Reports curated by the Center for Open Science (\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}, retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
+We downloaded a database of published Registered Reports curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
 Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in Cortex because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
@@
 We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf.
-Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for papers that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
-Conceptual replications and internal replications were not counted as replications in this narrow sense:
-The reason to code replication status was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
+Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for papers that did contain it determined whether the coded hypothesis was a close replication with the goal to verify a previously published result.
+Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
 AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(65.13 \%\)).
@@
 Figure~\ref{fig:powerbaserate} visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
-For example, if we assume no publication bias and no QRPs, more than \(90\%\) of the hypotheses authors of standard reports study must be true and study designs must have more than \(90\%\) power for the true effect size.
+For example, assuming no publication bias and no QRPs, even if all hypotheses authors of standard reports tested were true, their study designs would need to have more than \(90\%\) power for the true effect size.
 This is highly unlikely, meaning that the standard literature is unlikely to reflect reality.
@@
 \url{https://doi.org/10.1177/1745691614543974}
+
+\leavevmode\hypertarget{ref-SingletonThorn2019}{}%
+Singleton Thorn, F., Dudgeon, P., \& Fidler, F.
+(2019, September).
+\emph{Statistical power and effect sizes in psychology are decreasing over time}.
+Presented at the Metascience 2019 Symposium, Stanford, CA, USA.
+Retrieved from \url{https://www.metascience2019.org/poster-session/felix-singleton-thorn/}
 

### 2020-01-14 preprint/manuscript.Rmd
minor text tweaks

@@
 keywords          : "Publication bias, Registered Reports, hypothesis testing"
-#wordcount         : "6465"
+#wordcount         : "6442"
 
@@
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known. 
-Since its introduction at the journal Cortex in 2013, the format has rapidly gained popularity and is offered by 222 journals at the time of writing (http://cos.io/rr).
+Since its introduction at the journal *Cortex* in 2013, the format has rapidly gained popularity and is offered by 222 journals at the time of writing (http://cos.io/rr).
 
@@
 
-For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase "test$^\ast$ the hypothes$^\ast$" and the ISSNs of all journals listed in the ESI Psychiatry/Psychology category.
+For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase "test$^\ast$ the hypothes$^\ast$" and the ISSNs of all 633 journals listed in the ESI Psychiatry/Psychology category.
 Using the same sample size as @Fanelli2010, we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed "20190120" (seed was not preregistered, but no other seeds were tried).
@@
 (ref:sampling) Sampling process and exclusions for standard reports and Registered Reports.
-Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded.
+Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had been excluded erroneously.
 "Preregistered": study had been preregistered but was not a full RR; "results-blind review": article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); "ambiguous": four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance (we chose to exclude these cases to be conservative).
@@
 We downloaded a database of published Registered Reports curated by the Center for Open Science^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than "Psychiatry/Psychology" or "Multidisciplinary" in the ESI.
-Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in Cortex because the ESI counts this journal towards the separate category "Neuroscience and Behavior".
-Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., Royal Society Open Science) were hand-coded by AS. 
+Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in *Cortex* because the ESI counts this journal towards the separate category "Neuroscience and Behavior".
+Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., *Royal Society Open Science*) were hand-coded by AS. 
 This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
@@
 We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all Registered Reports and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
-.
 
@@
 We searched the full texts of all papers for the string "replic$^\ast$" [cf.
-@Makel2012; @Kohler2019; @Mueller-Langer2019; @Pridemore2018], and for papers that did contain it determined whether the coded hypothesis was a close replication with the goal to verify a previously published result.
+@Makel2012; @Kohler2019; @Mueller-Langer2019; @Pridemore2018] and, for papers that did contain it, determined whether the coded hypothesis was a close replication with the goal to verify a previously published result.
 Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
@@
 
-> A one-sided proportion test with an alpha level of $5\%$ will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports [we later changed the term to "standard reports"] in psychology.
+> A one-sided proportion test with an alpha level of $5\%$ will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports^[We later changed the term to "standard reports".] in psychology.
 > In addition to testing if there is a statistically significant difference between RRs and conventional reports, we will test if the difference is smaller than our smallest effect size of interest using an equivalence test for proportion tests with an alpha level of $5\%$ [@Lakens2018a].
@@
 The preregistered one-sided proportions test with an alpha level of $5\%$ showed that this difference of $-`r printnum((prop.support.SR-prop.support.RR)*100)` \%$ was statistically significant, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
-Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$ at $\alpha = 5\%$, $z = `r printnum(min(tostresult$TOST_z1, tostresult$TOST_z2))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
+Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$ at $\alpha = 5\%$, $z = `r printnum(min(abs(tostresult$TOST_z1), abs(tostresult$TOST_z2)))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
 We thus accept our hypothesis that the positive result rate in Registered Reports is lower than in standard reports.
@@
 ## Exploratory Analyses
-As described in the Method section, we only classified close or direct replications of previously published work as replications. 
+As described in the Method section, we only classified direct replications of previously published work as replications. 
 This means that our non-replication category also contains some conceptual replications and "internal" replications (where original and replication are published in the same paper). 
@@
 However, this difference cannot account for the stark overall difference between standard reports and Registered Reports described above: 
-Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports, $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$, was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(reptost$TOST_z1, reptost$TOST_z2))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
+Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports, $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$, was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(reptost$TOST_z1), abs(reptost$TOST_z2)))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
 
@@
 The difference between the positive result rate for standard reports in our sample ($`r printnum(prop.support.SR*100)`\%$) and Fanelli's ($`r printnum(prop.support.Fanelli*100)`\%$) is $`r printnum((prop.support.SR-prop.support.Fanelli)*100)`\%$.
-This difference is not significantly different from 0 in a two-sided proportions test ($\chi^2 = `r printnum(Fanelliproptest$statistic)`$, $p= `r printp(Fanelliproptest$p.value)`$) but also not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(Fanellitost$TOST_z1, Fanellitost$TOST_z2))`$, $p= `r printp(max(Fanellitost$TOST_p1, Fanellitost$TOST_p2))`$), both at $\alpha = 5\%$.
+This difference is not significantly different from 0 in a two-sided proportions test ($\chi^2 = `r printnum(Fanelliproptest$statistic)`$, $p= `r printp(Fanelliproptest$p.value)`$) but also not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(Fanellitost$TOST_z1), abs(Fanellitost$TOST_z2)))`$, $p= `r printp(max(Fanellitost$TOST_p1, Fanellitost$TOST_p2))`$), both at $\alpha = 5\%$.
 In other words, we can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least $\pm `r SESOI*100`\%$ between them. 
@@
 For the majority of Registered Reports (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==1))`), we identified one hypothesis-introduction phrase; the remaining ones used two (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==2))` RRs), three (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==3))` RRs), or four (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==4))` RR) different phrases or had no identifiable hypothesis introduction (`r length(which((hypintros$abstract.count+hypintros$fulltext.count)==0))` RR).
-In this total set of `r nrow(intros.long)` hypothesis introductions, we found `r length(uniquephrases)` unique phrases, showing substantial linguistic variation (see Tables 2 and 3).
-In order to condense the information, we listed all unique word stems (e.g., the word stem "hypothes$^\ast$" captures the words "hypothesis", "hypotheses", "hypothesize", "hypothesized", and so on) and analysed their frequency among all hypothesis introductions.
+In this total set of `r nrow(intros.long)` hypothesis introductions, we found `r length(uniquephrases)` unique phrases showing substantial linguistic variation (see Tables 2 and 3).
+To condense the information, we listed all unique word stems (e.g., the word stem "hypothes$^\ast$" captures the words "hypothesis", "hypotheses", "hypothesize", "hypothesized", and so on) and analysed their frequency among all hypothesis introductions.
 Excluding words that are common but too unspecific by themselves, such as "that", "to", or "whether", the five most frequent word stems were "hypothes$^\ast$" (`r wordoccurrences.df[1,2]` occurrences), "replicat$^\ast$" (`r wordoccurrences.df[2,2]`), "test$^\ast$" (`r wordoccurrences.df[3,2]`), "examine$^\ast$" (`r wordoccurrences.df[4,2]`), and "predict$^\ast$" (`r wordoccurrences.df[5,2]`).
 Clearly "test$^\ast$" and "hypothes$^\ast$" are quite popular, yet they co-occurred only `r test.and.hypothes` times and more than half of all hypothesis introductions (`r nrow(intros.long)-test.or.hypothes`/`r nrow(intros.long)`) contained neither word.
-Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 ($`r printnum(30/43*100)`\%$) hypothesis introductions found in original Registered Reports contained either "test$^\ast$" or "hypothes$^\ast$" or both, but the same was true for only 16 out of 54 ($`r printnum(16/54*100)`\%$) hypothesis introductions in direct replication Registered Reports.
+Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 ($`r printnum(30/43*100)`\%$) hypothesis introductions in original Registered Reports contained either "test$^\ast$" or "hypothes$^\ast$" or both, but the same was true for only 16 out of 54 ($`r printnum(16/54*100)`\%$) hypothesis introductions in direct replication Registered Reports.
 
 We noticed that direct replication Registered Reports generally tended to use different language to describe their hypothesis.
-As the high frequency of the word stem "replicat$^\ast$" suggests, these studies were often not framed as new tests of a previously tested hypothesis, but as attempts to replicate a previously documented effect or to repeat a previously conducted experiment.
+As the high frequency of the word stem "replicat$^\ast$" suggests, these studies were often not framed as *tests* of a previously tested hypothesis, but as attempts to repeat a previously conducted procedure.
 Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
@@
 
-(ref:table3) Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)
+(ref:table3) Hypothesis introduction phrases in direct replication Registered Reports (testing previously studied hypotheses)
 
@@
   , note = "Table contains 53 hypothesis introduction phrases from 40 Registered Reports.
-One additional RR had no hypothesis introduction.
+One additional RR had no identifiable hypothesis introduction.
 Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each."
@@
 Figure\ \@ref(fig:powerbaserate) visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
-For example, assuming no publication bias and no QRPs, even if all hypotheses authors of standard reports tested were true, their study designs would need to have more than $90\%$ power for the true effect size.
+For example, assuming no publication bias and no QRPs, even if *all* hypotheses authors of standard reports tested were true, their study designs would need to have more than $90\%$ power for the true effect size.
 This is highly unlikely, meaning that the standard literature is unlikely to reflect reality. 

### 2020-01-14 preprint/manuscript.tex
minor text tweaks

@@
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
-Since its introduction at the journal Cortex in 2013, the format has rapidly gained popularity and is offered by 222 journals at the time of writing (\url{http://cos.io/rr}).
+Since its introduction at the journal \emph{Cortex} in 2013, the format has rapidly gained popularity and is offered by 222 journals at the time of writing (\url{http://cos.io/rr}).
 
@@
 
-For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} and the ISSNs of all journals listed in the ESI Psychiatry/Psychology category.
+For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} and the ISSNs of all 633 journals listed in the ESI Psychiatry/Psychology category.
 Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed \enquote{20190120} (seed was not preregistered, but no other seeds were tried).
@@
 \includegraphics[width=\textwidth]{sampling_process_flowchart} \caption{Sampling process and exclusions for standard reports and Registered Reports.
-Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded.
+Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had been excluded erroneously.
 \enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance (we chose to exclude these cases to be conservative).}\label{fig:sampling}
@@
 We downloaded a database of published Registered Reports curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
-Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in Cortex because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
-Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., Royal Society Open Science) were hand-coded by AS.
+Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in \emph{Cortex} because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
+Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., \emph{Royal Society Open Science}) were hand-coded by AS.
 This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
@@
 We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf.
-Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for papers that did contain it determined whether the coded hypothesis was a close replication with the goal to verify a previously published result.
+Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018) and, for papers that did contain it, determined whether the coded hypothesis was a close replication with the goal to verify a previously published result.
 Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
@@
 \begin{quote}
-A one-sided proportion test with an alpha level of \(5\%\) will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports {[}we later changed the term to \enquote{standard reports}{]} in psychology.
+A one-sided proportion test with an alpha level of \(5\%\) will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports\footnote{We later changed the term to \enquote{standard reports}.} in psychology.
 In addition to testing if there is a statistically significant difference between RRs and conventional reports, we will test if the difference is smaller than our smallest effect size of interest using an equivalence test for proportion tests with an alpha level of \(5\%\) (Lakens, Scheel, \& Isager, 2018).
@@
 
-As described in the Method section, we only classified close or direct replications of previously published work as replications.
+As described in the Method section, we only classified direct replications of previously published work as replications.
 This means that our non-replication category also contains some conceptual replications and \enquote{internal} replications (where original and replication are published in the same paper).
@@
 The difference between the positive result rate for standard reports in our sample (\(96.05\%\)) and Fanelli's (\(91.49\%\)) is \(4.56\%\).
-This difference is not significantly different from 0 in a two-sided proportions test (\(\chi^2 = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = -3.73\), \(p= .306\)), both at \(\alpha = 5\%\).
+This difference is not significantly different from 0 in a two-sided proportions test (\(\chi^2 = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 0.51\), \(p= .306\)), both at \(\alpha = 5\%\).
 In other words, we can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least \(\pm 6\%\) between them.
@@
 For the majority of Registered Reports (49), we identified one hypothesis-introduction phrase; the remaining ones used two (16 RRs), three (4 RRs), or four (1 RR) different phrases or had no identifiable hypothesis introduction (1 RR).
-In this total set of 97 hypothesis introductions, we found 64 unique phrases, showing substantial linguistic variation (see Tables 2 and 3).
-In order to condense the information, we listed all unique word stems (e.g., the word stem \enquote{hypothes\(^\ast\)} captures the words \enquote{hypothesis}, \enquote{hypotheses}, \enquote{hypothesize}, \enquote{hypothesized}, and so on) and analysed their frequency among all hypothesis introductions.
+In this total set of 97 hypothesis introductions, we found 64 unique phrases showing substantial linguistic variation (see Tables 2 and 3).
+To condense the information, we listed all unique word stems (e.g., the word stem \enquote{hypothes\(^\ast\)} captures the words \enquote{hypothesis}, \enquote{hypotheses}, \enquote{hypothesize}, \enquote{hypothesized}, and so on) and analysed their frequency among all hypothesis introductions.
 Excluding words that are common but too unspecific by themselves, such as \enquote{that}, \enquote{to}, or \enquote{whether}, the five most frequent word stems were \enquote{hypothes\(^\ast\)} (34 occurrences), \enquote{replicat\(^\ast\)} (24), \enquote{test\(^\ast\)} (20), \enquote{examine\(^\ast\)} (8), and \enquote{predict\(^\ast\)} (8).
 Clearly \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times and more than half of all hypothesis introductions (51/97) contained neither word.
-Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions found in original Registered Reports contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, but the same was true for only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication Registered Reports.
+Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions in original Registered Reports contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, but the same was true for only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication Registered Reports.
 
 We noticed that direct replication Registered Reports generally tended to use different language to describe their hypothesis.
-As the high frequency of the word stem \enquote{replicat\(^\ast\)} suggests, these studies were often not framed as new tests of a previously tested hypothesis, but as attempts to replicate a previously documented effect or to repeat a previously conducted experiment.
+As the high frequency of the word stem \enquote{replicat\(^\ast\)} suggests, these studies were often not framed as \emph{tests} of a previously tested hypothesis, but as attempts to repeat a previously conducted procedure.
 Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
@@
 
-\caption{\label{tab:unnamed-chunk-7}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
+\caption{\label{tab:unnamed-chunk-7}Hypothesis introduction phrases in direct replication Registered Reports (testing previously studied hypotheses)}
 
@@
 \normalsize{\textit{Note.} Table contains 53 hypothesis introduction phrases from 40 Registered Reports.
-One additional RR had no hypothesis introduction.
+One additional RR had no identifiable hypothesis introduction.
 Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each.}
@@
 Figure~\ref{fig:powerbaserate} visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
-For example, assuming no publication bias and no QRPs, even if all hypotheses authors of standard reports tested were true, their study designs would need to have more than \(90\%\) power for the true effect size.
+For example, assuming no publication bias and no QRPs, even if \emph{all} hypotheses authors of standard reports tested were true, their study designs would need to have more than \(90\%\) power for the true effect size.
 This is highly unlikely, meaning that the standard literature is unlikely to reflect reality.

### 2020-01-15 appendix/positive_results_SRs_RRs_appendix.Rmd
minor fix to TOST reporting, changed file name

--- 2020-01-13 appendix/appendix.Rmd
@@
 The difference between this group of standard reports and all Registered Reports ($`r printnum((prop.support.SR.round1-prop.support.RR)*100)` \%$) is thus nearly identical to the one found in the main analysis ($`r printnum((prop.support.SR-prop.support.RR)*100)` \%$).
-Recalculating the one-sided proportions test and the equivalence test (both with an alpha level of $5\%$) shows that this difference is still statistically significant, $\chi^2 = `r printnum(proptestresult.robcheck$statistic)`$, $p `r printp(proptestresult.robcheck$p.value)`$, and still not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$, $z = `r printnum(min(tostresult.robcheck$TOST_z1, tostresult.robcheck$TOST_z2))`$, $p `r printp(max(tostresult.robcheck$TOST_p1, tostresult.robcheck$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
+Recalculating the one-sided proportions test and the equivalence test (both with an alpha level of $5\%$) shows that this difference is still statistically significant, $\chi^2 = `r printnum(proptestresult.robcheck$statistic)`$, $p `r printp(proptestresult.robcheck$p.value)`$, and still not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$, $z = `r printnum(min(abs(tostresult.robcheck$TOST_z1), abs(tostresult.robcheck$TOST_z2)))`$, $p `r printp(max(tostresult.robcheck$TOST_p1, tostresult.robcheck$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
 We thus conclude that the decision to replace excluded standard reports by resampling does not affect our results or conclusions in a meaningful way.

### 2020-01-15 appendix/positive_results_SRs_RRs_appendix.Rmd
fixed changed links to Appendix caused by file name change

@@
 This PDF was created in RMarkdown.
-The reproducible RMarkdown file, containing embedded code for the analysis in section 4.1, is available in our online repository at <https://osf.io/dbhgr> ([`appendix/appendix.Rmd`](https://osf.io/t4kc3/)).
+The reproducible RMarkdown file, containing embedded code for the analysis in section 4.1, is available in our online repository at <https://osf.io/dbhgr> ([`appendix/positive_results_SRs_RRs_appendix.Rmd`](https://osf.io/qw798/)).
 

### 2020-01-15 preprint/positive_results_SRs_RRs.Rmd
weird Git issue? I should be pulling these changes, not pushing them

--- 2020-01-14 preprint/manuscript.Rmd
@@
 ### Data, materials, and online resources
-The data and code necessary to reproduce all analyses reported here, as well as the [Appendix](https://osf.io/vcqya/), the [preregistration document](https://osf.io/sy927/) and additional supplementary files, are available at <https://osf.io/dbhgr>.
-The manuscript including figures and statistical analyses, the Appendix, and the [codebook](https://osf.io/6jrkz/) available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.
+The data and code necessary to reproduce all analyses reported here, as well as the [Appendix](https://osf.io/qw798/), the [preregistration document](https://osf.io/sy927/) and additional supplementary files, are available at <https://osf.io/dbhgr>.
+The manuscript including figures and statistical analyses, the [Appendix](https://osf.io/qw798/), and the [codebook](https://osf.io/6jrkz/) available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.
 

### 2020-01-15 preprint/positive_results_SRs_RRs.tex
weird Git issue? I should be pulling these changes, not pushing them

--- 2020-01-14 preprint/manuscript.tex
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/mainplot-1.pdf}
+\includegraphics{positive_results_SRs_RRs_files/figure-latex/mainplot-1.pdf}
 \caption{\label{fig:mainplot}Positive result rates for standard reports and Registered Reports. Error bars indicate \(95 \%\) confidence intervals around the observed positive result rate.}
@@
 
-{\centering \includegraphics[width=0.6\textwidth]{manuscript_files/figure-latex/powerbaserate-1}
+{\centering \includegraphics[width=0.6\textwidth]{positive_results_SRs_RRs_files/figure-latex/powerbaserate-1}
 
@@
 
-The data and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/vcqya/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration document} and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
-The manuscript including figures and statistical analyses, the Appendix, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
+The data and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration document} and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
+The manuscript including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
 

### 2020-01-15 preprint/positive_results_SRs_RRs.tex
fixed a typo

@@
 
-In addition to bias protection, Registered Reportss promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
+In addition to bias protection, Registered Reports promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
 Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., \(90\%\) power for a given effect size of interest).

### 2020-01-15 preprint/positive_results_SRs_RRs.Rmd

@@
 
-In addition to bias protection, Registered Reportss promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
+In addition to bias protection, Registered Reports promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
 Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., $90\%$ power for a given effect size of interest).

### 2020-01-28 preprint/positive_results_SRs_RRs.Rmd
tiny text change

@@
 For more than half a century, scientists have repeatedly noticed a suspiciously high "success" rate in Psychology:
-Studying 362 empirical articles published in four Psychology journals in 1955/56, @Sterling1959 found that a whopping $97.28\%$ of the studies that used significance tests rejected the null hypothesis.
+Studying 362 empirical articles published in four Psychology journals in 1955/56, @Sterling1959 found that $97.28\%$ of the studies that used significance tests rejected the null hypothesis. 
 A replication of this study performed on articles published in 1986/87 reported $95.56\%$ statistically significant results [@Sterling1995]. 

### 2020-01-28 preprint/positive_results_SRs_RRs.tex
tiny text change

@@
 For more than half a century, scientists have repeatedly noticed a suspiciously high \enquote{success} rate in Psychology:
-Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that a whopping \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
+Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
 A replication of this study performed on articles published in 1986/87 reported \(95.56\%\) statistically significant results (Sterling, Rosenbaum, \& Weinkam, 1995).

### 2020-02-04 preprint/positive_results_SRs_RRs.tex
small changes incorporating feedback from Emma, Chris, and Leo

@@
 We compared the results in the full population of published Registered Reports in Psychology (\(N = 71\) as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (\(N = 152\)) by searching 633 journals for the phrase `test* the hypothes*' (replicating a method by Fanelli, 2010).
-Analysing the first hypothesis reported in each paper, we found \(96.05\%\) positive results in standard reports, but only \(43.66\%\) positive results in Registered Reports.
-The difference remained nearly as large when direct replications were excluded from the analysis (\(95.95\%\) vs \(50\%\) positive results).
+Analysing the first hypothesis reported in each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports.
+The difference remained nearly as large when direct replications were excluded from the analysis (\(96\%\) vs \(50\%\) positive results).
 This large gap suggests that psychologists under-report negative results to an extent that threatens cumulative science.
@@
 
-Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature (Winter \& Happee, 2013; but see van Assen, van Aert, Nuijten, \& Wicherts, 2014).
+Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature (Cleophas \& Cleophas, 1999; see also de Winter \& Happee, 2013; and van Assen, van Aert, Nuijten, \& Wicherts, 2014, for a critique).
 How problematic selective publishing is in practice remains an empirical question:
@@
 Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of \emph{p}-hacking via restricted flexibility in data analysis.
-However, preregistration does not prevent file-drawering or reviewer bias and may thus be toothless in fighting publication bias.
+However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias (Goldacre et al., 2016; Rasmussen, Lee, \& Bero, 2009; but see Kaplan \& Irvin, 2015).
 A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers, 2013; Chambers, Dienes, McIntosh, Rotshtein, \& Willmes, 2015; Jonas \& Cesario, 2016; Nosek \& Lakens, 2014).
 Registered Reports (RRs) are a new publication format with a restructured submission timeline:
-Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline to a journal.
+Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal.
 The protocol undergoes peer review, and, if successful, receives \enquote{in-principle acceptance}, meaning that the journal commits to publishing the final article following data collection regardless of the statistical significance of the results.
 The authors then collect and analyse the data and write up the final report.
-The final report undergoes another round of peer review, but this time only to check if the authors adhered to the plan outlined in their protocol (and, if applicable, if the data passes pre-specified quality checks).
+The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
-Since its introduction at the journal \emph{Cortex} in 2013, the format has rapidly gained popularity and is offered by 222 journals at the time of writing (\url{http://cos.io/rr}).
+Since its introduction at the journal \emph{Cortex} in 2013, the format has rapidly gained popularity and is offered by 225 journals at the time of writing (\url{http://cos.io/rr}).
 
 In addition to bias protection, Registered Reports promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
-Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., \(90\%\) power for a given effect size of interest).
+Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., \(90\%\) power for a given effect size of interest\footnote{An overview of the requirements specified by each participating journal is available at \url{https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870}}).
 
@@
 Therefore, if the emerging Registered Reports literature in Psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
-At this time, we have good reasons to believe in a difference in bias, but less reason to believe in a difference in the proportion of true hypotheses (at least regarding original hypotheses, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate.
+At this time, we have good reasons to believe in a difference in bias, but less reason to believe in a difference in the proportion of true hypotheses (at least regarding original work, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate.
 Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.
@@
 Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found \(60.5\%\) unsupported hypotheses across all included Registered Reports, \(66\%\) for replication attempts, and \(54.5\%\) for novel research.
-They compared these numbers to an estimate of \(5-20\%\) null results in the standard literature.
-This \(5-20\%\) estimate is based on data from Fanelli (2012), who coded only the first hypothesis of each paper (identical to Fanelli, 2010), and Cristea and Ioannidis (2018), who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
+They compared these numbers to an estimate of 5--20\(\%\) null results in the standard literature.
+This 5--20\(\%\) estimate is based on data from Fanelli (2012), who coded only the first hypothesis of each paper (identical to Fanelli, 2010), and Cristea and Ioannidis (2018), who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
 
@@
 We used the same method as Fanelli (2010) to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
-We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
+We excluded papers if they were incomplete, unpublished, or retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
 An overview of the sampling process and all exclusions is shown in Figure~\ref{fig:sampling}.
@@
 For papers not clearly labelled as Registered Reports, we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
-Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
+Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because we could not verify that they were Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
 Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).
@@
 We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports.
-Because neither hypotheses, authors, nor editors were randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
+Because hypotheses, authors, and editors were not randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
 Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
@@
 Our study presents a systematic comparison of positive results in Registered Reports and the standard literature.
-The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the published research we are used to.
-Standard publication formats seem to lead psychological scientists to miss out on many high-quality studies with negative results, which are available in the Registered Reports literature.
+The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the existing body of published research.
+Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered Reports literature.
 The absence of negative results is a serious threat to a cumulative science.
 In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?} The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
-In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a more credible record of the research scientists conduct.
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a more credible scientific record.
 
@@
 Conceptualisation: A.S.
-and D.L.; data curation, formal analysis, and software: A.S.
-and M.S.; investigation, methodology, and validation: A.S., M.S., and D.L; supervision: A.S and D.L.; visualisation and writing -- original draft: A.S; writing -- review and editing: A.S., M.S., and D.L.
+\& D.L.; data curation, formal analysis, and software: A.S.
+\& M.S.; investigation, methodology, and validation: A.S., M.S., \& D.L; supervision: A.S \& D.L.; visualisation and writing---original draft: A.S; writing---review and editing: A.S., M.S., \& D.L.
 
@@
 
-This work was funded by VIDI grant 452-17-013. We thank Stuart Ritchie for valuable comments that helped improve this manuscript.
+This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leo Tiokhin, and Stuart Ritchie for valuable comments that helped improve this manuscript.
 
@@
 
+\leavevmode\hypertarget{ref-Cleophas1999}{}%
+Cleophas, R.
+C., \& Cleophas, T.
+J.
+(1999).
+Is selective reporting of clinical research unethical as well as unscientific?
+\emph{International Journal of Clinical Pharmacology and Therapeutics}, \emph{37}(1), 1--7.
+
 \leavevmode\hypertarget{ref-Cristea2018}{}%
@@
 
+\leavevmode\hypertarget{ref-deWinter2013}{}%
+de Winter, J., \& Happee, R.
+(2013).
+Why Selective Publication of Statistically Significant Results Can Be Effective.
+\emph{PLOS ONE}, \emph{8}(6), e66463.
+\url{https://doi.org/10.1371/journal.pone.0066463}
+
 \leavevmode\hypertarget{ref-Fanelli2010}{}%
@@
 \url{https://doi.org/10.1177/1948550615598377}
+
+\leavevmode\hypertarget{ref-Goldacre2016}{}%
+Goldacre, B., Drysdale, H., Powell-Smith, A., Dale, A., Milosevic, I., Slade, E., \ldots{} Heneghan, C.
+(2016).
+The COMPare Trials Project.
+Retrieved February 3, 2020, from \url{http://compare-trials.org}
 
@@
 \url{https://doi.org/10.1080/23743603.2015.1070611}
+
+\leavevmode\hypertarget{ref-Kaplan2015}{}%
+Kaplan, R.
+M., \& Irvin, V.
+L.
+(2015).
+Likelihood of Null Effects of Large NHLBI Clinical Trials Has Increased over Time.
+\emph{PLOS ONE}, \emph{10}(8), e0132382.
+\url{https://doi.org/10.1371/journal.pone.0132382}
 
@@
 \url{https://doi.org/10.1146/annurev-criminol-032317-091849}
+
+\leavevmode\hypertarget{ref-Rasmussen2009}{}%
+Rasmussen, N., Lee, K., \& Bero, L.
+(2009).
+Association of trial registration with the results and conclusions of published trials of new oncology drugs.
+\emph{Trials}, \emph{10}(1), 116.
+\url{https://doi.org/10.1186/1745-6215-10-116}
 
@@
 
-\leavevmode\hypertarget{ref-Winter2013}{}%
-Winter, J.
-de, \& Happee, R.
-(2013).
-Why Selective Publication of Statistically Significant Results Can Be Effective.
-\emph{PLOS ONE}, \emph{8}(6), e66463.
-\url{https://doi.org/10.1371/journal.pone.0066463}
-
 \leavevmode\hypertarget{ref-Wiseman2019}{}%

### 2020-02-04 preprint/positive_results_SRs_RRs.Rmd

@@
 We compared the results in the full population of published Registered Reports in Psychology ($N = 71$ as of November 2018) with a random sample of hypothesis-testing studies from the standard literature ($N = 152$) by searching 633 journals for the phrase ‘test* the hypothes*’ [replicating a method by @Fanelli2010].
-Analysing the first hypothesis reported in each paper, we found $96.05\%$ positive results in standard reports, but only $43.66\%$ positive results in Registered Reports.
-The difference remained nearly as large when direct replications were excluded from the analysis ($95.95\%$ vs $50\%$ positive results).
+Analysing the first hypothesis reported in each paper, we found $96\%$ positive results in standard reports, but only $44\%$ positive results in Registered Reports.
+The difference remained nearly as large when direct replications were excluded from the analysis ($96\%$ vs $50\%$ positive results).
 This large gap suggests that psychologists under-report negative results to an extent that threatens cumulative science.
@@
 keywords          : "Publication bias, Registered Reports, hypothesis testing"
-#wordcount         : "6442"
+#wordcount         : "6492"
 
@@
 
-Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature [@Winter2013; but see @vanAssen2014].
+Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature [@Cleophas1999; see also @deWinter2013; and @vanAssen2014, for a critique].
 How problematic selective publishing is in practice remains an empirical question: 
@@
 Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of *p*-hacking via restricted flexibility in data analysis.
-However, preregistration does not prevent file-drawering or reviewer bias and may thus be toothless in fighting publication bias. 
+However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias [@Rasmussen2009; @Goldacre2016; but see @Kaplan2015]. 
 A more effective safeguard against both publication bias and QRPs is promised by Registered Reports [@Chambers2013; @Nosek2014; @Chambers2015; @Jonas2016]. 
 Registered Reports (RRs) are a new publication format with a restructured submission timeline: 
-Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline to a journal. 
+Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal.
 The protocol undergoes peer review, and, if successful, receives "in-principle acceptance", meaning that the journal commits to publishing the final article following data collection regardless of the statistical significance of the results.
 The authors then collect and analyse the data and write up the final report. 
-The final report undergoes another round of peer review, but this time only to check if the authors adhered to the plan outlined in their protocol (and, if applicable, if the data passes pre-specified quality checks).
+The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known. 
-Since its introduction at the journal *Cortex* in 2013, the format has rapidly gained popularity and is offered by 222 journals at the time of writing (http://cos.io/rr).
+Since its introduction at the journal *Cortex* in 2013, the format has rapidly gained popularity and is offered by 225 journals at the time of writing (http://cos.io/rr).
 
 In addition to bias protection, Registered Reports promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
-Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., $90\%$ power for a given effect size of interest).
+Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., $90\%$ power for a given effect size of interest^[An overview of the requirements specified by each participating journal is available at https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870]).
 
@@
 Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found $60.5\%$ unsupported hypotheses across all included Registered Reports, $66\%$ for replication attempts, and $54.5\%$ for novel research.
-They compared these numbers to an estimate of $5-20\%$ null results in the standard literature. 
-This $5-20\%$ estimate is based on data from @Fanelli2012, who coded only the first hypothesis of each paper [identical to @Fanelli2010], and @Cristea2018, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
+They compared these numbers to an estimate of 5--20$\%$ null results in the standard literature. 
+This 5--20$\%$ estimate is based on data from @Fanelli2012, who coded only the first hypothesis of each paper [identical to @Fanelli2010], and @Cristea2018, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
 
@@
 We used the same method as @Fanelli2010 to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population. 
-We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
+We excluded papers if they were incomplete, unpublished, or retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
 An overview of the sampling process and all exclusions is shown in Figure\ \@ref(fig:sampling).
@@
 For papers not clearly labelled as Registered Reports, we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly. 
-Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.\ \@ref(fig:sampling)).
+Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because we could not verify that they were Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.\ \@ref(fig:sampling)).
 Note that we excluded all eight "Registered Replication Reports" [RRRs; @Simons2014; @Simons2018] in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing [@RRRwebsite, decision was not preregistered].
@@
 We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports. 
-Because neither hypotheses, authors, nor editors were randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
+Because hypotheses, authors, and editors were not randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
 Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
@@
 Our study presents a systematic comparison of positive results in Registered Reports and the standard literature.
-The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the published research we are used to.
-Standard publication formats seem to lead psychological scientists to miss out on many high-quality studies with negative results, which are available in the Registered Reports literature.
+The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the existing body of published research.
+Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered Reports literature.
 The absence of negative results is a serious threat to a cumulative science.
 In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
-In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a more credible record of the research scientists conduct.
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a more credible scientific record.
 
@@
 Conceptualisation: A.S.
-and D.L.; data curation, formal analysis, and software: A.S.
-and M.S.; investigation, methodology, and validation: A.S., M.S., and D.L; supervision: A.S and D.L.; visualisation and writing -- original draft: A.S; writing -- review and editing: A.S., M.S., and D.L.
+& D.L.; data curation, formal analysis, and software: A.S.
+& M.S.; investigation, methodology, and validation: A.S., M.S., & D.L; supervision: A.S & D.L.; visualisation and writing---original draft: A.S; writing---review and editing: A.S., M.S., & D.L.
 
 ### Acknowledgements
-This work was funded by VIDI grant 452-17-013. We thank Stuart Ritchie for valuable comments that helped improve this manuscript.
+This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leo Tiokhin, and Stuart Ritchie for valuable comments that helped improve this manuscript.
 

### 2020-02-05 preprint/positive_results_SRs_RRs.Rmd

@@
 keywords          : "Publication bias, Registered Reports, hypothesis testing"
-#wordcount         : "6492"
+#wordcount         : "6488"
 
@@
   - \usepackage{setspace}
-  - \captionsetup[figure]{font={stretch=1, small}, skip=12pt}
+  - \captionsetup[figure]{font={stretch=1, small}, skip=10pt}
   - \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
@@
 A replication of this study performed on articles published in 1986/87 reported $95.56\%$ statistically significant results [@Sterling1995]. 
-Similarly, a seminal study by @Fanelli2010 compared the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology reported support for their first or main hypothesis, the highest estimate of all disciplines in the study.
+Similarly, a seminal study by @Fanelli2010 compared the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
 For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$.
-In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very high.
+In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very large.
 
@@
 These include editors and reviewers selectively rejecting manuscripts with negative results ["reviewer bias", @Greenwald1975; @Mahoney1977] and researchers deciding not to submit studies with negative results for publication ["file-drawering"; @Rosenthal1979].
-Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is [typically, though not always, leading to an inflated type-I error rate, see also @Lakens2019b].
-These include presenting unexpected results as having been predicted a priori [HARKing, short for "hypothesising after results are known"; @Kerr1998] and exploiting flexibility in data analysis to obtain statistically significant results ["*p*-hacking"; @Simmons2011].
+Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is [typically, though not always, leading to an inflated type-I error rate; see @Lakens2019b].
+These include presenting unexpected results as having been predicted *a priori* [HARKing, short for "hypothesising after results are known"; @Kerr1998] and exploiting flexibility in data analysis to obtain statistically significant results ["*p*-hacking"; @Simmons2011].
 Evidence for both categories of bias exist: 
@@
 But how many positive results would such an unbiased literature contain in reality? 
-We set out to explore this question by comparing the rate of positive results in a sample from the current Psychology literature to a set of studies that were published in a new format created to minimise QRPs and publication bias: Registered Reports.
+We set out to explore this question by comparing the rate of positive results in the current Psychology literature to studies published in a new format designed to minimise QRPs and publication bias: Registered Reports.
 
@@
 Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal.
-The protocol undergoes peer review, and, if successful, receives "in-principle acceptance", meaning that the journal commits to publishing the final article following data collection regardless of the statistical significance of the results.
-The authors then collect and analyse the data and write up the final report. 
+The protocol undergoes peer review, and, if successful, receives "in-principle acceptance", meaning that the journal commits to publishing the final article following data collection, regardless of the statistical significance of the results.
+The authors then collect and analyse the data and complete the final report. 
 The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
@@
 
-In addition to bias protection, Registered Reports promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
+In addition to bias protection, Registered Reports promise high-quality research: Stage-1  (pre-data) peer review increases the likelihood that methodological flaws and immature or misguided ideas will be identified and addressed before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
 Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., $90\%$ power for a given effect size of interest^[An overview of the requirements specified by each participating journal is available at https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870]).
@@
 At this time, we have good reasons to believe in a difference in bias, but less reason to believe in a difference in the proportion of true hypotheses (at least regarding original work, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate.
-Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also mean that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about the high-quality negative results we are missing because of it.
+Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also indicate that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about high-quality negative results we are missing because of it.
 
@@
 Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found $60.5\%$ unsupported hypotheses across all included Registered Reports, $66\%$ for replication attempts, and $54.5\%$ for novel research.
-They compared these numbers to an estimate of 5--20$\%$ null results in the standard literature. 
-This 5--20$\%$ estimate is based on data from @Fanelli2012, who coded only the first hypothesis of each paper [identical to @Fanelli2010], and @Cristea2018, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
+They compared these numbers to an estimate of 5--20$\%$ null results in the standard literature [based on data from @Fanelli2012, who coded only the first hypothesis of each paper; and @Cristea2018, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS].
 
@@
 ## Analysis
-We planned to test our hypothesis in the following way (quoting directly from our preregistration, [https://osf.io/sy927](https://osf.io/sy927), point 9):
+We planned to test our hypothesis in the following way (quoting directly from our preregistration, [https://osf.io/sy927](https://osf.io/sy927)):
 
@@
 `r n.support.SR` out of `r n.SR` standard reports and `r n.support.RR` out of `r n.RR` Registered Reports had positive results, meaning that the positive result rate was $`r printnum(prop.support.SR*100)` \%$ for standard reports ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]) and $`r printnum(prop.support.RR*100)` \%$ for Registered Reports ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]; see Fig.\ \@ref(fig:mainplot)).
-The preregistered one-sided proportions test with an alpha level of $5\%$ showed that this difference of $-`r printnum((prop.support.SR-prop.support.RR)*100)` \%$ was statistically significant, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
+The preregistered one-sided proportions test with an alpha level of $5\%$ showed that this difference of $`r printnum((prop.support.SR-prop.support.RR)*100)` \%$ was statistically significant, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
 Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$ at $\alpha = 5\%$, $z = `r printnum(min(abs(tostresult$TOST_z1), abs(tostresult$TOST_z2)))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
@@
 Excluding words that are common but too unspecific by themselves, such as "that", "to", or "whether", the five most frequent word stems were "hypothes$^\ast$" (`r wordoccurrences.df[1,2]` occurrences), "replicat$^\ast$" (`r wordoccurrences.df[2,2]`), "test$^\ast$" (`r wordoccurrences.df[3,2]`), "examine$^\ast$" (`r wordoccurrences.df[4,2]`), and "predict$^\ast$" (`r wordoccurrences.df[5,2]`).
-Clearly "test$^\ast$" and "hypothes$^\ast$" are quite popular, yet they co-occurred only `r test.and.hypothes` times and more than half of all hypothesis introductions (`r nrow(intros.long)-test.or.hypothes`/`r nrow(intros.long)`) contained neither word.
+Clearly, "test$^\ast$" and "hypothes$^\ast$" are quite popular, yet they co-occurred only `r test.and.hypothes` times and more than half of all hypothesis introductions (`r nrow(intros.long)-test.or.hypothes`/`r nrow(intros.long)`) contained neither word.
 Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 ($`r printnum(30/43*100)`\%$) hypothesis introductions in original Registered Reports contained either "test$^\ast$" or "hypothes$^\ast$" or both, but the same was true for only 16 out of 54 ($`r printnum(16/54*100)`\%$) hypothesis introductions in direct replication Registered Reports.
@@
 
-It is a-priori plausible that Registered Reports are currently used for a population of hypotheses that are less likely to be true: 
+It is *a-priori* plausible that Registered Reports are currently used for a population of hypotheses that are less likely to be true: 
 For example, authors may use the format strategically for studies they expect to yield negative results (which would be difficult to publish otherwise). 
@@
 Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
-As mentioned above, it is a-priori plausible that the Registered Reports format is used selectively for particularly risky hypotheses. 
+As mentioned above, it is *a-priori* plausible that the Registered Reports format is used selectively for particularly risky hypotheses. 
 This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in Psychology. 
@@
 As our results show, this phrase was virtually absent in the Registered Report population. 
-The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for "test$^\ast$ the hypothes$^\ast$" will miss most of the hypothesis-testing studies in the psychological literature.
-Results based on this search phrase may thus not generalise to all published studies. 
+The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for "test$^\ast$ the hypothes$^\ast$" might miss most of the hypothesis-testing studies in the psychological literature, and results obtained this way may not generalise to all published studies.
 For example, it is possible that authors are more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., "we examined the role of ...").
@@
 @Motyl2017 report $89.17\%$ and $92.01\%$ significant results for "critical" hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively. 
-Therefore, although the search term used to find standard reports might limit the generalisability of our results, this search strategy seems to yield comparable estimates as the selection strategies used in different studies.
+Therefore, although the search term used to find standard reports might limit the generalisability of our results, it seems to yield comparable estimates as the selection strategies used in different studies.
 
@@
 In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
-In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a more credible scientific record.
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature---and may be one solution to achieve a more credible scientific record.
 
@@
 ### Data, materials, and online resources
-The data and code necessary to reproduce all analyses reported here, as well as the [Appendix](https://osf.io/qw798/), the [preregistration document](https://osf.io/sy927/) and additional supplementary files, are available at <https://osf.io/dbhgr>.
+Data and code necessary to reproduce all analyses reported here, as well as the [Appendix](https://osf.io/qw798/), the [preregistration](https://osf.io/sy927/), and additional supplementary files, are available at <https://osf.io/dbhgr>.
 The manuscript including figures and statistical analyses, the [Appendix](https://osf.io/qw798/), and the [codebook](https://osf.io/6jrkz/) available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.
@@
 ### Acknowledgements
-This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leo Tiokhin, and Stuart Ritchie for valuable comments that helped improve this manuscript.
+This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leonid Tiokhin, and Stuart Ritchie for valuable comments that helped improve this manuscript.
 

### 2020-02-05 preprint/positive_results_SRs_RRs.tex

@@
 \usepackage{setspace}
-\captionsetup[figure]{font={stretch=1, small}, skip=12pt}
+\captionsetup[figure]{font={stretch=1, small}, skip=10pt}
 \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
@@
 A replication of this study performed on articles published in 1986/87 reported \(95.56\%\) statistically significant results (Sterling, Rosenbaum, \& Weinkam, 1995).
-Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first or main hypothesis, the highest estimate of all disciplines in the study.
+Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
 For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
-In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very high.
+In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very large.
 
@@
 These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Greenwald, 1975; Mahoney, 1977) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
-Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate, see also Lakens, 2019).
-These include presenting unexpected results as having been predicted a priori (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
+Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate; see Lakens, 2019).
+These include presenting unexpected results as having been predicted \emph{a priori} (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
 Evidence for both categories of bias exist:
@@
 But how many positive results would such an unbiased literature contain in reality?
-We set out to explore this question by comparing the rate of positive results in a sample from the current Psychology literature to a set of studies that were published in a new format created to minimise QRPs and publication bias: Registered Reports.
+We set out to explore this question by comparing the rate of positive results in the current Psychology literature to studies published in a new format designed to minimise QRPs and publication bias: Registered Reports.
 
@@
 Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal.
-The protocol undergoes peer review, and, if successful, receives \enquote{in-principle acceptance}, meaning that the journal commits to publishing the final article following data collection regardless of the statistical significance of the results.
-The authors then collect and analyse the data and write up the final report.
+The protocol undergoes peer review, and, if successful, receives \enquote{in-principle acceptance}, meaning that the journal commits to publishing the final article following data collection, regardless of the statistical significance of the results.
+The authors then collect and analyse the data and complete the final report.
 The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
@@
 
-In addition to bias protection, Registered Reports promise high-quality research: Stage-1 peer review (pre data) increases the likelihood that methodological flaws and immature or misguided ideas will be spotted and fixed (or weeded out) before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
+In addition to bias protection, Registered Reports promise high-quality research: Stage-1 (pre-data) peer review increases the likelihood that methodological flaws and immature or misguided ideas will be identified and addressed before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
 Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., \(90\%\) power for a given effect size of interest\footnote{An overview of the requirements specified by each participating journal is available at \url{https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870}}).
@@
 Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found \(60.5\%\) unsupported hypotheses across all included Registered Reports, \(66\%\) for replication attempts, and \(54.5\%\) for novel research.
-They compared these numbers to an estimate of 5--20\(\%\) null results in the standard literature.
-This 5--20\(\%\) estimate is based on data from Fanelli (2012), who coded only the first hypothesis of each paper (identical to Fanelli, 2010), and Cristea and Ioannidis (2018), who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS.
+They compared these numbers to an estimate of 5--20\(\%\) null results in the standard literature (based on data from Fanelli, 2012, who coded only the first hypothesis of each paper; and Cristea \& Ioannidis, 2018, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS).
 
@@
 
-We planned to test our hypothesis in the following way (quoting directly from our preregistration, \url{https://osf.io/sy927}, point 9):
+We planned to test our hypothesis in the following way (quoting directly from our preregistration, \url{https://osf.io/sy927}):
 
@@
 146 out of 152 standard reports and 31 out of 71 Registered Reports had positive results, meaning that the positive result rate was \(96.05 \%\) for standard reports (\(95 \%\) CI {[}91.61, 98.54{]}) and \(43.66 \%\) for Registered Reports (\(95 \%\) CI {[}31.91, 55.95{]}; see Fig.~\ref{fig:mainplot}).
-The preregistered one-sided proportions test with an alpha level of \(5\%\) showed that this difference of \(-52.39 \%\) was statistically significant, \(\chi^2 = 77.96\), \(p < .001\).
+The preregistered one-sided proportions test with an alpha level of \(5\%\) showed that this difference of \(52.39 \%\) was statistically significant, \(\chi^2 = 77.96\), \(p < .001\).
 Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\), \(z = 7.61\), \(p > .999\), meaning that we cannot reject differences more extreme than \(6\%\).
@@
 Excluding words that are common but too unspecific by themselves, such as \enquote{that}, \enquote{to}, or \enquote{whether}, the five most frequent word stems were \enquote{hypothes\(^\ast\)} (34 occurrences), \enquote{replicat\(^\ast\)} (24), \enquote{test\(^\ast\)} (20), \enquote{examine\(^\ast\)} (8), and \enquote{predict\(^\ast\)} (8).
-Clearly \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times and more than half of all hypothesis introductions (51/97) contained neither word.
+Clearly, \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times and more than half of all hypothesis introductions (51/97) contained neither word.
 Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions in original Registered Reports contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, but the same was true for only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication Registered Reports.
@@
 
-It is a-priori plausible that Registered Reports are currently used for a population of hypotheses that are less likely to be true:
+It is \emph{a-priori} plausible that Registered Reports are currently used for a population of hypotheses that are less likely to be true:
 For example, authors may use the format strategically for studies they expect to yield negative results (which would be difficult to publish otherwise).
@@
 Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
-As mentioned above, it is a-priori plausible that the Registered Reports format is used selectively for particularly risky hypotheses.
+As mentioned above, it is \emph{a-priori} plausible that the Registered Reports format is used selectively for particularly risky hypotheses.
 This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in Psychology.
@@
 As our results show, this phrase was virtually absent in the Registered Report population.
-The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for \enquote{test\(^\ast\) the hypothes\(^\ast\)} will miss most of the hypothesis-testing studies in the psychological literature.
-Results based on this search phrase may thus not generalise to all published studies.
+The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for \enquote{test\(^\ast\) the hypothes\(^\ast\)} might miss most of the hypothesis-testing studies in the psychological literature, and results obtained this way may not generalise to all published studies.
 For example, it is possible that authors are more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., \enquote{we examined the role of \ldots{}}).
@@
 Motyl et al. (2017) report \(89.17\%\) and \(92.01\%\) significant results for \enquote{critical} hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively.
-Therefore, although the search term used to find standard reports might limit the generalisability of our results, this search strategy seems to yield comparable estimates as the selection strategies used in different studies.
+Therefore, although the search term used to find standard reports might limit the generalisability of our results, it seems to yield comparable estimates as the selection strategies used in different studies.
 
@@
 In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?} The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
-In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a more credible scientific record.
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature---and may be one solution to achieve a more credible scientific record.
 
@@
 
-The data and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration document} and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
+Data and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
 The manuscript including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
@@
 
-This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leo Tiokhin, and Stuart Ritchie for valuable comments that helped improve this manuscript.
+This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leonid Tiokhin, and Stuart Ritchie for valuable comments that helped improve this manuscript.
 

### 2020-02-05 preprint/positive_results_SRs_RRs.tex
added link to dataset

@@
 
-Data and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
-The manuscript including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
+\href{https://osf.io/aqr2s/}{Data} and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
+The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
 

### 2020-02-05 preprint/positive_results_SRs_RRs.Rmd

@@
 ### Data, materials, and online resources
-Data and code necessary to reproduce all analyses reported here, as well as the [Appendix](https://osf.io/qw798/), the [preregistration](https://osf.io/sy927/), and additional supplementary files, are available at <https://osf.io/dbhgr>.
-The manuscript including figures and statistical analyses, the [Appendix](https://osf.io/qw798/), and the [codebook](https://osf.io/6jrkz/) available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.
+[Data](https://osf.io/aqr2s/) and code necessary to reproduce all analyses reported here, as well as the [Appendix](https://osf.io/qw798/), the [preregistration](https://osf.io/sy927/), and additional supplementary files, are available at <https://osf.io/dbhgr>.
+The manuscript, including figures and statistical analyses, the [Appendix](https://osf.io/qw798/), and the [codebook](https://osf.io/6jrkz/) available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.
 

### 2020-02-05 appendix/positive_results_SRs_RRs_appendix.Rmd
fixed link to Rmd file

--- 2020-01-15 appendix/positive_results_SRs_RRs_appendix.Rmd
@@
 This PDF was created in RMarkdown.
-The reproducible RMarkdown file, containing embedded code for the analysis in section 4.1, is available in our online repository at <https://osf.io/dbhgr> ([`appendix/appendix.Rmd`](https://osf.io/t4kc3/)).
+The reproducible RMarkdown file, containing embedded code for the analysis in section 4.1, is available in our online repository at <https://osf.io/dbhgr> ([`appendix/positive_results_SRs_RRs_appendix.Rmd`](https://osf.io/jq8yc/)).
 

### 2020-04-06 submission1/positive_results_SRs_RRs_submission.Rmd
Changed preprint to submission-ready manuscript for NHB: Shortened the abstract & removed Discussion subheadings, switched to "manuscript" mode, added line numbers, and tweaked the plots and tables to work in manuscript mode

--- 2020-02-05 preprint/positive_results_SRs_RRs.Rmd
@@
 abstract: > 
- When studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the evidence for scientific claims.
-Psychological scientists have been concerned about the degree of distortion in their literature due to publication bias and inflated Type-1 error rates.
-Registered Reports were developed with the goal to minimise such biases: In this new publication format, peer review and the decision to publish take place before the study results are known.
-We compared the results in the full population of published Registered Reports in Psychology ($N = 71$ as of November 2018) with a random sample of hypothesis-testing studies from the standard literature ($N = 152$) by searching 633 journals for the phrase ‘test* the hypothes*’ [replicating a method by @Fanelli2010].
-Analysing the first hypothesis reported in each paper, we found $96\%$ positive results in standard reports, but only $44\%$ positive results in Registered Reports.
-The difference remained nearly as large when direct replications were excluded from the analysis ($96\%$ vs $50\%$ positive results).
-This large gap suggests that psychologists under-report negative results to an extent that threatens cumulative science.
-Although our study did not directly test the effectiveness of Registered Reports at reducing bias, these results show that the introduction of Registered Reports has led to a much larger proportion of negative results appearing in the published literature compared to standard reports.
+ Selectively publishing results that support the tested hypotheses ('positive' results) distorts the available evidence for scientific claims.
+For the past decade, psychological scientists have been increasingly concerned about the degree of such distortion in their literature.
+A new publication format has been developed to prevent selective reporting: In Registered Reports, peer review and the decision to publish take place before results are known.
+We compared the results in published Registered Reports (N = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (N = 152) in Psychology.
+Analysing the first hypothesis of each paper, we found $96\%$ positive results in standard reports, but only $44\%$ positive results in Registered Reports.
+We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
 
@@
 
-```{r sampling, echo=FALSE, warning=FALSE, fig.cap = "(ref:sampling)", out.width = "\\textwidth", fig.env="figure*"}
+```{r sampling, echo=FALSE, warning=FALSE, fig.cap = "(ref:sampling)", out.width = "\\textwidth"}
 
@@
 
-```{r mainplot, echo=FALSE, warning=FALSE, fig.height=5, fig.cap="(ref:mainplot)"}
-#mainplot
+```{r mainplot, echo=FALSE, warning=FALSE, fig.height=4, fig.cap="(ref:mainplot)"}
+mainplot
 
@@
 #
-ggplot(mainplot.df, aes(x = is_RR, y = value, fill = support)) +
-                    geom_bar(stat = "identity",
-                             width = 0.5) +
-                    scale_fill_manual(values= c("#bcbddc", "#756bb1"),
-                                      name="first hypothesis") +
-                    annotate("text", label = paste("N =", n.SR),
-                             x = 1, y = 105, size = 5) +
-                    annotate("text", label = paste("N =", n.RR),
-                             x = 2, y = 105, size = 5) +
-                    geom_errorbar(aes(ymin = lower, ymax = upper),
-                                  width = 0.05, size = 0.5) +
-                    scale_x_discrete(breaks = waiver(),
-                                     labels = c("SR" = "Standard\nReports",
-                                                "RR" = "Registered\nReports"),
-                                     name = NULL)+
-                    scale_y_continuous(lim=c(0,110), breaks = c(seq(0, 100, 10)),
-                                       minor_breaks = c(seq(0, 100, 5)),
-                                       name = "% of papers", expand = c(0, 0))+
-                    theme_minimal(base_size = 20)+
-                    theme(panel.grid.major.x = element_blank(),
-                          panel.grid.minor.x = element_blank(),
-                          legend.margin = margin(0,0,0,-5.5)) +
-                    coord_fixed(ratio=0.03)
+
+#ggplot(mainplot.df, aes(x = is_RR, y = value, fill = support)) +
+#                    geom_bar(stat = "identity",
+#                             width = 0.5) +
+#                    scale_fill_manual(values= c("#bcbddc", "#756bb1"),
+#                                      name="first hypothesis") +
+#                    annotate("text", label = paste("N =", n.SR),
+#                             x = 1, y = 105, size = 5) +
+#                    annotate("text", label = paste("N =", n.RR),
+#                             x = 2, y = 105, size = 5) +
+#                    geom_errorbar(aes(ymin = lower, ymax = upper),
+#                                  width = 0.05, size = 0.5) +
+#                    scale_x_discrete(breaks = waiver(),
+#                                     labels = c("SR" = "Standard\nReports",
+#                                                "RR" = "Registered\nReports"),
+#                                     name = NULL)+
+#                    scale_y_continuous(lim=c(0,110), breaks = c(seq(0, 100, 10)),
+#                                       minor_breaks = c(seq(0, 100, 5)),
+#                                       name = "% of papers", expand = c(0, 0))+
+#                    theme_minimal(base_size = 20)+
+#                    theme(panel.grid.major.x = element_blank(),
+#                          panel.grid.minor.x = element_blank(),
+#                          legend.margin = margin(0,0,0,-5.5)) +
+#                    coord_fixed(ratio=0.03)
 ```
@@
 
-```{r powerbaserate, echo=FALSE, fig.width=5, fig.height=3, fig.align='center', warning=FALSE, fig.cap="(ref:powerbaserate)", out.width = "0.6\\textwidth", fig.env="figure*"}
+```{r powerbaserate, echo=FALSE, fig.width=5, fig.height=3, fig.align='center', warning=FALSE, fig.cap="(ref:powerbaserate)", out.width = "0.8\\textwidth"}
 
-# Important altrnative chunk options when using journal mode: 
+# Important alternative chunk options when using journal mode: 
 # 1. use out.width="0.6\\textwidth" (it's 0.8 in manuscript mode)
@@
 
-## Limitations
 We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports. 
@@
 
-## Conclusion
 Our study presents a systematic comparison of positive results in Registered Reports and the standard literature.

### 2020-04-06 submission1/positive_results_SRs_RRs_submission.tex
Changed preprint to submission-ready manuscript for NHB: Shortened the abstract & removed Discussion subheadings, switched to "manuscript" mode, added line numbers, and tweaked the plots and tables to work in manuscript mode

--- 2020-02-05 preprint/positive_results_SRs_RRs.tex
@@
 \keywords{Publication bias, Registered Reports, hypothesis testing}
-\usepackage{dblfloatfix}
-
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{float}
@@
 \abstract{
-When studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the evidence for scientific claims.
-Psychological scientists have been concerned about the degree of distortion in their literature due to publication bias and inflated Type-1 error rates.
-Registered Reports were developed with the goal to minimise such biases: In this new publication format, peer review and the decision to publish take place before the study results are known.
-We compared the results in the full population of published Registered Reports in Psychology (\(N = 71\) as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (\(N = 152\)) by searching 633 journals for the phrase `test* the hypothes*' (replicating a method by Fanelli, 2010).
-Analysing the first hypothesis reported in each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports.
-The difference remained nearly as large when direct replications were excluded from the analysis (\(96\%\) vs \(50\%\) positive results).
-This large gap suggests that psychologists under-report negative results to an extent that threatens cumulative science.
-Although our study did not directly test the effectiveness of Registered Reports at reducing bias, these results show that the introduction of Registered Reports has led to a much larger proportion of negative results appearing in the published literature compared to standard reports.
+Selectively publishing results that support the tested hypotheses (`positive' results) distorts the available evidence for scientific claims.
+For the past decade, psychological scientists have been increasingly concerned about the degree of such distortion in their literature.
+A new publication format has been developed to prevent selective reporting: In Registered Reports, peer review and the decision to publish take place before results are known.
+We compared the results in published Registered Reports (N = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (N = 152) in Psychology.
+Analysing the first hypothesis of each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports.
+We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
 }
@@
 
-\begin{figure*}
+\begin{figure}
 \includegraphics[width=\textwidth]{sampling_process_flowchart} \caption{Sampling process and exclusions for standard reports and Registered Reports.
@@
 \enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance (we chose to exclude these cases to be conservative).}\label{fig:sampling}
-\end{figure*}
+\end{figure}
 
@@
 \centering
-\includegraphics{positive_results_SRs_RRs_files/figure-latex/mainplot-1.pdf}
+\includegraphics{positive_results_SRs_RRs_submission_files/figure-latex/mainplot-1.pdf}
 \caption{\label{fig:mainplot}Positive result rates for standard reports and Registered Reports. Error bars indicate \(95 \%\) confidence intervals around the observed positive result rate.}
@@
 
-\begin{figure*}
-
-{\centering \includegraphics[width=0.6\textwidth]{positive_results_SRs_RRs_files/figure-latex/powerbaserate-1}
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\textwidth]{positive_results_SRs_RRs_submission_files/figure-latex/powerbaserate-1}
 
@@
 Plotted values were calculated using the equation \(PRR = \alpha*(1-t) + (1-\beta)*t\); with \(PRR =\) positive result rate, \(\alpha =\) probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), \(1-\beta =\) probability of obtaining a positive result when testing a true hypothesis (power), and \(t =\) proportion of true hypotheses; and solving for \(t\) and \(1-\beta\), respectively (with the simplifying assumption that all studies in one group have the same power).}\label{fig:powerbaserate}
-\end{figure*}
+\end{figure}
 
@@
 Rather, the numbers strongly suggest a reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
-
-\hypertarget{limitations}{%
-\subsection{Limitations}\label{limitations}}
 
@@
 Regardless of which hypothesis one chooses to analyse across a set of papers -- the first, the last, or the \enquote{critical} one -- the positive result rate turns out to be higher than what can be expected based on realistic estimates of the proportion of true hypotheses researchers study and the statistical power of their tests.
-
-\hypertarget{conclusion}{%
-\subsection{Conclusion}\label{conclusion}}
 

### 2020-04-06 submission1/positive_results_SRs_RRs_submission.Rmd
updated the number of journals currently offering RRs

@@
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known. 
-Since its introduction at the journal *Cortex* in 2013, the format has rapidly gained popularity and is offered by 225 journals at the time of writing (http://cos.io/rr).
+Since its introduction at the journal *Cortex* in 2013, the format has rapidly gained popularity and is offered by 242 journals at the time of writing (http://cos.io/rr).
 

### 2020-04-06 submission1/positive_results_SRs_RRs_submission.tex
updated the number of journals currently offering RRs

@@
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
-Since its introduction at the journal \emph{Cortex} in 2013, the format has rapidly gained popularity and is offered by 225 journals at the time of writing (\url{http://cos.io/rr}).
+Since its introduction at the journal \emph{Cortex} in 2013, the format has rapidly gained popularity and is offered by 242 journals at the time of writing (\url{http://cos.io/rr}).
 

### 2020-07-11 appendix/positive_results_SRs_RRs_appendix.Rmd
updated Appendix; created new shortened manuscript draft for submission 2

@@
 To facilitate the comparison between the preregistration and the procedure and analyses we eventually carried out, we annotated the preregistration document in Word, adding comments that for each 'decision unit' note whether it was carried out as preregistered and give a brief overview of relevant changes or additional details.
-The annotated preregistration document is provided in the file [`appendix/preregistration_annotated.docx`](https://osf.io/e79vb/) (to view the annotations the file must be opened with a word processor like MS Word).
+The annotated preregistration document is provided in the file [`appendix/preregistration_annotated.docx`](https://osf.io/e79vb/) (to view the annotations, the file must be opened with a word processor like MS Word).
 
@@
 ### 3.1.1 Registered Reports
-As described in the main manuscript, we selected Registered Reports by retrieving the Registered Reports database curated by the Center for Open Science^[retrieved from https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (COS) on 19th November 2018, determining the discipline each paper belonged to and excluding all non-Psychology papers, and then verifying if all Psychology papers on the list were indeed Registered Reports.
+To identify the Registered Reports population, we downloaded a database of published Registered Reports curated by the Center for Open Science^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (COS; retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than 'Psychiatry/Psychology' or 'Multidisciplinary' in the Essential Science Indicators (ESI) database.
+Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in *Cortex* because the ESI counts this journal towards the separate category 'Neuroscience and Behavior'.
+Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., *Royal Society Open Science*) were hand-coded by AS. 
+This deviates from our preregistration insofar as we had not specified *how* discipline membership would be determined.
+
+Following these exclusions, we verified the Registered Reports status of all remaining papers in our sample. 
+Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with https://cos.io/rr).
+For papers not clearly labelled as Registered Reports, we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
+
 The file [`raw_data/source_data/RR_database_categorised_Nov2018.csv`](https://osf.io/8ybrk/) contains the full list of papers that were included in the COS database when we accessed and copied it. 
-The file also contains a variable indicating the discipline category we identified for each paper ('Discipline'), whether the papers was indeed a Registered Report ('RR', only checked for Psychology papers), and optional comments with details regarding this coding process ('comments').
+The file also contains a variable indicating the discipline category we identified for each paper ('Discipline'), whether the papers was indeed a Registered Report ('RR'; only checked for Psychology papers), and optional comments with details regarding this coding process ('comments').
 
@@
 We implemented this exact procedure with the following changes:
-We used a current version of the Essential Science Indicators (ESI) database^[retrieved from http://help.incites.clarivate.com/incitesLiveESI/ESIGroup/overviewESI/esiJournalsList.html] (retrieved on 4th December 2018), we only searched journals from the 'Psychiatry/Psychology' discipline, we used ISSNs instead of journal names in our search query (to prevent the risk that names of journals on the list could be sub-strings of names of journals not on the list, which would then be searched as well), and we restricted the search to papers published between 2013 and 2018 (to match them to the RR population).
 
-Using a programming script written in Processing (The Processing Foundation, 2019) a single search query compatible with Web of Science was generated that contained the key phrase that had to occur in the paper ('test$^\ast$ the hypothes$^\ast$'), as well as the desired publication years (2013 up to and including 2018), and the ISSNs of all 633 journals listed as Psychiatry/Psychology journals in the ESI database (the journal list is provided in the file [`raw_data/source_data/ESI_journallist_Psychology_20181204.csv`](https://osf.io/x938b/)).
-The resulting search query is available in the file [`raw_data/source_data/SR_search_query_WoS.txt`](https://osf.io/9xah6/).
+* We used a current version of the Essential Science Indicators (ESI) database^[retrieved from http://help.incites.clarivate.com/incitesLiveESI/ESIGroup/overviewESI/esiJournalsList.html] (retrieved on 4th December 2018),
+* we only searched journals from the 'Psychiatry/Psychology' discipline,
+* we used ISSNs instead of journal names in our search query (to prevent the risk that names of journals on the list could be sub-strings of names of journals not on the list, which would then be searched as well), and
+* we restricted the search to papers published between 2013 and 2018 (to match them to the RR population).
+
+Using a programming script written in *Processing* (The Processing Foundation, 2019), a single search query compatible with Web of Science was generated that contained the key phrase that had to occur in the paper ('test$^\ast$ the hypothes$^\ast$'), as well as the desired publication years (2013 up to and including 2018), and the ISSNs of all 633 journals listed as Psychiatry/Psychology journals in the ESI database (the journal list is provided in the file [`raw_data/source_data/ESI_journallist_Psychology_20181204.csv`](https://osf.io/x938b/)).
+The resulting search query is available in the text file [`raw_data/source_data/SR_search_query_WoS.txt`](https://osf.io/9xah6/).
 
 The search yielded 1919 results which were exported and saved in the file [`raw_data/source_data/SR_search_results_WoS_20190107.csv`](https://osf.io/q5fgd/). 
-We randomly selected 150 papers from this list using the sample() function in R and the seed '20190120':
+We randomly selected 150 papers from this list using the sample() function in R and the seed '20190120' (the seed was not preregistered, but no other seeds were tried):
 ```{r eval=FALSE}
@@
 
-The same strategy and random seed were used to sample 8 replacement papers and later another replacement paper after one of the initial 8 had to be excluded:
+The same strategy and random seed were used to sample 8 replacement papers, and later another replacement paper after one of the initial 8 had to be excluded:
 
@@
 ## 3.2 Coding procedure
-### 3.2.1 Hypothesis support
-In our email correspondence with Daniele Fanelli, we asked for potential additional details of the coding procedure, but were told that not 'much more' than the information given in Fanelli (2010) had been used for coding instructions.
-All criteria we used are described in the main manuscript.
+### 3.2.1 Piloting
+Before preregistering our study, we conducted a pilot to assess if we could employ Fanelli's method successfully.
+Originally we had planned to first reproduce his results on the same sample of Psychiatry/Psychology articles used in Fanelli (2010). 
+Unfortunately the author refused to share the original data (or even a list of the coded articles) with us. 
+Instead, we received an excerpt which contained data for 11 records from the original sample, but no reference information of the coded articles (personal communication, 5th October 2018). 
+We were able to find these 11 articles based on the hypothesis quotes that had been coded, and used them as a pilot sample along with 10 randomly selected Registered Reports. 
+MS and AS independently coded all 21 pilot articles with only one major disagreement in each group. 
+In the standard reports group, this disagreement was also the only case of major disagreement with Fanelli's original coding, which we deemed satisfying to proceed.
 
-### 3.2.2 Replication status
+### 3.2.2 Hypothesis support
+In our email correspondence with Daniele Fanelli, we asked for potential additional details of the coding procedure, but were told that not 'much more' than the information given in Fanelli (2010) had been used for coding instructions:
+
+> By examining the abstract and/or full- text, it was determined whether the authors of each paper had concluded to have found a positive (full or partial) or negative (null or negative) support. 
+> If more than one hypothesis was being tested, only the first one to appear in the text was considered. 
+> We excluded meeting abstracts and papers that either did not test a hypothesis or for which we lacked sufficient information to determine the outcome.  (Fanelli, 2010, p. 8)
+
+Like Fanelli (2010), we coded hypotheses as having received 'support', 'partial support', or 'no support', which was recoded into a binary 'support' (full or partial) vs 'no support' variable for the analysis.
+Based on our experiences during the pilot, we added one coding criterion: 
+If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first *tested* hypothesis rather than the first hypothesis mentioned in the text.
+
+### 3.2.3 Replication status
+#### Initial coding approach (discarded)
 Since the difference between replication studies and original studies was not the main focus of our paper, and because definitions of (e.g.) direct versus conceptual replications can be difficult to apply, we originally aimed for a 'lightweight' coding criterion and coded two binary variables: 'contains replication' and 'contains original work'.
@@
 
+#### Eventual coding approach
 The main reason why we coded replication status in the first place was the idea that direct replication studies may sometimes or often be motivated by the authors' scepticism of the original result, and that such direct replication studies may be overrepresented in the Registered Reports population compared to the standard literature.
@@
 
-### 3.2.3 Hypothesis introductions
+### 3.2.4 Hypothesis introductions
 Hypothesis introduction phrases were first coded by MS and AS as short phrases taken from the coded hypothesis quotes. 
@@
 For the final analysis of hypothesis introductions in Registered Reports, AS revised the coding for all Registered Reports (but not standard reports) by starting with the coded hypothesis quotes and extracting minimal phrases that signalled that a hypothesis was being tested, stripped from all content-specific details in a consistent manner across all papers.
-Rather than focussing on the 'best' or just the first identifiable phrase, all identifiable hypothesis introduction phrases were coded, meaning that each paper could have one or several phrases. 
+Rather than focusing on the 'best' or just the first identifiable phrase, all identifiable hypothesis introduction phrases were coded, meaning that each paper could have one or several phrases. 
 There was only one Registered Report for which no hypothesis introduction could be identified.
@@
 
-### 3.2.4 Additional measures
+### 3.2.5 Additional measures
 For the sake of completeness, we report all other recorded measures not described thus far in the following (*all* recorded measures are included and described in the dataset [`raw_data/positive_results_in_registered_reports_data.xlsx`](https://osf.io/aqr2s/)).
@@
   + any remarks regarding the resolution of coding disagreements
-* While revising our coding criteria for replication status, we also coded if the coded hypothesis introduction for a paper contained the string 'replic' and if a paper was part of a special issue focussed on replication, but in the end did not use these two variables (we did not run any analyses on them).
+* While revising our coding criteria for replication status, we also coded if the coded hypothesis introduction for a paper contained the string 'replic' and if a paper was part of a special issue focused on replication, but in the end did not use these two variables (we did not run any analyses on them).
 

### 2020-07-11 submission2/positive_results_SRs_RRs_submission.Rmd
updated Appendix; created new shortened manuscript draft for submission 2

--- 2020-04-06 submission1/positive_results_SRs_RRs_submission.Rmd
@@
 Analysing the first hypothesis of each paper, we found $96\%$ positive results in standard reports, but only $44\%$ positive results in Registered Reports.
-We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
+We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered-Reports literature.
 
@@
 But when published findings are systematically biased, cumulative science breaks down: 
-Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
-Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct. 
-For more than half a century, scientists have repeatedly noticed a suspiciously high "success" rate in Psychology:
-Studying 362 empirical articles published in four Psychology journals in 1955/56, @Sterling1959 found that $97.28\%$ of the studies that used significance tests rejected the null hypothesis. 
-A replication of this study performed on articles published in 1986/87 reported $95.56\%$ statistically significant results [@Sterling1995]. 
+Unlike random error, bias does not cancel out when aggregating across studies$\,$---$\,$in the worst case it accumulates, leading us away from the truth rather than towards it.
+Unfortunately, there is reason to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
+
+Since the 1950s, scientists have repeatedly noted a suspiciously high "success" rate in Psychology:
+Studying 362 empirical articles published in four Psychology journals in 1955/56, @Sterling1959 found that $97.28\%$ of studies using significance tests rejected the null hypothesis. 
+A later replication of this study reported $95.56\%$ statistically significant results in articles from 1986/87 [@Sterling1995]. 
 Similarly, a seminal study by @Fanelli2010 compared the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
-For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$.
-In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very large.
+For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$.
+Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
 
 ## A biased literature
-@Sterling1959 already suspected a selection process behind the numbers he found: 
-"(...) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of [statistical] significance" (p. 31). 
-This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature. 
+A more plausible explanation for these numbers may be a selection bias towards statistically significant results in the published literature.
 We can distinguish two broad categories of bias: "publication bias" and "questionable research practices". 
-Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
-These include editors and reviewers selectively rejecting manuscripts with negative results ["reviewer bias", @Greenwald1975; @Mahoney1977] and researchers deciding not to submit studies with negative results for publication ["file-drawering"; @Rosenthal1979].
-Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is [typically, though not always, leading to an inflated type-I error rate; see @Lakens2019b].
+Publication bias describes publishing behaviours that give manuscripts which find support for their tested hypotheses a higher chance of being published than manuscripts with "negative" results. 
+These include editors and reviewers selectively rejecting manuscripts with negative results ['reviewer bias', @Greenwald1975; @Mahoney1977] and researchers deciding not to submit studies with negative results for publication ['file-drawering'; @Rosenthal1979].
+Questionable research practices (QRPs) describe research behaviours that make evidence in favour of a certain conclusion look stronger than it is [typically, though not always, leading to more false positives; see @Lakens2019b].
 These include presenting unexpected results as having been predicted *a priori* [HARKing, short for "hypothesising after results are known"; @Kerr1998] and exploiting flexibility in data analysis to obtain statistically significant results ["*p*-hacking"; @Simmons2011].
 Evidence for both categories of bias exist: 
-Publication bias has been shown in peer review [@Mahoney1977; @Atkinson1982] and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results [@Franco2014; @Franco2016]; and QRPs have been admitted by scientists in several survey studies [@John2012; @Fiedler2016; @Agnoli2017].
+Publication bias has been observed in peer review [@Mahoney1977; @Atkinson1982] and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results [@Franco2014; @Franco2016]; and QRPs have been admitted by scientists in several survey studies [@John2012; @Fiedler2016; @Agnoli2017].
 
-Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature [@Cleophas1999; see also @deWinter2013; and @vanAssen2014, for a critique].
-How problematic selective publishing is in practice remains an empirical question: 
-If most negative results that are currently missing from the literature are the result of immature ideas or poorly conducted studies, we should expect that a literature in which studies are selected based on their quality but not based on their results  would contain a similar proportion of positive results as the current one.
-But how many positive results would such an unbiased literature contain in reality? 
-We set out to explore this question by comparing the rate of positive results in the current Psychology literature to studies published in a new format designed to minimise QRPs and publication bias: Registered Reports.
+Some have argued that selecting for positive results is defensible$\,$---$\,$desirable, even$\,$---$\,$because it weeds out low-quality research that would only pollute the literature [e.g., @Cleophas1999].
+If most negative results that are currently missing from the literature are indeed due to immature ideas or poor methods, a literature that selects studies based on *quality* instead of results should contain a similar proportion of positive results as the current one.
+How many positive and negative results would such an unbiased literature contain in reality? 
+We investigated this question by comparing the rate of positive results in the Psychology literature to studies published in a new format designed to minimise publication bias and QRPs: Registered Reports.
 
 ## Methods to mitigate bias
-An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection [for a historical overview, see @Wiseman2019].
-Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of *p*-hacking via restricted flexibility in data analysis.
+An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, methods, and analysis plan before data collection [for a historical overview, see @Wiseman2019].
+Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before results are known) and by reducing the risk of *p*-hacking via restricted flexibility in data analysis.
 However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias [@Rasmussen2009; @Goldacre2016; but see @Kaplan2015]. 
-A more effective safeguard against both publication bias and QRPs is promised by Registered Reports [@Chambers2013; @Nosek2014; @Chambers2015; @Jonas2016]. 
-Registered Reports (RRs) are a new publication format with a restructured submission timeline: 
-Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal.
-The protocol undergoes peer review, and, if successful, receives "in-principle acceptance", meaning that the journal commits to publishing the final article following data collection, regardless of the statistical significance of the results.
+A more effective safeguard against both publication bias and QRPs is promised by Registered Reports [@Chambers2020].
+
+Registered Reports (RRs) are a publication format with a restructured submission timeline: 
+Before collecting data, authors submit a study protocol containing their hypotheses, planned methods, and analysis pipeline, which undergoes peer review.
+If successful, the journal commits to publishing the final article following data collection, regardless of whether the hypotheses are supported ("in-principle acceptance").
 The authors then collect and analyse the data and complete the final report. 
-The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
+The final report is peer-reviewed again, but this time only to ensure that the the registered plan was adhered to and stated conclusions are justified (and, if applicable, that the data pass pre-specified quality checks).
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known. 
-Since its introduction at the journal *Cortex* in 2013, the format has rapidly gained popularity and is offered by 242 journals at the time of writing (http://cos.io/rr).
+Since its introduction in 2013, the format has rapidly gained popularity and is offered by 250 journals at the time of writing (http://cos.io/rr).
 
-In addition to bias protection, Registered Reports promise high-quality research: Stage-1  (pre-data) peer review increases the likelihood that methodological flaws and immature or misguided ideas will be identified and addressed before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
-Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., $90\%$ power for a given effect size of interest^[An overview of the requirements specified by each participating journal is available at https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870]).
-
-Assuming a constant alpha level, the rate of positive results in a literature (i.e., the proportion of supported hypotheses among all tested hypotheses) is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
-The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature [see e.g., @Maxwell2004; @Szucs2017; @SingletonThorn2019].
-Therefore, if the emerging Registered Reports literature in Psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
-At this time, we have good reasons to believe in a difference in bias, but less reason to believe in a difference in the proportion of true hypotheses (at least regarding original work, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate.
-Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also indicate that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about high-quality negative results we are missing because of it.
+In addition to reducing bias, Registered Reports are designed to ensure high standards for research quality. 
+First, pre-data peer review increases the chance that methodological flaws and immature ideas will be identified and addressed before a study is conducted. 
+Second, authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected). 
+And third, many journals offering Registered Reports require that hypothesis tests are planned with high statistical power, reducing the risk of false negatives (e.g., $90\%$ power for a given effect size of interest^[An overview of the requirements specified by each participating journal is available at https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870]).
 
 ## The current study
-The goal of our study was to test if Registered Reports in Psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as "standard reports", SRs), and to estimate the size of this potential difference.
-We set out to replicate a study by @Fanelli2010 on a new sample of standard reports in Psychology and compared them to all published Registered Reports in Psychology. 
-Fanelli searched for articles containing the phrase "test$^\ast$ the hypothes$^\ast$", drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
-For standard reports we used the same sampling method (restricted to the Psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS). 
-We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies. 
-We additionally coded if studies were replications or original work because many published Registered Reports are replications. 
-If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, which could lead to a larger proportion of negative results regardless of bias.
+The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth "standard reports", SRs), and to estimate the size of this potential difference.
+Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature [@Maxwell2004; @Szucs2017], such a difference would be unlikely to be due to "failed" studies or false negatives$\,$---$\,$and more likely to be due to reduced publication bias and QRPs.
+Should the positive result rate in Registered Reports be much lower than in the standard literature, it might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.
 
-In a recent commentary on benefits and challenges of open-science practices for early-career researchers, @Allen2019 conducted a similar investigation: 
-They coded the proportion of null results in the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018. 
-We were not aware of their parallel efforts when we planned our study in September and October 2018. 
-Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found $60.5\%$ unsupported hypotheses across all included Registered Reports, $66\%$ for replication attempts, and $54.5\%$ for novel research.
-They compared these numbers to an estimate of 5--20$\%$ null results in the standard literature [based on data from @Fanelli2012, who coded only the first hypothesis of each paper; and @Cristea2018, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS].
+We set out to compare all published Registered Reports in Psychology with a new sample of standard reports obtained by replicating @Fanelli2010. 
+Fanelli searched for articles containing the phrase "test$^\ast$ the hypothes$^\ast$", drew a random sample of 150 articles per discipline, and coded if the first hypothesis in each article had been supported or not.
+For standard reports we used the same sampling method (restricted to the Psychology discipline), for Registered Reports we relied on a database curated by the Center for Open Science (COS). 
+We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and because it can easily be applied to a large set of studies. 
+Because we expected many more Registered Reports than standard reports to be close replications of earlier studies$\,$---$\,$and perhaps movitated by scepticism of the original results$\,$---$\,$we additionally examined the role of replications in our analysis.
 
-A major advantage of our study is that it allows us to draw a more meaningful comparison between Registered Reports and the standard literature because we apply a previously used method [@Fanelli2010; @Fanelli2012] to both groups.
+In a recent commentary, @Allen2019 reported a similar investigation: 
+With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found $60.5\%$ unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
+A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature using a previously established method [@Fanelli2010; @Fanelli2012].
 In addition, we replicate @Fanelli2010 and provide data to evaluate his method: The search term "test$^\ast$ the hypothes$^\ast$" might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
-Therefore we also coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
+To this end, we coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
 Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
-This allows others to verify (or contest) our results and may provide an interesting resource for future meta-scientific research.
+This allows others to verify (or contest) our results and can hopefully provide an interesting resource for future meta-scientific research.
 
@@
 Methods and analyses described here were preregistered unless otherwise noted. 
-A detailed comparison of our preregistration and the eventual procedure is provided in the supplement. 
-We report how we determined our sample size, all data exclusions, and all measures in the study.
+Our online materials include an Appendix with fine-grained methodological details and an annotated preregistration document with detailed comparisons to the eventual procedure (https://osf.io/dbhgr).
 
 ## Sample
-We used the same method as @Fanelli2010 to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population. 
-We excluded papers if they were incomplete, unpublished, or retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
+We used the same method as @Fanelli2010 to obtain a new sample of standard reports in Psychology, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
+We excluded papers in both groups if they were incomplete, unpublished, or retracted (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
 An overview of the sampling process and all exclusions is shown in Figure\ \@ref(fig:sampling).
 
-For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase "test$^\ast$ the hypothes$^\ast$" and the ISSNs of all 633 journals listed in the ESI Psychiatry/Psychology category.
-Using the same sample size as @Fanelli2010, we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed "20190120" (seed was not preregistered, but no other seeds were tried).
-We initially excluded eight papers and replaced them (decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had been excluded erroneously, leading to a final sample size of 152 (see Fig.\ \@ref(fig:sampling)).
+Standard reports were selected by searching the 633 journals listed under "Psychiatry/Psychology" in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase "test$^\ast$ the hypothes$^\ast$" in title, abstract, or keywords.
+Using the same sample size as @Fanelli2010, we randomly selected 150 papers from the 1919 search results.
+Excluded papers were replaced by resampling (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.\ \@ref(fig:sampling)).
 
@@
 
-For Registered Reports we aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase "test$^\ast$ the hypothes$^\ast$".
-We downloaded a database of published Registered Reports curated by the Center for Open Science^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than "Psychiatry/Psychology" or "Multidisciplinary" in the ESI.
-Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in *Cortex* because the ESI counts this journal towards the separate category "Neuroscience and Behavior".
-Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., *Royal Society Open Science*) were hand-coded by AS. 
-This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
-
-Following these exclusions, we verified the Registered Reports status of all remaining papers in our sample. 
-Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with https://cos.io/rr).
-For papers not clearly labelled as Registered Reports, we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly. 
-Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because we could not verify that they were Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.\ \@ref(fig:sampling)).
-Note that we excluded all eight "Registered Replication Reports" [RRRs; @Simons2014; @Simons2018] in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing [@RRRwebsite, decision was not preregistered].
+We aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether they used the phrase "test$^\ast$ the hypothes$^\ast$". 
+Registered Reports were selected through a Registered-Reports database curated by the Center for Open Science^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (retrieved 19th November 2018).
+After excluding non-Psychology papers, we verified that all remaining papers were indeed Registered Reports by consulting the journal submission guidelines, relevant editorials, or contacting the editors directly.
+Papers were counted as Registered Reports if we could establish that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with https://cos.io/rr).
+We excluded 80 of the 151 entries in the COS Registered Reports database, leaving 71 Registered Reports for the final analysis (see Fig.\ \@ref(fig:sampling)). 
+Note that we excluded all eight "Registered Replication Reports" [RRRs; @Simons2014; @Simons2018] in our sample because this format explicitly focuses on effect size estimation and not hypothesis testing [@RRRwebsite, decision was not preregistered].
 
 ## Measures and coding procedure
+
 The main dependent variable was whether the first hypothesis was supported or not, as reported by the authors.
-We tried to follow Fanelli's [-@Fanelli2010] coding procedure as closely as possible, which he describes as follows:
+We tried to follow Fanelli's coding procedure as closely as possible:
 
@@
 > If more than one hypothesis was being tested, only the first one to appear in the text was considered. 
-> We excluded meeting abstracts and papers that either did not test a hypothesis or for which we lacked sufficient information to determine the outcome. (p. 8)
-
-Like @Fanelli2010, we coded hypotheses as having received "support", "partial support", or "no support", which was recoded into a binary "support" (full or partial) vs "no support" variable for the analysis.
-Coding disagreements between full and partial support were deemed minor since they would not affect the final results.
-Thus, only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.
-
-Before preregistering our study, we conducted a pilot to assess if we could employ Fanelli's method successfully.
-Originally we had planned to first reproduce his results on the same sample of Psychiatry/Psychology articles used in @Fanelli2010. 
-Unfortunately the author refused to share the original data (or even a list of the coded articles) with us. 
-Instead, we received an excerpt which contained data for 11 records from the original sample, but no reference information of the coded articles (personal communication, 5th October 2018). 
-We were able to find these 11 articles based on the hypothesis quotes that had been coded, and used them as a pilot sample along with 10 randomly selected Registered Reports. 
-MS and AS independently coded all 21 pilot articles with only one major disagreement in each group. 
-In the standard reports group, this disagreement was also the only case of major disagreement with Fanelli's original coding, which we deemed satisfying to proceed.
+> We excluded meeting abstracts and papers that either did not test a hypothesis or for which we lacked sufficient information to determine the outcome.  [@Fanelli2010, p. 8]
 
@@
 
-Based on our experiences during the pilot, we added one coding criterion: 
-If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first *tested* hypothesis rather than the first hypothesis mentioned in the text.
-In Registered Reports we coded the first preregistered hypothesis, thus excluding unregistered pilot studies. 
+In Registered Reports, we coded the first *preregistered* hypothesis, thus excluding unregistered pilot studies. 
+Coding disagreements between "full" and "partial" support were deemed minor since they would not affect the final results. 
+Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
 MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code ($`r sum(included$coded_by_AS & included$is_RR==1)`$ RRs and $`r sum(included$coded_by_AS & included$is_RR==0)`$ SRs).
 Only `r support.disagreement.major` disagreements were major (Cohen's kappa = `r printp(kappa.support)`) and subsequently resolved by discussion; `r support.disagreement.minor` were minor (disagreement between "support" and "partial support").
-We had preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
 
 ### Hypothesis introductions
-Selecting papers that use the phrase "test$^\ast$ the hypothes$^\ast$" might yield different results than alternative search phrases. 
-Getting a better overview of "natural" descriptions of hypotheses would be useful for future investigations of the generalisability of Fanelli's [-@Fanelli2010] results and could inspire new research questions.
-We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all Registered Reports and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
+Selecting standard reports based on the phrase "test$^\ast$ the hypothes$^\ast$" might yield different results than alternative search phrases. 
+To get a better overview of "natural" descriptions of hypotheses and facilitate future investigations of the generalisability of Fanelli's [-@Fanelli2010] results, we extracted the phrase used to introduce the coded hypothesis in all Registered Reports and tried to identify clusters of common expressions.
 
 ### Replication status
-We also wanted to code if a study was a replication of a previously published one: 
-We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study. 
-A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias. 
-After an initial coding attempt with ill-defined coding criteria had led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered): 
-We searched the full texts of all papers for the string "replic$^\ast$" [cf.
-@Makel2012; @Kohler2019; @Mueller-Langer2019; @Pridemore2018] and, for papers that did contain it, determined whether the coded hypothesis was a close replication with the goal to verify a previously published result.
+We expected a large proportion of Registered Reports to be replications, many of which may have been motivated by scepticism of the original study. 
+Because this circumstance alone could potentially lead to a lower positive result rate in Registered Reports, we additionally coded if hypotheses were close replications of previously published work.
+Due to ill-specified coding criteria in our preregistration (see Appendix), we used an unregistered coding strategy: 
+We determined whether the coded hypothesis of papers whose full text contained the string "replic$^\ast$" [cf.
+@Makel2012; @Mueller-Langer2019] was a close replication with the goal to verify a previously published result.
 Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
@@
 ### Additional measures
-All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above. 
-All of these are documented in the Appendix and in our shared dataset and codebook.
+All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above, and are documented in the Appendix and in our shared dataset and codebook.
 
@@
 
-We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if we found a negative difference between Registered Reports and standard reports that was significantly different from 0 *and* not statistically equivalent to a range from $-6\%$ to $+6\%$ (both at $\alpha = 5\%$).
+We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 *and* not statistically equivalent to a range from $-6\%$ to $+6\%$ (both at $\alpha = 5\%$).
 
@@
 
-## Confirmatory Analyses
+## Preregistered analysis
 
-`r n.support.SR` out of `r n.SR` standard reports and `r n.support.RR` out of `r n.RR` Registered Reports had positive results, meaning that the positive result rate was $`r printnum(prop.support.SR*100)` \%$ for standard reports ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]) and $`r printnum(prop.support.RR*100)` \%$ for Registered Reports ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]; see Fig.\ \@ref(fig:mainplot)).
-The preregistered one-sided proportions test with an alpha level of $5\%$ showed that this difference of $`r printnum((prop.support.SR-prop.support.RR)*100)` \%$ was statistically significant, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
-Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$ at $\alpha = 5\%$, $z = `r printnum(min(abs(tostresult$TOST_z1), abs(tostresult$TOST_z2)))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
+`r n.support.RR` out of `r n.RR` Registered Reports and `r n.support.SR` out of `r n.SR` standard reports had positive results, meaning that the positive result rate was $`r printnum(prop.support.RR*100)` \%$ for Registered Reports ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]) and $`r printnum(prop.support.SR*100)` \%$ for standard reports ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]; see Fig.\ \@ref(fig:mainplot)).
+This difference of $`r printnum((prop.support.RR-prop.support.SR)*100)` \%$ was statistically significant in the preregistered one-sided proportions test with $\alpha = 5\%$, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
+Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$ at $\alpha = 5\%$ ($z = `r printnum(min(abs(tostresult$TOST_z1), abs(tostresult$TOST_z2)))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$), meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
 We thus accept our hypothesis that the positive result rate in Registered Reports is lower than in standard reports.
@@
 
-## Exploratory Analyses
-As described in the Method section, we only classified direct replications of previously published work as replications. 
-This means that our non-replication category also contains some conceptual replications and "internal" replications (where original and replication are published in the same paper). 
-For ease of communication we will nonetheless refer to this category as "original" studies.
-As expected, direct replications were much more common among Registered Reports than standard reports: `r n.rep.RR` out of `r n.RR` Registered Reports ($`r printnum(prop.rep.RR*100)`\%$), but only `r n.rep.SR` out of `r n.SR` standard reports ($`r printnum(prop.rep.SR*100)`\%$) were classified as direct replications of previously published work.
-However, this difference cannot account for the stark overall difference between standard reports and Registered Reports described above: 
-Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports, $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$, was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(reptost$TOST_z1), abs(reptost$TOST_z2)))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
+## Exploratory analyses
+For ease of communication we will refer to papers that were classified as close replications of previously published work as "replications" and to all other studies as "original", even though the latter include some conceptual replications and internal replications (as explained above).
+As expected, replications were much more common among Registered Reports ($`r n.rep.RR` / `r n.RR` = `r printnum(prop.rep.RR*100)`\%$) than standard reports ($`r n.rep.SR` / `r n.SR` = `r printnum(prop.rep.SR*100)`\%$), and replication Registered Reports had a descriptively lower positive result rate than original Registered Reports (see Table 1).
+However, this finding fails to explain the main result described above:
+When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, $`r printnum((prop.orig.support.RR-prop.orig.support.SR)*100)`\%$, was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(reptost$TOST_z1), abs(reptost$TOST_z2)))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
 
@@
 
-Since our standard-reports sample represents a direct replication of @Fanelli2010 for the discipline Psychiatry & Psychology, another interesting question to ask is how our results compare to Fanelli's.
-The difference between the positive result rate for standard reports in our sample ($`r printnum(prop.support.SR*100)`\%$) and Fanelli's ($`r printnum(prop.support.Fanelli*100)`\%$) is $`r printnum((prop.support.SR-prop.support.Fanelli)*100)`\%$.
-This difference is not significantly different from 0 in a two-sided proportions test ($\chi^2 = `r printnum(Fanelliproptest$statistic)`$, $p= `r printp(Fanelliproptest$p.value)`$) but also not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(Fanellitost$TOST_z1), abs(Fanellitost$TOST_z2)))`$, $p= `r printp(max(Fanellitost$TOST_p1, Fanellitost$TOST_p2))`$), both at $\alpha = 5\%$.
-In other words, we can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least $\pm `r SESOI*100`\%$ between them. 
-The data are inconclusive.
+Since our standard-reports sample represents a direct replication of @Fanelli2010 for the discipline Psychiatry & Psychology, another interesting question is how our results compare to Fanelli's.
+The difference between the positive result rates of standard reports in our sample and Fanelli's ($`r printnum(prop.support.SR*100)`\% - `r printnum(prop.support.Fanelli*100)`\% = `r printnum((prop.support.SR-prop.support.Fanelli)*100)`\%$) is not significantly different from 0 in a two-sided proportions test ($\chi^2 = `r printnum(Fanelliproptest$statistic)`$, $p= `r printp(Fanelliproptest$p.value)`$) but also not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(Fanellitost$TOST_z1), abs(Fanellitost$TOST_z2)))`$, $p= `r printp(max(Fanellitost$TOST_p1, Fanellitost$TOST_p2))`$), both at $\alpha = 5\%$.
+The data are inconclusive: 
+We can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least $\pm `r SESOI*100`\%$ between them.
 
@@
 source(here("analysis", "03_hypothesis_introduction_analyses.R"))
+
+unique(intros.long$phrase[which(intros.long$is_replication == 0 &
+                                                intros.long$hypothes == TRUE &
+                                                intros.long$test == FALSE &
+                                                intros.long$predict == FALSE &
+                                                intros.long$examin == FALSE)])
+
 ```
 Finally, we analysed the language that was used to introduce or refer to hypotheses in Registered Reports.
-We were interested in whether the search phrase "test$^\ast$ the hypothes$^\ast$" used by Fanelli captures the way researchers write about hypothesis tests reasonably well.
-The answer is a resounding "no":
+We found extremely little overlap with Fanelli's search phrase "test$^\ast$ the hypothes$^\ast$":
 Searching the abstracts, titles, and keywords of the Registered Reports sample showed that only `r testthehypothes.RR`/`r n.RR` Registered Reports would have been detected with this search phrase. 
-To get an overview of analogous hypothesis-introduction phrases researchers used in Registered Reports, we stripped the hypothesis quotes of Registered Reports from all content-specific information and extracted "minimal" phrases that most distinctively indicated that a hypothesis was being described.
+To analyse which other hypothesis-introduction phrases researchers used in Registered Reports, we stripped the coded hypothesis quotes from all content-specific information and extracted "minimal" phrases that most distinctively indicated that a hypothesis was being described.
 For example, from the hypothesis quote "(f)or Study 1, we predicted that participants reading about academic (vs.
@@
 In this total set of `r nrow(intros.long)` hypothesis introductions, we found `r length(uniquephrases)` unique phrases showing substantial linguistic variation (see Tables 2 and 3).
-To condense the information, we listed all unique word stems (e.g., the word stem "hypothes$^\ast$" captures the words "hypothesis", "hypotheses", "hypothesize", "hypothesized", and so on) and analysed their frequency among all hypothesis introductions.
-Excluding words that are common but too unspecific by themselves, such as "that", "to", or "whether", the five most frequent word stems were "hypothes$^\ast$" (`r wordoccurrences.df[1,2]` occurrences), "replicat$^\ast$" (`r wordoccurrences.df[2,2]`), "test$^\ast$" (`r wordoccurrences.df[3,2]`), "examine$^\ast$" (`r wordoccurrences.df[4,2]`), and "predict$^\ast$" (`r wordoccurrences.df[5,2]`).
-Clearly, "test$^\ast$" and "hypothes$^\ast$" are quite popular, yet they co-occurred only `r test.and.hypothes` times and more than half of all hypothesis introductions (`r nrow(intros.long)-test.or.hypothes`/`r nrow(intros.long)`) contained neither word.
-Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 ($`r printnum(30/43*100)`\%$) hypothesis introductions in original Registered Reports contained either "test$^\ast$" or "hypothes$^\ast$" or both, but the same was true for only 16 out of 54 ($`r printnum(16/54*100)`\%$) hypothesis introductions in direct replication Registered Reports.
+We then listed all unique word stems within those phrases and analysed their frequency.
+Excluding words that are common but too unspecific by themselves (e.g., "that", "to", "whether"), the five most frequent word stems were "hypothes$^\ast$" (`r wordoccurrences.df[1,2]` occurrences), "replicat$^\ast$" (`r wordoccurrences.df[2,2]`), "test$^\ast$" (`r wordoccurrences.df[3,2]`), "examine$^\ast$" (`r wordoccurrences.df[4,2]`), and "predict$^\ast$" (`r wordoccurrences.df[5,2]`).
+Clearly, "test$^\ast$" and "hypothes$^\ast$" are quite popular, yet they co-occurred only `r test.and.hypothes` times, and more than half of all hypothesis introductions (`r nrow(intros.long)-test.or.hypothes`/`r nrow(intros.long)`) contained neither word.
 
-We noticed that direct replication Registered Reports generally tended to use different language to describe their hypothesis.
-As the high frequency of the word stem "replicat$^\ast$" suggests, these studies were often not framed as *tests* of a previously tested hypothesis, but as attempts to repeat a previously conducted procedure.
-Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
+`r printnum(n.hypintros.fivewords.RR, numerals = FALSE, capitalize = TRUE)` of the `r n.RR` Registered Reports ($`r printnum(n.hypintros.fivewords.RR/n.RR*100)` \%$) had at least one of these five most frequent word stems in their title, abstract, or keywords, meaning that a regular literature search (without access to full texts) with the search terms "hypothes$^\ast$ *OR* replicat$^\ast$ *OR* test$^\ast$ *OR* examine$^\ast$ *OR* predict$^\ast$" would have been effective in identifying these papers.
+We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question could be useful for future meta-research.
 
-Tables 2 and 3 list all unique hypothesis introductions and their frequency in original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems ("hypothes$^\ast$", "replicat$^\ast$", "test$^\ast$", "examine$^\ast$", "predict$^\ast$").
-Using five as a cut-off value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.
+Lastly, we noticed an interesting difference in language use between original and replication Registered Reports: 
+As the high frequency of the word stem "replicat$^\ast$" suggests, replications were often framed as attempts to repeat a previously conducted *procedure* rather than as attempts to test a previously tested *hypothesis*.
+Tables 2 and 3 list all unique hypothesis introductions and their frequency in original Registered Reports and replication Registered Reports, respectively, grouped by the five most frequent word stems ("hypothes$^\ast$", "replicat$^\ast$", "test$^\ast$", "examine$^\ast$", "predict$^\ast$").
 
@@
 
-It is important to keep in mind that not all hypotheses could be coded from the abstract: For `r n.hypintro.fulltext.only` Registered Reports, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
-Therefore we additionally tested how many of the Registered Reports would have been detected in a regular search using our five most frequent word stems. 
-We searched titles, abstracts, and keywords for "hypothes$^\ast$" OR "replicat$^\ast$" OR "test$^\ast$" OR "examine$^\ast$" OR "predict$^\ast$" and found that $`r n.hypintros.fivewords.RR`/`r n.RR`$ Registered Reports ($`r printnum(n.hypintros.fivewords.RR/n.RR*100)` \%$) would have been detected this way.
-We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question would be very useful for future meta-research.
+# Discussion
+We examined the proportion of Psychology articles that find support for their first tested hypothesis and discovered a large difference ($`r printnum(prop.support.SR*100)` \%$ vs $`r printnum(prop.support.RR*100)` \%$) between a random sample of standard reports and the full population of Registered Reports (at the time of data collection).
+More than half of the analysed hypothesis tests in Registered Reports were close replications of previous work, but the difference between standard reports and Registered Reports remained large when close replications were excluded from the analysis ($`r printnum(prop.orig.support.SR*100)` \%$ vs $`r printnum(prop.orig.support.RR*100)` \%$).
+Clearly, the emerging literature of Registered Reports appears to be publishing a much larger proportion of null results than the standard literature.
 
-# Discussion
-We examined the proportion of Psychology articles that find support for their first tested hypothesis and discovered a large difference ($`r printnum(prop.support.SR*100)` \%$ vs $`r printnum(prop.support.RR*100)` \%$) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
-More than half of the analysed hypothesis tests in Registered Reports were direct replications of previous work, but the difference between standard reports and Registered Reports was still large when direct replications were excluded from the analysis ($`r printnum(prop.orig.support.SR*100)` \%$ vs $`r printnum(prop.orig.support.RR*100)` \%$).
-The introduction of Registered Reports has clearly led to a much larger proportion of null results appearing in the published literature compared to standard reports.
-
-The positive result rate we found in standard reports ($`r printnum(prop.support.SR*100)` \%$) is slightly higher than the $91.5\%$ reported by @Fanelli2010, although this difference was not statistically significant.
+The positive result rate we found in standard reports ($`r printnum(prop.support.SR*100)` \%$) is slightly but non-significantly higher than the $91.5\%$ reported by @Fanelli2010. 
 Our replication in a more recent sample of the Psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 [cf.
@@
 To explain the $`r printnum((prop.support.SR - prop.support.RR)*100)` \%$ gap between standard reports and Registered Reports, we must assume some combination of differences in bias, statistical power, or the proportion of true hypotheses researchers choose to examine.
-Figure\ \@ref(fig:powerbaserate) visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
-For example, assuming no publication bias and no QRPs, even if *all* hypotheses authors of standard reports tested were true, their study designs would need to have more than $90\%$ power for the true effect size.
-This is highly unlikely, meaning that the standard literature is unlikely to reflect reality. 
-As we noted above, there is good reason to assume that methodological rigour and statistical power in Registered Reports are as high as in standard reports or higher, leaving the rate of true hypotheses and bias as remaining explanations.
+Figure\ \@ref(fig:powerbaserate) visualises the combinations of statistical power and proportion of true hypotheses that could produce the observed positive result rates if the literature were completely unbiased.
+Assuming no publication bias and no QRPs, authors of standard reports would need to test almost exclusively true hypotheses ($>90\%$) with more than $90\%$ power.
+Because this is highly implausible, the standard literature is unlikely to reflect reality. 
+As noted above, methodological rigour and statistical power in Registered Reports likely meet or exceed the level of standard reports, leaving the rate of true hypotheses and bias as remaining explanations.
 
@@
 However, assuming over $90\%$ true hypotheses in the standard literature is neither realistic, nor would it be desirable for a science that wants to advance knowledge beyond trivial facts. 
-We thus believe that this factor alone is not sufficient to explain the gap between the positive result rates in Registered Reports and standard reports. 
-Rather, the numbers strongly suggest a reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
+We thus believe that this factor alone is not sufficient to explain the large difference in positive results.
+Rather, the numbers strongly suggest a reduction of publication bias and/or QRPs in the Registered-Reports literature.
+Nonetheless, the prior probability of hypotheses in Registered Reports and standard reports may differ and should be studied in future research.
 
-We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports. 
-Because hypotheses, authors, and editors were not randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
-Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
-As mentioned above, it is *a-priori* plausible that the Registered Reports format is used selectively for particularly risky hypotheses. 
-This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in Psychology. 
-It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias. 
-Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use. 
-This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
+## Limitations
+Our study was not an experiment$\,$---$\,$hypotheses, authors, and editors were not randomly assigned to each publication format$\,$---$\,$and thus precludes strong causal inferences.
+As discussed above, it seems highly plausible that Registered Reports reduce publication bias and QRPs, which in turn reduces the positive result rate. 
+Yet we neither know exactly how effective Registered Reports are at reducing bias, nor how large the effect on positive results would be in the absence of potential confounds. 
+One such confound, as just discussed, could be that Registered Reports may be used for particularly risky hypotheses.
+Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use. 
+This would lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
 
-A second limitation of the current study [and of @Fanelli2010] is that standard reports were selected using the search term "test$^\ast$ the hypothes$^\ast$". 
-As our results show, this phrase was virtually absent in the Registered Report population. 
-The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for "test$^\ast$ the hypothes$^\ast$" might miss most of the hypothesis-testing studies in the psychological literature, and results obtained this way may not generalise to all published studies.
-For example, it is possible that authors are more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., "we examined the role of ...").
-If this were true, using other strategies to select standard reports might yield lower estimates for the positive result rate. 
-However, this does not seem to be the case: 
-Studies using different selection criteria for articles and hypotheses have found very similar rates of supported hypotheses. 
-For example, the positive result rates in @Sterling1959, @Sterling1995, and the original studies included in the Reproducibility Project: Psychology [@OSC2015] were $97.28\%$, $95.56\%$, and $97\%$, respectively.
-@Motyl2017 report $89.17\%$ and $92.01\%$ significant results for "critical" hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively. 
-Therefore, although the search term used to find standard reports might limit the generalisability of our results, it seems to yield comparable estimates as the selection strategies used in different studies.
+Another limitation of the current study [and of @Fanelli2010] is that standard reports were selected using the search phrase "test$^\ast$ the hypothes$^\ast$".
+This phrase was virtually absent in  Registered Reports, suggesting that this search strategy may not yield a representative sample of the population of hypothesis-testing studies in the literature.
+The use of the phrase might even be confounded with the outcome of a study:
+For example, authors may be more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., "we examined the role of ...").
+A similar concern could be raised for the decision to code only the first reported hypothesis of each article.
+The first hypothesis test may not be representative for all hypothesis tests reported in a paper, and the order of reporting may differ between standard reports and Registered Reports. 
+For example, standard-report authors might tend to present supported hypotheses first, whereas Registered-Report authors might be more likely to present their hypotheses in "chronological" order.
 
-A final limitation is the decision to code only the first reported hypothesis. 
-The first hypothesis test may not be representative for all hypothesis tests reported in a paper, and the order of reporting may differ between standard reports and Registered Reports. 
-Perhaps Registered-Report authors are more likely to present their hypotheses in "chronological" order, whereas standard-report authors tend to rearrange the order in which hypotheses are reported based on their outcomes, and present supported hypotheses first.
-Here again, the converging estimates from the four studies cited above (none of which use the first-hypothesis rule) make it seem unlikely that our result is an artefact of this decision. 
-Regardless of which hypothesis one chooses to analyse across a set of papers -- the first, the last, or the "critical" one -- the positive result rate turns out to be higher than what can be expected based on realistic estimates of the proportion of true hypotheses researchers study and the statistical power of their tests.
+Both of these potential confounds might lead to an inflated estimate of the positive result rate in standard reports.
+However, studies using different selection criteria for articles and hypotheses have found very similar rates of supported hypotheses in the literature: 
+$97.28\%$ in @Sterling1959, $95.56\%$ in @Sterling1995, and $97\%$ in the original studies included in the Reproducibility Project: Psychology [@OSC2015].
+In addition, @Motyl2017 report $89.17\%$ and $92.01\%$ significant results for "critical" hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively. 
+Although the selection criteria for articles and hypotheses in our study may limit the generalisability of the results, this level of convergence makes it seem unlikely that alternative methods would have yielded dramatically different conclusions.
 
+## Conclusion
 Our study presents a systematic comparison of positive results in Registered Reports and the standard literature.
 The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the existing body of published research.
-Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered Reports literature.
+Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered-Reports literature.
 The absence of negative results is a serious threat to a cumulative science.
 In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
-In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature---and may be one solution to achieve a more credible scientific record.
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature$\,$---$\,$and may be one solution to achieve a more credible scientific record.
 
@@
 
-### Conflicts of Interest
-The authors declare that they have no conflicts of interest with respect to the authorship or the publication of this article.
+### Reporting
+We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.
 
@@
 & D.L.; data curation, formal analysis, and software: A.S.
-& M.S.; investigation, methodology, and validation: A.S., M.S., & D.L; supervision: A.S & D.L.; visualisation and writing---original draft: A.S; writing---review and editing: A.S., M.S., & D.L.
+& M.S.; investigation, methodology, and validation: A.S., M.S., & D.L; supervision: A.S & D.L.; visualisation and writing$\,$---$\,$original draft: A.S; writing$\,$---$\,$review and editing: A.S., M.S., & D.L.
+
+### Conflicts of Interest
+The authors declare that they have no conflicts of interest with respect to the authorship or the publication of this article.
 
@@
 This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leonid Tiokhin, and Stuart Ritchie for valuable comments that helped improve this manuscript.
+
+### Prior versions
+A preprint of this manuscript has been published on *PsyArXiv* (https://doi.org/10.31234/osf.io/p6e9c).
+All sections of the present manuscript have been shortened to comply with the submission guidelines, but are intended to contain the same arguments, methods, results, and conclusions as the preprint.
 

### 2020-07-11 submission2/positive_results_SRs_RRs_submission.tex
updated Appendix; created new shortened manuscript draft for submission 2

--- 2020-04-06 submission1/positive_results_SRs_RRs_submission.tex
@@
 Analysing the first hypothesis of each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports.
-We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
+We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered-Reports literature.
 }
@@
 But when published findings are systematically biased, cumulative science breaks down:
-Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
-Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
-For more than half a century, scientists have repeatedly noticed a suspiciously high \enquote{success} rate in Psychology:
-Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
-A replication of this study performed on articles published in 1986/87 reported \(95.56\%\) statistically significant results (Sterling, Rosenbaum, \& Weinkam, 1995).
+Unlike random error, bias does not cancel out when aggregating across studies\(\,\)---\(\,\)in the worst case it accumulates, leading us away from the truth rather than towards it.
+Unfortunately, there is reason to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
+
+Since the 1950s, scientists have repeatedly noted a suspiciously high \enquote{success} rate in Psychology:
+Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of studies using significance tests rejected the null hypothesis.
+A later replication of this study reported \(95.56\%\) statistically significant results in articles from 1986/87 (Sterling, Rosenbaum, \& Weinkam, 1995).
 Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
-For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
-In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very large.
+For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
+Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
 
@@
 
-Sterling (1959) already suspected a selection process behind the numbers he found:
-\enquote{(\ldots{}) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of {[}statistical{]} significance} (p.~31).
-This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature.
+A more plausible explanation for these numbers may be a selection bias towards statistically significant results in the published literature.
 We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
-Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
+Publication bias describes publishing behaviours that give manuscripts which find support for their tested hypotheses a higher chance of being published than manuscripts with \enquote{negative} results.
 These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Greenwald, 1975; Mahoney, 1977) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
-Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate; see Lakens, 2019).
+Questionable research practices (QRPs) describe research behaviours that make evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to more false positives; see Lakens, 2019).
 These include presenting unexpected results as having been predicted \emph{a priori} (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
 Evidence for both categories of bias exist:
-Publication bias has been shown in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; John, Loewenstein, \& Prelec, 2012).
+Publication bias has been observed in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; John, Loewenstein, \& Prelec, 2012).
 
-Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature (Cleophas \& Cleophas, 1999; see also de Winter \& Happee, 2013; and van Assen, van Aert, Nuijten, \& Wicherts, 2014, for a critique).
-How problematic selective publishing is in practice remains an empirical question:
-If most negative results that are currently missing from the literature are the result of immature ideas or poorly conducted studies, we should expect that a literature in which studies are selected based on their quality but not based on their results would contain a similar proportion of positive results as the current one.
-But how many positive results would such an unbiased literature contain in reality?
-We set out to explore this question by comparing the rate of positive results in the current Psychology literature to studies published in a new format designed to minimise QRPs and publication bias: Registered Reports.
+Some have argued that selecting for positive results is defensible\(\,\)---\(\,\)desirable, even\(\,\)---\(\,\)because it weeds out low-quality research that would only pollute the literature (e.g., Cleophas \& Cleophas, 1999).
+If most negative results that are currently missing from the literature are indeed due to immature ideas or poor methods, a literature that selects studies based on \emph{quality} instead of results should contain a similar proportion of positive results as the current one.
+How many positive and negative results would such an unbiased literature contain in reality?
+We investigated this question by comparing the rate of positive results in the Psychology literature to studies published in a new format designed to minimise publication bias and QRPs: Registered Reports.
 
@@
 
-An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
-Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of \emph{p}-hacking via restricted flexibility in data analysis.
+An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, methods, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
+Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before results are known) and by reducing the risk of \emph{p}-hacking via restricted flexibility in data analysis.
 However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias (Goldacre et al., 2016; Rasmussen, Lee, \& Bero, 2009; but see Kaplan \& Irvin, 2015).
-A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers, 2013; Chambers, Dienes, McIntosh, Rotshtein, \& Willmes, 2015; Jonas \& Cesario, 2016; Nosek \& Lakens, 2014).
-Registered Reports (RRs) are a new publication format with a restructured submission timeline:
-Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal.
-The protocol undergoes peer review, and, if successful, receives \enquote{in-principle acceptance}, meaning that the journal commits to publishing the final article following data collection, regardless of the statistical significance of the results.
+A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers \& Tzavella, 2020).
+
+Registered Reports (RRs) are a publication format with a restructured submission timeline:
+Before collecting data, authors submit a study protocol containing their hypotheses, planned methods, and analysis pipeline, which undergoes peer review.
+If successful, the journal commits to publishing the final article following data collection, regardless of whether the hypotheses are supported (\enquote{in-principle acceptance}).
 The authors then collect and analyse the data and complete the final report.
-The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
+The final report is peer-reviewed again, but this time only to ensure that the the registered plan was adhered to and stated conclusions are justified (and, if applicable, that the data pass pre-specified quality checks).
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
-Since its introduction at the journal \emph{Cortex} in 2013, the format has rapidly gained popularity and is offered by 242 journals at the time of writing (\url{http://cos.io/rr}).
+Since its introduction in 2013, the format has rapidly gained popularity and is offered by 250 journals at the time of writing (\url{http://cos.io/rr}).
 
-In addition to bias protection, Registered Reports promise high-quality research: Stage-1 (pre-data) peer review increases the likelihood that methodological flaws and immature or misguided ideas will be identified and addressed before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
-Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., \(90\%\) power for a given effect size of interest\footnote{An overview of the requirements specified by each participating journal is available at \url{https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870}}).
-
-Assuming a constant alpha level, the rate of positive results in a literature (i.e., the proportion of supported hypotheses among all tested hypotheses) is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
-The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature (see e.g., Maxwell, 2004; Singleton Thorn, Dudgeon, \& Fidler, 2019; Szucs \& Ioannidis, 2017).
-Therefore, if the emerging Registered Reports literature in Psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
-At this time, we have good reasons to believe in a difference in bias, but less reason to believe in a difference in the proportion of true hypotheses (at least regarding original work, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate.
-Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also indicate that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about high-quality negative results we are missing because of it.
+In addition to reducing bias, Registered Reports are designed to ensure high standards for research quality.
+First, pre-data peer review increases the chance that methodological flaws and immature ideas will be identified and addressed before a study is conducted.
+Second, authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
+And third, many journals offering Registered Reports require that hypothesis tests are planned with high statistical power, reducing the risk of false negatives (e.g., \(90\%\) power for a given effect size of interest\footnote{An overview of the requirements specified by each participating journal is available at \url{https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870}}).
 
@@
 
-The goal of our study was to test if Registered Reports in Psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
-We set out to replicate a study by Fanelli (2010) on a new sample of standard reports in Psychology and compared them to all published Registered Reports in Psychology.
-Fanelli searched for articles containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}, drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
-For standard reports we used the same sampling method (restricted to the Psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS).
-We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
-We additionally coded if studies were replications or original work because many published Registered Reports are replications.
-If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, which could lead to a larger proportion of negative results regardless of bias.
+The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
+Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature (Maxwell, 2004; Szucs \& Ioannidis, 2017), such a difference would be unlikely to be due to \enquote{failed} studies or false negatives\(\,\)---\(\,\)and more likely to be due to reduced publication bias and QRPs.
+Should the positive result rate in Registered Reports be much lower than in the standard literature, it might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.
 
-In a recent commentary on benefits and challenges of open-science practices for early-career researchers, Allen and Mehler (2019) conducted a similar investigation:
-They coded the proportion of null results in the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018.
-We were not aware of their parallel efforts when we planned our study in September and October 2018.
-Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found \(60.5\%\) unsupported hypotheses across all included Registered Reports, \(66\%\) for replication attempts, and \(54.5\%\) for novel research.
-They compared these numbers to an estimate of 5--20\(\%\) null results in the standard literature (based on data from Fanelli, 2012, who coded only the first hypothesis of each paper; and Cristea \& Ioannidis, 2018, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS).
+We set out to compare all published Registered Reports in Psychology with a new sample of standard reports obtained by replicating Fanelli (2010).
+Fanelli searched for articles containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}, drew a random sample of 150 articles per discipline, and coded if the first hypothesis in each article had been supported or not.
+For standard reports we used the same sampling method (restricted to the Psychology discipline), for Registered Reports we relied on a database curated by the Center for Open Science (COS).
+We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and because it can easily be applied to a large set of studies.
+Because we expected many more Registered Reports than standard reports to be close replications of earlier studies\(\,\)---\(\,\)and perhaps movitated by scepticism of the original results\(\,\)---\(\,\)we additionally examined the role of replications in our analysis.
 
-A major advantage of our study is that it allows us to draw a more meaningful comparison between Registered Reports and the standard literature because we apply a previously used method (Fanelli, 2010, 2012) to both groups.
+In a recent commentary, Allen and Mehler (2019) reported a similar investigation:
+With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found \(60.5\%\) unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
+A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature using a previously established method (Fanelli, 2010, 2012).
 In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
-Therefore we also coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
+To this end, we coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
 Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
-This allows others to verify (or contest) our results and may provide an interesting resource for future meta-scientific research.
+This allows others to verify (or contest) our results and can hopefully provide an interesting resource for future meta-scientific research.
 
@@
 Methods and analyses described here were preregistered unless otherwise noted.
-A detailed comparison of our preregistration and the eventual procedure is provided in the supplement.
-We report how we determined our sample size, all data exclusions, and all measures in the study.
+Our online materials include an Appendix with fine-grained methodological details and an annotated preregistration document with detailed comparisons to the eventual procedure (\url{https://osf.io/dbhgr}).
 
@@
 
-We used the same method as Fanelli (2010) to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
-We excluded papers if they were incomplete, unpublished, or retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
+We used the same method as Fanelli (2010) to obtain a new sample of standard reports in Psychology, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
+We excluded papers in both groups if they were incomplete, unpublished, or retracted (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
 An overview of the sampling process and all exclusions is shown in Figure~\ref{fig:sampling}.
 
-For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} and the ISSNs of all 633 journals listed in the ESI Psychiatry/Psychology category.
-Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed \enquote{20190120} (seed was not preregistered, but no other seeds were tried).
-We initially excluded eight papers and replaced them (decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had been excluded erroneously, leading to a final sample size of 152 (see Fig.~\ref{fig:sampling}).
+Standard reports were selected by searching the 633 journals listed under \enquote{Psychiatry/Psychology} in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} in title, abstract, or keywords.
+Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results.
+Excluded papers were replaced by resampling (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.~\ref{fig:sampling}).
 
@@
 
-For Registered Reports we aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
-We downloaded a database of published Registered Reports curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
-Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in \emph{Cortex} because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
-Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., \emph{Royal Society Open Science}) were hand-coded by AS.
-This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
-
-Following these exclusions, we verified the Registered Reports status of all remaining papers in our sample.
-Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
-For papers not clearly labelled as Registered Reports, we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
-Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because we could not verify that they were Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
-Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).
+We aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
+Registered Reports were selected through a Registered-Reports database curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved 19th November 2018).
+After excluding non-Psychology papers, we verified that all remaining papers were indeed Registered Reports by consulting the journal submission guidelines, relevant editorials, or contacting the editors directly.
+Papers were counted as Registered Reports if we could establish that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
+We excluded 80 of the 151 entries in the COS Registered Reports database, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
+Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focuses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).
 
@@
 The main dependent variable was whether the first hypothesis was supported or not, as reported by the authors.
-We tried to follow Fanelli's (2010) coding procedure as closely as possible, which he describes as follows:
+We tried to follow Fanelli's coding procedure as closely as possible:
 
@@
 If more than one hypothesis was being tested, only the first one to appear in the text was considered.
-We excluded meeting abstracts and papers that either did not test a hypothesis or for which we lacked sufficient information to determine the outcome. (p.~8)
+We excluded meeting abstracts and papers that either did not test a hypothesis or for which we lacked sufficient information to determine the outcome. (Fanelli, 2010, p. 8)
 \end{quote}
 
-Like Fanelli (2010), we coded hypotheses as having received \enquote{support}, \enquote{partial support}, or \enquote{no support}, which was recoded into a binary \enquote{support} (full or partial) vs \enquote{no support} variable for the analysis.
-Coding disagreements between full and partial support were deemed minor since they would not affect the final results.
-Thus, only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.
-
-Before preregistering our study, we conducted a pilot to assess if we could employ Fanelli's method successfully.
-Originally we had planned to first reproduce his results on the same sample of Psychiatry/Psychology articles used in Fanelli (2010).
-Unfortunately the author refused to share the original data (or even a list of the coded articles) with us.
-Instead, we received an excerpt which contained data for 11 records from the original sample, but no reference information of the coded articles (personal communication, 5th October 2018).
-We were able to find these 11 articles based on the hypothesis quotes that had been coded, and used them as a pilot sample along with 10 randomly selected Registered Reports.
-MS and AS independently coded all 21 pilot articles with only one major disagreement in each group.
-In the standard reports group, this disagreement was also the only case of major disagreement with Fanelli's original coding, which we deemed satisfying to proceed.
-
-Based on our experiences during the pilot, we added one coding criterion:
-If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first \emph{tested} hypothesis rather than the first hypothesis mentioned in the text.
-In Registered Reports we coded the first preregistered hypothesis, thus excluding unregistered pilot studies.
+In Registered Reports, we coded the first \emph{preregistered} hypothesis, thus excluding unregistered pilot studies.
+Coding disagreements between \enquote{full} and \enquote{partial} support were deemed minor since they would not affect the final results.
+Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
 MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
 Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
-We had preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
 
@@
 
-Selecting papers that use the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} might yield different results than alternative search phrases.
-Getting a better overview of \enquote{natural} descriptions of hypotheses would be useful for future investigations of the generalisability of Fanelli's (2010) results and could inspire new research questions.
-We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all Registered Reports and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
+Selecting standard reports based on the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} might yield different results than alternative search phrases.
+To get a better overview of \enquote{natural} descriptions of hypotheses and facilitate future investigations of the generalisability of Fanelli's (2010) results, we extracted the phrase used to introduce the coded hypothesis in all Registered Reports and tried to identify clusters of common expressions.
 
@@
 
-We also wanted to code if a study was a replication of a previously published one:
-We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study.
-A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
-After an initial coding attempt with ill-defined coding criteria had led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
-We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf.
-Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018) and, for papers that did contain it, determined whether the coded hypothesis was a close replication with the goal to verify a previously published result.
+We expected a large proportion of Registered Reports to be replications, many of which may have been motivated by scepticism of the original study.
+Because this circumstance alone could potentially lead to a lower positive result rate in Registered Reports, we additionally coded if hypotheses were close replications of previously published work.
+Due to ill-specified coding criteria in our preregistration (see Appendix), we used an unregistered coding strategy:
+We determined whether the coded hypothesis of papers whose full text contained the string \enquote{replic\(^\ast\)} (cf.
+Makel, Plucker, \& Hegarty, 2012; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019) was a close replication with the goal to verify a previously published result.
 Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
@@
 
-All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above.
-All of these are documented in the Appendix and in our shared dataset and codebook.
+All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above, and are documented in the Appendix and in our shared dataset and codebook.
 
@@
 
-We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if we found a negative difference between Registered Reports and standard reports that was significantly different from 0 \emph{and} not statistically equivalent to a range from \(-6\%\) to \(+6\%\) (both at \(\alpha = 5\%\)).
+We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 \emph{and} not statistically equivalent to a range from \(-6\%\) to \(+6\%\) (both at \(\alpha = 5\%\)).
 
@@
 
-\hypertarget{confirmatory-analyses}{%
-\subsection{Confirmatory Analyses}\label{confirmatory-analyses}}
+\hypertarget{preregistered-analysis}{%
+\subsection{Preregistered analysis}\label{preregistered-analysis}}
 
-146 out of 152 standard reports and 31 out of 71 Registered Reports had positive results, meaning that the positive result rate was \(96.05 \%\) for standard reports (\(95 \%\) CI {[}91.61, 98.54{]}) and \(43.66 \%\) for Registered Reports (\(95 \%\) CI {[}31.91, 55.95{]}; see Fig.~\ref{fig:mainplot}).
-The preregistered one-sided proportions test with an alpha level of \(5\%\) showed that this difference of \(52.39 \%\) was statistically significant, \(\chi^2 = 77.96\), \(p < .001\).
-Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\), \(z = 7.61\), \(p > .999\), meaning that we cannot reject differences more extreme than \(6\%\).
+31 out of 71 Registered Reports and 146 out of 152 standard reports had positive results, meaning that the positive result rate was \(43.66 \%\) for Registered Reports (\(95 \%\) CI {[}31.91, 55.95{]}) and \(96.05 \%\) for standard reports (\(95 \%\) CI {[}91.61, 98.54{]}; see Fig.~\ref{fig:mainplot}).
+This difference of \(-52.39 \%\) was statistically significant in the preregistered one-sided proportions test with \(\alpha = 5\%\), \(\chi^2 = 77.96\), \(p < .001\).
+Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\) (\(z = 7.61\), \(p > .999\)), meaning that we cannot reject differences more extreme than \(6\%\).
 We thus accept our hypothesis that the positive result rate in Registered Reports is lower than in standard reports.
@@
 \hypertarget{exploratory-analyses}{%
-\subsection{Exploratory Analyses}\label{exploratory-analyses}}
+\subsection{Exploratory analyses}\label{exploratory-analyses}}
 
-As described in the Method section, we only classified direct replications of previously published work as replications.
-This means that our non-replication category also contains some conceptual replications and \enquote{internal} replications (where original and replication are published in the same paper).
-For ease of communication we will nonetheless refer to this category as \enquote{original} studies.
-As expected, direct replications were much more common among Registered Reports than standard reports: 41 out of 71 Registered Reports (\(57.75\%\)), but only 4 out of 152 standard reports (\(2.63\%\)) were classified as direct replications of previously published work.
-However, this difference cannot account for the stark overall difference between standard reports and Registered Reports described above:
-Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports, \(45.95\%\), was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
+For ease of communication we will refer to papers that were classified as close replications of previously published work as \enquote{replications} and to all other studies as \enquote{original}, even though the latter include some conceptual replications and internal replications (as explained above).
+As expected, replications were much more common among Registered Reports (\(41 / 71 = 57.75\%\)) than standard reports (\(4 / 152 = 2.63\%\)), and replication Registered Reports had a descriptively lower positive result rate than original Registered Reports (see Table 1).
+However, this finding fails to explain the main result described above:
+When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, \(-45.95\%\), was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
 
@@
 
-Since our standard-reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question to ask is how our results compare to Fanelli's.
-The difference between the positive result rate for standard reports in our sample (\(96.05\%\)) and Fanelli's (\(91.49\%\)) is \(4.56\%\).
-This difference is not significantly different from 0 in a two-sided proportions test (\(\chi^2 = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 0.51\), \(p= .306\)), both at \(\alpha = 5\%\).
-In other words, we can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least \(\pm 6\%\) between them.
-The data are inconclusive.
+Since our standard-reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question is how our results compare to Fanelli's.
+The difference between the positive result rates of standard reports in our sample and Fanelli's (\(96.05\% - 91.49\% = 4.56\%\)) is not significantly different from 0 in a two-sided proportions test (\(\chi^2 = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 0.51\), \(p= .306\)), both at \(\alpha = 5\%\).
+The data are inconclusive:
+We can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least \(\pm 6\%\) between them.
 
 Finally, we analysed the language that was used to introduce or refer to hypotheses in Registered Reports.
-We were interested in whether the search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} used by Fanelli captures the way researchers write about hypothesis tests reasonably well.
-The answer is a resounding \enquote{no}:
+We found extremely little overlap with Fanelli's search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}:
 Searching the abstracts, titles, and keywords of the Registered Reports sample showed that only 2/71 Registered Reports would have been detected with this search phrase.
-To get an overview of analogous hypothesis-introduction phrases researchers used in Registered Reports, we stripped the hypothesis quotes of Registered Reports from all content-specific information and extracted \enquote{minimal} phrases that most distinctively indicated that a hypothesis was being described.
+To analyse which other hypothesis-introduction phrases researchers used in Registered Reports, we stripped the coded hypothesis quotes from all content-specific information and extracted \enquote{minimal} phrases that most distinctively indicated that a hypothesis was being described.
 For example, from the hypothesis quote \enquote{(f)or Study 1, we predicted that participants reading about academic (vs.~social) behaviors would show a better anagram performance} we extracted the hypothesis-introduction phrase \enquote{predicted that}.
@@
 In this total set of 97 hypothesis introductions, we found 64 unique phrases showing substantial linguistic variation (see Tables 2 and 3).
-To condense the information, we listed all unique word stems (e.g., the word stem \enquote{hypothes\(^\ast\)} captures the words \enquote{hypothesis}, \enquote{hypotheses}, \enquote{hypothesize}, \enquote{hypothesized}, and so on) and analysed their frequency among all hypothesis introductions.
-Excluding words that are common but too unspecific by themselves, such as \enquote{that}, \enquote{to}, or \enquote{whether}, the five most frequent word stems were \enquote{hypothes\(^\ast\)} (34 occurrences), \enquote{replicat\(^\ast\)} (24), \enquote{test\(^\ast\)} (20), \enquote{examine\(^\ast\)} (8), and \enquote{predict\(^\ast\)} (8).
-Clearly, \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times and more than half of all hypothesis introductions (51/97) contained neither word.
-Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions in original Registered Reports contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, but the same was true for only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication Registered Reports.
+We then listed all unique word stems within those phrases and analysed their frequency.
+Excluding words that are common but too unspecific by themselves (e.g., \enquote{that}, \enquote{to}, \enquote{whether}), the five most frequent word stems were \enquote{hypothes\(^\ast\)} (34 occurrences), \enquote{replicat\(^\ast\)} (24), \enquote{test\(^\ast\)} (20), \enquote{examine\(^\ast\)} (8), and \enquote{predict\(^\ast\)} (8).
+Clearly, \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times, and more than half of all hypothesis introductions (51/97) contained neither word.
 
-We noticed that direct replication Registered Reports generally tended to use different language to describe their hypothesis.
-As the high frequency of the word stem \enquote{replicat\(^\ast\)} suggests, these studies were often not framed as \emph{tests} of a previously tested hypothesis, but as attempts to repeat a previously conducted procedure.
-Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
+Sixty-nine of the 71 Registered Reports (\(97.18 \%\)) had at least one of these five most frequent word stems in their title, abstract, or keywords, meaning that a regular literature search (without access to full texts) with the search terms \enquote{hypothes\(^\ast\) \emph{OR} replicat\(^\ast\) \emph{OR} test\(^\ast\) \emph{OR} examine\(^\ast\) \emph{OR} predict\(^\ast\)} would have been effective in identifying these papers.
+We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question could be useful for future meta-research.
 
-Tables 2 and 3 list all unique hypothesis introductions and their frequency in original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
-Using five as a cut-off value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.
+Lastly, we noticed an interesting difference in language use between original and replication Registered Reports:
+As the high frequency of the word stem \enquote{replicat\(^\ast\)} suggests, replications were often framed as attempts to repeat a previously conducted \emph{procedure} rather than as attempts to test a previously tested \emph{hypothesis}.
+Tables 2 and 3 list all unique hypothesis introductions and their frequency in original Registered Reports and replication Registered Reports, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
 
@@
 
-It is important to keep in mind that not all hypotheses could be coded from the abstract: For 21 Registered Reports, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
-Therefore we additionally tested how many of the Registered Reports would have been detected in a regular search using our five most frequent word stems.
-We searched titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) Registered Reports (\(97.18 \%\)) would have been detected this way.
-We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question would be very useful for future meta-research.
-
 \hypertarget{discussion}{%
@@
 
-We examined the proportion of Psychology articles that find support for their first tested hypothesis and discovered a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
-More than half of the analysed hypothesis tests in Registered Reports were direct replications of previous work, but the difference between standard reports and Registered Reports was still large when direct replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
-The introduction of Registered Reports has clearly led to a much larger proportion of null results appearing in the published literature compared to standard reports.
+We examined the proportion of Psychology articles that find support for their first tested hypothesis and discovered a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data collection).
+More than half of the analysed hypothesis tests in Registered Reports were close replications of previous work, but the difference between standard reports and Registered Reports remained large when close replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
+Clearly, the emerging literature of Registered Reports appears to be publishing a much larger proportion of null results than the standard literature.
 
-The positive result rate we found in standard reports (\(96.05 \%\)) is slightly higher than the \(91.5\%\) reported by Fanelli (2010), although this difference was not statistically significant.
+The positive result rate we found in standard reports (\(96.05 \%\)) is slightly but non-significantly higher than the \(91.5\%\) reported by Fanelli (2010).
 Our replication in a more recent sample of the Psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 (cf.
@@
 To explain the \(52.39 \%\) gap between standard reports and Registered Reports, we must assume some combination of differences in bias, statistical power, or the proportion of true hypotheses researchers choose to examine.
-Figure~\ref{fig:powerbaserate} visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
-For example, assuming no publication bias and no QRPs, even if \emph{all} hypotheses authors of standard reports tested were true, their study designs would need to have more than \(90\%\) power for the true effect size.
-This is highly unlikely, meaning that the standard literature is unlikely to reflect reality.
-As we noted above, there is good reason to assume that methodological rigour and statistical power in Registered Reports are as high as in standard reports or higher, leaving the rate of true hypotheses and bias as remaining explanations.
+Figure~\ref{fig:powerbaserate} visualises the combinations of statistical power and proportion of true hypotheses that could produce the observed positive result rates if the literature were completely unbiased.
+Assuming no publication bias and no QRPs, authors of standard reports would need to test almost exclusively true hypotheses (\(>90\%\)) with more than \(90\%\) power.
+Because this is highly implausible, the standard literature is unlikely to reflect reality.
+As noted above, methodological rigour and statistical power in Registered Reports likely meet or exceed the level of standard reports, leaving the rate of true hypotheses and bias as remaining explanations.
 
@@
 However, assuming over \(90\%\) true hypotheses in the standard literature is neither realistic, nor would it be desirable for a science that wants to advance knowledge beyond trivial facts.
-We thus believe that this factor alone is not sufficient to explain the gap between the positive result rates in Registered Reports and standard reports.
-Rather, the numbers strongly suggest a reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
+We thus believe that this factor alone is not sufficient to explain the large difference in positive results.
+Rather, the numbers strongly suggest a reduction of publication bias and/or QRPs in the Registered-Reports literature.
+Nonetheless, the prior probability of hypotheses in Registered Reports and standard reports may differ and should be studied in future research.
 
-We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports.
-Because hypotheses, authors, and editors were not randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
-Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
-As mentioned above, it is \emph{a-priori} plausible that the Registered Reports format is used selectively for particularly risky hypotheses.
-This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in Psychology.
-It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias.
-Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use.
-This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
+\hypertarget{limitations}{%
+\subsection{Limitations}\label{limitations}}
 
-A second limitation of the current study (and of Fanelli, 2010) is that standard reports were selected using the search term \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
-As our results show, this phrase was virtually absent in the Registered Report population.
-The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for \enquote{test\(^\ast\) the hypothes\(^\ast\)} might miss most of the hypothesis-testing studies in the psychological literature, and results obtained this way may not generalise to all published studies.
-For example, it is possible that authors are more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., \enquote{we examined the role of \ldots{}}).
-If this were true, using other strategies to select standard reports might yield lower estimates for the positive result rate.
-However, this does not seem to be the case:
-Studies using different selection criteria for articles and hypotheses have found very similar rates of supported hypotheses.
-For example, the positive result rates in Sterling (1959), Sterling et al.
-(1995), and the original studies included in the Reproducibility Project: Psychology (Open Science Collaboration, 2015) were \(97.28\%\), \(95.56\%\), and \(97\%\), respectively.
-Motyl et al. (2017) report \(89.17\%\) and \(92.01\%\) significant results for \enquote{critical} hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively.
-Therefore, although the search term used to find standard reports might limit the generalisability of our results, it seems to yield comparable estimates as the selection strategies used in different studies.
+Our study was not an experiment\(\,\)---\(\,\)hypotheses, authors, and editors were not randomly assigned to each publication format\(\,\)---\(\,\)and thus precludes strong causal inferences.
+As discussed above, it seems highly plausible that Registered Reports reduce publication bias and QRPs, which in turn reduces the positive result rate.
+Yet we neither know exactly how effective Registered Reports are at reducing bias, nor how large the effect on positive results would be in the absence of potential confounds.
+One such confound, as just discussed, could be that Registered Reports may be used for particularly risky hypotheses.
+Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use.
+This would lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
 
-A final limitation is the decision to code only the first reported hypothesis.
+Another limitation of the current study (and of Fanelli, 2010) is that standard reports were selected using the search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
+This phrase was virtually absent in Registered Reports, suggesting that this search strategy may not yield a representative sample of the population of hypothesis-testing studies in the literature.
+The use of the phrase might even be confounded with the outcome of a study:
+For example, authors may be more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., \enquote{we examined the role of \ldots{}}).
+A similar concern could be raised for the decision to code only the first reported hypothesis of each article.
 The first hypothesis test may not be representative for all hypothesis tests reported in a paper, and the order of reporting may differ between standard reports and Registered Reports.
-Perhaps Registered-Report authors are more likely to present their hypotheses in \enquote{chronological} order, whereas standard-report authors tend to rearrange the order in which hypotheses are reported based on their outcomes, and present supported hypotheses first.
-Here again, the converging estimates from the four studies cited above (none of which use the first-hypothesis rule) make it seem unlikely that our result is an artefact of this decision.
-Regardless of which hypothesis one chooses to analyse across a set of papers -- the first, the last, or the \enquote{critical} one -- the positive result rate turns out to be higher than what can be expected based on realistic estimates of the proportion of true hypotheses researchers study and the statistical power of their tests.
+For example, standard-report authors might tend to present supported hypotheses first, whereas Registered-Report authors might be more likely to present their hypotheses in \enquote{chronological} order.
+
+Both of these potential confounds might lead to an inflated estimate of the positive result rate in standard reports.
+However, studies using different selection criteria for articles and hypotheses have found very similar rates of supported hypotheses in the literature:
+\(97.28\%\) in Sterling (1959), \(95.56\%\) in Sterling et al. (1995), and \(97\%\) in the original studies included in the Reproducibility Project: Psychology (Open Science Collaboration, 2015).
+In addition, Motyl et al. (2017) report \(89.17\%\) and \(92.01\%\) significant results for \enquote{critical} hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively.
+Although the selection criteria for articles and hypotheses in our study may limit the generalisability of the results, this level of convergence makes it seem unlikely that alternative methods would have yielded dramatically different conclusions.
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
 
@@
 The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the existing body of published research.
-Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered Reports literature.
+Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered-Reports literature.
 The absence of negative results is a serious threat to a cumulative science.
 In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?} The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
-In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature---and may be one solution to achieve a more credible scientific record.
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature\(\,\)---\(\,\)and may be one solution to achieve a more credible scientific record.
 
@@
 
-\hypertarget{conflicts-of-interest}{%
-\subsubsection{Conflicts of Interest}\label{conflicts-of-interest}}
+\hypertarget{reporting}{%
+\subsubsection{Reporting}\label{reporting}}
 
-The authors declare that they have no conflicts of interest with respect to the authorship or the publication of this article.
+We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.
 
@@
 \& D.L.; data curation, formal analysis, and software: A.S.
-\& M.S.; investigation, methodology, and validation: A.S., M.S., \& D.L; supervision: A.S \& D.L.; visualisation and writing---original draft: A.S; writing---review and editing: A.S., M.S., \& D.L.
+\& M.S.; investigation, methodology, and validation: A.S., M.S., \& D.L; supervision: A.S \& D.L.; visualisation and writing\(\,\)---\(\,\)original draft: A.S; writing\(\,\)---\(\,\)review and editing: A.S., M.S., \& D.L.
+
+\hypertarget{conflicts-of-interest}{%
+\subsubsection{Conflicts of Interest}\label{conflicts-of-interest}}
+
+The authors declare that they have no conflicts of interest with respect to the authorship or the publication of this article.
 
@@
 This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leonid Tiokhin, and Stuart Ritchie for valuable comments that helped improve this manuscript.
+
+\hypertarget{prior-versions}{%
+\subsubsection{Prior versions}\label{prior-versions}}
+
+A preprint of this manuscript has been published on \emph{PsyArXiv} (\url{https://doi.org/10.31234/osf.io/p6e9c}).
+All sections of the present manuscript have been shortened to comply with the submission guidelines, but are intended to contain the same arguments, methods, results, and conclusions as the preprint.
 
@@
 
-\leavevmode\hypertarget{ref-Chambers2013}{}%
-Chambers, C. (2013). Registered reports: A new publishing initiative at Cortex, \emph{49}(3), 609--610. Retrieved from \url{http://orca.cf.ac.uk/45177/1/Chambers_Cortex_2013b_GreenOA.pdf}
-
-\leavevmode\hypertarget{ref-Chambers2015}{}%
-Chambers, C., Dienes, Z., McIntosh, R., Rotshtein, P., \& Willmes, K.
-(2015).
-Registered Reports: Realigning incentives in scientific publishing.
-\emph{Cortex}, \emph{66}, 1--2.
-\url{https://doi.org/10.1016/j.cortex.2015.03.022}
+\leavevmode\hypertarget{ref-Chambers2020}{}%
+Chambers, C. D., \& Tzavella, L. (2020). \emph{Registered Reports: Past, Present and Future} (preprint). MetaArXiv. \url{https://doi.org/10.31222/osf.io/43298}
 
@@
 \emph{International Journal of Clinical Pharmacology and Therapeutics}, \emph{37}(1), 1--7.
-
-\leavevmode\hypertarget{ref-Cristea2018}{}%
-Cristea, I.
-A., \& Ioannidis, J.
-P.
-A.
-(2018).
-P values in display items are ubiquitous and almost invariably significant: A survey of top science journals.
-\emph{PLOS ONE}, \emph{13}(5), e0197440.
-\url{https://doi.org/10.1371/journal.pone.0197440}
-
-\leavevmode\hypertarget{ref-deWinter2013}{}%
-de Winter, J., \& Happee, R.
-(2013).
-Why Selective Publication of Statistically Significant Results Can Be Effective.
-\emph{PLOS ONE}, \emph{8}(6), e66463.
-\url{https://doi.org/10.1371/journal.pone.0066463}
 
@@
 
-\leavevmode\hypertarget{ref-Jonas2016}{}%
-Jonas, K.
-J., \& Cesario, J.
-(2016).
-How can preregistration contribute to research in our field?
-\emph{Comprehensive Results in Social Psychology}, \emph{1}(1-3), 1--7.
-\url{https://doi.org/10.1080/23743603.2015.1070611}
-
 \leavevmode\hypertarget{ref-Kaplan2015}{}%
@@
 Kerr, N. L. (1998). HARKing: Hypothesizing after the results are known. \emph{Personality and Social Psychology Review}, \emph{2}(3), 196--217. \url{https://doi.org/10.1207/s15327957pspr0203_4}
-
-\leavevmode\hypertarget{ref-Kohler2019}{}%
-Köhler, T., \& Cortina, J.
-M.
-(2019).
-Play It Again, Sam!
-An Analysis of Constructive Replication in the Organizational Sciences.
-\emph{Journal of Management}, 014920631984398.
-\url{https://doi.org/10.1177/0149206319843985}
 
@@
 
-\leavevmode\hypertarget{ref-Nosek2014}{}%
-Nosek, B.
-A., \& Lakens, D.
-(2014).
-Registered Reports: A Method to Increase the Credibility of Published Results.
-\emph{Social Psychology}, \emph{45}(3), 137--141.
-\url{https://doi.org/10.1027/1864-9335/a000192}
-
 \leavevmode\hypertarget{ref-OSC2015}{}%
 Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716. \url{https://doi.org/10.1126/science.aac4716}
-
-\leavevmode\hypertarget{ref-Pridemore2018}{}%
-Pridemore, W.
-A., Makel, M.
-C., \& Plucker, J.
-A.
-(2018).
-Replication in Criminology and the Social Sciences.
-\emph{Annual Review of Criminology}, \emph{1}(1), 19--38.
-\url{https://doi.org/10.1146/annurev-criminol-032317-091849}
 
@@
 
-\leavevmode\hypertarget{ref-SingletonThorn2019}{}%
-Singleton Thorn, F., Dudgeon, P., \& Fidler, F.
-(2019, September).
-\emph{Statistical power and effect sizes in psychology are decreasing over time}.
-Presented at the Metascience 2019 Symposium, Stanford, CA, USA.
-Retrieved from \url{https://www.metascience2019.org/poster-session/felix-singleton-thorn/}
-
 \leavevmode\hypertarget{ref-Sterling1959}{}%
@@
 
-\leavevmode\hypertarget{ref-vanAssen2014}{}%
-van Assen, M.
-A.
-L.
-M., van Aert, R.
-C.
-M., Nuijten, M.
-B., \& Wicherts, J.
-M.
-(2014).
-Why Publishing Everything Is More Effective than Selective Publishing of Statistically Significant Results.
-\emph{PLOS ONE}, \emph{9}(1), e84896.
-\url{https://doi.org/10.1371/journal.pone.0084896}
-
 \leavevmode\hypertarget{ref-R-reshape2}{}%

### 2020-07-12 submission2/positive_results_SRs_RRs_submission.Rmd
final minor edits

@@
 keywords          : "Publication bias, Registered Reports, hypothesis testing"
-#wordcount         : "6488"
+#wordcount         : "5870"
 
@@
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known. 
-Since its introduction in 2013, the format has rapidly gained popularity and is offered by 250 journals at the time of writing (http://cos.io/rr).
+Since its introduction in 2013, the format has rapidly gained popularity and is offered by 256 journals at the time of writing (http://cos.io/rr).
 
@@
 We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and because it can easily be applied to a large set of studies. 
-Because we expected many more Registered Reports than standard reports to be close replications of earlier studies$\,$---$\,$and perhaps movitated by scepticism of the original results$\,$---$\,$we additionally examined the role of replications in our analysis.
+Because we expected many more Registered Reports than standard reports to be close replications of earlier studies$\,$---$\,$and perhaps motivated by scepticism of the original results$\,$---$\,$we additionally examined the role of replications in our analysis.
 
@@
 Our online materials include an Appendix with fine-grained methodological details and an annotated preregistration document with detailed comparisons to the eventual procedure (https://osf.io/dbhgr).
+Appendix and open dataset also list all measures we collected but do not describe here (all of which were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed here).
 
@@
 There were `r rep.disagreements` disagreements (Cohen's kappa = `r printp(kappa.rep)`), all were resolved by discussion.
-
-### Additional measures
-All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above, and are documented in the Appendix and in our shared dataset and codebook.
 
@@
 
-`r printnum(n.hypintros.fivewords.RR, numerals = FALSE, capitalize = TRUE)` of the `r n.RR` Registered Reports ($`r printnum(n.hypintros.fivewords.RR/n.RR*100)` \%$) had at least one of these five most frequent word stems in their title, abstract, or keywords, meaning that a regular literature search (without access to full texts) with the search terms "hypothes$^\ast$ *OR* replicat$^\ast$ *OR* test$^\ast$ *OR* examine$^\ast$ *OR* predict$^\ast$" would have been effective in identifying these papers.
+`r n.hypintros.fivewords.RR` of the `r n.RR` Registered Reports ($`r printnum(n.hypintros.fivewords.RR/n.RR*100)` \%$) had at least one of these five most frequent word stems in their title, abstract, or keywords, meaning that a regular literature search (without access to full texts) with the search terms "hypothes$^\ast$ *OR* replicat$^\ast$ *OR* test$^\ast$ *OR* examine$^\ast$ *OR* predict$^\ast$" would have been effective in identifying these papers.
 We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question could be useful for future meta-research.
@@
 Another limitation of the current study [and of @Fanelli2010] is that standard reports were selected using the search phrase "test$^\ast$ the hypothes$^\ast$".
-This phrase was virtually absent in  Registered Reports, suggesting that this search strategy may not yield a representative sample of the population of hypothesis-testing studies in the literature.
+This phrase was virtually absent in  Registered Reports, suggesting that the search strategy may not yield a representative sample of the population of hypothesis-testing studies in the literature.
 The use of the phrase might even be confounded with the outcome of a study:

### 2020-07-12 submission2/positive_results_SRs_RRs_submission.tex
final minor edits

@@
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
-Since its introduction in 2013, the format has rapidly gained popularity and is offered by 250 journals at the time of writing (\url{http://cos.io/rr}).
+Since its introduction in 2013, the format has rapidly gained popularity and is offered by 256 journals at the time of writing (\url{http://cos.io/rr}).
 
@@
 We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and because it can easily be applied to a large set of studies.
-Because we expected many more Registered Reports than standard reports to be close replications of earlier studies\(\,\)---\(\,\)and perhaps movitated by scepticism of the original results\(\,\)---\(\,\)we additionally examined the role of replications in our analysis.
+Because we expected many more Registered Reports than standard reports to be close replications of earlier studies\(\,\)---\(\,\)and perhaps motivated by scepticism of the original results\(\,\)---\(\,\)we additionally examined the role of replications in our analysis.
 
@@
 Our online materials include an Appendix with fine-grained methodological details and an annotated preregistration document with detailed comparisons to the eventual procedure (\url{https://osf.io/dbhgr}).
+Appendix and open dataset also list all measures we collected but do not describe here (all of which were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed here).
 
@@
 There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.
-
-\hypertarget{additional-measures}{%
-\subsubsection{Additional measures}\label{additional-measures}}
-
-All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above, and are documented in the Appendix and in our shared dataset and codebook.
 
@@
 
-Sixty-nine of the 71 Registered Reports (\(97.18 \%\)) had at least one of these five most frequent word stems in their title, abstract, or keywords, meaning that a regular literature search (without access to full texts) with the search terms \enquote{hypothes\(^\ast\) \emph{OR} replicat\(^\ast\) \emph{OR} test\(^\ast\) \emph{OR} examine\(^\ast\) \emph{OR} predict\(^\ast\)} would have been effective in identifying these papers.
+69 of the 71 Registered Reports (\(97.18 \%\)) had at least one of these five most frequent word stems in their title, abstract, or keywords, meaning that a regular literature search (without access to full texts) with the search terms \enquote{hypothes\(^\ast\) \emph{OR} replicat\(^\ast\) \emph{OR} test\(^\ast\) \emph{OR} examine\(^\ast\) \emph{OR} predict\(^\ast\)} would have been effective in identifying these papers.
 We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question could be useful for future meta-research.
@@
 Another limitation of the current study (and of Fanelli, 2010) is that standard reports were selected using the search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
-This phrase was virtually absent in Registered Reports, suggesting that this search strategy may not yield a representative sample of the population of hypothesis-testing studies in the literature.
+This phrase was virtually absent in Registered Reports, suggesting that the search strategy may not yield a representative sample of the population of hypothesis-testing studies in the literature.
 The use of the phrase might even be confounded with the outcome of a study:

### 2021-01-21 submission2/positive_results_SRs_RRs_revision1.Rmd
Created new version of the manuscript for the revision

--- 2020-07-12 submission2/positive_results_SRs_RRs_submission.Rmd
@@
 Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
+These two assumptions appear highly implausible a priori, and available evidence on average statistical power in the literature shows that at least one does not hold [e.g., @Szucs2017].
 
@@
 Evidence for both categories of bias exist: 
-Publication bias has been observed in peer review [@Mahoney1977; @Atkinson1982] and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results [@Franco2014; @Franco2016]; and QRPs have been admitted by scientists in several survey studies [@John2012; @Fiedler2016; @Agnoli2017].
+Publication bias has been observed in peer review [@Mahoney1977; @Atkinson1982] and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results [@Franco2014; @Franco2016]; and QRPs have been admitted by scientists in several survey studies [@John2012; @Fiedler2016; @Agnoli2017; @Fraser2018; @Makel2019].
 
@@
 The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth "standard reports", SRs), and to estimate the size of this potential difference.
-Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature [@Maxwell2004; @Szucs2017], such a difference would be unlikely to be due to "failed" studies or false negatives$\,$---$\,$and more likely to be due to reduced publication bias and QRPs.
+Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature [@Maxwell2004; @Szucs2017], such a difference would be unlikely to be due to "failed" studies or false negatives.
 Should the positive result rate in Registered Reports be much lower than in the standard literature, it might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.
@@
 With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found $60.5\%$ unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
-A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature using a previously established method [@Fanelli2010; @Fanelli2012].
+A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature.
 In addition, we replicate @Fanelli2010 and provide data to evaluate his method: The search term "test$^\ast$ the hypothes$^\ast$" might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
@@
 # Methods
-After conducting a pilot to test the planned procedure, we preregistered our study (https://osf.io/s8e97). 
+After conducting a pilot to test the planned procedure, we preregistered our study (https://osf.io/sy927/). 
 Methods and analyses described here were preregistered unless otherwise noted. 
@@
 
+The sample size of standard reports was pre-specifided to replicate Fanelli's [-@Fanelli2010] ($n = 150$) since it matched the maximum number of available Registered Reports ($n = 151$, see below) and piloting indicated that the required coding time would just fit our resource constraints.
 Standard reports were selected by searching the 633 journals listed under "Psychiatry/Psychology" in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase "test$^\ast$ the hypothes$^\ast$" in title, abstract, or keywords.
-Using the same sample size as @Fanelli2010, we randomly selected 150 papers from the 1919 search results.
-Excluded papers were replaced by resampling (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.\ \@ref(fig:sampling)).
+We then randomly selected 150 papers from the 1919 papers that resulted from this search.
+Excluded papers were replaced by resampling twice (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.\ \@ref(fig:sampling)).
 
@@
 
-We aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether they used the phrase "test$^\ast$ the hypothes$^\ast$". 
+The sample size of Registered Report was determined by our goal to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether they used the phrase "test$^\ast$ the hypothes$^\ast$".
 Registered Reports were selected through a Registered-Reports database curated by the Center for Open Science^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (retrieved 19th November 2018).
@@
 We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+Coders were not blind to condition (Registered Report vs standard report) because access to the full text was often necessary, the content of which would have made most Registered Reports clearly identifiable.
 
@@
 `r n.support.RR` out of `r n.RR` Registered Reports and `r n.support.SR` out of `r n.SR` standard reports had positive results, meaning that the positive result rate was $`r printnum(prop.support.RR*100)` \%$ for Registered Reports ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]) and $`r printnum(prop.support.SR*100)` \%$ for standard reports ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]; see Fig.\ \@ref(fig:mainplot)).
-This difference of $`r printnum((prop.support.RR-prop.support.SR)*100)` \%$ was statistically significant in the preregistered one-sided proportions test with $\alpha = 5\%$, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
+This difference of $`r printnum((prop.support.RR-prop.support.SR)*100)` \%$ was statistically significant in the preregistered one-sided proportions test with $\alpha = 5\%$, $\chi^2(`r proptestresult$parameter`) = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
 Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$ at $\alpha = 5\%$ ($z = `r printnum(min(abs(tostresult$TOST_z1), abs(tostresult$TOST_z2)))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$), meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
@@
 However, this finding fails to explain the main result described above:
-When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, $`r printnum((prop.orig.support.RR-prop.orig.support.SR)*100)`\%$, was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(reptost$TOST_z1), abs(reptost$TOST_z2)))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
+When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, $`r printnum((prop.orig.support.RR-prop.orig.support.SR)*100)`\%$, was still significantly different from 0 ($\chi^2(`r origproptest$parameter`) = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(reptost$TOST_z1), abs(reptost$TOST_z2)))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
 
@@
 Since our standard-reports sample represents a direct replication of @Fanelli2010 for the discipline Psychiatry & Psychology, another interesting question is how our results compare to Fanelli's.
-The difference between the positive result rates of standard reports in our sample and Fanelli's ($`r printnum(prop.support.SR*100)`\% - `r printnum(prop.support.Fanelli*100)`\% = `r printnum((prop.support.SR-prop.support.Fanelli)*100)`\%$) is not significantly different from 0 in a two-sided proportions test ($\chi^2 = `r printnum(Fanelliproptest$statistic)`$, $p= `r printp(Fanelliproptest$p.value)`$) but also not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(Fanellitost$TOST_z1), abs(Fanellitost$TOST_z2)))`$, $p= `r printp(max(Fanellitost$TOST_p1, Fanellitost$TOST_p2))`$), both at $\alpha = 5\%$.
+The difference between the positive result rates of standard reports in our sample and Fanelli's ($`r printnum(prop.support.SR*100)`\% - `r printnum(prop.support.Fanelli*100)`\% = `r printnum((prop.support.SR-prop.support.Fanelli)*100)`\%$) is not significantly different from 0 in a two-sided proportions test ($\chi^2(`r Fanelliproptest$parameter`) = `r printnum(Fanelliproptest$statistic)`$, $p= `r printp(Fanelliproptest$p.value)`$) but also not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(Fanellitost$TOST_z1), abs(Fanellitost$TOST_z2)))`$, $p= `r printp(max(Fanellitost$TOST_p1, Fanellitost$TOST_p2))`$), both at $\alpha = 5\%$.
 The data are inconclusive: 
@@
 Assuming no publication bias and no QRPs, authors of standard reports would need to test almost exclusively true hypotheses ($>90\%$) with more than $90\%$ power.
-Because this is highly implausible, the standard literature is unlikely to reflect reality. 
+Because this is highly implausible and contradicted by available evidence [e.g., @Szucs2017], the standard literature is unlikely to reflect reality. 
 As noted above, methodological rigour and statistical power in Registered Reports likely meet or exceed the level of standard reports, leaving the rate of true hypotheses and bias as remaining explanations.

### 2021-01-21 submission2/positive_results_SRs_RRs_revision1.tex
Created new version of the manuscript for the revision

--- 2020-07-12 submission2/positive_results_SRs_RRs_submission.tex
@@
 Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
+These two assumptions appear highly implausible a priori, and available evidence on average statistical power in the literature shows that at least one does not hold (e.g., Szucs \& Ioannidis, 2017).
 
@@
 Evidence for both categories of bias exist:
-Publication bias has been observed in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; John, Loewenstein, \& Prelec, 2012).
+Publication bias has been observed in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; Fraser, Parker, Nakagawa, Barnett, \& Fidler, 2018; John, Loewenstein, \& Prelec, 2012; Makel, Hodges, Cook, \& Plucker, 2019).
 
@@
 The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
-Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature (Maxwell, 2004; Szucs \& Ioannidis, 2017), such a difference would be unlikely to be due to \enquote{failed} studies or false negatives\(\,\)---\(\,\)and more likely to be due to reduced publication bias and QRPs.
+Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature (Maxwell, 2004; Szucs \& Ioannidis, 2017), such a difference would be unlikely to be due to \enquote{failed} studies or false negatives.
 Should the positive result rate in Registered Reports be much lower than in the standard literature, it might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.
@@
 With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found \(60.5\%\) unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
-A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature using a previously established method (Fanelli, 2010, 2012).
+A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature.
 In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
@@
 
-After conducting a pilot to test the planned procedure, we preregistered our study (\url{https://osf.io/s8e97}).
+After conducting a pilot to test the planned procedure, we preregistered our study (\url{https://osf.io/sy927/}).
 Methods and analyses described here were preregistered unless otherwise noted.
@@
 
+The sample size of standard reports was pre-specifided to replicate Fanelli's (2010) (\(n = 150\)) since it matched the maximum number of available Registered Reports (\(n = 151\), see below) and piloting indicated that the required coding time would just fit our resource constraints.
 Standard reports were selected by searching the 633 journals listed under \enquote{Psychiatry/Psychology} in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} in title, abstract, or keywords.
-Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results.
-Excluded papers were replaced by resampling (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.~\ref{fig:sampling}).
+We then randomly selected 150 papers from the 1919 papers that resulted from this search.
+Excluded papers were replaced by resampling twice (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.~\ref{fig:sampling}).
 
@@
 
-We aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
+The sample size of Registered Report was determined by our goal to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
 Registered Reports were selected through a Registered-Reports database curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved 19th November 2018).
@@
 31 out of 71 Registered Reports and 146 out of 152 standard reports had positive results, meaning that the positive result rate was \(43.66 \%\) for Registered Reports (\(95 \%\) CI {[}31.91, 55.95{]}) and \(96.05 \%\) for standard reports (\(95 \%\) CI {[}91.61, 98.54{]}; see Fig.~\ref{fig:mainplot}).
-This difference of \(-52.39 \%\) was statistically significant in the preregistered one-sided proportions test with \(\alpha = 5\%\), \(\chi^2 = 77.96\), \(p < .001\).
+This difference of \(-52.39 \%\) was statistically significant in the preregistered one-sided proportions test with \(\alpha = 5\%\), \(\chi^2(1) = 77.96\), \(p < .001\).
 Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\) (\(z = 7.61\), \(p > .999\)), meaning that we cannot reject differences more extreme than \(6\%\).
@@
 \centering
-\includegraphics{positive_results_SRs_RRs_submission_files/figure-latex/mainplot-1.pdf}
+\includegraphics{positive_results_SRs_RRs_revision1_files/figure-latex/mainplot-1.pdf}
 \caption{\label{fig:mainplot}Positive result rates for standard reports and Registered Reports. Error bars indicate \(95 \%\) confidence intervals around the observed positive result rate.}
@@
 However, this finding fails to explain the main result described above:
-When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, \(-45.95\%\), was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
+When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, \(-45.95\%\), was still significantly different from 0 (\(\chi^2(1) = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
 
@@
 Since our standard-reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question is how our results compare to Fanelli's.
-The difference between the positive result rates of standard reports in our sample and Fanelli's (\(96.05\% - 91.49\% = 4.56\%\)) is not significantly different from 0 in a two-sided proportions test (\(\chi^2 = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 0.51\), \(p= .306\)), both at \(\alpha = 5\%\).
+The difference between the positive result rates of standard reports in our sample and Fanelli's (\(96.05\% - 91.49\% = 4.56\%\)) is not significantly different from 0 in a two-sided proportions test (\(\chi^2(1) = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 0.51\), \(p= .306\)), both at \(\alpha = 5\%\).
 The data are inconclusive:
@@
 Assuming no publication bias and no QRPs, authors of standard reports would need to test almost exclusively true hypotheses (\(>90\%\)) with more than \(90\%\) power.
-Because this is highly implausible, the standard literature is unlikely to reflect reality.
+Because this is highly implausible and contradicted by available evidence (e.g., Szucs \& Ioannidis, 2017), the standard literature is unlikely to reflect reality.
 As noted above, methodological rigour and statistical power in Registered Reports likely meet or exceed the level of standard reports, leaving the rate of true hypotheses and bias as remaining explanations.
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{positive_results_SRs_RRs_submission_files/figure-latex/powerbaserate-1}
+{\centering \includegraphics[width=0.8\textwidth]{positive_results_SRs_RRs_revision1_files/figure-latex/powerbaserate-1}
 
@@
 \leavevmode\hypertarget{ref-Chambers2020}{}%
-Chambers, C. D., \& Tzavella, L. (2020). \emph{Registered Reports: Past, Present and Future} (preprint). MetaArXiv. \url{https://doi.org/10.31222/osf.io/43298}
+Chambers, C. D., \& Tzavella, L. (2020). \emph{Registered Reports: Past, Present and Future} (Preprint). MetaArXiv. \url{https://doi.org/10.31222/osf.io/43298}
 
@@
 
+\leavevmode\hypertarget{ref-Fraser2018}{}%
+Fraser, H., Parker, T., Nakagawa, S., Barnett, A., \& Fidler, F.
+(2018).
+Questionable research practices in ecology and evolution.
+\emph{PLOS ONE}, \emph{13}(7), e0200303.
+\url{https://doi.org/10.1371/journal.pone.0200303}
+
 \leavevmode\hypertarget{ref-Goldacre2016}{}%
-Goldacre, B., Drysdale, H., Powell-Smith, A., Dale, A., Milosevic, I., Slade, E., \ldots{} Heneghan, C.
-(2016).
-The COMPare Trials Project.
-Retrieved February 3, 2020, from \url{http://compare-trials.org}
+Goldacre, B., Drysdale, H., Powell-Smith, A., Dale, A., Milosevic, I., Slade, E., \ldots{} Heneghan, C. (2016). The COMPare Trials Project. \emph{COMPare}. http://compare-trials.org.
 
@@
 
+\leavevmode\hypertarget{ref-Makel2019}{}%
+Makel, M. C., Hodges, J., Cook, B. G., \& Plucker, J. (2019). Questionable and Open Research Practices in Education Research. \url{https://doi.org/10.35542/osf.io/f7srb}
+
 \leavevmode\hypertarget{ref-Makel2012}{}%
@@
 (2019).
-Replication studies in economics---How many and which papers are chosen for replication, and why?
+Replication studies in economicsHow many and which papers are chosen for replication, and why?
 \emph{Research Policy}, \emph{48}(1), 62--83.
@@
 \leavevmode\hypertarget{ref-RRRwebsite}{}%
-Registered Replication Reports. (n.d.). Retrieved December 28, 2019, from \url{https://www.psychologicalscience.org/publications/replication}
+Registered Replication Reports. (n.d.). \emph{Association for Psychological Science - APS}. https://www.psychologicalscience.org/publications/replication.
 
 \leavevmode\hypertarget{ref-Rohatgi2018}{}%
-Rohatgi, A. (2018). \emph{WebPlotDigitizer - Web Based Plot Digitizer}. Austin, Texas, USA. Retrieved from \url{https://automeris.io/WebPlotDigitizer}
+Rohatgi, A. (2018). \emph{WebPlotDigitizer - Web Based Plot Digitizer}. Austin, Texas, USA.
 
@@
 \leavevmode\hypertarget{ref-RStudioTeam2019}{}%
-RStudio Team. (2019). \emph{RStudio: Integrated development environment for r}. Boston, MA: RStudio, Inc. Retrieved from \url{http://www.rstudio.com/}
+RStudio Team. (2019). \emph{RStudio: Integrated development environment for r}. Boston, MA: RStudio, Inc.
 
@@
 (1959).
-Publication Decisions and their Possible Effects on Inferences Drawn from Tests of Significance---or Vice Versa.
+Publication Decisions and their Possible Effects on Inferences Drawn from Tests of Significanceor Vice Versa.
 \emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.

### 2021-02-18 analysis/02_quantitative_analyses.R
Analysis script updated with a new analysis (within-journal comparison of positive results in RRs vs SRs) added during revision

@@ -16,7 +16,10 @@
 #####  * 4: Exploratory analysis:                   #####
 #####       positive result rate in standard        #####
 #####       reports compared to Fanelli (2010)      #####
-#####  * 5: Robustness check:                       #####
+#####  * 5: Additional analysis:                    #####
+#####       Within-journal comparison of Registered #####
+#####       Reports and standard reports            #####
+#####  * 6: Robustness check:                       #####
 #####       Run main analysis without replacement   #####
 #####       standard reports                        #####
 #####                                               #####
@@ -30,19 +33,21 @@
 ## 1. Setup: load packages and data 
 ##==============================================================================##
 
-# Four packages are needed: TOSTER to calculate equivalence tests, ggplot2 for
+# Five packages are needed: TOSTER to calculate equivalence tests, ggplot2 for
 # creating the plot for Figure 2 in the manuscript, papaja for Table 1 in 
-# the manuscript, and here to locate the data file when loading it. If you  
-# want to run these analyses outside of our R project, you may need to adjust
-# the command to load the data, and you can do this without making use of the
-# here package. papaja was not yet on CRAN when this was written and has to 
-# be installed from Github, using the devtools package. Its role in this script
-# is very minor though -- all analyses can be reproduced without papaja.
+# the manuscript, tidyr to run the additional analysis 5, and here to locate 
+# the data file when loading it. If you want to run these analyses outside of 
+# our R project, you may need to adjust the command to load the data, and you 
+# can do this without making use of the here package. papaja was not yet on 
+# CRAN when this was written and has to be installed from Github, using the 
+# devtools package. Its role in this script is very minor though -- all 
+# analyses can be reproduced without papaja.
 
 # Install packages if needed by uncommenting the respective line(s):
 # install.packages("here")  # install here
 # install.packages("TOSTER")  # install TOSTER
 # install.packages("ggplot2")  # install ggplot2
+# install.packages("tidyr")  # install tidyr
 # install.packages("devtools")  # install devtools to install papaja
 # devtools::install_github("crsh/papaja")  # install papaja
 
[…]

### 2021-02-18 submission2/positive_results_SRs_RRs_revision1.Rmd
Updated revised manuscript

@@
 A later replication of this study reported $95.56\%$ statistically significant results in articles from 1986/87 [@Sterling1995]. 
-Similarly, a seminal study by @Fanelli2010 compared the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
+Similarly, a seminal study by @Fanelli2010 analysed authors' verbal conclusions in hypothesis-testing papers sampled from the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology claimed support for their first hypothesis$\,$---$\,$the highest estimate of all disciplines in the study.
 For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$.
@@
 
-Some have argued that selecting for positive results is defensible$\,$---$\,$desirable, even$\,$---$\,$because it weeds out low-quality research that would only pollute the literature [e.g., @Cleophas1999].
+Some have argued that negative results are often uninformative or the result of low-quality research and should not be published at the same rate as positive results to avoid cluttering the literature [e.g., @Cleophas1999; @Mitchell2014; @Baumeister2016].
 If most negative results that are currently missing from the literature are indeed due to immature ideas or poor methods, a literature that selects studies based on *quality* instead of results should contain a similar proportion of positive results as the current one.
@@
 Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature [@Maxwell2004; @Szucs2017], such a difference would be unlikely to be due to "failed" studies or false negatives.
-Should the positive result rate in Registered Reports be much lower than in the standard literature, it might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.
+Barring large confounfds, such as substantial differences in the prior probability of hypotheses tested in Registered Reports versus the standard literature, a much lower positive result rate in Registered Reports might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.
 
@@
 
-The sample size of standard reports was pre-specifided to replicate Fanelli's [-@Fanelli2010] ($n = 150$) since it matched the maximum number of available Registered Reports ($n = 151$, see below) and piloting indicated that the required coding time would just fit our resource constraints.
+The sample size of standard reports was pre-specified to replicate the one used by Fanelli [-@Fanelli2010], $n = 150$, since it matched the maximum number of Registered Reports available at the time ($n = 151$, see below) and piloting indicated that the required coding time would just fit our resource constraints.
 Standard reports were selected by searching the 633 journals listed under "Psychiatry/Psychology" in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase "test$^\ast$ the hypothes$^\ast$" in title, abstract, or keywords.
@@
 In Registered Reports, we coded the first *preregistered* hypothesis, thus excluding unregistered pilot studies.
+The coding procedure was identical for both article formats in all other respects. 
 Coding disagreements between "full" and "partial" support were deemed minor since they would not affect the final results. 
@@
 We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
-Coders were not blind to condition (Registered Report vs standard report) because access to the full text was often necessary, the content of which would have made most Registered Reports clearly identifiable.
+Because removing all indicators that could have identified Registered Reports as such from their full texts would have been practically impossible, coding was not blind to publication format (Registered Report vs standard report).
 
@@
 
-We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 *and* not statistically equivalent to a range from $-6\%$ to $+6\%$ (both at $\alpha = 5\%$).
+We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 *and* not statistically equivalent to a range from $-6\%$ to $+6\%$ (both at $\alpha = 5\%$)^[Note that these inference criteria are logically equivalent to "significantly smaller than 0 and not statistically equivalent to a range from $-6\%$ to $0\%$": Since the first criterion (statistically smaller than 0) requires the $90\%$ CI to end below 0, half of the equivalence range specified in the second criterion $\,$---$\,$from $0\%$ to $+6\%\,$---$\,$ is redundant (which we failed to notice before preregistering the analysis).].
+Specifying a smallest effect size of interest of $6\%$ absolute risk reduction provides an initial yardstick to evaluate our results and make our prediction falsifiable.
+However, the value of $\pm 6\%$ does not possess an intrinsic theoretical meaning. 
+As the emerging meta-psychological literature matures, we hope to see future research base the smallest effect size of interest on increasingly well-informed empirical and theoretical considerations.
 
@@
 However, this finding fails to explain the main result described above:
-When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, $`r printnum((prop.orig.support.RR-prop.orig.support.SR)*100)`\%$, was still significantly different from 0 ($\chi^2(`r origproptest$parameter`) = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(reptost$TOST_z1), abs(reptost$TOST_z2)))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
+When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, $`r printnum((prop.orig.support.RR-prop.orig.support.SR)*100)`\%$, was still significantly smaller than 0 ($\chi^2(`r origproptest$parameter`) = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(reptost$TOST_z1), abs(reptost$TOST_z2)))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
 
@@
 ## Limitations
+Since coders could not be blinded to an article's publication format, their judgment may have been biased.
 Our study was not an experiment$\,$---$\,$hypotheses, authors, and editors were not randomly assigned to each publication format$\,$---$\,$and thus precludes strong causal inferences.
@@
 Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use. 
-This would lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
+As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and type-I error inflation for all empirical articles they publish.
+This could lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective. 
+Additional research, ideally with prospective and experimental or quasi-experimental study designs, is needed to further investigate the influence of such factors.
+However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (*`r bfjournals[1]`*, *`r bfjournals[2]`*, and *`r bfjournals[3]`*) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
+In these three journals, $`r n.support.SR.bf`/`r n.SR.bf`$ ($`r printnum(prop.support.SR.bf*100)`\%$; $95 \%$ CI [`r printnum(min(SR.binom.bf$conf.int)*100)`, `r printnum(max(SR.binom.bf$conf.int)*100)`]) standard reports had positive results, compared to only $`r n.support.RR.bf`/`r n.RR.bf`$ ($`r printnum(prop.support.RR.bf*100)`\%$; $95 \%$ CI [`r printnum(min(RR.binom.bf$conf.int)*100)`, `r printnum(max(RR.binom.bf$conf.int)*100)`]) Registered Reports.
 
@@
 The absence of negative results is a serious threat to a cumulative science. 
-In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
+In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" 
+The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left. 
 In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature$\,$---$\,$and may be one solution to achieve a more credible scientific record.

### 2021-02-18 submission2/positive_results_SRs_RRs_revision1.tex
Updated revised manuscript

@@
 A later replication of this study reported \(95.56\%\) statistically significant results in articles from 1986/87 (Sterling, Rosenbaum, \& Weinkam, 1995).
-Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
+Similarly, a seminal study by Fanelli (2010) analysed authors' verbal conclusions in hypothesis-testing papers sampled from the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology claimed support for their first hypothesis\(\,\)---\(\,\)the highest estimate of all disciplines in the study.
 For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
@@
 
-Some have argued that selecting for positive results is defensible\(\,\)---\(\,\)desirable, even\(\,\)---\(\,\)because it weeds out low-quality research that would only pollute the literature (e.g., Cleophas \& Cleophas, 1999).
+Some have argued that negative results are often uninformative or the result of low-quality research and should not be published at the same rate as positive results to avoid cluttering the literature (e.g., Cleophas \& Cleophas, 1999; Baumeister, 2016; Mitchell, 2014).
 If most negative results that are currently missing from the literature are indeed due to immature ideas or poor methods, a literature that selects studies based on \emph{quality} instead of results should contain a similar proportion of positive results as the current one.
@@
 Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature (Maxwell, 2004; Szucs \& Ioannidis, 2017), such a difference would be unlikely to be due to \enquote{failed} studies or false negatives.
-Should the positive result rate in Registered Reports be much lower than in the standard literature, it might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.
+Barring large confounfds, such as substantial differences in the prior probability of hypotheses tested in Registered Reports versus the standard literature, a much lower positive result rate in Registered Reports might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.
 
@@
 
-The sample size of standard reports was pre-specifided to replicate Fanelli's (2010) (\(n = 150\)) since it matched the maximum number of available Registered Reports (\(n = 151\), see below) and piloting indicated that the required coding time would just fit our resource constraints.
+The sample size of standard reports was pre-specified to replicate the one used by Fanelli (2010), \(n = 150\), since it matched the maximum number of Registered Reports available at the time (\(n = 151\), see below) and piloting indicated that the required coding time would just fit our resource constraints.
 Standard reports were selected by searching the 633 journals listed under \enquote{Psychiatry/Psychology} in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} in title, abstract, or keywords.
@@
 In Registered Reports, we coded the first \emph{preregistered} hypothesis, thus excluding unregistered pilot studies.
+The coding procedure was identical for both article formats in all other respects.
 Coding disagreements between \enquote{full} and \enquote{partial} support were deemed minor since they would not affect the final results.
@@
 
-We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 \emph{and} not statistically equivalent to a range from \(-6\%\) to \(+6\%\) (both at \(\alpha = 5\%\)).
+We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 \emph{and} not statistically equivalent to a range from \(-6\%\) to \(+6\%\) (both at \(\alpha = 5\%\))\footnote{Note that these inference criteria are logically equivalent to \enquote{significantly smaller than 0 and not statistically equivalent to a range from \(-6\%\) to \(0\%\)}: Since the first criterion (statistically smaller than 0) requires the \(90\%\) CI to end below 0, half of the equivalence range specified in the second criterion \(\,\)---\(\,\)from \(0\%\) to \(+6\%\,\)---\(\,\) is redundant (which we failed to notice before preregistering the analysis).}.
+Specifying a smallest effect size of interest of \(6\%\) absolute risk reduction provides an initial yardstick to evaluate our results and make our prediction falsifiable.
+However, the value of \(\pm 6\%\) does not possess an intrinsic theoretical meaning.
+As the emerging meta-psychological literature matures, we hope to see future research base the smallest effect size of interest on increasingly well-informed empirical and theoretical considerations.
 
@@
 However, this finding fails to explain the main result described above:
-When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, \(-45.95\%\), was still significantly different from 0 (\(\chi^2(1) = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
+When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, \(-45.95\%\), was still significantly smaller than 0 (\(\chi^2(1) = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
 
@@
 
+Since coders could not be blinded to an article's publication format, their judgment may have been biased.
 Our study was not an experiment\(\,\)---\(\,\)hypotheses, authors, and editors were not randomly assigned to each publication format\(\,\)---\(\,\)and thus precludes strong causal inferences.
@@
 Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use.
-This would lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
+As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and type-I error inflation for all empirical articles they publish.
+This could lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
+Additional research, ideally with prospective and experimental or quasi-experimental study designs, is needed to further investigate the influence of such factors.
+However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (\emph{Attention, Perception, and Psychophysics}, \emph{Cognition and Emotion}, and \emph{Frontiers in Psychology}) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
+In these three journals, \(11/13\) (\(84.62\%\); \(95 \%\) CI {[}54.55, 98.08{]}) standard reports had positive results, compared to only \(7/14\) (\(50.00\%\); \(95 \%\) CI {[}23.04, 76.96{]}) Registered Reports.
 
@@
 The absence of negative results is a serious threat to a cumulative science.
-In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?} The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
+In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?}
+The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
 In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature\(\,\)---\(\,\)and may be one solution to achieve a more credible scientific record.
@@
 \href{https://osf.io/aqr2s/}{Data} and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
-The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
+The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
 
@@
 Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-Baumeister2016}{}%
+Baumeister, R.
+F.
+(2016).
+Charting the future of social psychology on stormy seas: Winners, losers, and recommendations.
+\emph{Journal of Experimental Social Psychology}, \emph{66}, 153--158.
+\url{https://doi.org/10.1016/j.jesp.2016.02.003}
 
@@
 
+\leavevmode\hypertarget{ref-Mitchell2014}{}%
+Mitchell, J. (2014). On the evidentiary emptiness of failed replications.
+
 \leavevmode\hypertarget{ref-Motyl2017}{}%
@@
 
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
 \leavevmode\hypertarget{ref-Wiseman2019}{}%

### 2021-03-10 preprint/positive_results_SRs_RRs.Rmd
Updated preprint to the accepted version of the manuscript (i.e., made a papaja "journal" mode version of positive_results_SRs_RRs_revision1.Rmd, and added a citation disclaimer box on the title page)

@@
 abstract: >
- When studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the evidence for scientific claims.
-Psychological scientists have been concerned about the degree of distortion in their literature due to publication bias and inflated Type-1 error rates.
-Registered Reports were developed with the goal to minimise such biases: In this new publication format, peer review and the decision to publish take place before the study results are known.
-We compared the results in the full population of published Registered Reports in Psychology ($N = 71$ as of November 2018) with a random sample of hypothesis-testing studies from the standard literature ($N = 152$) by searching 633 journals for the phrase ‘test* the hypothes*’ [replicating a method by @Fanelli2010].
-Analysing the first hypothesis reported in each paper, we found $96\%$ positive results in standard reports, but only $44\%$ positive results in Registered Reports.
-The difference remained nearly as large when direct replications were excluded from the analysis ($96\%$ vs $50\%$ positive results).
-This large gap suggests that psychologists under-report negative results to an extent that threatens cumulative science.
-Although our study did not directly test the effectiveness of Registered Reports at reducing bias, these results show that the introduction of Registered Reports has led to a much larger proportion of negative results appearing in the published literature compared to standard reports.
+ \vspace{0.4cm}
+ \begin{tcolorbox}[colback=white,colframe=electricviolet,coltext=electricviolet,
+    fontupper=\normalsize,borderline={0.3mm}{0.3mm}{white}]
+  The present version of this manuscript has been accepted for publication at \textsl{Advances in Methods and Practices in Psychological Science}. Please cite as:
+   \vspace{0.2cm}
+  \begin{center}
+  Scheel, A.
+M., Schijen, M., \& Lakens, D.
+(in press).
+An excess of positive results: Comparing the standard Psychology literature with Registered Reports.
+\textsl{Advances in Methods and Practices in Psychological Science}.
+  \end{center}
+ \end{tcolorbox}
+ \vspace{0.5cm}
+
+ Selectively publishing results that support the tested hypotheses ('positive' results) distorts the available evidence for scientific claims.
+For the past decade, psychological scientists have been increasingly concerned about the degree of such distortion in their literature.
+A new publication format has been developed to prevent selective reporting: In Registered Reports, peer review and the decision to publish take place before results are known.
+We compared the results in published Registered Reports (N = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (N = 152) in Psychology.
+Analysing the first hypothesis of each paper, we found $96\%$ positive results in standard reports, but only $44\%$ positive results in Registered Reports.
+We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered-Reports literature.
 
 keywords          : "Publication bias, Registered Reports, hypothesis testing"
-#wordcount         : "6488"
+#wordcount         : "5870"
 
@@
   - \floatname{textbox}{Box}
+  - \usepackage[most]{tcolorbox}
+  - \definecolor{electricviolet}{rgb}{0.56, 0.0, 1.0}
 
 bibliography      : ["prr.bib","prr_software.bib"]
+# IMPORTANT: To successfully knit this document, prr.bib must be edited manually:
+# All instances of "howpublished" must be changed to "url". This is an issue for
+# three references: Goldacre 2016, Mitchell 2014, and RRR (nd).
 
@@
 But when published findings are systematically biased, cumulative science breaks down: 
-Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
-Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct. 
-For more than half a century, scientists have repeatedly noticed a suspiciously high "success" rate in Psychology:
-Studying 362 empirical articles published in four Psychology journals in 1955/56, @Sterling1959 found that $97.28\%$ of the studies that used significance tests rejected the null hypothesis. 
-A replication of this study performed on articles published in 1986/87 reported $95.56\%$ statistically significant results [@Sterling1995]. 
-Similarly, a seminal study by @Fanelli2010 compared the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
-For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$.
-In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very large.
+Unlike random error, bias does not cancel out when aggregating across studies$\,$---$\,$in the worst case it accumulates, leading us away from the truth rather than towards it.
+Unfortunately, there is reason to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
+
+Since the 1950s, scientists have repeatedly noted a suspiciously high "success" rate in Psychology:
+Studying 362 empirical articles published in four Psychology journals in 1955/56, @Sterling1959 found that $97.28\%$ of studies using significance tests rejected the null hypothesis. 
+A later replication of this study reported $95.56\%$ statistically significant results in articles from 1986/87 [@Sterling1995]. 
+Similarly, a seminal study by @Fanelli2010 analysed authors' verbal conclusions in hypothesis-testing papers sampled from the literatures of 20 disciplines and found that $91.5\%$ of papers published in Psychology claimed support for their first hypothesis$\,$---$\,$the highest estimate of all disciplines in the study.
+For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed $90\%$.
+Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
+These two assumptions appear highly implausible a priori, and available evidence on average statistical power in the literature shows that at least one does not hold [e.g., @Szucs2017].
 
 ## A biased literature
-@Sterling1959 already suspected a selection process behind the numbers he found: 
-"(...) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of [statistical] significance" (p. 31). 
-This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature. 
+A more plausible explanation for these numbers may be a selection bias towards statistically significant results in the published literature.
 We can distinguish two broad categories of bias: "publication bias" and "questionable research practices". 
-Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
-These include editors and reviewers selectively rejecting manuscripts with negative results ["reviewer bias", @Greenwald1975; @Mahoney1977] and researchers deciding not to submit studies with negative results for publication ["file-drawering"; @Rosenthal1979].
-Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is [typically, though not always, leading to an inflated type-I error rate; see @Lakens2019b].
+Publication bias describes publishing behaviours that give manuscripts which find support for their tested hypotheses a higher chance of being published than manuscripts with "negative" results. 
+These include editors and reviewers selectively rejecting manuscripts with negative results ['reviewer bias', @Greenwald1975; @Mahoney1977] and researchers deciding not to submit studies with negative results for publication ['file-drawering'; @Rosenthal1979].
+Questionable research practices (QRPs) describe research behaviours that make evidence in favour of a certain conclusion look stronger than it is [typically, though not always, leading to more false positives; see @Lakens2019b].
 These include presenting unexpected results as having been predicted *a priori* [HARKing, short for "hypothesising after results are known"; @Kerr1998] and exploiting flexibility in data analysis to obtain statistically significant results ["*p*-hacking"; @Simmons2011].
 Evidence for both categories of bias exist: 
-Publication bias has been shown in peer review [@Mahoney1977; @Atkinson1982] and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results [@Franco2014; @Franco2016]; and QRPs have been admitted by scientists in several survey studies [@John2012; @Fiedler2016; @Agnoli2017].
+Publication bias has been observed in peer review [@Mahoney1977; @Atkinson1982] and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results [@Franco2014; @Franco2016]; and QRPs have been admitted by scientists in several survey studies [@John2012; @Fiedler2016; @Agnoli2017; @Fraser2018; @Makel2019].
 
-Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature [@Cleophas1999; see also @deWinter2013; and @vanAssen2014, for a critique].
-How problematic selective publishing is in practice remains an empirical question: 
-If most negative results that are currently missing from the literature are the result of immature ideas or poorly conducted studies, we should expect that a literature in which studies are selected based on their quality but not based on their results  would contain a similar proportion of positive results as the current one.
-But how many positive results would such an unbiased literature contain in reality? 
-We set out to explore this question by comparing the rate of positive results in the current Psychology literature to studies published in a new format designed to minimise QRPs and publication bias: Registered Reports.
+Some have argued that negative results are often uninformative or the result of low-quality research and should not be published at the same rate as positive results to avoid cluttering the literature [e.g., @Cleophas1999; @Mitchell2014; @Baumeister2016].
+If most negative results that are currently missing from the literature are indeed due to immature ideas or poor methods, a literature that selects studies based on *quality* instead of results should contain a similar proportion of positive results as the current one.
+How many positive and negative results would such an unbiased literature contain in reality? 
+We investigated this question by comparing the rate of positive results in the Psychology literature to studies published in a new format designed to minimise publication bias and QRPs: Registered Reports.
 
 ## Methods to mitigate bias
-An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection [for a historical overview, see @Wiseman2019].
-Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of *p*-hacking via restricted flexibility in data analysis.
+An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, methods, and analysis plan before data collection [for a historical overview, see @Wiseman2019].
+Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before results are known) and by reducing the risk of *p*-hacking via restricted flexibility in data analysis.
 However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias [@Rasmussen2009; @Goldacre2016; but see @Kaplan2015]. 
-A more effective safeguard against both publication bias and QRPs is promised by Registered Reports [@Chambers2013; @Nosek2014; @Chambers2015; @Jonas2016]. 
-Registered Reports (RRs) are a new publication format with a restructured submission timeline: 
-Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal.
-The protocol undergoes peer review, and, if successful, receives "in-principle acceptance", meaning that the journal commits to publishing the final article following data collection, regardless of the statistical significance of the results.
+A more effective safeguard against both publication bias and QRPs is promised by Registered Reports [@Chambers2020].
+
+Registered Reports (RRs) are a publication format with a restructured submission timeline: 
+Before collecting data, authors submit a study protocol containing their hypotheses, planned methods, and analysis pipeline, which undergoes peer review.
+If successful, the journal commits to publishing the final article following data collection, regardless of whether the hypotheses are supported ("in-principle acceptance").
 The authors then collect and analyse the data and complete the final report. 
-The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
+The final report is peer-reviewed again, but this time only to ensure that the the registered plan was adhered to and stated conclusions are justified (and, if applicable, that the data pass pre-specified quality checks).
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known. 
-Since its introduction at the journal *Cortex* in 2013, the format has rapidly gained popularity and is offered by 225 journals at the time of writing (http://cos.io/rr).
+Since its introduction in 2013, the format has rapidly gained popularity and is offered by 256 journals at the time of writing (http://cos.io/rr).
 
-In addition to bias protection, Registered Reports promise high-quality research: Stage-1  (pre-data) peer review increases the likelihood that methodological flaws and immature or misguided ideas will be identified and addressed before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
-Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., $90\%$ power for a given effect size of interest^[An overview of the requirements specified by each participating journal is available at https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870]).
-
-Assuming a constant alpha level, the rate of positive results in a literature (i.e., the proportion of supported hypotheses among all tested hypotheses) is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
-The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature [see e.g., @Maxwell2004; @Szucs2017; @SingletonThorn2019].
-Therefore, if the emerging Registered Reports literature in Psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
-At this time, we have good reasons to believe in a difference in bias, but less reason to believe in a difference in the proportion of true hypotheses (at least regarding original work, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate.
-Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also indicate that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about high-quality negative results we are missing because of it.
+In addition to reducing bias, Registered Reports are designed to ensure high standards for research quality. 
+First, pre-data peer review increases the chance that methodological flaws and immature ideas will be identified and addressed before a study is conducted. 
+Second, authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected). 
+And third, many journals offering Registered Reports require that hypothesis tests are planned with high statistical power, reducing the risk of false negatives (e.g., $90\%$ power for a given effect size of interest^[An overview of the requirements specified by each participating journal is available at https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870]).
 
 ## The current study
-The goal of our study was to test if Registered Reports in Psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as "standard reports", SRs), and to estimate the size of this potential difference.
-We set out to replicate a study by @Fanelli2010 on a new sample of standard reports in Psychology and compared them to all published Registered Reports in Psychology. 
-Fanelli searched for articles containing the phrase "test$^\ast$ the hypothes$^\ast$", drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
-For standard reports we used the same sampling method (restricted to the Psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS). 
-We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies. 
-We additionally coded if studies were replications or original work because many published Registered Reports are replications. 
-If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, which could lead to a larger proportion of negative results regardless of bias.
+The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth "standard reports", SRs), and to estimate the size of this potential difference.
+Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature [@Maxwell2004; @Szucs2017], such a difference would be unlikely to be due to "failed" studies or false negatives.
+Barring large confounfds, such as substantial differences in the prior probability of hypotheses tested in Registered Reports versus the standard literature, a much lower positive result rate in Registered Reports might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.
 
-In a recent commentary on benefits and challenges of open-science practices for early-career researchers, @Allen2019 conducted a similar investigation: 
-They coded the proportion of null results in the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018. 
-We were not aware of their parallel efforts when we planned our study in September and October 2018. 
-Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found $60.5\%$ unsupported hypotheses across all included Registered Reports, $66\%$ for replication attempts, and $54.5\%$ for novel research.
-They compared these numbers to an estimate of 5--20$\%$ null results in the standard literature [based on data from @Fanelli2012, who coded only the first hypothesis of each paper; and @Cristea2018, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS].
+We set out to compare all published Registered Reports in Psychology with a new sample of standard reports obtained by replicating @Fanelli2010. 
+Fanelli searched for articles containing the phrase "test$^\ast$ the hypothes$^\ast$", drew a random sample of 150 articles per discipline, and coded if the first hypothesis in each article had been supported or not.
+For standard reports we used the same sampling method (restricted to the Psychology discipline), for Registered Reports we relied on a database curated by the Center for Open Science (COS). 
+We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and because it can easily be applied to a large set of studies. 
+Because we expected many more Registered Reports than standard reports to be close replications of earlier studies$\,$---$\,$and perhaps motivated by scepticism of the original results$\,$---$\,$we additionally examined the role of replications in our analysis.
 
-A major advantage of our study is that it allows us to draw a more meaningful comparison between Registered Reports and the standard literature because we apply a previously used method [@Fanelli2010; @Fanelli2012] to both groups.
+In a recent commentary, @Allen2019 reported a similar investigation: 
+With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found $60.5\%$ unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
+A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature.
 In addition, we replicate @Fanelli2010 and provide data to evaluate his method: The search term "test$^\ast$ the hypothes$^\ast$" might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
-Therefore we also coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
+To this end, we coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
 Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
-This allows others to verify (or contest) our results and may provide an interesting resource for future meta-scientific research.
+This allows others to verify (or contest) our results and can hopefully provide an interesting resource for future meta-scientific research.
 
 # Methods
-After conducting a pilot to test the planned procedure, we preregistered our study (https://osf.io/s8e97). 
+After conducting a pilot to test the planned procedure, we preregistered our study (https://osf.io/sy927/). 
 Methods and analyses described here were preregistered unless otherwise noted. 
-A detailed comparison of our preregistration and the eventual procedure is provided in the supplement. 
-We report how we determined our sample size, all data exclusions, and all measures in the study.
+Our online materials include an Appendix with fine-grained methodological details and an annotated preregistration document with detailed comparisons to the eventual procedure (https://osf.io/dbhgr).
+Appendix and open dataset also list all measures we collected but do not describe here (all of which were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed here).
 
 ## Sample
-We used the same method as @Fanelli2010 to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population. 
-We excluded papers if they were incomplete, unpublished, or retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
+We used the same method as @Fanelli2010 to obtain a new sample of standard reports in Psychology, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
+We excluded papers in both groups if they were incomplete, unpublished, or retracted (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
 An overview of the sampling process and all exclusions is shown in Figure\ \@ref(fig:sampling).
 
-For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase "test$^\ast$ the hypothes$^\ast$" and the ISSNs of all 633 journals listed in the ESI Psychiatry/Psychology category.
-Using the same sample size as @Fanelli2010, we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed "20190120" (seed was not preregistered, but no other seeds were tried).
-We initially excluded eight papers and replaced them (decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had been excluded erroneously, leading to a final sample size of 152 (see Fig.\ \@ref(fig:sampling)).
+The sample size of standard reports was pre-specified to replicate the one used by Fanelli [-@Fanelli2010], $n = 150$, since it matched the maximum number of Registered Reports available at the time ($n = 151$, see below) and piloting indicated that the required coding time would just fit our resource constraints.
+Standard reports were selected by searching the 633 journals listed under "Psychiatry/Psychology" in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase "test$^\ast$ the hypothes$^\ast$" in title, abstract, or keywords.
+We then randomly selected 150 papers from the 1919 papers that resulted from this search.
+Excluded papers were replaced by resampling twice (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.\ \@ref(fig:sampling)).
 
@@
 
-For Registered Reports we aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase "test$^\ast$ the hypothes$^\ast$".
-We downloaded a database of published Registered Reports curated by the Center for Open Science^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than "Psychiatry/Psychology" or "Multidisciplinary" in the ESI.
-Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in *Cortex* because the ESI counts this journal towards the separate category "Neuroscience and Behavior".
-Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., *Royal Society Open Science*) were hand-coded by AS. 
-This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
-
-Following these exclusions, we verified the Registered Reports status of all remaining papers in our sample. 
-Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with https://cos.io/rr).
-For papers not clearly labelled as Registered Reports, we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly. 
-Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because we could not verify that they were Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.\ \@ref(fig:sampling)).
-Note that we excluded all eight "Registered Replication Reports" [RRRs; @Simons2014; @Simons2018] in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing [@RRRwebsite, decision was not preregistered].
+The sample size of Registered Report was determined by our goal to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether they used the phrase "test$^\ast$ the hypothes$^\ast$".
+Registered Reports were selected through a Registered-Reports database curated by the Center for Open Science^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] (retrieved 19th November 2018).
+After excluding non-Psychology papers, we verified that all remaining papers were indeed Registered Reports by consulting the journal submission guidelines, relevant editorials, or contacting the editors directly.
+Papers were counted as Registered Reports if we could establish that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with https://cos.io/rr).
+We excluded 80 of the 151 entries in the COS Registered Reports database, leaving 71 Registered Reports for the final analysis (see Fig.\ \@ref(fig:sampling)). 
+Note that we excluded all eight "Registered Replication Reports" [RRRs; @Simons2014; @Simons2018] in our sample because this format explicitly focuses on effect size estimation and not hypothesis testing [@RRRwebsite, decision was not preregistered].
 
 ## Measures and coding procedure
+
 The main dependent variable was whether the first hypothesis was supported or not, as reported by the authors.
-We tried to follow Fanelli's [-@Fanelli2010] coding procedure as closely as possible, which he describes as follows:
+We tried to follow Fanelli's coding procedure as closely as possible:
 
@@
 
-Based on our experiences during the pilot, we added one coding criterion: 
-If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first *tested* hypothesis rather than the first hypothesis mentioned in the text.
-In Registered Reports we coded the first preregistered hypothesis, thus excluding unregistered pilot studies. 
+In Registered Reports, we coded the first *preregistered* hypothesis, thus excluding unregistered pilot studies.
+The coding procedure was identical for both article formats in all other respects. 
+Coding disagreements between "full" and "partial" support were deemed minor since they would not affect the final results. 
+Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
 MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code ($`r sum(included$coded_by_AS & included$is_RR==1)`$ RRs and $`r sum(included$coded_by_AS & included$is_RR==0)`$ SRs).
 Only `r support.disagreement.major` disagreements were major (Cohen's kappa = `r printp(kappa.support)`) and subsequently resolved by discussion; `r support.disagreement.minor` were minor (disagreement between "support" and "partial support").
-We had preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+Because removing all indicators that could have identified Registered Reports as such from their full texts would have been practically impossible, coding was not blind to publication format (Registered Report vs standard report).
 
 ### Hypothesis introductions
-Selecting papers that use the phrase "test$^\ast$ the hypothes$^\ast$" might yield different results than alternative search phrases. 
-Getting a better overview of "natural" descriptions of hypotheses would be useful for future investigations of the generalisability of Fanelli's [-@Fanelli2010] results and could inspire new research questions.
-We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all Registered Reports and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
+Selecting standard reports based on the phrase "test$^\ast$ the hypothes$^\ast$" might yield different results than alternative search phrases. 
+To get a better overview of "natural" descriptions of hypotheses and facilitate future investigations of the generalisability of Fanelli's [-@Fanelli2010] results, we extracted the phrase used to introduce the coded hypothesis in all Registered Reports and tried to identify clusters of common expressions.
 
 ### Replication status
-We also wanted to code if a study was a replication of a previously published one: 
-We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study. 
-A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias. 
-After an initial coding attempt with ill-defined coding criteria had led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered): 
-We searched the full texts of all papers for the string "replic$^\ast$" [cf.
-@Makel2012; @Kohler2019; @Mueller-Langer2019; @Pridemore2018] and, for papers that did contain it, determined whether the coded hypothesis was a close replication with the goal to verify a previously published result.
+We expected a large proportion of Registered Reports to be replications, many of which may have been motivated by scepticism of the original study. 
+Because this circumstance alone could potentially lead to a lower positive result rate in Registered Reports, we additionally coded if hypotheses were close replications of previously published work.
+Due to ill-specified coding criteria in our preregistration (see Appendix), we used an unregistered coding strategy: 
+We determined whether the coded hypothesis of papers whose full text contained the string "replic$^\ast$" [cf.
+@Makel2012; @Mueller-Langer2019] was a close replication with the goal to verify a previously published result.
 Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
@@
 There were `r rep.disagreements` disagreements (Cohen's kappa = `r printp(kappa.rep)`), all were resolved by discussion.
-
-### Additional measures
-All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above. 
-All of these are documented in the Appendix and in our shared dataset and codebook.
 
@@
 
-We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if we found a negative difference between Registered Reports and standard reports that was significantly different from 0 *and* not statistically equivalent to a range from $-6\%$ to $+6\%$ (both at $\alpha = 5\%$).
+We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 *and* not statistically equivalent to a range from $-6\%$ to $+6\%$ (both at $\alpha = 5\%$)^[Note that these inference criteria are logically equivalent to "significantly smaller than 0 and not statistically equivalent to a range from $-6\%$ to $0\%$": Since the first criterion (statistically smaller than 0) requires the $90\%$ CI to end below 0, half of the equivalence range specified in the second criterion $\,$---$\,$from $0\%$ to $+6\%\,$---$\,$ is redundant (which we failed to notice before preregistering the analysis).].
+Specifying a smallest effect size of interest of $6\%$ absolute risk reduction provides an initial yardstick to evaluate our results and make our prediction falsifiable.
+However, the value of $\pm 6\%$ does not possess an intrinsic theoretical meaning. 
+As the emerging meta-psychological literature matures, we hope to see future research base the smallest effect size of interest on increasingly well-informed empirical and theoretical considerations.
 
@@
 
-## Confirmatory Analyses
+## Preregistered analysis
 
-`r n.support.SR` out of `r n.SR` standard reports and `r n.support.RR` out of `r n.RR` Registered Reports had positive results, meaning that the positive result rate was $`r printnum(prop.support.SR*100)` \%$ for standard reports ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]) and $`r printnum(prop.support.RR*100)` \%$ for Registered Reports ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]; see Fig.\ \@ref(fig:mainplot)).
-The preregistered one-sided proportions test with an alpha level of $5\%$ showed that this difference of $`r printnum((prop.support.SR-prop.support.RR)*100)` \%$ was statistically significant, $\chi^2 = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
-Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$ at $\alpha = 5\%$, $z = `r printnum(min(abs(tostresult$TOST_z1), abs(tostresult$TOST_z2)))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$, meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
+`r n.support.RR` out of `r n.RR` Registered Reports and `r n.support.SR` out of `r n.SR` standard reports had positive results, meaning that the positive result rate was $`r printnum(prop.support.RR*100)` \%$ for Registered Reports ($95 \%$ CI [`r printnum(min(RR.binom$conf.int)*100)`, `r printnum(max(RR.binom$conf.int)*100)`]) and $`r printnum(prop.support.SR*100)` \%$ for standard reports ($95 \%$ CI [`r printnum(min(SR.binom$conf.int)*100)`, `r printnum(max(SR.binom$conf.int)*100)`]; see Fig.\ \@ref(fig:mainplot)).
+This difference of $`r printnum((prop.support.RR-prop.support.SR)*100)` \%$ was statistically significant in the preregistered one-sided proportions test with $\alpha = 5\%$, $\chi^2(`r proptestresult$parameter`) = `r printnum(proptestresult$statistic)`$, $p `r printp(proptestresult$p.value)`$.
+Unsurprisingly, the difference was not statistically equivalent to a range between $`r -SESOI*100` \%$ and $`r SESOI*100` \%$ at $\alpha = 5\%$ ($z = `r printnum(min(abs(tostresult$TOST_z1), abs(tostresult$TOST_z2)))`$, $p `r printp(max(tostresult$TOST_p1, tostresult$TOST_p2))`$), meaning that we cannot reject differences more extreme than $`r SESOI*100`\%$.
 We thus accept our hypothesis that the positive result rate in Registered Reports is lower than in standard reports.
@@
 
-## Exploratory Analyses
-As described in the Method section, we only classified direct replications of previously published work as replications. 
-This means that our non-replication category also contains some conceptual replications and "internal" replications (where original and replication are published in the same paper). 
-For ease of communication we will nonetheless refer to this category as "original" studies.
-As expected, direct replications were much more common among Registered Reports than standard reports: `r n.rep.RR` out of `r n.RR` Registered Reports ($`r printnum(prop.rep.RR*100)`\%$), but only `r n.rep.SR` out of `r n.SR` standard reports ($`r printnum(prop.rep.SR*100)`\%$) were classified as direct replications of previously published work.
-However, this difference cannot account for the stark overall difference between standard reports and Registered Reports described above: 
-Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports, $`r printnum((prop.orig.support.SR-prop.orig.support.RR)*100)`\%$, was still significantly different from 0 ($\chi^2 = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(reptost$TOST_z1), abs(reptost$TOST_z2)))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
+## Exploratory analyses
+For ease of communication we will refer to papers that were classified as close replications of previously published work as "replications" and to all other studies as "original", even though the latter include some conceptual replications and internal replications (as explained above).
+As expected, replications were much more common among Registered Reports ($`r n.rep.RR` / `r n.RR` = `r printnum(prop.rep.RR*100)`\%$) than standard reports ($`r n.rep.SR` / `r n.SR` = `r printnum(prop.rep.SR*100)`\%$), and replication Registered Reports had a descriptively lower positive result rate than original Registered Reports (see Table 1).
+However, this finding fails to explain the main result described above:
+When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, $`r printnum((prop.orig.support.RR-prop.orig.support.SR)*100)`\%$, was still significantly smaller than 0 ($\chi^2(`r origproptest$parameter`) = `r printnum(origproptest$statistic)`$, $p `r printp(origproptest$p.value)`$) and not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(reptost$TOST_z1), abs(reptost$TOST_z2)))`$, $p `r printp(max(reptost$TOST_p1, reptost$TOST_p2))`$), both at $\alpha = 5\%$.
 
@@
 
-Since our standard-reports sample represents a direct replication of @Fanelli2010 for the discipline Psychiatry & Psychology, another interesting question to ask is how our results compare to Fanelli's.
-The difference between the positive result rate for standard reports in our sample ($`r printnum(prop.support.SR*100)`\%$) and Fanelli's ($`r printnum(prop.support.Fanelli*100)`\%$) is $`r printnum((prop.support.SR-prop.support.Fanelli)*100)`\%$.
-This difference is not significantly different from 0 in a two-sided proportions test ($\chi^2 = `r printnum(Fanelliproptest$statistic)`$, $p= `r printp(Fanelliproptest$p.value)`$) but also not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(Fanellitost$TOST_z1), abs(Fanellitost$TOST_z2)))`$, $p= `r printp(max(Fanellitost$TOST_p1, Fanellitost$TOST_p2))`$), both at $\alpha = 5\%$.
-In other words, we can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least $\pm `r SESOI*100`\%$ between them. 
-The data are inconclusive.
+Since our standard-reports sample represents a direct replication of @Fanelli2010 for the discipline Psychiatry & Psychology, another interesting question is how our results compare to Fanelli's.
+The difference between the positive result rates of standard reports in our sample and Fanelli's ($`r printnum(prop.support.SR*100)`\% - `r printnum(prop.support.Fanelli*100)`\% = `r printnum((prop.support.SR-prop.support.Fanelli)*100)`\%$) is not significantly different from 0 in a two-sided proportions test ($\chi^2(`r Fanelliproptest$parameter`) = `r printnum(Fanelliproptest$statistic)`$, $p= `r printp(Fanelliproptest$p.value)`$) but also not statistically equivalent to a range between $`r -SESOI*100`\%$ and $`r SESOI*100`\%$ ($z = `r printnum(min(abs(Fanellitost$TOST_z1), abs(Fanellitost$TOST_z2)))`$, $p= `r printp(max(Fanellitost$TOST_p1, Fanellitost$TOST_p2))`$), both at $\alpha = 5\%$.
+The data are inconclusive: 
+We can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least $\pm `r SESOI*100`\%$ between them.
 
@@
 In this total set of `r nrow(intros.long)` hypothesis introductions, we found `r length(uniquephrases)` unique phrases showing substantial linguistic variation (see Tables 2 and 3).
-To condense the information, we listed all unique word stems (e.g., the word stem "hypothes$^\ast$" captures the words "hypothesis", "hypotheses", "hypothesize", "hypothesized", and so on) and analysed their frequency among all hypothesis introductions.
-Excluding words that are common but too unspecific by themselves, such as "that", "to", or "whether", the five most frequent word stems were "hypothes$^\ast$" (`r wordoccurrences.df[1,2]` occurrences), "replicat$^\ast$" (`r wordoccurrences.df[2,2]`), "test$^\ast$" (`r wordoccurrences.df[3,2]`), "examine$^\ast$" (`r wordoccurrences.df[4,2]`), and "predict$^\ast$" (`r wordoccurrences.df[5,2]`).
-Clearly, "test$^\ast$" and "hypothes$^\ast$" are quite popular, yet they co-occurred only `r test.and.hypothes` times and more than half of all hypothesis introductions (`r nrow(intros.long)-test.or.hypothes`/`r nrow(intros.long)`) contained neither word.
-Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 ($`r printnum(30/43*100)`\%$) hypothesis introductions in original Registered Reports contained either "test$^\ast$" or "hypothes$^\ast$" or both, but the same was true for only 16 out of 54 ($`r printnum(16/54*100)`\%$) hypothesis introductions in direct replication Registered Reports.
+We then listed all unique word stems within those phrases and analysed their frequency.
+Excluding words that are common but too unspecific by themselves (e.g., "that", "to", "whether"), the five most frequent word stems were "hypothes$^\ast$" (`r wordoccurrences.df[1,2]` occurrences), "replicat$^\ast$" (`r wordoccurrences.df[2,2]`), "test$^\ast$" (`r wordoccurrences.df[3,2]`), "examine$^\ast$" (`r wordoccurrences.df[4,2]`), and "predict$^\ast$" (`r wordoccurrences.df[5,2]`).
+Clearly, "test$^\ast$" and "hypothes$^\ast$" are quite popular, yet they co-occurred only `r test.and.hypothes` times, and more than half of all hypothesis introductions (`r nrow(intros.long)-test.or.hypothes`/`r nrow(intros.long)`) contained neither word.
 
-We noticed that direct replication Registered Reports generally tended to use different language to describe their hypothesis.
-As the high frequency of the word stem "replicat$^\ast$" suggests, these studies were often not framed as *tests* of a previously tested hypothesis, but as attempts to repeat a previously conducted procedure.
-Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
+`r n.hypintros.fivewords.RR` of the `r n.RR` Registered Reports ($`r printnum(n.hypintros.fivewords.RR/n.RR*100)` \%$) had at least one of these five most frequent word stems in their title, abstract, or keywords, meaning that a regular literature search (without access to full texts) with the search terms "hypothes$^\ast$ *OR* replicat$^\ast$ *OR* test$^\ast$ *OR* examine$^\ast$ *OR* predict$^\ast$" would have been effective in identifying these papers.
+We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question could be useful for future meta-research.
 
-Tables 2 and 3 list all unique hypothesis introductions and their frequency in original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems ("hypothes$^\ast$", "replicat$^\ast$", "test$^\ast$", "examine$^\ast$", "predict$^\ast$").
-Using five as a cut-off value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.
+Lastly, we noticed an interesting difference in language use between original and replication Registered Reports: 
+As the high frequency of the word stem "replicat$^\ast$" suggests, replications were often framed as attempts to repeat a previously conducted *procedure* rather than as attempts to test a previously tested *hypothesis*.
+Tables 2 and 3 list all unique hypothesis introductions and their frequency in original Registered Reports and replication Registered Reports, respectively, grouped by the five most frequent word stems ("hypothes$^\ast$", "replicat$^\ast$", "test$^\ast$", "examine$^\ast$", "predict$^\ast$").
 
@@
 To explain the $`r printnum((prop.support.SR - prop.support.RR)*100)` \%$ gap between standard reports and Registered Reports, we must assume some combination of differences in bias, statistical power, or the proportion of true hypotheses researchers choose to examine.
-Figure\ \@ref(fig:powerbaserate) visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
-For example, assuming no publication bias and no QRPs, even if *all* hypotheses authors of standard reports tested were true, their study designs would need to have more than $90\%$ power for the true effect size.
-This is highly unlikely, meaning that the standard literature is unlikely to reflect reality. 
-As we noted above, there is good reason to assume that methodological rigour and statistical power in Registered Reports are as high as in standard reports or higher, leaving the rate of true hypotheses and bias as remaining explanations.
+Figure\ \@ref(fig:powerbaserate) visualises the combinations of statistical power and proportion of true hypotheses that could produce the observed positive result rates if the literature were completely unbiased.
+Assuming no publication bias and no QRPs, authors of standard reports would need to test almost exclusively true hypotheses ($>90\%$) with more than $90\%$ power.
+Because this is highly implausible and contradicted by available evidence [e.g., @Szucs2017], the standard literature is unlikely to reflect reality. 
+As noted above, methodological rigour and statistical power in Registered Reports likely meet or exceed the level of standard reports, leaving the rate of true hypotheses and bias as remaining explanations.
 
@@
 
-# Important altrnative chunk options when using journal mode: 
+# Important alternative chunk options when using journal mode: 
 # 1. use out.width="0.6\\textwidth" (it's 0.8 in manuscript mode)
@@
 However, assuming over $90\%$ true hypotheses in the standard literature is neither realistic, nor would it be desirable for a science that wants to advance knowledge beyond trivial facts. 
-We thus believe that this factor alone is not sufficient to explain the gap between the positive result rates in Registered Reports and standard reports. 
-Rather, the numbers strongly suggest a reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
+We thus believe that this factor alone is not sufficient to explain the large difference in positive results.
+Rather, the numbers strongly suggest a reduction of publication bias and/or QRPs in the Registered-Reports literature.
+Nonetheless, the prior probability of hypotheses in Registered Reports and standard reports may differ and should be studied in future research.
 
 ## Limitations
-We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports. 
-Because hypotheses, authors, and editors were not randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
-Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
-As mentioned above, it is *a-priori* plausible that the Registered Reports format is used selectively for particularly risky hypotheses. 
-This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in Psychology. 
-It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias. 
-Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use. 
-This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
+Since coders could not be blinded to an article's publication format, their judgment may have been biased.
+Our study was not an experiment$\,$---$\,$hypotheses, authors, and editors were not randomly assigned to each publication format$\,$---$\,$and thus precludes strong causal inferences.
+As discussed above, it seems highly plausible that Registered Reports reduce publication bias and QRPs, which in turn reduces the positive result rate. 
+Yet we neither know exactly how effective Registered Reports are at reducing bias, nor how large the effect on positive results would be in the absence of potential confounds. 
+One such confound, as just discussed, could be that Registered Reports may be used for particularly risky hypotheses.
+Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use. 
+As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and type-I error inflation for all empirical articles they publish.
+This could lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective. 
+Additional research, ideally with prospective and experimental or quasi-experimental study designs, is needed to further investigate the influence of such factors.
+However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (*`r bfjournals[1]`*, *`r bfjournals[2]`*, and *`r bfjournals[3]`*) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
+In these three journals, $`r n.support.SR.bf`/`r n.SR.bf`$ ($`r printnum(prop.support.SR.bf*100)`\%$; $95 \%$ CI [`r printnum(min(SR.binom.bf$conf.int)*100)`, `r printnum(max(SR.binom.bf$conf.int)*100)`]) standard reports had positive results, compared to only $`r n.support.RR.bf`/`r n.RR.bf`$ ($`r printnum(prop.support.RR.bf*100)`\%$; $95 \%$ CI [`r printnum(min(RR.binom.bf$conf.int)*100)`, `r printnum(max(RR.binom.bf$conf.int)*100)`]) Registered Reports.
 
-A second limitation of the current study [and of @Fanelli2010] is that standard reports were selected using the search term "test$^\ast$ the hypothes$^\ast$". 
-As our results show, this phrase was virtually absent in the Registered Report population. 
-The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for "test$^\ast$ the hypothes$^\ast$" might miss most of the hypothesis-testing studies in the psychological literature, and results obtained this way may not generalise to all published studies.
-For example, it is possible that authors are more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., "we examined the role of ...").
-If this were true, using other strategies to select standard reports might yield lower estimates for the positive result rate. 
-However, this does not seem to be the case: 
-Studies using different selection criteria for articles and hypotheses have found very similar rates of supported hypotheses. 
-For example, the positive result rates in @Sterling1959, @Sterling1995, and the original studies included in the Reproducibility Project: Psychology [@OSC2015] were $97.28\%$, $95.56\%$, and $97\%$, respectively.
-@Motyl2017 report $89.17\%$ and $92.01\%$ significant results for "critical" hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively. 
-Therefore, although the search term used to find standard reports might limit the generalisability of our results, it seems to yield comparable estimates as the selection strategies used in different studies.
+Another limitation of the current study [and of @Fanelli2010] is that standard reports were selected using the search phrase "test$^\ast$ the hypothes$^\ast$".
+This phrase was virtually absent in  Registered Reports, suggesting that the search strategy may not yield a representative sample of the population of hypothesis-testing studies in the literature.
+The use of the phrase might even be confounded with the outcome of a study:
+For example, authors may be more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., "we examined the role of ...").
+A similar concern could be raised for the decision to code only the first reported hypothesis of each article.
+The first hypothesis test may not be representative for all hypothesis tests reported in a paper, and the order of reporting may differ between standard reports and Registered Reports. 
+For example, standard-report authors might tend to present supported hypotheses first, whereas Registered-Report authors might be more likely to present their hypotheses in "chronological" order.
 
-A final limitation is the decision to code only the first reported hypothesis. 
-The first hypothesis test may not be representative for all hypothesis tests reported in a paper, and the order of reporting may differ between standard reports and Registered Reports. 
-Perhaps Registered-Report authors are more likely to present their hypotheses in "chronological" order, whereas standard-report authors tend to rearrange the order in which hypotheses are reported based on their outcomes, and present supported hypotheses first.
-Here again, the converging estimates from the four studies cited above (none of which use the first-hypothesis rule) make it seem unlikely that our result is an artefact of this decision. 
-Regardless of which hypothesis one chooses to analyse across a set of papers -- the first, the last, or the "critical" one -- the positive result rate turns out to be higher than what can be expected based on realistic estimates of the proportion of true hypotheses researchers study and the statistical power of their tests.
+Both of these potential confounds might lead to an inflated estimate of the positive result rate in standard reports.
+However, studies using different selection criteria for articles and hypotheses have found very similar rates of supported hypotheses in the literature: 
+$97.28\%$ in @Sterling1959, $95.56\%$ in @Sterling1995, and $97\%$ in the original studies included in the Reproducibility Project: Psychology [@OSC2015].
+In addition, @Motyl2017 report $89.17\%$ and $92.01\%$ significant results for "critical" hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively. 
+Although the selection criteria for articles and hypotheses in our study may limit the generalisability of the results, this level of convergence makes it seem unlikely that alternative methods would have yielded dramatically different conclusions.
 
@@
 The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the existing body of published research. 
-Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered Reports literature.
+Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered-Reports literature. 
 The absence of negative results is a serious threat to a cumulative science. 
-In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
-In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature---and may be one solution to achieve a more credible scientific record.
+In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" 
+The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left. 
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature$\,$---$\,$and may be one solution to achieve a more credible scientific record.
 

### 2021-03-10 preprint/positive_results_SRs_RRs.tex
Updated preprint to the accepted version of the manuscript (i.e., made a papaja "journal" mode version of positive_results_SRs_RRs_revision1.Rmd, and added a citation disclaimer box on the title page)

@@
 \floatname{textbox}{Box}
+\usepackage[most]{tcolorbox}
+\definecolor{electricviolet}{rgb}{0.56, 0.0, 1.0}
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
 \abstract{
-When studies with positive results that support the tested hypotheses have a higher probability of being published than studies with negative results, the literature will give a distorted view of the evidence for scientific claims.
-Psychological scientists have been concerned about the degree of distortion in their literature due to publication bias and inflated Type-1 error rates.
-Registered Reports were developed with the goal to minimise such biases: In this new publication format, peer review and the decision to publish take place before the study results are known.
-We compared the results in the full population of published Registered Reports in Psychology (\(N = 71\) as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (\(N = 152\)) by searching 633 journals for the phrase `test* the hypothes*' (replicating a method by Fanelli, 2010).
-Analysing the first hypothesis reported in each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports.
-The difference remained nearly as large when direct replications were excluded from the analysis (\(96\%\) vs \(50\%\) positive results).
-This large gap suggests that psychologists under-report negative results to an extent that threatens cumulative science.
-Although our study did not directly test the effectiveness of Registered Reports at reducing bias, these results show that the introduction of Registered Reports has led to a much larger proportion of negative results appearing in the published literature compared to standard reports.
+\vspace{0.4cm} \begin{tcolorbox}[colback=white,colframe=electricviolet,coltext=electricviolet,
+   fontupper=\normalsize,borderline={0.3mm}{0.3mm}{white}]
+ The present version of this manuscript has been accepted for publication at \textsl{Advances in Methods and Practices in Psychological Science}. Please cite as:
+  \vspace{0.2cm}
+ \begin{center}
+ Scheel, A.
+M., Schijen, M., \& Lakens, D.
+(in press).
+An excess of positive results: Comparing the standard Psychology literature with Registered Reports.
+\textsl{Advances in Methods and Practices in Psychological Science}.
+ \end{center}
+\end{tcolorbox} \vspace{0.5cm}
+
+Selectively publishing results that support the tested hypotheses (`positive' results) distorts the available evidence for scientific claims.
+For the past decade, psychological scientists have been increasingly concerned about the degree of such distortion in their literature.
+A new publication format has been developed to prevent selective reporting: In Registered Reports, peer review and the decision to publish take place before results are known.
+We compared the results in published Registered Reports (N = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (N = 152) in Psychology.
+Analysing the first hypothesis of each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports.
+We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered-Reports literature.
 }
@@
 But when published findings are systematically biased, cumulative science breaks down:
-Unlike random error, bias does not cancel out when aggregating across studies -- in the worst case it accumulates, leading us away from the truth rather than towards it.
-Unfortunately there are good reasons to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
-For more than half a century, scientists have repeatedly noticed a suspiciously high \enquote{success} rate in Psychology:
-Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of the studies that used significance tests rejected the null hypothesis.
-A replication of this study performed on articles published in 1986/87 reported \(95.56\%\) statistically significant results (Sterling, Rosenbaum, \& Weinkam, 1995).
-Similarly, a seminal study by Fanelli (2010) compared the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology reported support for their first hypothesis, the highest estimate of all disciplines in the study.
-For these percentages to be a realistic representation of the research that psychologists perform, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
-In other words: nearly all predictions researchers make must be correct, and either the studied effect sizes or the used sample sizes (given the same study design) must consistently be very large.
+Unlike random error, bias does not cancel out when aggregating across studies\(\,\)---\(\,\)in the worst case it accumulates, leading us away from the truth rather than towards it.
+Unfortunately, there is reason to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
+
+Since the 1950s, scientists have repeatedly noted a suspiciously high \enquote{success} rate in Psychology:
+Studying 362 empirical articles published in four Psychology journals in 1955/56, Sterling (1959) found that \(97.28\%\) of studies using significance tests rejected the null hypothesis.
+A later replication of this study reported \(95.56\%\) statistically significant results in articles from 1986/87 (Sterling, Rosenbaum, \& Weinkam, 1995).
+Similarly, a seminal study by Fanelli (2010) analysed authors' verbal conclusions in hypothesis-testing papers sampled from the literatures of 20 disciplines and found that \(91.5\%\) of papers published in Psychology claimed support for their first hypothesis\(\,\)---\(\,\)the highest estimate of all disciplines in the study.
+For these percentages to be a realistic representation of the research psychologists conduct, both statistical power and the proportion of true hypotheses (i.e., the prior probability that the null hypothesis is false) that are tested must exceed \(90\%\).
+Put differently, nearly all predictions researchers make must be correct, and either the studied effects or the used samples (given the same design) must consistently be very large.
+These two assumptions appear highly implausible a priori, and available evidence on average statistical power in the literature shows that at least one does not hold (e.g., Szucs \& Ioannidis, 2017).
 
@@
 
-Sterling (1959) already suspected a selection process behind the numbers he found:
-\enquote{(\ldots{}) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of {[}statistical{]} significance} (p.~31).
-This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature.
+A more plausible explanation for these numbers may be a selection bias towards statistically significant results in the published literature.
 We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
-Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
+Publication bias describes publishing behaviours that give manuscripts which find support for their tested hypotheses a higher chance of being published than manuscripts with \enquote{negative} results.
 These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Greenwald, 1975; Mahoney, 1977) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
-Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate; see Lakens, 2019).
+Questionable research practices (QRPs) describe research behaviours that make evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to more false positives; see Lakens, 2019).
 These include presenting unexpected results as having been predicted \emph{a priori} (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
 Evidence for both categories of bias exist:
-Publication bias has been shown in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; John, Loewenstein, \& Prelec, 2012).
-
-Some have argued that selecting for statistically significant results is defensible -- desirable, even -- because it weeds out low-quality research that would only pollute the literature (Cleophas \& Cleophas, 1999; see also de Winter \& Happee, 2013; and van Assen, van Aert, Nuijten, \& Wicherts, 2014, for a critique).
-How problematic selective publishing is in practice remains an empirical question:
-If most negative results that are currently missing from the literature are the result of immature ideas or poorly conducted studies, we should expect that a literature in which studies are selected based on their quality but not based on their results would contain a similar proportion of positive results as the current one.
-But how many positive results would such an unbiased literature contain in reality?
-We set out to explore this question by comparing the rate of positive results in the current Psychology literature to studies published in a new format designed to minimise QRPs and publication bias: Registered Reports.
+Publication bias has been observed in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; Fraser, Parker, Nakagawa, Barnett, \& Fidler, 2018; John, Loewenstein, \& Prelec, 2012; Makel, Hodges, Cook, \& Plucker, 2019).
+
+Some have argued that negative results are often uninformative or the result of low-quality research and should not be published at the same rate as positive results to avoid cluttering the literature (e.g., Cleophas \& Cleophas, 1999; Baumeister, 2016; Mitchell, 2014).
+If most negative results that are currently missing from the literature are indeed due to immature ideas or poor methods, a literature that selects studies based on \emph{quality} instead of results should contain a similar proportion of positive results as the current one.
+How many positive and negative results would such an unbiased literature contain in reality?
+We investigated this question by comparing the rate of positive results in the Psychology literature to studies published in a new format designed to minimise publication bias and QRPs: Registered Reports.
 
@@
 
-An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
-Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of \emph{p}-hacking via restricted flexibility in data analysis.
+An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, methods, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
+Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before results are known) and by reducing the risk of \emph{p}-hacking via restricted flexibility in data analysis.
 However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias (Goldacre et al., 2016; Rasmussen, Lee, \& Bero, 2009; but see Kaplan \& Irvin, 2015).
-A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers, 2013; Chambers, Dienes, McIntosh, Rotshtein, \& Willmes, 2015; Jonas \& Cesario, 2016; Nosek \& Lakens, 2014).
-Registered Reports (RRs) are a new publication format with a restructured submission timeline:
-Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal.
-The protocol undergoes peer review, and, if successful, receives \enquote{in-principle acceptance}, meaning that the journal commits to publishing the final article following data collection, regardless of the statistical significance of the results.
+A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers \& Tzavella, 2020).
+
+Registered Reports (RRs) are a publication format with a restructured submission timeline:
+Before collecting data, authors submit a study protocol containing their hypotheses, planned methods, and analysis pipeline, which undergoes peer review.
+If successful, the journal commits to publishing the final article following data collection, regardless of whether the hypotheses are supported (\enquote{in-principle acceptance}).
 The authors then collect and analyse the data and complete the final report.
-The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
+The final report is peer-reviewed again, but this time only to ensure that the the registered plan was adhered to and stated conclusions are justified (and, if applicable, that the data pass pre-specified quality checks).
 Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
-Since its introduction at the journal \emph{Cortex} in 2013, the format has rapidly gained popularity and is offered by 225 journals at the time of writing (\url{http://cos.io/rr}).
-
-In addition to bias protection, Registered Reports promise high-quality research: Stage-1 (pre-data) peer review increases the likelihood that methodological flaws and immature or misguided ideas will be identified and addressed before a study is conducted, and authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
-Many journals offering Registered Reports also require that planned hypothesis tests are based on a power analysis that ensures a high probability of finding a statistically significant result if there is a true effect of the expected size (e.g., \(90\%\) power for a given effect size of interest\footnote{An overview of the requirements specified by each participating journal is available at \url{https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870}}).
-
-Assuming a constant alpha level, the rate of positive results in a literature (i.e., the proportion of supported hypotheses among all tested hypotheses) is influenced by three factors: the proportion of true hypotheses among all tested hypotheses, statistical power, and bias.
-The Registered Reports format combines powerful safeguards against publication bias and QRPs with standards for research quality that are at least equal to ordinary peer review, and often include statistical power requirements that likely exceed those in the standard literature (see e.g., Maxwell, 2004; Singleton Thorn, Dudgeon, \& Fidler, 2019; Szucs \& Ioannidis, 2017).
-Therefore, if the emerging Registered Reports literature in Psychology contains fewer positive results than the standard literature, the cause must be either the difference in bias or a lower proportion of true hypotheses tested in Registered Reports (or a combination of the two).
-At this time, we have good reasons to believe in a difference in bias, but less reason to believe in a difference in the proportion of true hypotheses (at least regarding original work, see below), which would make bias a more plausible explanation of a potential difference in the positive result rate.
-Considering the high standards for research quality in Registered Reports, a large difference in positive results between Registered Reports and the standard literature would also indicate that publication bias is not a desirable filter for poorly conducted studies, but that we should worry about high-quality negative results we are missing because of it.
+Since its introduction in 2013, the format has rapidly gained popularity and is offered by 256 journals at the time of writing (\url{http://cos.io/rr}).
+
+In addition to reducing bias, Registered Reports are designed to ensure high standards for research quality.
+First, pre-data peer review increases the chance that methodological flaws and immature ideas will be identified and addressed before a study is conducted.
+Second, authors typically have to include outcome-neutral control conditions that allow verifying data quality once results are in (studies failing these quality checks may be rejected).
+And third, many journals offering Registered Reports require that hypothesis tests are planned with high statistical power, reducing the risk of false negatives (e.g., \(90\%\) power for a given effect size of interest\footnote{An overview of the requirements specified by each participating journal is available at \url{https://docs.google.com/spreadsheets/d/1D4_k-8C_UENTRtbPzXfhjEyu3BfLxdOsn9j-otrO870}}).
 
@@
 
-The goal of our study was to test if Registered Reports in Psychology show a lower positive result rate than articles published in the traditional way (henceforth referred to as \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
-We set out to replicate a study by Fanelli (2010) on a new sample of standard reports in Psychology and compared them to all published Registered Reports in Psychology.
-Fanelli searched for articles containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}, drew a random sample of 150 articles per discipline, and for each of these coded if the first hypothesis mentioned in the abstract or full text had been supported or not.
-For standard reports we used the same sampling method (restricted to the Psychology discipline), and for Registered Reports we relied on a database curated by the Center for Open Science (COS).
-We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and his method can easily be applied to a large set of studies.
-We additionally coded if studies were replications or original work because many published Registered Reports are replications.
-If replications are motivated by scepticism of the original results, the prior probability of hypotheses tested in these studies may be lower than in original studies, which could lead to a larger proportion of negative results regardless of bias.
-
-In a recent commentary on benefits and challenges of open-science practices for early-career researchers, Allen and Mehler (2019) conducted a similar investigation:
-They coded the proportion of null results in the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018.
-We were not aware of their parallel efforts when we planned our study in September and October 2018.
-Allen and Mehler used a self-developed method to code the percentage of unsupported hypotheses in Registered Reports (counting all hypotheses in each paper) and found \(60.5\%\) unsupported hypotheses across all included Registered Reports, \(66\%\) for replication attempts, and \(54.5\%\) for novel research.
-They compared these numbers to an estimate of 5--20\(\%\) null results in the standard literature (based on data from Fanelli, 2012, who coded only the first hypothesis of each paper; and Cristea \& Ioannidis, 2018, who coded the percentage of statistically significant results in figures and tables of articles published in Nature, Science, and PNAS).
-
-A major advantage of our study is that it allows us to draw a more meaningful comparison between Registered Reports and the standard literature because we apply a previously used method (Fanelli, 2010, 2012) to both groups.
+The goal of our study was to test if Registered Reports in Psychology have a lower positive result rate than articles published in the traditional way (henceforth \enquote{standard reports}, SRs), and to estimate the size of this potential difference.
+Because the standards for research quality in Registered Reports are at least equal to ordinary peer review, and the statistical power requirements may exceed those in the standard literature (Maxwell, 2004; Szucs \& Ioannidis, 2017), such a difference would be unlikely to be due to \enquote{failed} studies or false negatives.
+Barring large confounfds, such as substantial differences in the prior probability of hypotheses tested in Registered Reports versus the standard literature, a much lower positive result rate in Registered Reports might then indicate that publication bias is not a desirable filter for poorly conducted studies, and that we ought to worry about high-quality negative results we are missing because of it.
+
+We set out to compare all published Registered Reports in Psychology with a new sample of standard reports obtained by replicating Fanelli (2010).
+Fanelli searched for articles containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}, drew a random sample of 150 articles per discipline, and coded if the first hypothesis in each article had been supported or not.
+For standard reports we used the same sampling method (restricted to the Psychology discipline), for Registered Reports we relied on a database curated by the Center for Open Science (COS).
+We chose this method because Fanelli's 2010 and 2012 studies (both use the same coding method) have been highly influential, and because it can easily be applied to a large set of studies.
+Because we expected many more Registered Reports than standard reports to be close replications of earlier studies\(\,\)---\(\,\)and perhaps motivated by scepticism of the original results\(\,\)---\(\,\)we additionally examined the role of replications in our analysis.
+
+In a recent commentary, Allen and Mehler (2019) reported a similar investigation:
+With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found \(60.5\%\) unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
+A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature.
 In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
-Therefore we also coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
+To this end, we coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
 Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
-This allows others to verify (or contest) our results and may provide an interesting resource for future meta-scientific research.
+This allows others to verify (or contest) our results and can hopefully provide an interesting resource for future meta-scientific research.
 
@@
 
-After conducting a pilot to test the planned procedure, we preregistered our study (\url{https://osf.io/s8e97}).
+After conducting a pilot to test the planned procedure, we preregistered our study (\url{https://osf.io/sy927/}).
 Methods and analyses described here were preregistered unless otherwise noted.
-A detailed comparison of our preregistration and the eventual procedure is provided in the supplement.
-We report how we determined our sample size, all data exclusions, and all measures in the study.
+Our online materials include an Appendix with fine-grained methodological details and an annotated preregistration document with detailed comparisons to the eventual procedure (\url{https://osf.io/dbhgr}).
+Appendix and open dataset also list all measures we collected but do not describe here (all of which were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed here).
 
@@
 
-We used the same method as Fanelli (2010) to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
-We excluded papers if they were incomplete, unpublished, or retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
+We used the same method as Fanelli (2010) to obtain a new sample of standard reports in Psychology, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
+We excluded papers in both groups if they were incomplete, unpublished, or retracted (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
 An overview of the sampling process and all exclusions is shown in Figure~\ref{fig:sampling}.
 
-For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} and the ISSNs of all 633 journals listed in the ESI Psychiatry/Psychology category.
-Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed \enquote{20190120} (seed was not preregistered, but no other seeds were tried).
-We initially excluded eight papers and replaced them (decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had been excluded erroneously, leading to a final sample size of 152 (see Fig.~\ref{fig:sampling}).
+The sample size of standard reports was pre-specified to replicate the one used by Fanelli (2010), \(n = 150\), since it matched the maximum number of Registered Reports available at the time (\(n = 151\), see below) and piloting indicated that the required coding time would just fit our resource constraints.
+Standard reports were selected by searching the 633 journals listed under \enquote{Psychiatry/Psychology} in the Essential Science Indicators database for papers published between 2013 and 2018 that contained the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} in title, abstract, or keywords.
+We then randomly selected 150 papers from the 1919 papers that resulted from this search.
+Excluded papers were replaced by resampling twice (this decision was not preregistered), which led to accidental oversampling and a final sample size of 152 (see Fig.~\ref{fig:sampling}).
 
@@
 
-For Registered Reports we aimed to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
-We downloaded a database of published Registered Reports curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
-Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 Registered Reports published in \emph{Cortex} because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
-Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., \emph{Royal Society Open Science}) were hand-coded by AS.
-This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
-
-Following these exclusions, we verified the Registered Reports status of all remaining papers in our sample.
-Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
-For papers not clearly labelled as Registered Reports, we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
-Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because we could not verify that they were Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
-Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).
+The sample size of Registered Report was determined by our goal to include all published Registered Reports in the field of Psychology that tested at least one hypothesis, regardless of whether they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
+Registered Reports were selected through a Registered-Reports database curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved 19th November 2018).
+After excluding non-Psychology papers, we verified that all remaining papers were indeed Registered Reports by consulting the journal submission guidelines, relevant editorials, or contacting the editors directly.
+Papers were counted as Registered Reports if we could establish that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
+We excluded 80 of the 151 entries in the COS Registered Reports database, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
+Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focuses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).
 
@@
 If more than one hypothesis was being tested, only the first one to appear in the text was considered.
-We excluded meeting abstracts and papers that either did not test a hypothesis or for which we lacked sufficient information to determine the outcome. (p.~8)
+We excluded meeting abstracts and papers that either did not test a hypothesis or for which we lacked sufficient information to determine the outcome. (Fanelli, 2010, p. 8)
 \end{quote}
 
-Like Fanelli (2010), we coded hypotheses as having received \enquote{support}, \enquote{partial support}, or \enquote{no support}, which was recoded into a binary \enquote{support} (full or partial) vs \enquote{no support} variable for the analysis.
-Coding disagreements between full and partial support were deemed minor since they would not affect the final results.
-Thus, only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.
-
-Before preregistering our study, we conducted a pilot to assess if we could employ Fanelli's method successfully.
-Originally we had planned to first reproduce his results on the same sample of Psychiatry/Psychology articles used in Fanelli (2010).
-Unfortunately the author refused to share the original data (or even a list of the coded articles) with us.
-Instead, we received an excerpt which contained data for 11 records from the original sample, but no reference information of the coded articles (personal communication, 5th October 2018).
-We were able to find these 11 articles based on the hypothesis quotes that had been coded, and used them as a pilot sample along with 10 randomly selected Registered Reports.
-MS and AS independently coded all 21 pilot articles with only one major disagreement in each group.
-In the standard reports group, this disagreement was also the only case of major disagreement with Fanelli's original coding, which we deemed satisfying to proceed.
-
-Based on our experiences during the pilot, we added one coding criterion:
-If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first \emph{tested} hypothesis rather than the first hypothesis mentioned in the text.
-In Registered Reports we coded the first preregistered hypothesis, thus excluding unregistered pilot studies.
+In Registered Reports, we coded the first \emph{preregistered} hypothesis, thus excluding unregistered pilot studies.
+The coding procedure was identical for both article formats in all other respects.
+Coding disagreements between \enquote{full} and \enquote{partial} support were deemed minor since they would not affect the final results.
+Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
 MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
 Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
-We had preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+Because removing all indicators that could have identified Registered Reports as such from their full texts would have been practically impossible, coding was not blind to publication format (Registered Report vs standard report).
 
@@
 There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.
-
-\hypertarget{additional-measures}{%
-\subsubsection{Additional measures}\label{additional-measures}}
-
-All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above.
-All of these are documented in the Appendix and in our shared dataset and codebook.
 
@@
 
-We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if we found a negative difference between Registered Reports and standard reports that was significantly different from 0 \emph{and} not statistically equivalent to a range from \(-6\%\) to \(+6\%\) (both at \(\alpha = 5\%\)).
+We would accept our hypothesis that Registered Reports have a lower positive result rate than standard reports if the observed difference between Registered Reports and standard reports was significantly smaller than 0 \emph{and} not statistically equivalent to a range from \(-6\%\) to \(+6\%\) (both at \(\alpha = 5\%\))\footnote{Note that these inference criteria are logically equivalent to \enquote{significantly smaller than 0 and not statistically equivalent to a range from \(-6\%\) to \(0\%\)}: Since the first criterion (statistically smaller than 0) requires the \(90\%\) CI to end below 0, half of the equivalence range specified in the second criterion \(\,\)---\(\,\)from \(0\%\) to \(+6\%\,\)---\(\,\) is redundant (which we failed to notice before preregistering the analysis).}.
+Specifying a smallest effect size of interest of \(6\%\) absolute risk reduction provides an initial yardstick to evaluate our results and make our prediction falsifiable.
+However, the value of \(\pm 6\%\) does not possess an intrinsic theoretical meaning.
+As the emerging meta-psychological literature matures, we hope to see future research base the smallest effect size of interest on increasingly well-informed empirical and theoretical considerations.
 
@@
 
-\hypertarget{confirmatory-analyses}{%
-\subsection{Confirmatory Analyses}\label{confirmatory-analyses}}
-
-146 out of 152 standard reports and 31 out of 71 Registered Reports had positive results, meaning that the positive result rate was \(96.05 \%\) for standard reports (\(95 \%\) CI {[}91.61, 98.54{]}) and \(43.66 \%\) for Registered Reports (\(95 \%\) CI {[}31.91, 55.95{]}; see Fig.~\ref{fig:mainplot}).
-The preregistered one-sided proportions test with an alpha level of \(5\%\) showed that this difference of \(52.39 \%\) was statistically significant, \(\chi^2 = 77.96\), \(p < .001\).
-Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\), \(z = 7.61\), \(p > .999\), meaning that we cannot reject differences more extreme than \(6\%\).
+\hypertarget{preregistered-analysis}{%
+\subsection{Preregistered analysis}\label{preregistered-analysis}}
+
+31 out of 71 Registered Reports and 146 out of 152 standard reports had positive results, meaning that the positive result rate was \(43.66 \%\) for Registered Reports (\(95 \%\) CI {[}31.91, 55.95{]}) and \(96.05 \%\) for standard reports (\(95 \%\) CI {[}91.61, 98.54{]}; see Fig.~\ref{fig:mainplot}).
+This difference of \(-52.39 \%\) was statistically significant in the preregistered one-sided proportions test with \(\alpha = 5\%\), \(\chi^2(1) = 77.96\), \(p < .001\).
+Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\) (\(z = 7.61\), \(p > .999\)), meaning that we cannot reject differences more extreme than \(6\%\).
 We thus accept our hypothesis that the positive result rate in Registered Reports is lower than in standard reports.
@@
 \hypertarget{exploratory-analyses}{%
-\subsection{Exploratory Analyses}\label{exploratory-analyses}}
-
-As described in the Method section, we only classified direct replications of previously published work as replications.
-This means that our non-replication category also contains some conceptual replications and \enquote{internal} replications (where original and replication are published in the same paper).
-For ease of communication we will nonetheless refer to this category as \enquote{original} studies.
-As expected, direct replications were much more common among Registered Reports than standard reports: 41 out of 71 Registered Reports (\(57.75\%\)), but only 4 out of 152 standard reports (\(2.63\%\)) were classified as direct replications of previously published work.
-However, this difference cannot account for the stark overall difference between standard reports and Registered Reports described above:
-Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports, \(45.95\%\), was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
+\subsection{Exploratory analyses}\label{exploratory-analyses}}
+
+For ease of communication we will refer to papers that were classified as close replications of previously published work as \enquote{replications} and to all other studies as \enquote{original}, even though the latter include some conceptual replications and internal replications (as explained above).
+As expected, replications were much more common among Registered Reports (\(41 / 71 = 57.75\%\)) than standard reports (\(4 / 152 = 2.63\%\)), and replication Registered Reports had a descriptively lower positive result rate than original Registered Reports (see Table 1).
+However, this finding fails to explain the main result described above:
+When analysing only original papers, the difference between the positive result rates of Registered Reports and standard reports, \(-45.95\%\), was still significantly smaller than 0 (\(\chi^2(1) = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).
 
@@
 
-Since our standard-reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question to ask is how our results compare to Fanelli's.
-The difference between the positive result rate for standard reports in our sample (\(96.05\%\)) and Fanelli's (\(91.49\%\)) is \(4.56\%\).
-This difference is not significantly different from 0 in a two-sided proportions test (\(\chi^2 = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 0.51\), \(p= .306\)), both at \(\alpha = 5\%\).
-In other words, we can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least \(\pm 6\%\) between them.
-The data are inconclusive.
+Since our standard-reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question is how our results compare to Fanelli's.
+The difference between the positive result rates of standard reports in our sample and Fanelli's (\(96.05\% - 91.49\% = 4.56\%\)) is not significantly different from 0 in a two-sided proportions test (\(\chi^2(1) = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 0.51\), \(p= .306\)), both at \(\alpha = 5\%\).
+The data are inconclusive:
+We can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least \(\pm 6\%\) between them.
 
 Finally, we analysed the language that was used to introduce or refer to hypotheses in Registered Reports.
-We were interested in whether the search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} used by Fanelli captures the way researchers write about hypothesis tests reasonably well.
-The answer is a resounding \enquote{no}:
+We found extremely little overlap with Fanelli's search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}:
 Searching the abstracts, titles, and keywords of the Registered Reports sample showed that only 2/71 Registered Reports would have been detected with this search phrase.
-To get an overview of analogous hypothesis-introduction phrases researchers used in Registered Reports, we stripped the hypothesis quotes of Registered Reports from all content-specific information and extracted \enquote{minimal} phrases that most distinctively indicated that a hypothesis was being described.
+To analyse which other hypothesis-introduction phrases researchers used in Registered Reports, we stripped the coded hypothesis quotes from all content-specific information and extracted \enquote{minimal} phrases that most distinctively indicated that a hypothesis was being described.
 For example, from the hypothesis quote \enquote{(f)or Study 1, we predicted that participants reading about academic (vs.~social) behaviors would show a better anagram performance} we extracted the hypothesis-introduction phrase \enquote{predicted that}.
@@
 In this total set of 97 hypothesis introductions, we found 64 unique phrases showing substantial linguistic variation (see Tables 2 and 3).
-To condense the information, we listed all unique word stems (e.g., the word stem \enquote{hypothes\(^\ast\)} captures the words \enquote{hypothesis}, \enquote{hypotheses}, \enquote{hypothesize}, \enquote{hypothesized}, and so on) and analysed their frequency among all hypothesis introductions.
-Excluding words that are common but too unspecific by themselves, such as \enquote{that}, \enquote{to}, or \enquote{whether}, the five most frequent word stems were \enquote{hypothes\(^\ast\)} (34 occurrences), \enquote{replicat\(^\ast\)} (24), \enquote{test\(^\ast\)} (20), \enquote{examine\(^\ast\)} (8), and \enquote{predict\(^\ast\)} (8).
-Clearly, \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times and more than half of all hypothesis introductions (51/97) contained neither word.
-Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions in original Registered Reports contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, but the same was true for only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication Registered Reports.
-
-We noticed that direct replication Registered Reports generally tended to use different language to describe their hypothesis.
-As the high frequency of the word stem \enquote{replicat\(^\ast\)} suggests, these studies were often not framed as \emph{tests} of a previously tested hypothesis, but as attempts to repeat a previously conducted procedure.
-Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
-
-Tables 2 and 3 list all unique hypothesis introductions and their frequency in original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
-Using five as a cut-off value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.
+We then listed all unique word stems within those phrases and analysed their frequency.
+Excluding words that are common but too unspecific by themselves (e.g., \enquote{that}, \enquote{to}, \enquote{whether}), the five most frequent word stems were \enquote{hypothes\(^\ast\)} (34 occurrences), \enquote{replicat\(^\ast\)} (24), \enquote{test\(^\ast\)} (20), \enquote{examine\(^\ast\)} (8), and \enquote{predict\(^\ast\)} (8).
+Clearly, \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times, and more than half of all hypothesis introductions (51/97) contained neither word.
+
+69 of the 71 Registered Reports (\(97.18 \%\)) had at least one of these five most frequent word stems in their title, abstract, or keywords, meaning that a regular literature search (without access to full texts) with the search terms \enquote{hypothes\(^\ast\) \emph{OR} replicat\(^\ast\) \emph{OR} test\(^\ast\) \emph{OR} examine\(^\ast\) \emph{OR} predict\(^\ast\)} would have been effective in identifying these papers.
+We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question could be useful for future meta-research.
+
+Lastly, we noticed an interesting difference in language use between original and replication Registered Reports:
+As the high frequency of the word stem \enquote{replicat\(^\ast\)} suggests, replications were often framed as attempts to repeat a previously conducted \emph{procedure} rather than as attempts to test a previously tested \emph{hypothesis}.
+Tables 2 and 3 list all unique hypothesis introductions and their frequency in original Registered Reports and replication Registered Reports, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
 
@@
 
-We examined the proportion of Psychology articles that find support for their first tested hypothesis and discovered a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data analysis).
-More than half of the analysed hypothesis tests in Registered Reports were direct replications of previous work, but the difference between standard reports and Registered Reports was still large when direct replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
-The introduction of Registered Reports has clearly led to a much larger proportion of null results appearing in the published literature compared to standard reports.
-
-The positive result rate we found in standard reports (\(96.05 \%\)) is slightly higher than the \(91.5\%\) reported by Fanelli (2010), although this difference was not statistically significant.
+We examined the proportion of Psychology articles that find support for their first tested hypothesis and discovered a large difference (\(96.05 \%\) vs \(43.66 \%\)) between a random sample of standard reports and the full population of Registered Reports (at the time of data collection).
+More than half of the analysed hypothesis tests in Registered Reports were close replications of previous work, but the difference between standard reports and Registered Reports remained large when close replications were excluded from the analysis (\(95.95 \%\) vs \(50.00 \%\)).
+Clearly, the emerging literature of Registered Reports appears to be publishing a much larger proportion of null results than the standard literature.
+
+The positive result rate we found in standard reports (\(96.05 \%\)) is slightly but non-significantly higher than the \(91.5\%\) reported by Fanelli (2010).
 Our replication in a more recent sample of the Psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 (cf.
@@
 To explain the \(52.39 \%\) gap between standard reports and Registered Reports, we must assume some combination of differences in bias, statistical power, or the proportion of true hypotheses researchers choose to examine.
-Figure~\ref{fig:powerbaserate} visualises the combinations of statistical power and proportion of true hypotheses that would produce the observed positive result rates if the literature were completely unbiased.
-For example, assuming no publication bias and no QRPs, even if \emph{all} hypotheses authors of standard reports tested were true, their study designs would need to have more than \(90\%\) power for the true effect size.
-This is highly unlikely, meaning that the standard literature is unlikely to reflect reality.
-As we noted above, there is good reason to assume that methodological rigour and statistical power in Registered Reports are as high as in standard reports or higher, leaving the rate of true hypotheses and bias as remaining explanations.
+Figure~\ref{fig:powerbaserate} visualises the combinations of statistical power and proportion of true hypotheses that could produce the observed positive result rates if the literature were completely unbiased.
+Assuming no publication bias and no QRPs, authors of standard reports would need to test almost exclusively true hypotheses (\(>90\%\)) with more than \(90\%\) power.
+Because this is highly implausible and contradicted by available evidence (e.g., Szucs \& Ioannidis, 2017), the standard literature is unlikely to reflect reality.
+As noted above, methodological rigour and statistical power in Registered Reports likely meet or exceed the level of standard reports, leaving the rate of true hypotheses and bias as remaining explanations.
 
@@
 However, assuming over \(90\%\) true hypotheses in the standard literature is neither realistic, nor would it be desirable for a science that wants to advance knowledge beyond trivial facts.
-We thus believe that this factor alone is not sufficient to explain the gap between the positive result rates in Registered Reports and standard reports.
-Rather, the numbers strongly suggest a reduction of publication bias and/or Type-1 error inflation in the Registered Reports literature.
+We thus believe that this factor alone is not sufficient to explain the large difference in positive results.
+Rather, the numbers strongly suggest a reduction of publication bias and/or QRPs in the Registered-Reports literature.
+Nonetheless, the prior probability of hypotheses in Registered Reports and standard reports may differ and should be studied in future research.
 
@@
 
-We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports.
-Because hypotheses, authors, and editors were not randomly assigned to each publication format, we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses.
-Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment.
-As mentioned above, it is \emph{a-priori} plausible that the Registered Reports format is used selectively for particularly risky hypotheses.
-This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in Psychology.
-It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias.
-Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use.
-This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
-
-A second limitation of the current study (and of Fanelli, 2010) is that standard reports were selected using the search term \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
-As our results show, this phrase was virtually absent in the Registered Report population.
-The wide variety of ways to introduce a hypothesis we observed in Registered Reports suggests that a search for \enquote{test\(^\ast\) the hypothes\(^\ast\)} might miss most of the hypothesis-testing studies in the psychological literature, and results obtained this way may not generalise to all published studies.
-For example, it is possible that authors are more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., \enquote{we examined the role of \ldots{}}).
-If this were true, using other strategies to select standard reports might yield lower estimates for the positive result rate.
-However, this does not seem to be the case:
-Studies using different selection criteria for articles and hypotheses have found very similar rates of supported hypotheses.
-For example, the positive result rates in Sterling (1959), Sterling et al.
-(1995), and the original studies included in the Reproducibility Project: Psychology (Open Science Collaboration, 2015) were \(97.28\%\), \(95.56\%\), and \(97\%\), respectively.
-Motyl et al. (2017) report \(89.17\%\) and \(92.01\%\) significant results for \enquote{critical} hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively.
-Therefore, although the search term used to find standard reports might limit the generalisability of our results, it seems to yield comparable estimates as the selection strategies used in different studies.
-
-A final limitation is the decision to code only the first reported hypothesis.
+Since coders could not be blinded to an article's publication format, their judgment may have been biased.
+Our study was not an experiment\(\,\)---\(\,\)hypotheses, authors, and editors were not randomly assigned to each publication format\(\,\)---\(\,\)and thus precludes strong causal inferences.
+As discussed above, it seems highly plausible that Registered Reports reduce publication bias and QRPs, which in turn reduces the positive result rate.
+Yet we neither know exactly how effective Registered Reports are at reducing bias, nor how large the effect on positive results would be in the absence of potential confounds.
+One such confound, as just discussed, could be that Registered Reports may be used for particularly risky hypotheses.
+Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use.
+As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and type-I error inflation for all empirical articles they publish.
+This could lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
+Additional research, ideally with prospective and experimental or quasi-experimental study designs, is needed to further investigate the influence of such factors.
+However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (\emph{Attention, Perception, and Psychophysics}, \emph{Cognition and Emotion}, and \emph{Frontiers in Psychology}) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
+In these three journals, \(11/13\) (\(84.62\%\); \(95 \%\) CI {[}54.55, 98.08{]}) standard reports had positive results, compared to only \(7/14\) (\(50.00\%\); \(95 \%\) CI {[}23.04, 76.96{]}) Registered Reports.
+
+Another limitation of the current study (and of Fanelli, 2010) is that standard reports were selected using the search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
+This phrase was virtually absent in Registered Reports, suggesting that the search strategy may not yield a representative sample of the population of hypothesis-testing studies in the literature.
+The use of the phrase might even be confounded with the outcome of a study:
+For example, authors may be more likely to describe their research explicitly as a hypothesis test when they found positive results, but prefer more vague language for unsupported hypotheses (e.g., \enquote{we examined the role of \ldots{}}).
+A similar concern could be raised for the decision to code only the first reported hypothesis of each article.
 The first hypothesis test may not be representative for all hypothesis tests reported in a paper, and the order of reporting may differ between standard reports and Registered Reports.
-Perhaps Registered-Report authors are more likely to present their hypotheses in \enquote{chronological} order, whereas standard-report authors tend to rearrange the order in which hypotheses are reported based on their outcomes, and present supported hypotheses first.
-Here again, the converging estimates from the four studies cited above (none of which use the first-hypothesis rule) make it seem unlikely that our result is an artefact of this decision.
-Regardless of which hypothesis one chooses to analyse across a set of papers -- the first, the last, or the \enquote{critical} one -- the positive result rate turns out to be higher than what can be expected based on realistic estimates of the proportion of true hypotheses researchers study and the statistical power of their tests.
+For example, standard-report authors might tend to present supported hypotheses first, whereas Registered-Report authors might be more likely to present their hypotheses in \enquote{chronological} order.
+
+Both of these potential confounds might lead to an inflated estimate of the positive result rate in standard reports.
+However, studies using different selection criteria for articles and hypotheses have found very similar rates of supported hypotheses in the literature:
+\(97.28\%\) in Sterling (1959), \(95.56\%\) in Sterling et al. (1995), and \(97\%\) in the original studies included in the Reproducibility Project: Psychology (Open Science Collaboration, 2015).
+In addition, Motyl et al. (2017) report \(89.17\%\) and \(92.01\%\) significant results for \enquote{critical} hypothesis tests in papers published in 2003-2004 and 2013-2014, respectively.
+Although the selection criteria for articles and hypotheses in our study may limit the generalisability of the results, this level of convergence makes it seem unlikely that alternative methods would have yielded dramatically different conclusions.
 
@@
 The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the existing body of published research.
-Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered Reports literature.
+Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered-Reports literature.
 The absence of negative results is a serious threat to a cumulative science.
-In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?} The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
-In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature---and may be one solution to achieve a more credible scientific record.
+In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?}
+The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
+In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature\(\,\)---\(\,\)and may be one solution to achieve a more credible scientific record.
 
@@
 \href{https://osf.io/aqr2s/}{Data} and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
-The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
+The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
+
+\hypertarget{reporting}{%
+\subsubsection{Reporting}\label{reporting}}
+
+We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.
+
+\hypertarget{author-contributions}{%
+\subsubsection{Author Contributions}\label{author-contributions}}
+
+Conceptualisation: A.S.
+\& D.L.; data curation, formal analysis, and software: A.S.
+\& M.S.; investigation, methodology, and validation: A.S., M.S., \& D.L; supervision: A.S \& D.L.; visualisation and writing\(\,\)---\(\,\)original draft: A.S; writing\(\,\)---\(\,\)review and editing: A.S., M.S., \& D.L.
 
@@
 
-\hypertarget{author-contributions}{%
-\subsubsection{Author Contributions}\label{author-contributions}}
-
-Conceptualisation: A.S.
-\& D.L.; data curation, formal analysis, and software: A.S.
-\& M.S.; investigation, methodology, and validation: A.S., M.S., \& D.L; supervision: A.S \& D.L.; visualisation and writing---original draft: A.S; writing---review and editing: A.S., M.S., \& D.L.
-
 \hypertarget{acknowledgements}{%
@@
 
-\leavevmode\hypertarget{ref-Chambers2013}{}%
-Chambers, C. (2013). Registered reports: A new publishing initiative at Cortex, \emph{49}(3), 609--610. Retrieved from \url{http://orca.cf.ac.uk/45177/1/Chambers_Cortex_2013b_GreenOA.pdf}
-
-\leavevmode\hypertarget{ref-Chambers2015}{}%
-Chambers, C., Dienes, Z., McIntosh, R., Rotshtein, P., \& Willmes, K.
-(2015).
-Registered Reports: Realigning incentives in scientific publishing.
-\emph{Cortex}, \emph{66}, 1--2.
-\url{https://doi.org/10.1016/j.cortex.2015.03.022}
+\leavevmode\hypertarget{ref-Baumeister2016}{}%
+Baumeister, R.
+F.
+(2016).
+Charting the future of social psychology on stormy seas: Winners, losers, and recommendations.
+\emph{Journal of Experimental Social Psychology}, \emph{66}, 153--158.
+\url{https://doi.org/10.1016/j.jesp.2016.02.003}
+
+\leavevmode\hypertarget{ref-Chambers2020}{}%
+Chambers, C. D., \& Tzavella, L. (2020). \emph{Registered Reports: Past, Present and Future} (Preprint). MetaArXiv. \url{https://doi.org/10.31222/osf.io/43298}
 
@@
 
-\leavevmode\hypertarget{ref-Cristea2018}{}%
-Cristea, I.
-A., \& Ioannidis, J.
-P.
-A.
-(2018).
-P values in display items are ubiquitous and almost invariably significant: A survey of top science journals.
-\emph{PLOS ONE}, \emph{13}(5), e0197440.
-\url{https://doi.org/10.1371/journal.pone.0197440}
-
-\leavevmode\hypertarget{ref-deWinter2013}{}%
-de Winter, J., \& Happee, R.
-(2013).
-Why Selective Publication of Statistically Significant Results Can Be Effective.
-\emph{PLOS ONE}, \emph{8}(6), e66463.
-\url{https://doi.org/10.1371/journal.pone.0066463}
-
 \leavevmode\hypertarget{ref-Fanelli2010}{}%
@@
 
+\leavevmode\hypertarget{ref-Fraser2018}{}%
+Fraser, H., Parker, T., Nakagawa, S., Barnett, A., \& Fidler, F.
+(2018).
+Questionable research practices in ecology and evolution.
+\emph{PLOS ONE}, \emph{13}(7), e0200303.
+\url{https://doi.org/10.1371/journal.pone.0200303}
+
 \leavevmode\hypertarget{ref-Goldacre2016}{}%
@@
 The COMPare Trials Project.
-Retrieved February 3, 2020, from \url{http://compare-trials.org}
+\emph{COMPare}.
+Retrieved from \url{http://compare-trials.org}
 
@@
 \url{https://doi.org/10.1177/0956797611430953}
-
-\leavevmode\hypertarget{ref-Jonas2016}{}%
-Jonas, K.
-J., \& Cesario, J.
-(2016).
-How can preregistration contribute to research in our field?
-\emph{Comprehensive Results in Social Psychology}, \emph{1}(1-3), 1--7.
-\url{https://doi.org/10.1080/23743603.2015.1070611}
 
@@
 
-\leavevmode\hypertarget{ref-Kohler2019}{}%
-Köhler, T., \& Cortina, J.
-M.
-(2019).
-Play It Again, Sam!
-An Analysis of Constructive Replication in the Organizational Sciences.
-\emph{Journal of Management}, 014920631984398.
-\url{https://doi.org/10.1177/0149206319843985}
-
 \leavevmode\hypertarget{ref-R-TOSTER}{}%
@@
 \url{https://doi.org/10.1037/1082-989X.9.2.147}
+
+\leavevmode\hypertarget{ref-Mitchell2014}{}%
+Mitchell, J. (2014). On the evidentiary emptiness of failed replications. Retrieved from \url{https://jasonmitchell.fas.harvard.edu/Papers/Mitchell/_failed/_science/_2014.pdf}
 
@@
 \leavevmode\hypertarget{ref-RRRwebsite}{}%
-Registered Replication Reports. (n.d.). Retrieved December 28, 2019, from \url{https://www.psychologicalscience.org/publications/replication}
+Registered Replication Reports. (n.d.). \emph{Association for Psychological Science - APS}. Retrieved from \url{https://www.psychologicalscience.org/publications/replication}
 
 \leavevmode\hypertarget{ref-Rohatgi2018}{}%
-Rohatgi, A. (2018). \emph{WebPlotDigitizer - Web Based Plot Digitizer}. Austin, Texas, USA. Retrieved from \url{https://automeris.io/WebPlotDigitizer}
+Rohatgi, A. (2018). \emph{WebPlotDigitizer - Web Based Plot Digitizer}. Austin, Texas, USA.
 

### 2022-03-10 preprint/positive_results_SRs_RRs.Rmd
updated disclaimer from "article is in press" to "article is published" (with DOI and all) and made very minor copy edits (e.g. added Mitchell's middle initials)

@@
     email         : "a.m.scheel@tue.nl"
-  - name          : "Mitchell Schijen"
+  - name          : "Mitchell R. M. J. Schijen"
     affiliation   : "1"
@@
     fontupper=\normalsize,borderline={0.3mm}{0.3mm}{white}]
-  The present version of this manuscript has been accepted for publication at \textsl{Advances in Methods and Practices in Psychological Science}. Please cite as:
+  A copy-edited version of this manuscript is now published at \textsl{Advances in Methods and Practices in Psychological Science}. Please cite as:
    \vspace{0.2cm}
@@
   Scheel, A.
-M., Schijen, M., \& Lakens, D.
-(in press).
+M., Schijen, M.
+R.
+M.
+J., \& Lakens, D.
+(2021).
 An excess of positive results: Comparing the standard Psychology literature with Registered Reports.
-\textsl{Advances in Methods and Practices in Psychological Science}.
+\textsl{Advances in Methods and Practices in Psychological Science, 4}(2).
+\url{https://doi.org/10.1177/25152459211007467}
   \end{center}
@@
 A new publication format has been developed to prevent selective reporting: In Registered Reports, peer review and the decision to publish take place before results are known.
-We compared the results in published Registered Reports (N = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (N = 152) in Psychology.
+We compared the results in published Registered Reports (*N* = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (*N* = 152) in Psychology.
 Analysing the first hypothesis of each paper, we found $96\%$ positive results in standard reports, but only $44\%$ positive results in Registered Reports.
-We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered-Reports literature.
+We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-I error inflation in the Registered-Reports literature.
 
@@
 But when published findings are systematically biased, cumulative science breaks down: 
-Unlike random error, bias does not cancel out when aggregating across studies$\,$---$\,$in the worst case it accumulates, leading us away from the truth rather than towards it.
+Unlike random error, bias does not cancel out when aggregating across studies$\,$---$\,$in the worst case, it accumulates, leading us away from the truth rather than towards it.
 Unfortunately, there is reason to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
@@
 These include editors and reviewers selectively rejecting manuscripts with negative results ['reviewer bias', @Greenwald1975; @Mahoney1977] and researchers deciding not to submit studies with negative results for publication ['file-drawering'; @Rosenthal1979].
-Questionable research practices (QRPs) describe research behaviours that make evidence in favour of a certain conclusion look stronger than it is [typically, though not always, leading to more false positives; see @Lakens2019b].
+Questionable research practices (QRPs) describe research behaviours that make evidence in favour of a certain conclusion look stronger than it is [typically, though not always, leading to more false positives; see @Lakens2019].
 These include presenting unexpected results as having been predicted *a priori* [HARKing, short for "hypothesising after results are known"; @Kerr1998] and exploiting flexibility in data analysis to obtain statistically significant results ["*p*-hacking"; @Simmons2011].
 Evidence for both categories of bias exist: 
-Publication bias has been observed in peer review [@Mahoney1977; @Atkinson1982] and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results [@Franco2014; @Franco2016]; and QRPs have been admitted by scientists in several survey studies [@John2012; @Fiedler2016; @Agnoli2017; @Fraser2018; @Makel2019].
+Publication bias has been observed in peer review [@Mahoney1977; @Atkinson1982] and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results [@Franco2014; @Franco2016]; and QRPs have been admitted by scientists in several survey studies [@John2012; @Fiedler2016; @Agnoli2017; @Fraser2018; @Makel2021].
 
@@
 Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
-MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code ($`r sum(included$coded_by_AS & included$is_RR==1)`$ RRs and $`r sum(included$coded_by_AS & included$is_RR==0)`$ SRs).
-Only `r support.disagreement.major` disagreements were major (Cohen's kappa = `r printp(kappa.support)`) and subsequently resolved by discussion; `r support.disagreement.minor` were minor (disagreement between "support" and "partial support").
-We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+M.S.
+coded all papers in the sample, A.S.
+double-coded all papers M.S.
+had found difficult to code or could not code ($`r sum(included$coded_by_AS & included$is_RR==1)`$ RRs and $`r sum(included$coded_by_AS & included$is_RR==0)`$ SRs).
+Only `r support.disagreement.major` disagreements were major (Cohen's $\kappa$ = `r printp(kappa.support)`) and subsequently resolved by discussion; `r support.disagreement.minor` were minor (disagreement between "support" and "partial support").
+We overturned the preregistered plan that A.S.
+would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
 Because removing all indicators that could have identified Registered Reports as such from their full texts would have been practically impossible, coding was not blind to publication format (Registered Report vs standard report).
@@
 Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
-AS coded all papers, DL double-coded `r rep.RR.coded.DL` Registered Reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR)*100)` \%$) and `r rep.SR.coded.DL` standard reports ($`r printnum(rep.SR.coded.DL/sum(included$is_RR==0)*100)` \%$).
-There were `r rep.disagreements` disagreements (Cohen's kappa = `r printp(kappa.rep)`), all were resolved by discussion.
+A.S.
+coded all papers, D.L.
+double-coded `r rep.RR.coded.DL` Registered Reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR)*100)` \%$) and `r rep.SR.coded.DL` standard reports ($`r printnum(rep.SR.coded.DL/sum(included$is_RR==0)*100)` \%$).
+There were `r rep.disagreements` disagreements (Cohen's $\kappa$ = `r printp(kappa.rep)`), all were resolved by discussion.
 
@@
 Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use. 
-As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and type-I error inflation for all empirical articles they publish.
+As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and Type-I error inflation for all empirical articles they publish.
 This could lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective. 
 Additional research, ideally with prospective and experimental or quasi-experimental study designs, is needed to further investigate the influence of such factors.
-However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (*`r bfjournals[1]`*, *`r bfjournals[2]`*, and *`r bfjournals[3]`*) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
+However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (*`r bfjournals[1]`*; *`r bfjournals[2]`*; and *`r bfjournals[3]`*) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
 In these three journals, $`r n.support.SR.bf`/`r n.SR.bf`$ ($`r printnum(prop.support.SR.bf*100)`\%$; $95 \%$ CI [`r printnum(min(SR.binom.bf$conf.int)*100)`, `r printnum(max(SR.binom.bf$conf.int)*100)`]) standard reports had positive results, compared to only $`r n.support.RR.bf`/`r n.RR.bf`$ ($`r printnum(prop.support.RR.bf*100)`\%$; $95 \%$ CI [`r printnum(min(RR.binom.bf$conf.int)*100)`, `r printnum(max(RR.binom.bf$conf.int)*100)`]) Registered Reports.
@@
 The absence of negative results is a serious threat to a cumulative science. 
-In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" 
+In 1959, Sterling asked: "What credence can then be given to inferences drawn from statistical tests of $H_0$ if the reader is not aware of all experimental outcomes of a kind?" (p. 33).
 The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left. 
@@
 & D.L.; data curation, formal analysis, and software: A.S.
-& M.S.; investigation, methodology, and validation: A.S., M.S., & D.L; supervision: A.S & D.L.; visualisation and writing$\,$---$\,$original draft: A.S; writing$\,$---$\,$review and editing: A.S., M.S., & D.L.
+& M.R.M.J.S.; investigation, methodology, and validation: A.S., M.R.M.J.S., & D.L; supervision: A.S & D.L.; visualisation and writing$\,$---$\,$original draft: A.S; writing$\,$---$\,$review and editing: A.S., M.R.M.J.S., & D.L.
 
@@
 ### Acknowledgements
-This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leonid Tiokhin, and Stuart Ritchie for valuable comments that helped improve this manuscript.
-
-### Prior versions
-A preprint of this manuscript has been published on *PsyArXiv* (https://doi.org/10.31234/osf.io/p6e9c).
-All sections of the present manuscript have been shortened to comply with the submission guidelines, but are intended to contain the same arguments, methods, results, and conclusions as the preprint.
+This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leo Tiokhin, Stuart Ritchie, and Simine Vazire for valuable comments that helped improve this manuscript.
 

### 2022-03-10 preprint/positive_results_SRs_RRs.tex
updated disclaimer from "article is in press" to "article is published" (with DOI and all) and made very minor copy edits (e.g. added Mitchell's middle initials)

@@
 
-\usepackage{etoolbox}
-\makeatletter
-\providecommand{\subtitle}[1]{% add subtitle to \maketitle
-  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
-}
-\makeatother
 % Manuscript styling
@@
 \shorttitle{Positive Results in Standard vs Registered Reports}
-\author{Anne M. Scheel\textsuperscript{1}, Mitchell Schijen\textsuperscript{1}, \& Daniël Lakens\textsuperscript{1}}
+\author{Anne M. Scheel\textsuperscript{1}, Mitchell R. M. J. Schijen\textsuperscript{1}, \& Daniël Lakens\textsuperscript{1}}
 \affiliation{
@@
    fontupper=\normalsize,borderline={0.3mm}{0.3mm}{white}]
- The present version of this manuscript has been accepted for publication at \textsl{Advances in Methods and Practices in Psychological Science}. Please cite as:
+ A copy-edited version of this manuscript is now published at \textsl{Advances in Methods and Practices in Psychological Science}. Please cite as:
   \vspace{0.2cm}
@@
  Scheel, A.
-M., Schijen, M., \& Lakens, D.
-(in press).
+M., Schijen, M.
+R.
+M.
+J., \& Lakens, D.
+(2021).
 An excess of positive results: Comparing the standard Psychology literature with Registered Reports.
-\textsl{Advances in Methods and Practices in Psychological Science}.
+\textsl{Advances in Methods and Practices in Psychological Science, 4}(2).
+\url{https://doi.org/10.1177/25152459211007467}
  \end{center}
@@
 A new publication format has been developed to prevent selective reporting: In Registered Reports, peer review and the decision to publish take place before results are known.
-We compared the results in published Registered Reports (N = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (N = 152) in Psychology.
+We compared the results in published Registered Reports (\emph{N} = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (\emph{N} = 152) in Psychology.
 Analysing the first hypothesis of each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports.
-We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered-Reports literature.
+We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-I error inflation in the Registered-Reports literature.
 }
@@
 But when published findings are systematically biased, cumulative science breaks down:
-Unlike random error, bias does not cancel out when aggregating across studies\(\,\)---\(\,\)in the worst case it accumulates, leading us away from the truth rather than towards it.
+Unlike random error, bias does not cancel out when aggregating across studies\(\,\)---\(\,\)in the worst case, it accumulates, leading us away from the truth rather than towards it.
 Unfortunately, there is reason to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.
@@
 Evidence for both categories of bias exist:
-Publication bias has been observed in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; Fraser, Parker, Nakagawa, Barnett, \& Fidler, 2018; John, Loewenstein, \& Prelec, 2012; Makel, Hodges, Cook, \& Plucker, 2019).
+Publication bias has been observed in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; Fraser, Parker, Nakagawa, Barnett, \& Fidler, 2018; John, Loewenstein, \& Prelec, 2012; Makel, Hodges, Cook, \& Plucker, 2021).
 
@@
 
-In a recent commentary, Allen and Mehler (2019) reported a similar investigation:
+In a recent commentary, Allen \& Mehler (2019) reported a similar investigation:
 With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found \(60.5\%\) unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
@@
 Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
-MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
-Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
-We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
+M.S. coded all papers in the sample, A.S. double-coded all papers M.S. had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
+Only 3 disagreements were major (Cohen's \(\kappa\) = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
+We overturned the preregistered plan that A.S.
+would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
 Because removing all indicators that could have identified Registered Reports as such from their full texts would have been practically impossible, coding was not blind to publication format (Registered Report vs standard report).
@@
 Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
-AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(65.13 \%\)).
-There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.
+A.S. coded all papers, D.L. double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(65.13 \%\)).
+There were 5 disagreements (Cohen's \(\kappa\) = .878), all were resolved by discussion.
 
@@
 Fanelli, 2012).
-Furthermore, our estimate of the positive result rate for Registered Reports (\(43.66 \%\)) is comparable to the \(39.5\%\) reported by Allen and Mehler (2019), despite some differences in method and studied population.
+Furthermore, our estimate of the positive result rate for Registered Reports (\(43.66 \%\)) is comparable to the \(39.5\%\) reported by Allen \& Mehler (2019), despite some differences in method and studied population.
 
@@
 Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use.
-As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and type-I error inflation for all empirical articles they publish.
+As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and Type-I error inflation for all empirical articles they publish.
 This could lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
 Additional research, ideally with prospective and experimental or quasi-experimental study designs, is needed to further investigate the influence of such factors.
-However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (\emph{Attention, Perception, and Psychophysics}, \emph{Cognition and Emotion}, and \emph{Frontiers in Psychology}) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
+However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (\emph{Attention, Perception, and Psychophysics}; \emph{Cognition and Emotion}; and \emph{Frontiers in Psychology}) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
 In these three journals, \(11/13\) (\(84.62\%\); \(95 \%\) CI {[}54.55, 98.08{]}) standard reports had positive results, compared to only \(7/14\) (\(50.00\%\); \(95 \%\) CI {[}23.04, 76.96{]}) Registered Reports.
@@
 The absence of negative results is a serious threat to a cumulative science.
-In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?}
+In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?} (p.~33).
 The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
@@
 \href{https://osf.io/aqr2s/}{Data} and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
-The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
+The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.24; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.34; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.27; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 2.10; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
 
@@
 \& D.L.; data curation, formal analysis, and software: A.S.
-\& M.S.; investigation, methodology, and validation: A.S., M.S., \& D.L; supervision: A.S \& D.L.; visualisation and writing\(\,\)---\(\,\)original draft: A.S; writing\(\,\)---\(\,\)review and editing: A.S., M.S., \& D.L.
+\& M.R.M.J.S.; investigation, methodology, and validation: A.S., M.R.M.J.S., \& D.L; supervision: A.S \& D.L.; visualisation and writing\(\,\)---\(\,\)original draft: A.S; writing\(\,\)---\(\,\)review and editing: A.S., M.R.M.J.S., \& D.L.
 
@@
 
-This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leonid Tiokhin, and Stuart Ritchie for valuable comments that helped improve this manuscript.
-
-\hypertarget{prior-versions}{%
-\subsubsection{Prior versions}\label{prior-versions}}
-
-A preprint of this manuscript has been published on \emph{PsyArXiv} (\url{https://doi.org/10.31234/osf.io/p6e9c}).
-All sections of the present manuscript have been shortened to comply with the submission guidelines, but are intended to contain the same arguments, methods, results, and conclusions as the preprint.
+This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leo Tiokhin, Stuart Ritchie, and Simine Vazire for valuable comments that helped improve this manuscript.
 
@@
 
-\leavevmode\hypertarget{ref-Lakens2019b}{}%
-Lakens, D. (2019). The Value of Preregistration for Psychological Science: A Conceptual Analysis. \url{https://doi.org/10.31234/osf.io/jbh4w}
+\leavevmode\hypertarget{ref-Lakens2019}{}%
+Lakens, D.
+(2019).
+The value of preregistration for psychological science: A conceptual analysis.
+\emph{Japanese Psychological Review}, \emph{62}(3), 221--230.
+\url{https://doi.org/10.24602/sjpr.62.3_221}
 
@@
 \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269.
-\url{https://doi.org/10.1016/j.ympev.2015.01.015}
+\url{https://doi.org/10.1177/2515245918770963}
 
@@
 
-\leavevmode\hypertarget{ref-Makel2019}{}%
-Makel, M. C., Hodges, J., Cook, B. G., \& Plucker, J. (2019). Questionable and Open Research Practices in Education Research. \url{https://doi.org/10.35542/osf.io/f7srb}
+\leavevmode\hypertarget{ref-Makel2021}{}%
+Makel, M.
+C., Hodges, J., Cook, B.
+G., \& Plucker, J.
+A.
+(2021).
+Both Questionable and Open Research Practices Are Prevalent in Education Research: \emph{Educational Researcher}.
+\url{https://doi.org/10.3102/0013189X211001356}
 
@@
 
+\leavevmode\hypertarget{ref-Agnoli2017}{}%
+Agnoli, F., Wicherts, J.
+M., Veldkamp, C.
+L.
+S., Albiero, P., \& Cubelli, R.
+(2017).
+Questionable research practices among italian research psychologists.
+\emph{PLOS ONE}, \emph{12}(3), e0172792.
+\url{https://doi.org/10.1371/journal.pone.0172792}
+
+\leavevmode\hypertarget{ref-Allen2019}{}%
+Allen, C., \& Mehler, D.
+M.
+A.
+(2019).
+Open science challenges, benefits and tips in early career and beyond.
+\emph{PLOS Biology}, \emph{17}(5), e3000246.
+\url{https://doi.org/10.1371/journal.pbio.3000246}
+
+\leavevmode\hypertarget{ref-R-codebook}{}%
+Arslan, R. C. (2018). How to automatically generate rich codebooks from study metadata. PsyArxiv. \url{https://doi.org/10.31234/osf.io/5qc6h}
+
+\leavevmode\hypertarget{ref-Atkinson1982}{}%
+Atkinson, D.
+R., Furlong, M.
+J., \& Wampold, B.
+E.
+(1982).
+Statistical significance, reviewer evaluations, and the scientific process: Is there a (statistically) significant relationship?
+\emph{Journal of Counseling Psychology}, \emph{29}(2), 189--194.
+\url{https://doi.org/10.1037/0022-0167.29.2.189}
+
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-Baumeister2016}{}%
+Baumeister, R.
+F.
+(2016).
+Charting the future of social psychology on stormy seas: Winners, losers, and recommendations.
+\emph{Journal of Experimental Social Psychology}, \emph{66}, 153--158.
+\url{https://doi.org/10.1016/j.jesp.2016.02.003}
+
+\leavevmode\hypertarget{ref-Chambers2020}{}%
+Chambers, C. D., \& Tzavella, L. (2020). \emph{Registered Reports: Past, Present and Future} (Preprint). MetaArXiv. \url{https://doi.org/10.31222/osf.io/43298}
+
+\leavevmode\hypertarget{ref-R-rio}{}%
+Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018). \emph{Rio: A swiss-army knife for data file i/o}.
+
+\leavevmode\hypertarget{ref-Cleophas1999}{}%
+Cleophas, R.
+C., \& Cleophas, T.
+J.
+(1999).
+Is selective reporting of clinical research unethical as well as unscientific?
+\emph{International Journal of Clinical Pharmacology and Therapeutics}, \emph{37}(1), 1--7.
+
+\leavevmode\hypertarget{ref-Fanelli2010}{}%
+Fanelli, D. (2010). "Positive" results increase down the hierarchy of the sciences. \emph{PLoS ONE}, \emph{5}(4), e10068. \url{https://doi.org/10.1371/journal.pone.0010068}
+
+\leavevmode\hypertarget{ref-Fanelli2012}{}%
+Fanelli, D. (2012). Negative results are disappearing from most disciplines and countries. \emph{Scientometrics}, \emph{90}(3), 891--904. \url{https://doi.org/10.1007/s11192-011-0494-7}
+
+\leavevmode\hypertarget{ref-Fiedler2016}{}%
+Fiedler, K., \& Schwarz, N. (2016). Questionable Research Practices Revisited. \emph{Social Psychological and Personality Science}, \emph{7}(1), 45--52. \url{https://doi.org/10.1177/1948550615612150}
+
+\leavevmode\hypertarget{ref-Franco2014}{}%
+Franco, A., Malhotra, N., \& Simonovits, G.
+(2014).
+Publication bias in the social sciences: Unlocking the file drawer.
+\emph{Science}, \emph{345}(6203), 1502--1505.
+\url{https://doi.org/10.1126/science.1255484}
+
+\leavevmode\hypertarget{ref-Franco2016}{}%
+Franco, A., Malhotra, N., \& Simonovits, G.
+(2016).
+Underreporting in Psychology Experiments: Evidence From a Study Registry.
+\emph{Social Psychological and Personality Science}, \emph{7}(1), 8--12.
+\url{https://doi.org/10.1177/1948550615598377}
+
+\leavevmode\hypertarget{ref-Fraser2018}{}%
+Fraser, H., Parker, T., Nakagawa, S., Barnett, A., \& Fidler, F.
+(2018).
+Questionable research practices in ecology and evolution.
+\emph{PLOS ONE}, \emph{13}(7), e0200303.
+\url{https://doi.org/10.1371/journal.pone.0200303}
+
+\leavevmode\hypertarget{ref-Goldacre2016}{}%
+Goldacre, B., Drysdale, H., Powell-Smith, A., Dale, A., Milosevic, I., Slade, E., \ldots{} Heneghan, C.
+(2016).
+The COMPare Trials Project.
+\emph{COMPare}.
+Retrieved from \url{http://compare-trials.org}
+
+\leavevmode\hypertarget{ref-Greenwald1975}{}%
+Greenwald, A. G. (1975). Consequences of Prejudice Against the Null Hypothesis. \emph{Psychological Bulletin}, \emph{82}(1), 1--20.
+
+\leavevmode\hypertarget{ref-John2012}{}%
+John, L.
+K., Loewenstein, G., \& Prelec, D.
+(2012).
+Measuring the Prevalence of Questionable Research Practices With Incentives for Truth Telling.
+\emph{Psychological Science}, \emph{23}(5), 524--532.
+\url{https://doi.org/10.1177/0956797611430953}
+
+\leavevmode\hypertarget{ref-Kaplan2015}{}%
+Kaplan, R.
+M., \& Irvin, V.
+L.
+(2015).
+Likelihood of Null Effects of Large NHLBI Clinical Trials Has Increased over Time.
+\emph{PLOS ONE}, \emph{10}(8), e0132382.
+\url{https://doi.org/10.1371/journal.pone.0132382}
+
+\leavevmode\hypertarget{ref-Kerr1998}{}%
+Kerr, N. L. (1998). HARKing: Hypothesizing after the results are known. \emph{Personality and Social Psychology Review}, \emph{2}(3), 196--217. \url{https://doi.org/10.1207/s15327957pspr0203_4}
+
+\leavevmode\hypertarget{ref-R-TOSTER}{}%
+Lakens, D.
+(2017).
+Equivalence tests: A practical primer for t-tests, correlations, and meta-analyses.
+\emph{Social Psychological and Personality Science}, \emph{1}, 1--8.
+\url{https://doi.org/10.1177/1948550617697177}
+
+\leavevmode\hypertarget{ref-Lakens2019}{}%
+Lakens, D.
+(2019).
+The value of preregistration for psychological science: A conceptual analysis.
+\emph{Japanese Psychological Review}, \emph{62}(3), 221--230.
+\url{https://doi.org/10.24602/sjpr.62.3_221}
+
+\leavevmode\hypertarget{ref-Lakens2018a}{}%
+Lakens, D., Scheel, A.
+M., \& Isager, P.
+M.
+(2018).
+Equivalence Testing for Psychological Research: A Tutorial.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269.
+\url{https://doi.org/10.1177/2515245918770963}
+
+\leavevmode\hypertarget{ref-Mahoney1977}{}%
+Mahoney, M.
+J.
+(1977).
+Publication Prejudices: An Experimental Study of Confirmatory Bias in the Peer Review System.
+\emph{Cognitive Therapy and Research}, \emph{1}(2), 161--175.
+\url{https://doi.org/10.1007/BF01173636}
+
+\leavevmode\hypertarget{ref-Makel2021}{}%
+Makel, M.
+C., Hodges, J., Cook, B.
+G., \& Plucker, J.
+A.
+(2021).
+Both Questionable and Open Research Practices Are Prevalent in Education Research: \emph{Educational Researcher}.
+\url{https://doi.org/10.3102/0013189X211001356}
+
+\leavevmode\hypertarget{ref-Makel2012}{}%
+Makel, M.
+C., Plucker, J.
+A., \& Hegarty, B.
+(2012).
+Replications in Psychology Research: How Often Do They Really Occur?
+\emph{Perspectives on Psychological Science}.
+\url{https://doi.org/10.1177/1745691612460688}
+
+\leavevmode\hypertarget{ref-Maxwell2004}{}%
+Maxwell, S.
+E.
+(2004).
+The Persistence of Underpowered Studies in Psychological Research: Causes, Consequences, and Remedies.
+\emph{Psychological Methods}, \emph{9}(2), 147--163.
+\url{https://doi.org/10.1037/1082-989X.9.2.147}
+
+\leavevmode\hypertarget{ref-Mitchell2014}{}%
+Mitchell, J. (2014). On the evidentiary emptiness of failed replications. Retrieved from \url{https://jasonmitchell.fas.harvard.edu/Papers/Mitchell/_failed/_science/_2014.pdf}
+
+\leavevmode\hypertarget{ref-Motyl2017}{}%
+Motyl, M., Demos, A.
+P., Carsel, T.
+S., Hanson, B.
+E., Melton, Z.
+J., Mueller, A.
+B., \ldots{} Skitka, L.
+J.
+(2017).
+The state of social and personality science: Rotten to the core, not so bad, getting better, or getting worse?
+\emph{Journal of Personality and Social Psychology}, \emph{113}(1), 34--58.
+\url{https://doi.org/10.1037/pspa0000084}
+
+\leavevmode\hypertarget{ref-Mueller-Langer2019}{}%
+Mueller-Langer, F., Fecher, B., Harhoff, D., \& Wagner, G.
+G.
+(2019).
+Replication studies in economicsHow many and which papers are chosen for replication, and why?
+\emph{Research Policy}, \emph{48}(1), 62--83.
+\url{https://doi.org/10.1016/j.respol.2018.07.019}
+
+\leavevmode\hypertarget{ref-R-here}{}%
+Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}
+
+\leavevmode\hypertarget{ref-OSC2015}{}%
+Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716. \url{https://doi.org/10.1126/science.aac4716}
+
+\leavevmode\hypertarget{ref-Rasmussen2009}{}%
+Rasmussen, N., Lee, K., \& Bero, L.
+(2009).
+Association of trial registration with the results and conclusions of published trials of new oncology drugs.
+\emph{Trials}, \emph{10}(1), 116.
+\url{https://doi.org/10.1186/1745-6215-10-116}
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-RRRwebsite}{}%
+Registered Replication Reports. (n.d.). \emph{Association for Psychological Science - APS}. Retrieved from \url{https://www.psychologicalscience.org/publications/replication}
+
+\leavevmode\hypertarget{ref-Rohatgi2018}{}%
+Rohatgi, A. (2018). \emph{WebPlotDigitizer - Web Based Plot Digitizer}. Austin, Texas, USA.
+
+\leavevmode\hypertarget{ref-Rosenthal1979}{}%
+Rosenthal, R. (1979). The file drawer problem and tolerance for null results. \emph{Psychological Bulletin}, \emph{86}(3), 638--641. \url{https://doi.org/10.1037/0033-2909.86.3.638}
+
+\leavevmode\hypertarget{ref-RStudioTeam2019}{}%
+RStudio Team. (2019). \emph{RStudio: Integrated development environment for r}. Boston, MA: RStudio, Inc.
+
+\leavevmode\hypertarget{ref-Simmons2011}{}%
+Simmons, J.
+P., Nelson, L.
+D., \& Simonsohn, U.
+(2011).
+False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
+\emph{Psychological Science}, \emph{22}(11), 1359--1366.
+\url{https://doi.org/10.1177/0956797611417632}
+
+\leavevmode\hypertarget{ref-Simons2018}{}%
+Simons, D.
+J.
+(2018).
+Introducing Advances in Methods and Practices in Psychological Science.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(1), 3--6.
+\url{https://doi.org/10.1177/2515245918757424}
+
+\leavevmode\hypertarget{ref-Simons2014}{}%
+Simons, D.
+J., Holcombe, A.
+O., \& Spellman, B.
+A.
+(2014).
+An Introduction to Registered Replication Reports at \emph{Perspectives} \emph{on} \emph{Psychological Science}.
+\emph{Perspectives on Psychological Science}, \emph{9}(5), 552--555.
+\url{https://doi.org/10.1177/1745691614543974}
+
+\leavevmode\hypertarget{ref-Sterling1959}{}%
+Sterling, T.
+D.
+(1959).
+Publication Decisions and their Possible Effects on Inferences Drawn from Tests of Significanceor Vice Versa.
+\emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.
+\url{https://doi.org/10.1080/01621459.1959.10501497}
+
+\leavevmode\hypertarget{ref-Sterling1995}{}%
+Sterling, T.
+D., Rosenbaum, W.
+L., \& Weinkam, J.
+J.
+(1995).
+Publication Decisions Revisited: The Effect of the Outcome of Statistical Tests on the Decision to Publish and Vice Versa.
+\emph{The American Statistician}, \emph{49}(1), 108.
+\url{https://doi.org/10.2307/2684823}
+
+\leavevmode\hypertarget{ref-Szucs2017}{}%
+Szucs, D., \& Ioannidis, J.
+P.
+A.
+(2017).
+Empirical assessment of published effect sizes and power in the recent cognitive neuroscience and psychology literature.
+\emph{PLOS Biology}, \emph{15}(3), e2000797.
+\url{https://doi.org/10.1371/journal.pbio.2000797}
+
+\leavevmode\hypertarget{ref-R-reshape2}{}%
+Wickham, H. (2007). Reshaping data with the reshape package. \emph{Journal of Statistical Software}, \emph{21}(12), 1--20. Retrieved from \url{http://www.jstatsoft.org/v21/i12/}
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-Wiseman2019}{}%
+Wiseman, R., Watt, C., \& Kornbrot, D. (2019). Registered reports: An early example and analysis. \emph{PeerJ}, \emph{7}, e6232. \url{https://doi.org/10.7717/peerj.6232}
+
+\leavevmode\hypertarget{ref-R-knitr}{}%
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}
+
+\leavevmode\hypertarget{ref-R-bookdown}{}%
+Xie, Y. (2016). \emph{Bookdown: Authoring books and technical documents with R markdown}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://github.com/rstudio/bookdown}
+
+\leavevmode\hypertarget{ref-R-rmarkdown}{}%
+Xie, Y., Allaire, J., \& Grolemund, G. (2018). \emph{R markdown: The definitive guide}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://bookdown.org/yihui/rmarkdown}
+
 \end{document}
